### 2016-08-11 nusselt_paper.tex
creates repo & adds initial tex/bib files

%\documentclass[iop]{emulateapj}
\documentclass[twocolumn]{aastex6}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{listings}
\usepackage{color}
\usepackage{bm}
\usepackage{empheq}
\usepackage{natbib}
\usepackage{cancel}
\usepackage{hyperref}
\usepackage[all]{hypcap}

\bibliographystyle{apj}

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}

\begin{document}
%%%%% Create nice title and abstract
\author{Evan H. Anders}
\affil{University of Colorado -- Boulder}
\author{Benjamin P. Brown}
\affil{University of Colorado -- Boulder}
\title{Heat transport in stratified convection across mach number blahdy blah}
\begin{abstract}
EVAN DON'T FORGET TO DO THIS
\end{abstract}
\maketitle

%%%%% Body of the paper

\section{Motivation}
Blah Blah stuff.

\section{Model \& Equations}

\subsection{The Fully Compressible Navier-Stokes Equations}
We solve over the Fully Compressible Navier-Stokes equations with an energy-conserving energy equation,
which take the form:
\begin{align}
&\begin{aligned}
&\frac{\partial \rho}{\partial t} + \Div{\rho\bm{u}} = 0
	\label{continuity_eqn}
\end{aligned}\\
&\begin{aligned}
&\rho\left(\frac{\partial \bm{u}}{\partial t} + \left(\bm{u}\cdot\nabla\right)\bm{u}\right) =
-\grad P + \rho\bm{g} - \nabla\cdot\stressT
	\label{momentum_eqn}
\end{aligned}\\
&\begin{aligned}
&\rho c_V\left(\frac{\partial T}{\partial t} + \left(\bm{u}\cdot\grad\right)T + (\gamma-1)T\Div{\bm{u}}\right) \\
&\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,
+ \Div{-\kappa\grad T} = -\left(\stressT\cdot\nabla\right)\cdot\bm{u} 
	\label{energy_eqn}
\end{aligned}
\end{align}
where the viscous stress tensor is defined such as
\begin{equation}
\Pi_{ij} \equiv -\mu\left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\Div{\bm{u}}\right),
\end{equation}
where $\mu$ is the \emph{dynamic viscosity} (in units of [mass $\cdot$ length$^{-1}$ $\cdot$ time$^{-1}$]) and $\delta_{ij}$
is the kronecker delta function.  We also define the \emph{kinematic viscosity}, which has units of a classic diffusion coefficient,
as $\nu \equiv \mu/\rho$.

Taking the dot product of the velocity and the equation of momentum conservation (Eq. \ref{momentum_eqn}) and adding it to the energy
equation

\subsection{Control Parameters}

\bibliography{biblio.bib}
\end{document}

### 2016-08-11 tex/nusselt_paper.tex
repo organization; more typing

%\documentclass[iop]{emulateapj}
\documentclass[aps, prl, twocolumn, groupedaddress]{revtex4-1}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{listings}
\usepackage{color}
\usepackage{bm}
\usepackage{empheq}
\usepackage{natbib}
\usepackage{cancel}
\usepackage[colorlinks=True, linkcolor=blue]{hyperref}
\usepackage[all]{hypcap}

\bibliographystyle{apj}

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}

\begin{document}
%%%%% Create nice title and abstract
\author{Evan H. Anders}
\affiliation{Department of Astrophysical \& Planetary Sciences, University of Colorado -- Boulder}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO}
\author{Benjamin P. Brown}
\affiliation{Department of Astrophysical \& Planetary Sciences, University of Colorado -- Boulder}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO}
\title{Heat transport in stratified convection across mach number blahdy blah}

\begin{abstract}
This is where an abstract defining what we're doing with stratified convection and Nusselt numbers will go.
\end{abstract}
\maketitle

%%%%% Body of the paper
\section{Introduction \label{section:intro}}
Blah Blah stuff.

\section{Model \& Equations \label{section:model}}
We study a fluid whose equation of state is that of an ideal gas, $P = R^*\rho T$ and whose
initial stratification is polytropic, where
\begin{equation}
\begin{split}
\rho(z) &= \rho_{00}(z_0 - z)^m \\
T(z)    &= T_{00}(z_0 - z)^m
\end{split}
\end{equation}
and $z$ increases upwards. We define the height of the atmosphere such that $n_\rho$ density scale heights fit in the
atmosphere, or such that $\ln[\rho(L_{z})/\rho(0)] = n_\rho$.  We nondimensionalize our equations such that 
$P = \rho = T = 1$ at the top of the atmosphere, requiring $z_0 \equiv L_z + 1$ and $R^* = T_{00} = \rho_{00} = 1$.  
We specify the entropy gradient at the top of the atmosphere as $\grad S(L_z) = -\epsilon$ such that the
polytropic index of the atmosphere is $m = (\gamma - 1)^{-1} - \epsilon = m_{ad} - \epsilon$.

We evolve the Fully Compressible Navier-Stokes equations with an energy-conserving energy equation,
which take the form:
\begin{align}
&\begin{aligned}
&\frac{D \ln\rho}{D t} + \Div{\bm{u}} = 0
	\label{eqn:continuity_eqn}
\end{aligned}\\
&\begin{aligned}
&\rho\frac{D\bm{u}}{D t}=
-\grad P + \rho\bm{g} - \nabla\cdot\stressT
	\label{eqn:momentum_eqn}
\end{aligned}\\
&\begin{aligned}
\rho c_V\left(\frac{D T}{D t} + (\gamma-1)T\Div{\bm{u}}\right) + &\Div{-\kappa\grad T} = \\
&-\left(\stressT\cdot\nabla\right)\cdot\bm{u} 
	\label{eqn:energy_eqn}
\end{aligned}
\end{align}
where $D/Dt \equiv \partial_t + \bm{u}\cdot\grad$ and the viscous stress tensor is defined as
\begin{equation}
\Pi_{ij} \equiv -\mu\left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\Div{\bm{u}}\right),
	\label{eqn:stress_tensor}
\end{equation}
where $\mu$ is the \emph{dynamic viscosity} (in units of [mass $\cdot$ length$^{-1}$ $\cdot$ time$^{-1}$]) and $\delta_{ij}$
is the kronecker delta function.  We also define the \emph{kinematic viscosity}, which has units of a classic diffusion coefficient,
as $\nu \equiv \mu/\rho$.  In a similar fashion, we define the thermal diffusivity, $\chi \equiv \kappa / \rho$ [note: Kundu has a $c_P$ on
the bottom, here].

Dotting Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to Eq. \ref{eqn:energy_eqn}, we retrieve the full energy equation in
conservation form,
\begin{equation}
\begin{split}
\frac{\partial}{\partial t}&\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +\\
&\Div{\rho\bm{u}\left[\frac{|\bm{u}|^2}{2} + h + \phi\right] + \bm{u}\cdot\stressT - \rho\chi\grad T} = 0,
	\label{eqn:energy_eqn_full}
\end{split}
\end{equation}
where $h \equiv c_V T + P/\rho$ is the system enthalpy and $\phi = -gz$ is the gravitational potential.  All of the

We use initial conditions of randomized temperature perturbations on the order of $10^{-6}$ below the background
temperature field (EVAN -- TRY TO DO 1E-6*EPSILON).

\subsection{Control Parameters}
In addition to the explicitly scaling the level of superadiabaticity of the background entropy gradient via $\epsilon$,
we utilize the nondimensional Prandtl (Pr) and Rayleigh (Ra) numbers to determine our atmospheric diffusivities.  Pr
is the ratio of kinematic viscosity to thermal diffusivity, which we set equal to one.  Ra is the ratiof buoyant driving
to diffusivity of the form
\begin{equation}
\text{Ra} \equiv \frac{g L_z^3 (\Delta S/c_P)}{\nu\chi},
	\label{eqn:ra_def}
\end{equation}
where $\Delta S/c_P$ is the entropy difference between the top and bottom boundaries of the reference state.  Note that
$\nu \propto \chi \propto \rho^{-1}$ such that Ra increases with depth as the square of the density.  In this work we
specify Ra at the top of the domain.

\begin{acknowledgements}
This work was supported by the CU/NSO Hale Graduate Fellowship blah.
\end{acknowledgements}

\bibliography{../biblio.bib}
\end{document}

### 2016-08-11 tex/nusselt_paper.tex
small updates -- gets some first refs in

@@
 \usepackage{cancel}
-\usepackage[colorlinks=True, linkcolor=blue]{hyperref}
+\usepackage[colorlinks=True, linkcolor=blue, citecolor=blue]{hyperref}
 \usepackage[all]{hypcap}
 
-\bibliographystyle{apj}
+\bibliographystyle{apsrev}
 
@@
 \section{Introduction \label{section:intro}}
-Blah Blah stuff.
+Talk about \cite{hurlburt&all1984, brummell&all1996, cattaneo&all1991},  and then talk about some
+\RB stuff, such as \cite{johnston&doering2009}.
 
@@
 We use initial conditions of randomized temperature perturbations on the order of $10^{-6}$ below the background
-temperature field (EVAN -- TRY TO DO 1E-6*EPSILON).
+temperature field (EVAN -- TRY TO DO 1E-6*EPSILON). We impose stress free, impenetrable, constant temperature boundary
+conditions.
 

### 2016-08-17 tex/nusselt_paper.tex
adds nusselt number definition and a small discussion on the Nusselt number

@@
 \section{Introduction \label{section:intro}}
-Talk about \cite{hurlburt&all1984, brummell&all1996, cattaneo&all1991},  and then talk about some
-\RB stuff, such as \cite{johnston&doering2009}.
+Compressible convection is ubiquitous among natural systems such as stellar envelopes and planetary atmospheres.
+The widely-studied \RB convection in which up- and downflows are symmetric and the Rayleigh number (Ra, the
+ratio of buoyant driving to diffusive damping) serves as the primary control parameter lacks a number of the
+key features which make studies of stratified convection difficult to master.  Early studies of stratified
+convection in two \cite{graham1975, chan&all1982, hurlburt&all1984, cattaneo&all1990} and three 
+\cite{malagoli&all1990, cattaneo&all1991, brummell&all1996} dimensions
+utilized polytropically stratified atmospheres, in which the temperature gradient, thermal diffusivity, and
+gravity are constant throughout the depth of the atmosphere and the atmosphere is in hydrostatic equilibrium.
+While perhaps not perfectly realistic and often abandoned for atmospheres constructed using more realistic
+radiative transfer properties (cite some papers), the polytrope is a particularly useful reference state for
+stratified convection studies.
+
+A canonical value of the ``polytropic index'' used in the study of convection of monatomic ideal gases is
+$m = 1$, such that the density and temperature profile are both linear.  Recently, \cite{brandenburg&all2005}
+argued that as the polytropic index approaches the adiabatic value of $m_{ad} = 1.5$, the convective flux of
+the system becomes negligible compared to the background flux gradient, and the Nusselt number of the
+system approaches zero.  They argue that, as a result, values of $m \rightarrow -1$ are ideal polytropes
+to study, as the radiative flux approaches zero and the convective flux carries the whole of the system
+flux in equilibrium.
+
+Here, we argue for The definition of a new Nusselt number, where the radiative flux is defined relative to
+the \emph{adiabatic} state rather than to a linear temperature profile.  We demonstrate that values
+of $m$ close to adiabatic show a Nusselt number (similar?) to \cite{johnston&doering2009} and that
+such values of $m$ are useful in allowing us to probe low-Mach number convection, such as that
+deep within the Sun's convection zone (cite a paper for that?)
 
@@
 
+The efficiency of convection is defined by the Nusselt number.  While the Nusselt number is well-defined in \RB convection
+as the amount of total convective and radiative flux divided by the steady-state background flux \cite{johnston&doering2009, otero&all2002},
+a well-defined Nusselt number is more elusive in stratified convection.  We suggest that a more general definition of the
+Nusselt number is similar to that defined by \RB convection, but where both the numerator and denominator have the
+radiative flux of the adiabatic temperature gradient of the atmosphere removed.  Such a definition was first used
+by \cite{hurlburt&all1984} who wrote it as
+\begin{equation}
+N \equiv \frac{F_T - F_A}{F - F_A},
+\end{equation}
+where $F_T$ is the sum of fluxes in the system, $F_A = \kappa g / c_P$ is the radiative flux of the corresponding adiabatic profile
+of the atmosphere, and $F = \Delta T / Lz$ is the radiative flux carried by a linear temperature profile across the domain.  Under
+the specific case of constant temperature boundary conditions, $\Delta T$ is constant and the denominator of the Nusselt number
+reduces to $F - F_A = -\kappa\epsilon \grad T_0 (\gamma-1)/\gamma$.  Thus, the denominator of the Nusselt number is directly proportional
+to the level of superadiabaticity of the background atmosphere, as is the time-dependent value of $F_T - F_A$.  Under the Boussinesq
+approximation of \RB convection, the lack of density variation means that the temperature field is directly linked to entropy, and
+the adiabatic temperature gradient is definitionally zero.  In the case of \cite{brandenburg&all2005}, the case of
+$\epsilon \rightarrow (m_{ad} + 1)$ is examined, but this also corresponds to the case where $g \rightarrow 0$ and the
+corresponding adiabatic atmospheric temperature gradient is isothermal.
+
 \subsection{Control Parameters}

### 2016-08-23 tex/nusselt_paper.tex
put figures into the paper, starts getting some discussion around them

--- 2016-08-11 tex/nusselt_paper.tex
@@
 \affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO}
-\title{Heat transport in stratified convection across mach number blahdy blah}
+\title{Convective heat transport in stratified atmospheres at low and high Mach number}
 
@@
 \section{Introduction \label{section:intro}}
-Blah Blah stuff.
+Convection is ubiquitous among natural systems such as stellar envelopes and planetary atmospheres.
+Compressible convection in such stratified atmospheres exhibits behavior which is much more complex than 
+what is seen in the widely-studied \RB convection.  Upflows and downflows are asymmetric, the well-defined
+Rayleigh Number (Ra, the ratio of buoyant driving to diffusive damping) becomes less defined and depth-dependent,
+and the Mach number of the flows becomes an additional control parameter.
+Early studies of stratified
+convection in two \cite{graham1975, chan&all1982, hurlburt&all1984, cattaneo&all1990} and three 
+\cite{malagoli&all1990, cattaneo&all1991, brummell&all1996} dimensions
+utilized polytropically stratified atmospheres, in which the temperature gradient, thermal diffusivity, and
+gravity are constant throughout the depth of the atmosphere and the atmosphere is initially in hydrostatic equilibrium.
+While often abandoned for atmospheres constructed using more realistic
+radiative transfer properties (cite some papers), the polytrope is a particularly useful reference state for
+stratified convection studies.
+
+A canonical value of the ``polytropic index'' used in the study of convection of monatomic ideal gases is
+$m = 1$, such that the density and temperature profile are both linear.  Recently, \cite{brandenburg&all2005}
+argued that as the polytropic index approaches the adiabatic value of $m_{ad} = 1.5$, the convective flux of
+the system becomes negligible compared to the background flux gradient, and the Nusselt number of the
+system approaches zero.  They argue that, as a result, values of $m \rightarrow -1$ are ideal polytropes
+to study, as the radiative flux approaches zero and the convective flux carries the whole of the system
+flux in equilibrium.
+
+Here, we argue for The definition of a new Nusselt number, where the radiative flux is defined relative to
+the \emph{adiabatic} state rather than to a linear temperature profile.  We demonstrate that values
+of $m$ close to adiabatic show a Nusselt number (similar?) to \cite{johnston&doering2009} and that
+such values of $m$ are useful in allowing us to probe low-Mach number convection, such as that
+deep within the Sun's convection zone (cite a paper for that?)
 
@@
 \begin{split}
-\rho(z) &= \rho_{00}(z_0 - z)^m \\
-T(z)    &= T_{00}(z_0 - z)^m
+\rho_0(z) &= \rho_{00}(z_0 - z)^m \\
+T_0(z)    &= T_{00}(z_0 - z)
+\label{eqn:polytrope}
 \end{split}
 \end{equation}
-and $z$ increases upwards. We define the height of the atmosphere such that $n_\rho$ density scale heights fit in the
-atmosphere, or such that $\ln[\rho(L_{z})/\rho(0)] = n_\rho$.  We nondimensionalize our equations such that 
-$P = \rho = T = 1$ at the top of the atmosphere, requiring $z_0 \equiv L_z + 1$ and $R^* = T_{00} = \rho_{00} = 1$.  
-We specify the entropy gradient at the top of the atmosphere as $\grad S(L_z) = -\epsilon$ such that the
-polytropic index of the atmosphere is $m = (\gamma - 1)^{-1} - \epsilon = m_{ad} - \epsilon$.
+and $z$ increases upwards within the bounds $z =\{0, L_{z}\}$.
+The height of the atmosphere is set by specifying the number of density scale heights it spans, $n_\rho$,
+which we set to be three throughout this study such that the density at the bottom of the atmosphere is larger
+than that at the top of the atmosphere by roughly a factor of 20.
+Variables are nondimensionalized at the top of the atmosphere as 
+$P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, requiring $z_0 \equiv L_z + 1$ and $R^* = T_{00} = \rho_{00} = 1$.  
+The polytropic index is set by the adiabatic index of a monatomic ideal gas, $\gamma = 5/3$ and the 
+control parameter $\epsilon$, such that $m = (\gamma - 1)^{-1} - \epsilon = m_{ad} - \epsilon$ 
+and the subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$.
 
-We evolve the Fully Compressible Navier-Stokes equations with an energy-conserving energy equation,
+The primary assumptions utilized in constructing a polytropic atmosphere are that acceleration due to 
+gravity is constant and that the conductive heat flux, $F_{\text{cond}} = -\kappa \grad T_0$ is
+constant throughout the atmosphere.  To ensure the second condition is met, it is traditional to use
+a constant value of $\kappa$ and $\grad T_0$.  The thermal conductivity is controlled by the
+non-dimensional Rayleigh number,
+\begin{equation}
+\text{Ra} = \frac{g L_z^3 (\Delta S_0 / c_P)}{\nu\chi},
+\end{equation}
+where $\Delta S_0$ is the entropy jump across the polytropic atmosphere, $\nu$ is the kinematic viscosity
+and $\kappa$ is the thermal diffusivity.  The relationship between the thermal and viscous diffusivities is
+set by the Prandtl number, Pr$ = \nu/\chi$, which we take to be one throughout this study.   The thermal
+and viscous diffusion coefficients are related to the dynamic viscosity, $\mu$ and $\kappa$ by the ratio
+$\nu \equiv \mu/\rho$ and $\chi \equiv \mu\/rho$.  As a result, $\text{Ra} \propto (\nu\chi)^{-1} \propto
+\rho^2$, such that for our atmospheres with $n_{\rho} = 3$, the Rayleigh number increases by a factor of
+approximately 400 from the top of the domain to the bottom of the domain.
+
+At the constant values of $n_\rho$ and Pr used, the primary control parameters of convection are $\epsilon$
+and Ra.  We decompose our atmosphere into the background polytrope ($\rho_{0}, T_{0}$) and the fluctuations
+about that background ($\bm{u}, \rho_{1}, T_{1}$).  The scaling of the entropy gradient with $\epsilon$
+is reflected in the evolved values of these fluctuations, which follow the scaling of
+Ma$^{1/2} \propto T_1/T_0 \propto \rho_{1}/\rho_{0} \propto \epsilon$, and which scale weakly with Ra (prove it,
+we have the data).
+
+\begin{figure}[t]
+\includegraphics[width=3.5in]{./figs/ma_v_eps.eps}
+\caption{Shown are characteristic mach numbers from IVPs spanning six decades of $\epsilon$, from
+very low Mach number to near Mach one.  A very strong Ma $\propto \epsilon^{1/2}$ relation is clear. 
+(need to actually do linear regression)
+\label{fig:ma_v_eps} }
+\end{figure}
+
+We start with initial conditions of random small perturbations compared to $\epsilon$ in the temperature
+field.  We evolve the Fully Compressible Navier-Stokes equations with an energy-conserving energy equation,
 which take the form:
@@
 \begin{equation}
-\Pi_{ij} \equiv -\mu\left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\Div{\bm{u}}\right),
+\Pi_{ij} \equiv -\mu\left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\Div{\bm{u}}\right).
 	\label{eqn:stress_tensor}
 \end{equation}
-where $\mu$ is the \emph{dynamic viscosity} (in units of [mass $\cdot$ length$^{-1}$ $\cdot$ time$^{-1}$]) and $\delta_{ij}$
-is the kronecker delta function.  We also define the \emph{kinematic viscosity}, which has units of a classic diffusion coefficient,
-as $\nu \equiv \mu/\rho$.  In a similar fashion, we define the thermal diffusivity, $\chi \equiv \kappa / \rho$ [note: Kundu has a $c_P$ on
-the bottom, here].
 
-Dotting Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to Eq. \ref{eqn:energy_eqn}, we retrieve the full energy equation in
-conservation form,
+In such stratified systems, the total convective flux can be defined as
 \begin{equation}
-\begin{split}
-\frac{\partial}{\partial t}&\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +\\
-&\Div{\rho\bm{u}\left[\frac{|\bm{u}|^2}{2} + h + \phi\right] + \bm{u}\cdot\stressT - \rho\chi\grad T} = 0,
+\bm{F}_{\text{conv}} = \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}},
+\end{equation}
+where $\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$ is the enthalpy flux, $\bm{F}_{\text{KE}} \equiv 
+\rho|\bm{u}|^2\bm{u}$ is the kinetic energy flux, $\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ is the potential
+energy flux (with $\phi \equiv -gz$), 
+and $\bm{F}_{\text{visc}} \equiv \bm{u}\cdot\stressT$ is the viscous flux.  Dotting 
+Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
+Eq. \ref{eqn:energy_eqn}, we retrieve the full energy equation in conservation form,
+\begin{equation}
+\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
+\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{rad}}} = 0
 	\label{eqn:energy_eqn_full}
-\end{split}
 \end{equation}
-where $h \equiv c_V T + P/\rho$ is the system enthalpy and $\phi = -gz$ is the gravitational potential.  All of the
+where $\bm{F}_{\text{rad}} = -\kappa \grad T$.
 
-We use initial conditions of randomized temperature perturbations on the order of $10^{-6}$ below the background
-temperature field (EVAN -- TRY TO DO 1E-6*EPSILON).
+The efficiency of convection is defined by the Nusselt number.  While the Nusselt number is well-defined in \RB convection
+as the amount of total flux divided by the steady-state background conductive flux 
+\cite{johnston&doering2009, otero&all2002},
+a well-defined Nusselt number is more elusive in stratified convection.  Convection generally 
+works to drive the overall \emph{entropy} gradient to zero.  In the case of the Boussinesq approximation of
+\RB convection, $\grad S = 0$ implies that $\grad T = 0$ because density is no longer a factor in determining the
+stratification.  However, once compressibility and stratification are considered, convection works to cause
+$\grad S = 0$ but \emph{not} necessarily $\grad T = 0$.  As such, even perfectly efficient convection will still
+have some amount of adiabatic conductive flux, $F_A \equiv -\kappa \grad T_{ad}$.  In the case of an initially
+superadiabatic polytrope, assuming that hydrostatic equilibrium is conserved to first order and that the system
+evolves towards a new, adiabatic polytropic state such that the temperature gradient takes the form
+$\grad T_{\text{ad}} = -g/c_P = \grad T_0 (1 - \epsilon(m_{ad} + 1))$.  In order to obtain a meaningful definition
+of the conductive flux, this constant adiabatic component must be subtracted, which yields
+$\bm{F}_{\text{rad}} - \bm{F}_{\text{ad}} = -\kappa\grad T_1 -\kappa\grad T_0\epsilon(m_{ad} + 1)$.  Unlike
+the full radiative flux, which is $O(\kappa\grad T)$, this is $O(\kappa\grad T_1) \approx O(\epsilon)$, and it
+is thus comparable to the other fluxes in the system, as would be expected.  Acknowledging this, we define the
+Nusselt number in the same form as \cite{hurlburt&all1984}, who wrote it as
+\begin{equation}
+N \equiv \frac{F_{\text{conv, z}} + F_{\text{rad, z}} - F_A}{F - F_A},
+\label{eqn:nusselt}
+\end{equation}
+where $F = \Delta T / Lz$ is the radiative flux carried by a
+linear temperature profile from the top boundary value to the bottom boundary value.
+It is important to note that such a definition explains the results of \cite{brandenburg&all2005}, who noted that
+as $m \rightarrow -1$, $F_{\text{rad}}\rightarrow 0$ and $F_{\text{conv}}$ becomes large.  As $m\rightarrow -1$,
+$g\rightarrow 0$, such that the adiabatic flux become zero and the Nusselt number definition reverts to a form
+more similar to that of \RB convection.
 
-\subsection{Control Parameters}
-In addition to the explicitly scaling the level of superadiabaticity of the background entropy gradient via $\epsilon$,
-we utilize the nondimensional Prandtl (Pr) and Rayleigh (Ra) numbers to determine our atmospheric diffusivities.  Pr
-is the ratio of kinematic viscosity to thermal diffusivity, which we set equal to one.  Ra is the ratiof buoyant driving
-to diffusivity of the form
-\begin{equation}
-\text{Ra} \equiv \frac{g L_z^3 (\Delta S/c_P)}{\nu\chi},
-	\label{eqn:ra_def}
-\end{equation}
-where $\Delta S/c_P$ is the entropy difference between the top and bottom boundaries of the reference state.  Note that
-$\nu \propto \chi \propto \rho^{-1}$ such that Ra increases with depth as the square of the density.  In this work we
-specify Ra at the top of the domain.
+***WE USE DEDALUS, EXPLAIN WHAT IT ARE***
+
+***EXPLAIN BOUNDARY CONDITIONS***
+
+***EXPLAIN WHAT THE CHARACTERISTIC TIME SCALE, THE BUOYANCY TIME, IS***
+
+\section{Results \label{section:results}}
+We ran initial value problems for a few hundreds of buoyancy times past the convective transients from 
+Rayleigh numbers around $R_{crit}$ up to Rayleigh numbers of $\approx 10^7 R_{crit}$.  While bulk thermodynamic
+structures are similar between low and high $\epsilon$, high $\epsilon$ runs start to exhibit shock fronts
+propagating away from downflow channels, such as those in Fig. \ref{fig:entropy_snapshots}, as reported in
+(cite Juri's paper from ~1990 that has this).
+\begin{figure}[t]
+\includegraphics[width=3.5in]{./figs/snapshots_fig.eps}
+\caption{Two characteristic snapshots after about 200 buoyancy times are shown at $\epsilon=10^{-4}$ (top)
+and $\epsilon=0.5$ (bottom) at Ra = $10^6$.  
+\label{fig:entropy_snapshots} }
+\end{figure}
+
+Despite diferent thermodynamic structures, the fluxes look fairly similar at low and high mach number (sort of?
+I don't think the ones I have are averaged over enough time, especially the eps=0.5 one, but I Pleiades is
+a bit slammed right now).  See Fig \ref{fig:flux_profiles}
+
+\begin{figure}[b]
+\includegraphics[width=3.5in]{./figs/fluxes_fig.eps}
+\caption{Flux profiles for low (top) and high (bottom) Mach number flows.  
+\label{fig:flux_profiles} }
+\end{figure}
+
+At low Rayleigh number, diffusivities are high and the flows are very laminar.  Such flows often achieve a
+steady state and have a well-defined Nusselt number which is independent of time.  However, as the Rayleigh
+number increases, the flows become increasingly time-dependent.  Even steady structures such as solid
+``rolls'' like those pictured in Fig. \ref{fig:entropy_snapshots} have highly time-dependent Nusselt numbers.
+This is, in part, due to the fact that cold downdrafts floating to the bottom of the domain can be entrained
+by upflows, or warm risen parcels can be entrainedi n the intense cold downdrafts.  Such events reverse the
+preferred direction of flux in the system, and even let the Nusselt number become negative for short periods of
+time.  See Fig. \ref{fig:nu_v_time}.  As a result, it is necessary to take a long time average of the fluxes
+before calculating the Nusselt number at higher Rayleigh number.
+
+\begin{figure}[t]
+\includegraphics[width=3.5in]{./figs/nu_v_time.eps}
+\caption{The evolution of the Nusselt number is shown at low ($10^2$) and high ($10^7$) Rayleigh number and at
+$\epsilon = 10^{-4}$.  At low Rayleigh number, the system is able to settle into a time invariant solution. As
+the Rayleigh number is raised, the thermodynamic structure become increasingly complex and time variant, and a
+time-average of the Nusselt number is required to obtain a sensible mean.
+\label{fig:nu_v_time} }
+\end{figure}
+
+The evolution of the Nusselt number as the Rayleigh number is increased is shown for both high and low
+$\epsilon$ in Fig. \ref{fig:nu_v_ra}.  Below convective onset, the Nusselt number is perfectly one. Just above
+onset, there is a brief range of highly inflated scaling between $N$ and Ra.  From about $10R_{crit}$ to roughly
+$10^{4-5}R_{crit}$, Ra and $N$ follow the relationship: (put a power law here)  Above about
+$10^5 R_{crit}$, the Nusselt number flattens out as Ra is increased -- perhaps this is some Featherstone 2016
+shennanigans.
+
+\begin{figure}[b]
+\includegraphics[width=3.5in]{./figs/nu_v_ra.eps}
+\caption{Variation of the Nusselt number as a function of the Rayleigh number is shown.
+\label{fig:nu_v_ra} }
+\end{figure}
 
 \begin{acknowledgements}
-This work was supported by the CU/NSO Hale Graduate Fellowship blah.
+This work was supported by the CU/NSO Hale Graduate Fellowship and Juri's allocation and Ben's allocation.
 \end{acknowledgements}

### 2016-08-31 tex/nusselt_paper.tex
overhauls intro & nusselt description

@@
 \usepackage{graphicx}
-\usepackage{epstopdf}
 \usepackage{listings}
@@
 \begin{abstract}
-This is where an abstract defining what we're doing with stratified convection and Nusselt numbers will go.
+Here we study the effects of varying the strength of buoyant driving (the Rayleigh number, Ra) and the
+characteristic flow speed (the Mach number, Ma) on convective heat transport in stratified atmospheres.
+We utilize polytropic reference states to condition the Mach number and study the evolution of the
+non-dimensional Nusselt number (Nu) as Ra is increased in various Ma regimes.
 \end{abstract}
@@
 Convection is ubiquitous among natural systems such as stellar envelopes and planetary atmospheres.
-Compressible convection in such stratified atmospheres exhibits behavior which is much more complex than 
-what is seen in the widely-studied \RB convection.  Upflows and downflows are asymmetric, the well-defined
-Rayleigh Number (Ra, the ratio of buoyant driving to diffusive damping) becomes less defined and depth-dependent,
-and the Mach number of the flows becomes an additional control parameter.
+In these systems, compressibility and buoyancy couple to produce complex effects which are not seen in
+the widely-studied \RB convection.
 Early studies of stratified
@@
 \cite{malagoli&all1990, cattaneo&all1991, brummell&all1996} dimensions
-utilized polytropically stratified atmospheres, in which the temperature gradient, thermal diffusivity, and
-gravity are constant throughout the depth of the atmosphere and the atmosphere is initially in hydrostatic equilibrium.
-While often abandoned for atmospheres constructed using more realistic
+utilized polytropically stratified atmospheres, in which the equation of hydrostatic equilibrium is satisfied
+under the assumptions of constant gravitational acceleration, thermal diffusivity and a linear temperature profile.
 radiative transfer properties (cite some papers), the polytrope is a particularly useful reference state for
@@
 
-A canonical value of the ``polytropic index'' used in the study of convection of monatomic ideal gases is
-$m = 1$, such that the density and temperature profile are both linear.  Recently, \cite{brandenburg&all2005}
-argued that as the polytropic index approaches the adiabatic value of $m_{ad} = 1.5$, the convective flux of
-the system becomes negligible compared to the background flux gradient, and the Nusselt number of the
-system approaches zero.  They argue that, as a result, values of $m \rightarrow -1$ are ideal polytropes
-to study, as the radiative flux approaches zero and the convective flux carries the whole of the system
-flux in equilibrium.
+Aside from the physical size of the domain in which convection occurs, \RB convection has two main control
+parameters.  These are the non-dimensional Rayleigh number (Ra, the ratio of buoyanty driving to diffusivity)
+and the Prandtl number (Pr, the ratio of viscous to thermal diffusivity).  In stratified atmospheres, Ra
+and Pr combine with the degree of stratification of the atmosphere and the characteristic Mach number of
+motions in the convective flows.  While there have been numerous studies of the effects of varying
+Ra, Pr, and atmospheric stratification (cite some), there are few studies of the effects of Mach number
+on the resulting heat transport properties of the resulting convection.
 
-Here, we argue for The definition of a new Nusselt number, where the radiative flux is defined relative to
-the \emph{adiabatic} state rather than to a linear temperature profile.  We demonstrate that values
-of $m$ close to adiabatic show a Nusselt number (similar?) to \cite{johnston&doering2009} and that
-such values of $m$ are useful in allowing us to probe low-Mach number convection, such as that
-deep within the Sun's convection zone (cite a paper for that?)
+In this letter, we hold the Prandtl number and density stratification constant in polytropic atmospheres.
+We examine the effects of varying the Rayleigh number and characteristic superadiabaticity of the reference
+polytrope as a means of probing dynamics at low and high Mach number.  We utilize the non-dimensional
+Nusselt number to study the heat transport characteristics at low and high Mach number.
 
@@
 We study a fluid whose equation of state is that of an ideal gas, $P = R^*\rho T$ and whose
-initial stratification is polytropic, where
+initial stratification is polytropic.
+The primary assumptions utilized in constructing a polytropic atmosphere are that the gravitational
+acceleration and conductive heat flux are invariant throughout the depth of the atmosphere. In order
+to satisfy the latter assumption, the thermal conductivity, $\kappa$ and temperature gradient
+$\grad T_0$ are often taken as constants, such that, \bm{$F}_{\text{cond}} = -\kappa \grad T_0 = \text{constant}$.
+Under these assumptions, solving the equation of hydrostatic equilibrium produces an atmosphere defined by
 \begin{equation}
@@
 and $z$ increases upwards within the bounds $z =\{0, L_{z}\}$.
-The height of the atmosphere is set by specifying the number of density scale heights it spans, $n_\rho$,
-which we set to be three throughout this study such that the density at the bottom of the atmosphere is larger
+We specify the number of density scale heights the atmosphere spans, $n_\rho$ to determine $L_{z}$. Throughout
+this study, we set $n_{\rho} = 3$ such that the density at the bottom of the atmosphere is larger
 than that at the top of the atmosphere by roughly a factor of 20.
-Variables are nondimensionalized at the top of the atmosphere as 
+Thermodynamic variables are nondimensionalized at the top of the atmosphere as 
 $P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, requiring $z_0 \equiv L_z + 1$ and $R^* = T_{00} = \rho_{00} = 1$.  
 The polytropic index is set by the adiabatic index of a monatomic ideal gas, $\gamma = 5/3$ and the 
-control parameter $\epsilon$, such that $m = (\gamma - 1)^{-1} - \epsilon = m_{ad} - \epsilon$ 
-and the subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$.
+superadiabatic excess \cite{graham1975}, $\epsilon$, such that $m = (\gamma - 1)^{-1} - \epsilon = m_{ad} - \epsilon$ 
+and the subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$,
+the negative value of the superadiabatic excess.
 
-The primary assumptions utilized in constructing a polytropic atmosphere are that acceleration due to 
-gravity is constant and that the conductive heat flux, $F_{\text{cond}} = -\kappa \grad T_0$ is
-constant throughout the atmosphere.  To ensure the second condition is met, it is traditional to use
-a constant value of $\kappa$ and $\grad T_0$.  The thermal conductivity is controlled by the
-non-dimensional Rayleigh number,
+Atmospheric diffusivities are set by the Rayleigh number and the Prandtl number.  We define the
+non-dimensional Rayleigh number as
 \begin{equation}
@@
 \end{equation}
-where $\Delta S_0$ is the entropy jump across the polytropic atmosphere, $\nu$ is the kinematic viscosity
-and $\kappa$ is the thermal diffusivity.  The relationship between the thermal and viscous diffusivities is
-set by the Prandtl number, Pr$ = \nu/\chi$, which we take to be one throughout this study.   The thermal
-and viscous diffusion coefficients are related to the dynamic viscosity, $\mu$ and $\kappa$ by the ratio
+where $\Delta S_0$ is the entropy difference between the top and bottom of the atmosphere, 
+$\nu$ is the kinematic viscosity (viscous diffusivity), and $\chi$ is the thermal dififusivity.  
+The relationship between the thermal and viscous diffusivities is
+set by the Prandtl number, Pr$ = \nu/\chi$.   We relate the dynamic viscosity, $\mu$ and the thermal conductivity,
+$\kappa$, to their corresponding diffusivities such that 
 $\nu \equiv \mu/\rho$ and $\chi \equiv \mu\/rho$.  As a result, $\text{Ra} \propto (\nu\chi)^{-1} \propto
 \rho^2$, such that for our atmospheres with $n_{\rho} = 3$, the Rayleigh number increases by a factor of
-approximately 400 from the top of the domain to the bottom of the domain.
+approximately 400 from the top of the domain to the bottom of the domain.  Such a formulation leaves Pr
+constant throughout the depth of the atmosphere, and in this paper we specifically study $\text{Pr} = 1$.
 
@@
 is reflected in the evolved values of these fluctuations, which follow the scaling of
-Ma$^{1/2} \propto T_1/T_0 \propto \rho_{1}/\rho_{0} \propto \epsilon$, and which scale weakly with Ra (prove it,
-we have the data).
+Ma$^{1/2} \propto T_1/T_0 \propto \rho_{1}/\rho_{0} \propto \epsilon$, and which scale as roughly $Ra^{0.3}$,
+see Fig. \ref{fig:ma_v_eps}.
 
 \begin{figure}[t]
-\includegraphics[width=3.5in]{./figs/ma_v_eps.eps}
+\includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
 \caption{Shown are characteristic mach numbers from IVPs spanning six decades of $\epsilon$, from
@@
 \cite{johnston&doering2009, otero&all2002},
-a well-defined Nusselt number is more elusive in stratified convection.  Convection generally 
-works to drive the overall \emph{entropy} gradient to zero.  In the case of the Boussinesq approximation of
-\RB convection, $\grad S = 0$ implies that $\grad T = 0$ because density is no longer a factor in determining the
-stratification.  However, once compressibility and stratification are considered, convection works to cause
-$\grad S = 0$ but \emph{not} necessarily $\grad T = 0$.  As such, even perfectly efficient convection will still
-have some amount of adiabatic conductive flux, $F_A \equiv -\kappa \grad T_{ad}$.  In the case of an initially
-superadiabatic polytrope, assuming that hydrostatic equilibrium is conserved to first order and that the system
-evolves towards a new, adiabatic polytropic state such that the temperature gradient takes the form
-$\grad T_{\text{ad}} = -g/c_P = \grad T_0 (1 - \epsilon(m_{ad} + 1))$.  In order to obtain a meaningful definition
-of the conductive flux, this constant adiabatic component must be subtracted, which yields
-$\bm{F}_{\text{rad}} - \bm{F}_{\text{ad}} = -\kappa\grad T_1 -\kappa\grad T_0\epsilon(m_{ad} + 1)$.  Unlike
-the full radiative flux, which is $O(\kappa\grad T)$, this is $O(\kappa\grad T_1) \approx O(\epsilon)$, and it
-is thus comparable to the other fluxes in the system, as would be expected.  Acknowledging this, we define the
-Nusselt number in the same form as \cite{hurlburt&all1984}, who wrote it as
+a well-defined Nusselt number is more elusive in stratified convection.  A traditional definition of the Nusselt
+number in stratified convection is \cite{graham1975,hurlburt1984}
 \begin{equation}
-N \equiv \frac{F_{\text{conv, z}} + F_{\text{rad, z}} - F_A}{F - F_A},
+N \equiv \frac{F_{\text{conv, z}} + F_{\text{rad, z}} - F_A}{F_{\text{ref}} - F_A},
 \label{eqn:nusselt}
 \end{equation}
-where $F = \Delta T / Lz$ is the radiative flux carried by a
-linear temperature profile from the top boundary value to the bottom boundary value.
-It is important to note that such a definition explains the results of \cite{brandenburg&all2005}, who noted that
-as $m \rightarrow -1$, $F_{\text{rad}}\rightarrow 0$ and $F_{\text{conv}}$ becomes large.  As $m\rightarrow -1$,
-$g\rightarrow 0$, such that the adiabatic flux become zero and the Nusselt number definition reverts to a form
-more similar to that of \RB convection.
+where $F_{\text{conv, z}}$ and $F_{\text{rad, z}}$ are the z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{rad}}$,
+respectively.  $F_A$ is the adiabatic conductive flux, defined as $F_A = -\kappa \grad T_{\text{ad}}$.  For an
+atmosphere in hydrostatic equilibrium, such as a polytrope, $\grad T_{\text{ad}} \equiv - g / c_{P}$, and thus
+$F_A = \kappa g / c_{P}$.  $F_{\text{ref}} = \Delta T / L_z$ is the conductive flux of a linear profile connecting the upper
+and lower plates, where $\Delta T = T_{u} - T_{\ell}$.
+
+Such a definition of the Nusselt number is general to both stratified and \RB convection.  Convection works to
+suppress entropy stratification and create isentropic atmospheres.  Under the Boussinesq approximation where
+density variations are ignored, entropy stratification is directly proportional to temperature stratification,
+such that $\grad S \rightarrow 0$ only when $\grad T \rightarrow 0$.  Thus, for \RB convection, 
+$\grad T_{\text{ad}} \equiv 0$ and the familiar form of $N$ is retrieved.  In the case of stratified convection,
+as $\epsilon \rightarrow m_{ad} + 1$, as in \cite{brandenburg2015}, $\grad P \propto g \rightarrow 0$ and
+the resulting $\grad T_{\text{ad}} \rightarrow 0$.  In such a case, $F_A \rightarrow 0$ and the familiar
+definition of the \RB nusselt number is appropriate to use. However, for any given values of $\epsilon$, including
+the very small values used in this work, Eq. \ref{eqn:nusselt} is the proper non-dimensional definition
+of the Nusselt number.
 
@@
 structures are similar between low and high $\epsilon$, high $\epsilon$ runs start to exhibit shock fronts
-propagating away from downflow channels, such as those in Fig. \ref{fig:entropy_snapshots}, as reported in
-(cite Juri's paper from ~1990 that has this).
+propagating away from downflow channels, such as those in Fig. \ref{fig:entropy_snapshots}, as reported in \cite{cattaneo&all1990}.
 \begin{figure}[t]
-\includegraphics[width=3.5in]{./figs/snapshots_fig.eps}
+\includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
 \caption{Two characteristic snapshots after about 200 buoyancy times are shown at $\epsilon=10^{-4}$ (top)
@@
 \begin{figure}[b]
-\includegraphics[width=3.5in]{./figs/fluxes_fig.eps}
+\includegraphics[width=3.4375in]{./figs/fluxes_fig.png}
 \caption{Flux profiles for low (top) and high (bottom) Mach number flows.  
@@
 \begin{figure}[t]
-\includegraphics[width=3.5in]{./figs/nu_v_time.eps}
+\includegraphics[width=3.4375in]{./figs/nu_v_time.png}
 \caption{The evolution of the Nusselt number is shown at low ($10^2$) and high ($10^7$) Rayleigh number and at
@@
 \begin{figure}[b]
-\includegraphics[width=3.5in]{./figs/nu_v_ra.eps}
+\includegraphics[width=3.4375in]{./figs/nu_v_ra.png}
 \caption{Variation of the Nusselt number as a function of the Rayleigh number is shown.

### 2016-08-31 tex/nusselt_paper.tex
moar updates, full 3 pages + spill over flushed out a bit

@@
 and the subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$,
-the negative value of the superadiabatic excess.
+the negative value of the superadiabatic excess.  We argue that the characteristic timescale of such an
+atmosphere is related to the characteristic atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$,
+not the characteristic thermal diffusion time, $t_{\text{th}} = L_z^2/\chi$.
 
@@
 $\kappa$, to their corresponding diffusivities such that 
-$\nu \equiv \mu/\rho$ and $\chi \equiv \mu\/rho$.  As a result, $\text{Ra} \propto (\nu\chi)^{-1} \propto
+$\nu \equiv \mu/\rho$ and $\chi \equiv \mu/\rho$.  As a result, $\text{Ra} \propto (\nu\chi)^{-1} \propto
 \rho^2$, such that for our atmospheres with $n_{\rho} = 3$, the Rayleigh number increases by a factor of
@@
 very low Mach number to near Mach one.  A very strong Ma $\propto \epsilon^{1/2}$ relation is clear. 
-(need to actually do linear regression)
 \label{fig:ma_v_eps} }
@@
 a well-defined Nusselt number is more elusive in stratified convection.  A traditional definition of the Nusselt
-number in stratified convection is \cite{graham1975,hurlburt1984}
+number in stratified convection is \cite{graham1975,hurlburt&all1984}
 \begin{equation}
@@
 $\grad T_{\text{ad}} \equiv 0$ and the familiar form of $N$ is retrieved.  In the case of stratified convection,
-as $\epsilon \rightarrow m_{ad} + 1$, as in \cite{brandenburg2015}, $\grad P \propto g \rightarrow 0$ and
+as $\epsilon \rightarrow m_{ad} + 1$, as in \cite{brandenburg&all2005}, $\grad P \propto g \rightarrow 0$ and
 the resulting $\grad T_{\text{ad}} \rightarrow 0$.  In such a case, $F_A \rightarrow 0$ and the familiar
@@
 
-***WE USE DEDALUS, EXPLAIN WHAT IT ARE***
-
-***EXPLAIN BOUNDARY CONDITIONS***
-
-***EXPLAIN WHAT THE CHARACTERISTIC TIME SCALE, THE BUOYANCY TIME, IS***
+We utilize the novel Dedalus pseudospectral framework (cite website?) to time-evolve Eqs. 
+\ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn}.  We use a dealiased Chebyshev (vertical)
+and Fourier (horizontal) grid in which the
+physical grid dimensions are 3/2 the size of the coefficient grid.  Our coefficient grid sizes range from
+64x256 grid points (low Ra) to 768x3072 grid points (Ra = $10^{7.66}$).  The atmosphere is bounded above
+and below by impenetrable, stress free, fixed temperature boundary conditions such that
+\begin{equation}
+w = \partial_z u = T_1 = 0
+\end{equation}
+at the boundaries.  Theh domain is horizontally periodic.
 
 \section{Results \label{section:results}}
+
 We ran initial value problems for a few hundreds of buoyancy times past the convective transients from 
-Rayleigh numbers around $R_{crit}$ up to Rayleigh numbers of $\approx 10^7 R_{crit}$.  While bulk thermodynamic
-structures are similar between low and high $\epsilon$, high $\epsilon$ runs start to exhibit shock fronts
-propagating away from downflow channels, such as those in Fig. \ref{fig:entropy_snapshots}, as reported in \cite{cattaneo&all1990}.
+Rayleigh numbers around $R_{crit}$ up to Rayleigh numbers of $\approx 10^7 R_{crit}$ (BOOTSTRAPPING?).  At
+high values of $\epsilon$, shock systems form in the upper atmosphere near downflow lanes 
+(see e.g. Fig. \ref{fig:entropy_snapshots}b) and propagate towards upflow lanes.  Such systems were reported in
+both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
+Low mach number flows, such as those on an $\epsilon = 10^{-4}$ atmosphere (e.g. Fig. \ref{fig:entropy_snapshots}a)
+have similar bulk thermodynamic structure but lack the complicating dynamics of shock heating.
+
 \begin{figure}[t]
@@
 
-Despite diferent thermodynamic structures, the fluxes look fairly similar at low and high mach number (sort of?
-I don't think the ones I have are averaged over enough time, especially the eps=0.5 one, but I Pleiades is
-a bit slammed right now).  See Fig \ref{fig:flux_profiles}
+Despite diferent thermodynamic structures, the properly normalized \emph{sum} of the fluxes for a given
+Ra is similar.  See, for example, Fig. \ref{fig:flux_profiles} to see time-averaged horizontal profiles of
+the vertical system fluxes.  At high $\epsilon$ and Ra, $\bm{F}_{\text{enth}}$ and $\bm{F}_{\text{KE}}$
+exhibit two local maxima over the depth of the domain, whereas at low $\epsilon$ and low Ma, there is only
+one local maximum near the bottom of the domain.  Viscous fluxes become important near the bottom boundary
+layer, and radiative flux is nearly zero everywhere in the domain except for near the boundaries where the
+fixed-temperature boundary conditions create large deviations in $\grad T$ away from $\grad T_{\text{ad}}$.
 
@@
 time.  See Fig. \ref{fig:nu_v_time}.  As a result, it is necessary to take a long time average of the fluxes
-before calculating the Nusselt number at higher Rayleigh number.
+before calculating the Nusselt number at higher Rayleigh number. (IS THIS USEFUL?)
 
@@
 $\epsilon$ in Fig. \ref{fig:nu_v_ra}.  Below convective onset, the Nusselt number is perfectly one. Just above
-onset, there is a brief range of highly inflated scaling between $N$ and Ra.  From about $10R_{crit}$ to roughly
-$10^{4-5}R_{crit}$, Ra and $N$ follow the relationship: (put a power law here)  Above about
-$10^5 R_{crit}$, the Nusselt number flattens out as Ra is increased -- perhaps this is some Featherstone 2016
-shennanigans.
+onset, there is a brief range of highly inflated scaling between $N$ and Ra.
 
-\begin{figure}[b]
+\begin{figure}[t]
 \includegraphics[width=3.4375in]{./figs/nu_v_ra.png}

### 2016-09-09 tex/nusselt_paper.tex
gets "good" rought drafts of 1st/2nd/part of 3rd section in.

@@
 %\documentclass[iop]{emulateapj}
-\documentclass[aps, prl, twocolumn, groupedaddress]{revtex4-1}
-\usepackage{amsmath}
+\documentclass[aps, prl, twocolumn, groupedaddress, amsfonts, amssymb, amsmath]{revtex4-1}
 \usepackage{graphicx}
-\usepackage{listings}
-\usepackage{color}
 \usepackage{bm}
-\usepackage{empheq}
 \usepackage{natbib}
-\usepackage{cancel}
-\usepackage[colorlinks=True, linkcolor=blue, citecolor=blue]{hyperref}
-\usepackage[all]{hypcap}
+%\usepackage[colorlinks=True, linkcolor=blue, citecolor=blue]{hyperref}
+%\usepackage[all]{hypcap}
 
@@
 \newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
+\newcommand{\nrho}{\ensuremath{n_{\rho}}}
 
@@
 \begin{abstract}
-Here we study the effects of varying the strength of buoyant driving (the Rayleigh number, Ra) and the
-characteristic flow speed (the Mach number, Ma) on convective heat transport in stratified atmospheres.
-We utilize polytropic reference states to condition the Mach number and study the evolution of the
-non-dimensional Nusselt number (Nu) as Ra is increased in various Ma regimes.
+Here we study stratified convection in the context of polytropically stratified atmospheres. 
+We hold the density stratification and Prandtl number (Pr) constant while studying the dependence
+of the Nusselt number (Nu), which quantifies the efficiency of convective heat transport, on
+variations of the Mach number (Ma) and the Rayleigh number (Ra).  In the low Ra regime, high and
+low Ma flows have very different scalings of Nu with Ra.  In the high Ra regime, high and low Ma flows
+have nearly the same scaling of Nu with Ra, with power laws near (enter here), reminiscent of the
+Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
 \end{abstract}
@@
 %%%%% Body of the paper
-\section{Introduction \label{section:intro}}
-Convection is ubiquitous among natural systems such as stellar envelopes and planetary atmospheres.
-In these systems, compressibility and buoyancy couple to produce complex effects which are not seen in
-the widely-studied \RB convection.
-Early studies of stratified
-convection in two \cite{graham1975, chan&all1982, hurlburt&all1984, cattaneo&all1990} and three 
-\cite{malagoli&all1990, cattaneo&all1991, brummell&all1996} dimensions
-utilized polytropically stratified atmospheres, in which the equation of hydrostatic equilibrium is satisfied
-under the assumptions of constant gravitational acceleration, thermal diffusivity and a linear temperature profile.
-radiative transfer properties (cite some papers), the polytrope is a particularly useful reference state for
-stratified convection studies.
+\section{Introduction}
+\refstepcounter{section}
+\label{sec:intro}
+Convection is essential to heat transport in the cores of high mass stars, the
+envelopes of low mass stars, and the atmospheres of terrestrial and jovian planets. In such systems, convection
+occurs in the presence of the atmospheric stratification, which can be small but extends up to 
+14 density scale heights in the Sun's convective envelope.
+Clearly a basic understanding of the
+properties of compressible convection in stratified media is important to understanding systems in astrophysics
+and planetary sciences.  Unfortunately, most attempts to learn about the properties of convection in these
+systems were overshadowed or muddied by additional attempts to make numerical models that include all of the
+complexities of the real system.  As such, we know little about the fundamental properties of stratified convection.
 
-Aside from the physical size of the domain in which convection occurs, \RB convection has two main control
-parameters.  These are the non-dimensional Rayleigh number (Ra, the ratio of buoyanty driving to diffusivity)
-and the Prandtl number (Pr, the ratio of viscous to thermal diffusivity).  In stratified atmospheres, Ra
-and Pr combine with the degree of stratification of the atmosphere and the characteristic Mach number of
-motions in the convective flows.  While there have been numerous studies of the effects of varying
-Ra, Pr, and atmospheric stratification (cite some), there are few studies of the effects of Mach number
-on the resulting heat transport properties of the resulting convection.
+Some of the earliest numerical experiments on stratified convection
+were performed in both two \cite{graham1975, chan&all1982,
+hurlburt&all1984, cattaneo&all1990} and three \cite{cattaneo&all1991, brummell&all1996} dimensions and
+revealed a number of basic properties in the moderate-to-high Mach number regime.
+Unlike the widely-studied \RB convection, in which upflows and downflows are symmetrical, highly stratified
+convection exhibits high-velocity, narrow downflow lanes and slow, broad upflow lanes.  As velocities approach
+the speed of sound, shocks begin to form near the downflow lanes at the top of the atmosphere and propagate toward the upflows.
+In \RB convection, the temperature gradient
+and by proxy the radiative flux approach zero in the convecting region.  In stratified convection, the 
+\emph{entropy} gradient is flattened by convection, but this does not necessitate the disappearance of the
+radiative flux due to contributions of thermodynamic variables other than temperature to the entropy.
 
-In this letter, we hold the Prandtl number and density stratification constant in polytropic atmospheres.
-We examine the effects of varying the Rayleigh number and characteristic superadiabaticity of the reference
-polytrope as a means of probing dynamics at low and high Mach number.  We utilize the non-dimensional
-Nusselt number to study the heat transport characteristics at low and high Mach number.
+In \RB convection, there exist two primary control parameters: the Rayleigh number (Ra), the ratio of
+buoyant driving to diffusive damping, and the Prandtl number (Pr), the ratio of viscous to thermal
+diffusivity.  Along with the aspect ratio of the physical domain, these two numbers entirely control the
+dynamics of the convection.  In stratified atmospheres, in addition to specifying the equation of state and
+fundamental properties of the gas, the two control parameters of \RB convection are joined by the degree of
+stratification across the domain and the characteristic Mach number (Ma) of the convective flows.  
+Polytropically stratified atmospheres, such as those used in early studies, are an ideal extension of
+\RB convection into the stratified realm as the two additional control parameters are directly linked to
+basic properties of the atmosphere.  The density stratification is set by the number of density scale heights
+the atmosphere spans (\nrho), and the Mach number is controlled by the superadiabatic excess ($\epsilon$),
+which is the deviation of the polytropic index from that of an adiabatic polytropic index \cite{graham1975}.
 
-\section{Model \& Equations \label{section:model}}
-We study a fluid whose equation of state is that of an ideal gas, $P = R^*\rho T$ and whose
-initial stratification is polytropic.
-The primary assumptions utilized in constructing a polytropic atmosphere are that the gravitational
+In this letter, we study the effects of variations of $\epsilon$ and Ra on the heat transport of convection
+in polytropically stratified atmospheres, characterized by the Nusselt number (Nu).  We hold \nrho and Pr
+constant across all simulations and examine moderate (4) and large (8) aspect ratios.  In section 
+\ref{sec:experiment}, we describe the construction of atmospheres, our equations, and our method for
+numerical time evolution.  We describe our findings in section \ref{sec:results} and discuss
+implications in section \ref{sec:discussion}.
+
+\section{Experiment} 
+\refstepcounter{section}
+\label{sec:experiment}
+We study a fluid composed of monatomic ideal gas particles, with an adiabatic index of $\gamma = 5/3$ and
+whose equation of state is $P = R^*\rho T$. 
+The initial stratification is polytropic, such that the gravitational
 acceleration and conductive heat flux are invariant throughout the depth of the atmosphere. In order
 to satisfy the latter assumption, the thermal conductivity, $\kappa$ and temperature gradient
-$\grad T_0$ are often taken as constants, such that, \bm{$F}_{\text{cond}} = -\kappa \grad T_0 = \text{constant}$.
+$\grad T_0$ are often taken as constants, such that $\bm{F}_{\text{cond,0}} = -\kappa \grad T_0 = \text{constant}$.
 Under these assumptions, solving the equation of hydrostatic equilibrium produces an atmosphere defined by
@@
 \rho_0(z) &= \rho_{00}(z_0 - z)^m \\
-T_0(z)    &= T_{00}(z_0 - z)
+T_0(z)    &= T_{00}(z_0 - z),
 \label{eqn:polytrope}
@@
 \end{equation}
-and $z$ increases upwards within the bounds $z =\{0, L_{z}\}$.
-We specify the number of density scale heights the atmosphere spans, $n_\rho$ to determine $L_{z}$. Throughout
-this study, we set $n_{\rho} = 3$ such that the density at the bottom of the atmosphere is larger
-than that at the top of the atmosphere by roughly a factor of 20.
+where $z$ increases upwards within the bounds $z =\{0, L_{z}\}$.
+We specify the number of density scale heights the atmosphere spans, $n_\rho$, to determine $L_{z}$. Throughout
+this letter, we set $n_{\rho} = 3$ such that the density at the bottom of the atmosphere is larger
+than at the top by a factor of 20.
 Thermodynamic variables are nondimensionalized at the top of the atmosphere as 
 $P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, requiring $z_0 \equiv L_z + 1$ and $R^* = T_{00} = \rho_{00} = 1$.  
-The polytropic index is set by the adiabatic index of a monatomic ideal gas, $\gamma = 5/3$ and the 
-superadiabatic excess \cite{graham1975}, $\epsilon$, such that $m = (\gamma - 1)^{-1} - \epsilon = m_{ad} - \epsilon$ 
-and the subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$,
-the negative value of the superadiabatic excess.  We argue that the characteristic timescale of such an
-atmosphere is related to the characteristic atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$,
-not the characteristic thermal diffusion time, $t_{\text{th}} = L_z^2/\chi$.
+The polytropic index is set by the adiabatic index and the
+superadiabatic excess, $\epsilon$, such that $m = m_{ad} - \epsilon$
+where $m_{ad} \equiv (\gamma-1)^{-1}$ is the adiabatic polytropic index.
+The subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$,
+the negative of the superadiabatic excess.  We argue that the characteristic timescale of such an
+atmosphere is not only linked to the characteristic thermal diffusion time, $t_{\text{th}} = L_z^2/\chi$,
+but is also related to the characteristic atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$.
+We will utilize buoyancy time units throughout this letter.
 
@@
 The relationship between the thermal and viscous diffusivities is
-set by the Prandtl number, Pr$ = \nu/\chi$.   We relate the dynamic viscosity, $\mu$ and the thermal conductivity,
+set by the Prandtl number, Pr$ = \nu/\chi$.   We relate the dynamic viscosity, $\mu$, and the thermal conductivity,
 $\kappa$, to their corresponding diffusivities such that 
@@
 \rho^2$, such that for our atmospheres with $n_{\rho} = 3$, the Rayleigh number increases by a factor of
-approximately 400 from the top of the domain to the bottom of the domain.  Such a formulation leaves Pr
-constant throughout the depth of the atmosphere, and in this paper we specifically study $\text{Pr} = 1$.
+400 from the top of the domain to the bottom of the domain.  Such a formulation leaves Pr
+constant throughout the depth of the atmosphere, and in this letter we impose $\text{Pr} = 1$.
 
@@
 Ma$^{1/2} \propto T_1/T_0 \propto \rho_{1}/\rho_{0} \propto \epsilon$, and which scale as roughly $Ra^{0.3}$,
-see Fig. \ref{fig:ma_v_eps}.
+as in Fig. \ref{fig:ma_v_eps}.
 
@@
 \includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
-\caption{Shown are characteristic mach numbers from IVPs spanning six decades of $\epsilon$, from
-very low Mach number to near Mach one.  A very strong Ma $\propto \epsilon^{1/2}$ relation is clear. 
+\caption{Figure (a) shows characteristic horizontally averaged maximum mach numbers which have been
+time averaged over 100$t_{b}$ starting 60$t_{b}$ after the start of IVP simulations. At low $\epsilon$,
+Ma shows a power law slope of 0.5048 and 0.5129 at Ra = $10^2$ and $10^5$, respectively (need err bars).
+When $\epsilon \rightarrow m_{ad}$, large deviations from this power law are seen and the system quickly
+approaches Ma $\approx 1$.  Ma shows weak scaling with $\epsilon$, and does not exceed Ma$ \approx 1$
 \label{fig:ma_v_eps} }
@@
 
-We start with initial conditions of random small perturbations compared to $\epsilon$ in the temperature
-field.  We evolve the Fully Compressible Navier-Stokes equations with an energy-conserving energy equation,
+We evolve the Fully Compressible Navier-Stokes equations,
 which take the form:
@@
 \begin{equation}
-\bm{F}_{\text{conv}} = \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}},
+\bm{F}_{\text{conv}} \equiv \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}},
 \end{equation}
@@
 energy flux (with $\phi \equiv -gz$), 
-and $\bm{F}_{\text{visc}} \equiv \bm{u}\cdot\stressT$ is the viscous flux.  Dotting 
+and $\bm{F}_{\text{visc}} \equiv \bm{u}\cdot\stressT$ is the viscous flux.  Taking an inner product of
 Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
-Eq. \ref{eqn:energy_eqn}, we retrieve the full energy equation in conservation form,
+Eq. \ref{eqn:energy_eqn}, the full energy equation in conservation form is retrieved,
 \begin{equation}
@@
 \end{equation}
-where $\bm{F}_{\text{rad}} = -\kappa \grad T$.
+where $\bm{F}_{\text{rad}} = -\kappa \grad T$.  An understanding of the flux terms is essential to characterizing
+the convective heat transport in our systems.
 
-The efficiency of convection is defined by the Nusselt number.  While the Nusselt number is well-defined in \RB convection
+The atmosphere is bounded above
+and below by impenetrable, stress free, fixed temperature boundary conditions such that
+\begin{equation}
+w = \partial_z u = T_1 = 0
+\end{equation}
+at the boundaries.
+
+We utilize the novel Dedalus pseudospectral framework (cite website?) to time-evolve Eqs. 
+\ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn} using a fourth-order Runge-Kutta timestepping scheme.  
+Variables are time-evolved on a dealiased Chebyshev (vertical)
+and Fourier (horizontal, periodic) domain in which the
+physical grid dimensions are 3/2 the size of the coefficient grid.  Our coefficient grid sizes range from
+64x256 grid points at the lowest values of Ra to 768x3072 grid points at Ra $\geq 10^{7}$.
+
+\section{Results}
+\refstepcounter{section}
+\label{sec:results}
+
+The efficiency of convection is quantified by the Nusselt number.  
+While the Nusselt number is well-defined in \RB convection
 as the amount of total flux divided by the steady-state background conductive flux 
@@
 where $F_{\text{conv, z}}$ and $F_{\text{rad, z}}$ are the z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{rad}}$,
-respectively.  $F_A$ is the adiabatic conductive flux, defined as $F_A = -\kappa \grad T_{\text{ad}}$.  For an
-atmosphere in hydrostatic equilibrium, such as a polytrope, $\grad T_{\text{ad}} \equiv - g / c_{P}$, and thus
+respectively.  $F_A$ is the adiabatic conductive flux, defined as $F_A = -\kappa \partial_z T_{\text{ad}}$.  For an
+atmosphere in hydrostatic equilibrium, such as a polytrope, $\partial_z T_{\text{ad}} \equiv - g / c_{P}$, and thus
 $F_A = \kappa g / c_{P}$.  $F_{\text{ref}} = \Delta T / L_z$ is the conductive flux of a linear profile connecting the upper
@@
 $\grad T_{\text{ad}} \equiv 0$ and the familiar form of $N$ is retrieved.  In the case of stratified convection,
-as $\epsilon \rightarrow m_{ad} + 1$, as in \cite{brandenburg&all2005}, $\grad P \propto g \rightarrow 0$ and
+as $\epsilon \rightarrow m_{ad} + 1$, $\grad P \propto g \rightarrow 0$ and
 the resulting $\grad T_{\text{ad}} \rightarrow 0$.  In such a case, $F_A \rightarrow 0$ and the familiar
-definition of the \RB nusselt number is appropriate to use. However, for any given values of $\epsilon$, including
+definition of the \RB nusselt number is appropriate to use, which explains why convection carries all of the
+atmosphereic flux in such a case \cite{brandenburg&all2005}. However, for any given values of $\epsilon$, including
 the very small values used in this work, Eq. \ref{eqn:nusselt} is the proper non-dimensional definition
@@
 
-We utilize the novel Dedalus pseudospectral framework (cite website?) to time-evolve Eqs. 
-\ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn}.  We use a dealiased Chebyshev (vertical)
-and Fourier (horizontal) grid in which the
-physical grid dimensions are 3/2 the size of the coefficient grid.  Our coefficient grid sizes range from
-64x256 grid points (low Ra) to 768x3072 grid points (Ra = $10^{7.66}$).  The atmosphere is bounded above
-and below by impenetrable, stress free, fixed temperature boundary conditions such that
-\begin{equation}
-w = \partial_z u = T_1 = 0
-\end{equation}
-at the boundaries.  Theh domain is horizontally periodic.
-
-\section{Results \label{section:results}}
-
-We ran initial value problems for a few hundreds of buoyancy times past the convective transients from 
-Rayleigh numbers around $R_{crit}$ up to Rayleigh numbers of $\approx 10^7 R_{crit}$ (BOOTSTRAPPING?).  At
+We solved initial value problems which started in hydrostatic equilibrium and experienced infinitesimal kicks
+in $T_1$ compared to $\epsilon$.  Solutions were time-evolved until a long-time average of $N$ showed little
+dependence on height. At
 high values of $\epsilon$, shock systems form in the upper atmosphere near downflow lanes 
-(see e.g. Fig. \ref{fig:entropy_snapshots}b) and propagate towards upflow lanes.  Such systems were reported in
+(see e.g. Fig. \ref{fig:entropy_snapshots}a) and propagate towards upflow lanes.  Such systems were reported in
 both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
-Low mach number flows, such as those on an $\epsilon = 10^{-4}$ atmosphere (e.g. Fig. \ref{fig:entropy_snapshots}a)
-have similar bulk thermodynamic structure but lack the complicating dynamics of shock heating.
+Low mach number flows, such as those in an $\epsilon = 10^{-4}$ atmosphere (e.g. Fig. \ref{fig:entropy_snapshots}b)
+have similar bulk thermodynamic structure but lack the complicating dynamics of shock heating. As Ra is
+increased to very large values (e.g. Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures no longer span
+the vertical extent of the domain but instead break up into small packets which traverse through the domain many
+times before diffusing.  The complicated nature of high Ra dynamics, especially in the low Ma regime where
+shocks are absent, has barred us from sufficiently converging any solutions in the regime of $Ra > 10^7$.
 
@@
 \includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
-\caption{Two characteristic snapshots after about 200 buoyancy times are shown at $\epsilon=10^{-4}$ (top)
-and $\epsilon=0.5$ (bottom) at Ra = $10^6$.  
+\caption{Characteristic entropy fields are shown. The time- and horizontally-
+averaged profile is removed in all cases.  At high
+$\epsilon$ (a), shock systems form near the upper downflow lanes and propel shock-heated material deep within
+the atmosphere at sufficiently high Ra.  At low $\epsilon$ but at the same Ra (b), shock systems are absent from
+the system, but otherwise the dynamics are similar.  As Ra is increased (c), downflow lanes no longer span
+the entirety of the domain and individual cold, small blobs are responsible for carrying the flux downward.
 \label{fig:entropy_snapshots} }
@@
 
-\begin{figure}[b]
+\begin{figure}[t]
 \includegraphics[width=3.4375in]{./figs/fluxes_fig.png}
@@
 preferred direction of flux in the system, and even let the Nusselt number become negative for short periods of
-time.  See Fig. \ref{fig:nu_v_time}.  As a result, it is necessary to take a long time average of the fluxes
+time.  As a result, it is necessary to take a long time average of the fluxes
 before calculating the Nusselt number at higher Rayleigh number. (IS THIS USEFUL?)
 
-\begin{figure}[t]
-\includegraphics[width=3.4375in]{./figs/nu_v_time.png}
-\caption{The evolution of the Nusselt number is shown at low ($10^2$) and high ($10^7$) Rayleigh number and at
-$\epsilon = 10^{-4}$.  At low Rayleigh number, the system is able to settle into a time invariant solution. As
-the Rayleigh number is raised, the thermodynamic structure become increasingly complex and time variant, and a
-time-average of the Nusselt number is required to obtain a sensible mean.
-\label{fig:nu_v_time} }
-\end{figure}
+%
+%\begin{figure}[t]
+%\includegraphics[width=3.4375in]{./figs/nu_v_time.png}
+%\caption{The evolution of the Nusselt number is shown at low ($10^2$) and high ($10^7$) Rayleigh number and at
+%$\epsilon = 10^{-4}$.  At low Rayleigh number, the system is able to settle into a time invariant solution. As
+%the Rayleigh number is raised, the thermodynamic structure become increasingly complex and time variant, and a
+%time-average of the Nusselt number is required to obtain a sensible mean.
+%\label{fig:nu_v_time} }
+%\end{figure}
 
@@
 
-\begin{acknowledgements}
+\section{Discussion}
+\refstepcounter{section}
+\label{sec:discussion}
+
+\subsection{acknowledgements}
 This work was supported by the CU/NSO Hale Graduate Fellowship and Juri's allocation and Ben's allocation.
-\end{acknowledgements}
+We thank Axel Brandenburg, Mark Rast, and Jeff Oishi for many useful discussions.
 

### 2016-09-22 tex/nusselt_paper.tex
incorporates Ben's comments and updates figures

@@
 14 density scale heights in the Sun's convective envelope.
-Clearly a basic understanding of the
+A basic understanding of the
 properties of compressible convection in stratified media is important to understanding systems in astrophysics
-and planetary sciences.  Unfortunately, most attempts to learn about the properties of convection in these
-systems were overshadowed or muddied by additional attempts to make numerical models that include all of the
-complexities of the real system.  As such, we know little about the fundamental properties of stratified convection.
+and planetary sciences.  Numerical constraints typically have restricted studies of stratified convection to
+moderately high Mach numbers, appropriate to regions near the Sun's surface.  As such, we know little about the
+fundamental properties of low-Mach number stratified convection, which occurs in the deep solar interior.
 
 Some of the earliest numerical experiments on stratified convection
-were performed in both two \cite{graham1975, chan&all1982,
+were performed in two \cite{graham1975, chan&all1982,
 hurlburt&all1984, cattaneo&all1990} and three \cite{cattaneo&all1991, brummell&all1996} dimensions and
 revealed a number of basic properties in the moderate-to-high Mach number regime.
-Unlike the widely-studied \RB convection, in which upflows and downflows are symmetrical, highly stratified
+Unlike the widely-studied \RB problem, in which upflows and downflows are symmetrical, highly stratified
 convection exhibits high-velocity, narrow downflow lanes and slow, broad upflow lanes.  As velocities approach
@@
 \label{sec:experiment}
-We study a fluid composed of monatomic ideal gas particles, with an adiabatic index of $\gamma = 5/3$ and
+In order to compare our results with previous studies and in an effort to examine a simplest case,
+we study a fluid composed of monatomic ideal gas particles, with an adiabatic index of $\gamma = 5/3$ and
 whose equation of state is $P = R^*\rho T$. 
@@
 The subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$,
-the negative of the superadiabatic excess.  We argue that the characteristic timescale of such an
-atmosphere is not only linked to the characteristic thermal diffusion time, $t_{\text{th}} = L_z^2/\chi$,
-but is also related to the characteristic atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$.
+the negative of the superadiabatic excess.  The characteristic timescale of such an
+atmosphere is related to the characteristic atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$.
 We will utilize buoyancy time units throughout this letter.
@@
 $\kappa$, to their corresponding diffusivities such that 
-$\nu \equiv \mu/\rho$ and $\chi \equiv \mu/\rho$.  As a result, $\text{Ra} \propto (\nu\chi)^{-1} \propto
+$\nu \equiv \mu/\rho$ and $\chi \equiv \kappa/\rho$.  As a result, $\text{Ra} \propto (\nu\chi)^{-1} \propto
 \rho^2$, such that for our atmospheres with $n_{\rho} = 3$, the Rayleigh number increases by a factor of
@@
 At the constant values of $n_\rho$ and Pr used, the primary control parameters of convection are $\epsilon$
-and Ra.  We decompose our atmosphere into the background polytrope ($\rho_{0}, T_{0}$) and the fluctuations
-about that background ($\bm{u}, \rho_{1}, T_{1}$).  The scaling of the entropy gradient with $\epsilon$
+and Ra.  We decompose our atmosphere into the background polytrope ($\ln\rho_{0}, T_{0}$) and the fluctuations
+about that background ($\bm{u}, \ln\rho_{1}, T_{1}$).  The scaling of the entropy gradient with $\epsilon$
 is reflected in the evolved values of these fluctuations, which follow the scaling of
@@
 \includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
-\caption{Figure (a) shows characteristic horizontally averaged maximum mach numbers which have been
-time averaged over 100$t_{b}$ starting 60$t_{b}$ after the start of IVP simulations. At low $\epsilon$,
-Ma shows a power law slope of 0.5048 and 0.5129 at Ra = $10^2$ and $10^5$, respectively (need err bars).
+\caption{(a) Characteristic horizontally averaged maximum Mach numbers which have been
+time averaged over 100$t_{b}$ starting roughly 100$t_{b}$ after the start of simulations. At low $\epsilon$,
+Ma shows power laws of $Ma \propto \epsilon^{0.5048}, \epsilon^{0.5129}$ at Ra = $10^2$ and $10^5$, respectively (need err bars).
 When $\epsilon \rightarrow m_{ad}$, large deviations from this power law are seen and the system quickly
@@
 We utilize the novel Dedalus pseudospectral framework (cite website?) to time-evolve Eqs. 
-\ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn} using a fourth-order Runge-Kutta timestepping scheme.  
+\ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn} using an implicit-explicit third-order four-step 
+Runge-Kutta timestepping scheme \cite{ascher&all1997}.  
 Variables are time-evolved on a dealiased Chebyshev (vertical)
 and Fourier (horizontal, periodic) domain in which the
-physical grid dimensions are 3/2 the size of the coefficient grid.  Our coefficient grid sizes range from
-64x256 grid points at the lowest values of Ra to 768x3072 grid points at Ra $\geq 10^{7}$.
+physical grid dimensions are 3/2 the size of the coefficient grid.  Our physical grid sizes range from
+96x384 grid points at the lowest values of Ra to 1152x4608 grid points at Ra $\geq 10^{7}$. 
+By using IMEX timestepping, we are able to study flows at moderate ($Ma \approx 1$) and very low ($Ma \approx 10^{-4}$)
+Mach number (Fig. \ref{fig:ma_v_eps}b).
 
@@
 
-Such a definition of the Nusselt number is general to both stratified and \RB convection.  Convection works to
+We contend that this is the general form of the Nusselt number.  To illustrate this, we consider a few limiting
+cases. Convection works to
 suppress entropy stratification and create isentropic atmospheres.  Under the Boussinesq approximation where
@@
 definition of the \RB nusselt number is appropriate to use, which explains why convection carries all of the
-atmosphereic flux in such a case \cite{brandenburg&all2005}. However, for any given values of $\epsilon$, including
-the very small values used in this work, Eq. \ref{eqn:nusselt} is the proper non-dimensional definition
-of the Nusselt number.
+atmosphereic flux in such a case \cite{brandenburg&all2005}. As $\epsilon \rightarrow 0$, 
+$\grad T_{\text{ad}}\rightarrow \grad T_0$, the atmospheric initial temperature profile.  This causes increasingly
+smaller velocity, temperature, and pressure perturbations (e.g. Fig. \ref{fig:ma_v_eps}), but due to the removal
+of the background radiative flux from the numerator and denominator in Eq. \ref{eqn:nusselt}, increasingly smaller
+perturbations have just as large of an effect on the nusselt number.
 
-We solved initial value problems which started in hydrostatic equilibrium and experienced infinitesimal kicks
-in $T_1$ compared to $\epsilon$.  Solutions were time-evolved until a long-time average of $N$ showed little
+We solved initial value problems which start in hydrostatic and thermal equilibrium and experienced infinitesimal 
+kicks compared to $\epsilon$ in $T_1$.  Solutions were time-evolved until a long-time average of $N$ showed little
 dependence on height. At
@@
 \includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
-\caption{Characteristic entropy fields are shown. The time- and horizontally-
+\caption{Characteristic entropy. The time- and horizontally-
 averaged profile is removed in all cases.  At high
 $\epsilon$ (a), shock systems form near the upper downflow lanes and propel shock-heated material deep within
-the atmosphere at sufficiently high Ra.  At low $\epsilon$ but at the same Ra (b), shock systems are absent from
-the system, but otherwise the dynamics are similar.  As Ra is increased (c), downflow lanes no longer span
+the atmosphere at sufficiently high Ra.  At low $\epsilon$ but at the same Ra (b), shock systems are absent, 
+but otherwise the dynamics are similar.  As Ra is increased (c), downflow lanes no longer span
 the entirety of the domain and individual cold, small blobs are responsible for carrying the flux downward.

### 2016-09-30 tex/nusselt_paper.tex
finishes ROUGH draft of all sections

@@
 \newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
+\newcommand{\lilstressT}{\ensuremath{\bm{\bar{\bar{\sigma}}}}}
 \newcommand{\nrho}{\ensuremath{n_{\rho}}}
+\newcommand{\approptoinn}[2]{\mathrel{\vcenter{
+	\offinterlineskip\halign{\hfil$##$\cr
+	#1\propto\cr\noalign{\kern2pt}#1\sim\cr\noalign{\kern-2pt}}}}}
+
+\newcommand{\appropto}{\mathpalette\approptoinn\relax}
 
@@
 \begin{abstract}
-Here we study stratified convection in the context of polytropically stratified atmospheres. 
-We hold the density stratification and Prandtl number (Pr) constant while studying the dependence
+Here we study stratified convection in the context of 
+plane-parallel polytropically stratified atmospheres. 
+We hold the density stratification ($n_\rho$) and Prandtl number (Pr) constant while studying the dependence
 of the Nusselt number (Nu), which quantifies the efficiency of convective heat transport, on
-variations of the Mach number (Ma) and the Rayleigh number (Ra).  In the low Ra regime, high and
-low Ma flows have very different scalings of Nu with Ra.  In the high Ra regime, high and low Ma flows
-have nearly the same scaling of Nu with Ra, with power laws near (enter here), reminiscent of the
-Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
+variations of the Mach number (Ma) and the Rayleigh number (Ra).  At large but still subsonic values of
+Ma, a scaling $Nu \appropto Ra^{0.45}$ for low values of Ra.  As Ra increases and flows become supersonic,
+this scaling gives way to a much weaker $Nu \appropto Ra^{0.20}$.  In the regime of $Ma \ll 1$, a consistent
+$Nu \appropto Ra^{0.3}$ is retrieved,  reminiscent of the Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
 \end{abstract}
@@
 revealed a number of basic properties in the moderate-to-high Mach number regime.
-Unlike the widely-studied \RB problem, in which upflows and downflows are symmetrical, highly stratified
-convection exhibits high-velocity, narrow downflow lanes and slow, broad upflow lanes.  As velocities approach
-the speed of sound, shocks begin to form near the downflow lanes at the top of the atmosphere and propagate toward the upflows.
-In \RB convection, the temperature gradient
-and by proxy the radiative flux approach zero in the convecting region.  In stratified convection, the 
-\emph{entropy} gradient is flattened by convection, but this does not necessitate the disappearance of the
-radiative flux due to contributions of thermodynamic variables other than temperature to the entropy.
+In the widely-studied \RB (hereafter RB) problem, upflows and downflows are symmetrical and
+the temperature gradient approaches zero in the convective interior causing the conductive flux to similarly 
+disappear.  Highly stratified convection, on the other hand, exhibits narrow downflow lanes broad upflow regions.
+Furthermore, the \emph{entropy} gradient is flattened by convection rather than the temperature gradient, which
+means that even in the presence of perfectly efficient convection a significant component of the flux can be
+carried by conduction.
 
-In \RB convection, there exist two primary control parameters: the Rayleigh number (Ra), the ratio of
+In RB convection, there exist two primary control parameters: the Rayleigh number (Ra), the ratio of
 buoyant driving to diffusive damping, and the Prandtl number (Pr), the ratio of viscous to thermal
@@
 dynamics of the convection.  In stratified atmospheres, in addition to specifying the equation of state and
-fundamental properties of the gas, the two control parameters of \RB convection are joined by the degree of
+fundamental properties of the gas, the two control parameters of RB convection are joined by the degree of
 stratification across the domain and the characteristic Mach number (Ma) of the convective flows.  
 Polytropically stratified atmospheres, such as those used in early studies, are an ideal extension of
-\RB convection into the stratified realm as the two additional control parameters are directly linked to
+RB convection into the stratified realm as the two additional control parameters are directly linked to
 basic properties of the atmosphere.  The density stratification is set by the number of density scale heights
-the atmosphere spans (\nrho), and the Mach number is controlled by the superadiabatic excess ($\epsilon$),
-which is the deviation of the polytropic index from that of an adiabatic polytropic index \cite{graham1975}.
+the atmosphere spans (\nrho), and Ma is controlled by the superadiabatic excess ($\epsilon$),
+the deviation of the polytropic index from the adiabatic polytropic index \cite{graham1975}.
 
-In this letter, we study the effects of variations of $\epsilon$ and Ra on the heat transport of convection
-in polytropically stratified atmospheres, characterized by the Nusselt number (Nu).  We hold \nrho and Pr
-constant across all simulations and examine moderate (4) and large (8) aspect ratios.  In section 
+In this letter we study the behavior of convective heat transport, quantified by
+the Nusselt number (Nu), in polytropically stratified atmospheres.  
+We vary $\epsilon$ and Ra while holding \nrho and Pr
+constant across all simulations and convective structures which arise in a domain with an aspect ratio of 4.  In section 
 \ref{sec:experiment}, we describe the construction of atmospheres, our equations, and our method for
@@
 whose equation of state is $P = R^*\rho T$. 
-The initial stratification is polytropic, such that the gravitational
-acceleration and conductive heat flux are invariant throughout the depth of the atmosphere. In order
-to satisfy the latter assumption, the thermal conductivity, $\kappa$ and temperature gradient
-$\grad T_0$ are often taken as constants, such that $\bm{F}_{\text{cond,0}} = -\kappa \grad T_0 = \text{constant}$.
+The initial stratification is polytropic and the gravitational
+acceleration and conductive heat flux are invariant throughout the depth of the atmosphere. We specify that both 
+the thermal conductivity, $\kappa$, and the temperature gradient, $\grad T_0$, are constant while constructing
+our atmosphere such that $\bm{F}_{\text{cond,0}} = -\kappa \grad T_0 = \text{constant}$.
 Under these assumptions, solving the equation of hydrostatic equilibrium produces an atmosphere defined by
@@
 where $m_{ad} \equiv (\gamma-1)^{-1}$ is the adiabatic polytropic index.
-The subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$,
-the negative of the superadiabatic excess.  The characteristic timescale of such an
+The subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$.  
+The characteristic timescale of such an
 atmosphere is related to the characteristic atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$.
@@
 \rho^2$, such that for our atmospheres with $n_{\rho} = 3$, the Rayleigh number increases by a factor of
-400 from the top of the domain to the bottom of the domain.  Such a formulation leaves Pr
+400 across the domain.  This formulation leaves Pr
 constant throughout the depth of the atmosphere, and in this letter we impose $\text{Pr} = 1$.
@@
 is reflected in the evolved values of these fluctuations, which follow the scaling of
-Ma$^{1/2} \propto T_1/T_0 \propto \rho_{1}/\rho_{0} \propto \epsilon$, and which scale as roughly $Ra^{0.3}$,
+Ma$^{1/2} \propto T_1/T_0 \propto \rho_{1}/\rho_{0} \propto \epsilon$, and which scale as roughly $Ra^{0.25}$,
 as in Fig. \ref{fig:ma_v_eps}.
@@
 \caption{(a) Characteristic horizontally averaged maximum Mach numbers which have been
-time averaged over 100$t_{b}$ starting roughly 100$t_{b}$ after the start of simulations. At low $\epsilon$,
-Ma shows power laws of $Ma \propto \epsilon^{0.5048}, \epsilon^{0.5129}$ at Ra = $10^2$ and $10^5$, respectively (need err bars).
+time averaged for over 100$t_{b}$ starting roughly 50$t_{b}$ after the start of simulations. For $\epsilon \leq 0.1$,
+an evident scaling of $Ma \propto \{\epsilon^{0.5015}, \epsilon^{0.5130}\}$ 
+at Ra = $\{10^2, 10^5\}$ is retrieved.
 When $\epsilon \rightarrow m_{ad}$, large deviations from this power law are seen and the system quickly
-approaches Ma $\approx 1$.  Ma shows weak scaling with $\epsilon$, and does not exceed Ma$ \approx 1$
+approaches Ma the supersonic regime.  
+(b) At high epsilon, $Ma$ scales as $Ra^{0.2606}$ until it reaches the supersonic regime, at which point it turns
+over and follows a power law of $Ra^{-0.1042}$.  At low epsilon, consistent power laws are achieved throughout all
+values of $Ra$ studied, where $Ma \propto \{Ra^{0.2606}, Ra^{0.2165}\}$ for $\epsilon = \{10^{-4}, 10^{-7}\}$. All
+error bars are negligible.  To study dynamics in the regime of deep solar convection ($Ma \approx 10^{-4}, 
+Ra \approx 10^{20}$), a superadiabatic excess of $\epsilon \approx 10^{-17}$ is appropriate.
 \label{fig:ma_v_eps} }
@@
 &\begin{aligned}
-&\frac{D \ln\rho}{D t} + \Div{\bm{u}} = 0
+&\frac{D \ln\rho}{D t} = -\Div{\bm{u}}
 	\label{eqn:continuity_eqn}
@@
 &\begin{aligned}
-&\rho\frac{D\bm{u}}{D t}=
--\grad P + \rho\bm{g} - \nabla\cdot\stressT
+\frac{D\bm{u}}{D t}=
+&-\grad T - T\grad\ln\rho + \bm{g} \\
+&\,\,\,\,-\nu\Div{\lilstressT} - \lilstressT\cdot\grad\nu - \nu\lilstressT\cdot\grad\ln\rho
 \label{eqn:momentum_eqn}
@@
 &\begin{aligned}
-\rho c_V\left(\frac{D T}{D t} + (\gamma-1)T\Div{\bm{u}}\right) + &\Div{-\kappa\grad T} = \\
-&-\left(\stressT\cdot\nabla\right)\cdot\bm{u} 
+\frac{D T}{D t} = &-(\gamma-1)T\Div{\bm{u}} + \frac{\chi}{c_V}\grad^2 T + \\
+&\grad T \cdot \grad\chi + \chi\grad T \cdot\grad\ln\rho +\nu\left(\lilstressT\cdot\nabla\right)\cdot\bm{u} 
 	\label{eqn:energy_eqn}
@@
 \begin{equation}
-\Pi_{ij} \equiv -\mu\left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\Div{\bm{u}}\right).
+\sigma_{ij} \equiv \left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\Div{\bm{u}}\right).
 	\label{eqn:stress_tensor}
@@
 energy flux (with $\phi \equiv -gz$), 
-and $\bm{F}_{\text{visc}} \equiv \bm{u}\cdot\stressT$ is the viscous flux.  Taking an inner product of
+and $\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$ is the viscous flux.  Taking an inner product of
 Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
@@
 
-We utilize the novel Dedalus pseudospectral framework (cite website?) to time-evolve Eqs. 
+\textbf{Using a linear eigenvalue solve, we found the critical Ra number to be blahblahblah}
+
+We utilize the novel Dedalus pseudospectral framework (http://dedalus-project.org/) to time-evolve Eqs. 
 \ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn} using an implicit-explicit third-order four-step 
@@
 The efficiency of convection is quantified by the Nusselt number.  
-While the Nusselt number is well-defined in \RB convection
+While the Nusselt number is well-defined in RB convection
 as the amount of total flux divided by the steady-state background conductive flux 
@@
 \begin{equation}
-N \equiv \frac{F_{\text{conv, z}} + F_{\text{rad, z}} - F_A}{F_{\text{ref}} - F_A},
+Nu \equiv \frac{F_{\text{conv, z}} + F_{\text{rad, z}} - F_A}{F_{\text{ref}} - F_A},
 \label{eqn:nusselt}
@@
 respectively.  $F_A$ is the adiabatic conductive flux, defined as $F_A = -\kappa \partial_z T_{\text{ad}}$.  For an
-atmosphere in hydrostatic equilibrium, such as a polytrope, $\partial_z T_{\text{ad}} \equiv - g / c_{P}$, and thus
-$F_A = \kappa g / c_{P}$.  $F_{\text{ref}} = \Delta T / L_z$ is the conductive flux of a linear profile connecting the upper
-and lower plates, where $\Delta T = T_{u} - T_{\ell}$.
+ideal gas atmosphere in hydrostatic equilibrium, $\partial_z T_{\text{ad}} \equiv - g / c_{P}$.
+$F_{\text{ref}} = \Delta T / L_z$ , where $\Delta T = T_{u} - T_{\ell}$, is the conductive flux of a linear profile connecting the upper
+and lower plates.
 
@@
 cases. Convection works to
-suppress entropy stratification and create isentropic atmospheres.  Under the Boussinesq approximation where
-density variations are ignored, entropy stratification is directly proportional to temperature stratification,
-such that $\grad S \rightarrow 0$ only when $\grad T \rightarrow 0$.  Thus, for \RB convection, 
-$\grad T_{\text{ad}} \equiv 0$ and the familiar form of $N$ is retrieved.  In the case of stratified convection,
+suppress entropy stratification and create isentropic atmospheres.  Under the Boussinesq approximation,
+density variations are ignored and entropy stratification is directly proportional to temperature stratification,
+such that $\grad S \rightarrow 0$ only when $\grad T \rightarrow 0$.  Thus, for RB convection, 
+$\grad T_{\text{ad}} \equiv 0$ and the familiar form of $Nu$ is retrieved.  In the case of stratified convection,
 as $\epsilon \rightarrow m_{ad} + 1$, $\grad P \propto g \rightarrow 0$ and
 the resulting $\grad T_{\text{ad}} \rightarrow 0$.  In such a case, $F_A \rightarrow 0$ and the familiar
-definition of the \RB nusselt number is appropriate to use, which explains why convection carries all of the
-atmosphereic flux in such a case \cite{brandenburg&all2005}. As $\epsilon \rightarrow 0$, 
+definition of the RB Nusselt number is appropriate to use, as convection carries all of the
+atmospheric flux in such a case \cite{brandenburg&all2005}. As $\epsilon \rightarrow 0$, 
 $\grad T_{\text{ad}}\rightarrow \grad T_0$, the atmospheric initial temperature profile.  This causes increasingly
-smaller velocity, temperature, and pressure perturbations (e.g. Fig. \ref{fig:ma_v_eps}), but due to the removal
-of the background radiative flux from the numerator and denominator in Eq. \ref{eqn:nusselt}, increasingly smaller
-perturbations have just as large of an effect on the nusselt number.
+smaller velocity, and thermodynamic perturbations (e.g. Fig. \ref{fig:ma_v_eps}), but the removal of the 
+O(1) background term in the numerator and denominator of Eq. \ref{eqn:nusselt}, makes the numerator and
+denominator both O($\epsilon$).
 
 We solved initial value problems which start in hydrostatic and thermal equilibrium and experienced infinitesimal 
-kicks compared to $\epsilon$ in $T_1$.  Solutions were time-evolved until a long-time average of $N$ showed little
+kicks compared to $\epsilon$ in $T_1$.  Solutions were time-evolved until a long-time average of $Nu$ showed little
 dependence on height. At
@@
 both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
+It is unsurprising that \cite{cattaneo&all1990} discovered that as $\gamma \rightarrow 1$, shocks are easier to
+find and produce, as in such a regime $m_{ad} \rightarrow \infty$ and, as a result, $\epsilon \rightarrow \infty$.
 Low mach number flows, such as those in an $\epsilon = 10^{-4}$ atmosphere (e.g. Fig. \ref{fig:entropy_snapshots}b)
-have similar bulk thermodynamic structure but lack the complicating dynamics of shock heating. As Ra is
-increased to very large values (e.g. Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures no longer span
-the vertical extent of the domain but instead break up into small packets which traverse through the domain many
-times before diffusing.  The complicated nature of high Ra dynamics, especially in the low Ma regime where
-shocks are absent, has barred us from sufficiently converging any solutions in the regime of $Ra > 10^7$.
+have similar bulk thermodynamic structure but lack the complicating dynamics of shock heating. This is interesting
+in light of the current literature, as low Mach number flows are in pressure equilibrium with the background and
+so pressure forces can no longer be the cause of narrow downflow lanes and broad upflow regions, as suggested
+by \cite{hurlburt&all1984}.  As Ra is
+increased to very large values (e.g. Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
+break up into small packets which traverse through the domain many
+times before diffusing rather than spanning the whole domain.  
+The complicated nature of high Ra dynamics, especially in the low Ma regime where
+shocks are absent, has barred us from sufficiently converging any solutions in the regime of $Ra > 10^6$
+at low $\epsilon$.
 
@@
 but otherwise the dynamics are similar.  As Ra is increased (c), downflow lanes no longer span
-the entirety of the domain and individual cold, small blobs are responsible for carrying the flux downward.
+the entirety of the domain and individual small blobs are responsible for carrying the flux.
 \label{fig:entropy_snapshots} }
@@
 
-Despite diferent thermodynamic structures, the properly normalized \emph{sum} of the fluxes for a given
-Ra is similar.  See, for example, Fig. \ref{fig:flux_profiles} to see time-averaged horizontal profiles of
-the vertical system fluxes.  At high $\epsilon$ and Ra, $\bm{F}_{\text{enth}}$ and $\bm{F}_{\text{KE}}$
-exhibit two local maxima over the depth of the domain, whereas at low $\epsilon$ and low Ma, there is only
-one local maximum near the bottom of the domain.  Viscous fluxes become important near the bottom boundary
-layer, and radiative flux is nearly zero everywhere in the domain except for near the boundaries where the
-fixed-temperature boundary conditions create large deviations in $\grad T$ away from $\grad T_{\text{ad}}$.
+At high values of Ra, the heat transport properties of the systems become increasingly complex and time-dependent.
+Large $\epsilon$ flows exhibit two local maxima in the enthalpy flux and kinetic energy flux: one in the upper 
+atmosphere caused by the shocks, and one in the lower atmosphere caused by the deep mixing of convective motions.
+At low $\epsilon$, only the deep maximum is present.  Furthermore, for low values of $\epsilon$, the presence
+of fixed-temperature boundary conditions allows the flux at the boundaries to vary.  Many runs at $Ra > 10^5$,
+$\epsilon = 10^{-4}$ exhibit time-dependent states of stratified convection (such as those shown in 
+Fig. \ref{fig:entropy_snapshots}), in which the flux entering the system at the bottom of the atmosphere exceeds
+that at the top.  These states are punctuated by states of vigorous shearing which flatten the bottom temperature
+gradient towards adiabatic, allowing the excess energy to exit through the upper boundary.  These shearing
+states will be covered in more detail in a future paper.  Regardless, a proper long-term average over shearing
+and non-shearing states retrieves an invariant flux profile (and therefore Nu profile) throughout the depth
+of the atmosphere (\textbf{After about 24 more hours, it'll be flat!  I don't have enough data at the parameters
+shown in Fig. \ref{flux_profiles} yet}).
 
@@
 \includegraphics[width=3.4375in]{./figs/fluxes_fig.png}
-\caption{Flux profiles for low (top) and high (bottom) Mach number flows.  
+\caption{Time-averaged flux profiles for low (top) and high (bottom) Mach number flows at $Ra = 10^6$.  
+The dashed lines correpond to the
+enthalpy flux (orange, positive) and kinetic energy flux (purple, negative).  The grey dash-dot line is the
+viscous flux, and the green dotted line is the radiative flux with the adiabatic radiative flux removed. All
+fluxes are normalized by $F_{ref} - F_A$, as in the calculation of the Nusselt number.  The solid black line is
+the properly normalized sum of all the fluxes, and under this normalization its height-averaged value is the
+Nusselt number.
 \label{fig:flux_profiles} }
@@
 
-At low Rayleigh number, diffusivities are high and the flows are very laminar.  Such flows often achieve a
-steady state and have a well-defined Nusselt number which is independent of time.  However, as the Rayleigh
-number increases, the flows become increasingly time-dependent.  Even steady structures such as solid
-``rolls'' like those pictured in Fig. \ref{fig:entropy_snapshots} have highly time-dependent Nusselt numbers.
-This is, in part, due to the fact that cold downdrafts floating to the bottom of the domain can be entrained
-by upflows, or warm risen parcels can be entrainedi n the intense cold downdrafts.  Such events reverse the
-preferred direction of flux in the system, and even let the Nusselt number become negative for short periods of
-time.  As a result, it is necessary to take a long time average of the fluxes
-before calculating the Nusselt number at higher Rayleigh number. (IS THIS USEFUL?)
-
-%
-%\begin{figure}[t]
-%\includegraphics[width=3.4375in]{./figs/nu_v_time.png}
-%\caption{The evolution of the Nusselt number is shown at low ($10^2$) and high ($10^7$) Rayleigh number and at
-%$\epsilon = 10^{-4}$.  At low Rayleigh number, the system is able to settle into a time invariant solution. As
-%the Rayleigh number is raised, the thermodynamic structure become increasingly complex and time variant, and a
-%time-average of the Nusselt number is required to obtain a sensible mean.
-%\label{fig:nu_v_time} }
-%\end{figure}
-
-The evolution of the Nusselt number as the Rayleigh number is increased is shown for both high and low
-$\epsilon$ in Fig. \ref{fig:nu_v_ra}.  Below convective onset, the Nusselt number is perfectly one. Just above
-onset, there is a brief range of highly inflated scaling between $N$ and Ra.
+After appropriately time-averaging the fluxes, a sensible Nusselt number is retrieved.  Nusselt numbers for
+all simulations at low and high Ma are plotted in Fig. \ref{fig:nu_v_ra}.  At $\epsilon = \{10^{-4}, 10^{-7}\}$,
+scaling laws of $Nu \propto Nu^{\{0.3090, 0.3087\}}$ are retrieved.  At $\epsilon = 0.5$, in the near-sonic
+regime ($Ra \leq 10^4$), the scaling of $Nu$ with $Ra$ is inflated, with $Nu \propto Ra^{0.4489}$.  As simulations
+pass into the supersonic regime and shocks start to form near the downflows, propoelling warm fluid deep
+into the atmosphere, that scaling drops to $Nu \propto Ra^{0.1936}$.  Error on all power law scalings is
+negligible.
 
@@
 \includegraphics[width=3.4375in]{./figs/nu_v_ra.png}
-\caption{Variation of the Nusselt number as a function of the Rayleigh number is shown.
+\caption{Variation of $Nu$ as $Ra$ increases is shown for $\epsilon = \{10^{-7}, 10^{-4}, 0.5\}$. 
+At high $\epsilon$, a clear transition from the subsonic to supersonic regime is evident in the scaling
+of Nu with Ra.  In the low $\epsilon$ regime Nu vs. Ra scalings collapse onto a similar line which is
+reminiscent of RB scalings \cite{johnston&doering2009}.
 \label{fig:nu_v_ra} }
@@
 \label{sec:discussion}
+Here we have presented a non-dimensional construction of polytropic atmospheres and the control parameters 
+which determine flow characteristics in such systems.  We argue that such systems are the natural extension
+of the RB problem to stratified systems, and should be used to understand the basic properties of stratified
+convection.  We have argued that the traditional definition of the Nusselt number in stratified atmospheres
+\cite{graham1975} is the correct one, and shown how it extends in extreme cases.
+
+Furthermore, we have demonstrated that low Ma flows exhibit the same broad-upflow / narrow downflow dynamics
+as are observed in high Mach number flows \cite{hurlburt&all1984}.  However, unlike at high Ma, pressure perturbations
+are no longer responsible this effect; rather, high temperature, low density upflows and low temperature,
+high density upflows causing appropriately signed entropy perturbations are responsible for the entirely
+buoyantly-driven flow.  It is possible that at low Ma, these flows begin to feel the pressure response of the
+top and bottom walls which leads them to deflect at the far boundary in a way that high Ma flows do not.
+
+The dynamics of these polytropic solutions are complex and highly time-dependent, even in two dimensions.
+Time-dependent oscillating shear states have developed spontaneously, as seen before in RB convection
+(\textbf{citation}).  Future work will aim to better understand the mechanisms of shearing states and
+whether or not these states are attainable in three-dimensional, non-rotating atmospheres.  While the
+two-dimensional work studied here offers a basis for comparing the heat transport abilities of stratified
+convection compared to RB convection \cite{johnston&doering2009}, it will be informative to study the low 
+Mach number systems presented here in three dimensions and in atmospheres bounded by stable regions.
 
 \subsection{acknowledgements}
-This work was supported by the CU/NSO Hale Graduate Fellowship and Juri's allocation and Ben's allocation.
+This work was supported by the CU/NSO George Ellery Hale Graduate Fellowship,
+Juri's allocation and Ben's allocation.
 We thank Axel Brandenburg, Mark Rast, and Jeff Oishi for many useful discussions.

### 2016-09-30 tex/nusselt_paper.tex
better draft than last night; discussion needs love and some text needs cutting.

@@
 plane-parallel polytropically stratified atmospheres. 
-We hold the density stratification ($n_\rho$) and Prandtl number (Pr) constant while studying the dependence
-of the Nusselt number (Nu), which quantifies the efficiency of convective heat transport, on
-variations of the Mach number (Ma) and the Rayleigh number (Ra).  At large but still subsonic values of
-Ma, a scaling $Nu \appropto Ra^{0.45}$ for low values of Ra.  As Ra increases and flows become supersonic,
-this scaling gives way to a much weaker $Nu \appropto Ra^{0.20}$.  In the regime of $Ma \ll 1$, a consistent
-$Nu \appropto Ra^{0.3}$ is retrieved,  reminiscent of the Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
+We hold the density stratification (\nrho) and Prandtl number (Pr) constant while varying the
+Mach number (Ma) and the Rayleigh number (Ra) to determine the behavior of the Nusselt number (Nu), 
+which quantifies the efficiency of convective heat transport.
+As Ra increases and $\text{Ma} \rightarrow 1$, a scaling of Nu $\appropto$ Ra$^{0.45}$ is observed.  
+As Ra increases to a regime where Ma $\geq 1$,
+this scaling gives way to a weaker Nu $\appropto$ Ra$^{0.20}$.  In the regime of Ma $\ll 1$, a consistent
+Nu $\appropto$ Ra$^{0.3}$ is retrieved,  reminiscent of the Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
 \end{abstract}
@@
 envelopes of low mass stars, and the atmospheres of terrestrial and jovian planets. In such systems, convection
-occurs in the presence of the atmospheric stratification, which can be small but extends up to 
+occurs in the presence of the atmospheric stratification which can be small but extends up to 
 14 density scale heights in the Sun's convective envelope.
@@
 properties of compressible convection in stratified media is important to understanding systems in astrophysics
-and planetary sciences.  Numerical constraints typically have restricted studies of stratified convection to
-moderately high Mach numbers, appropriate to regions near the Sun's surface.  As such, we know little about the
-fundamental properties of low-Mach number stratified convection, which occurs in the deep solar interior.
+and planetary sciences.  Numerical constraints have often restricted studies of stratified convection to
+moderately high Mach numbers, appropriate to regions near the Sun's surface.  As such, we know few
+fundamental properties of the low-Mach number stratified convection which occurs in the deep solar interior.
 
@@
 the temperature gradient approaches zero in the convective interior causing the conductive flux to similarly 
-disappear.  Highly stratified convection, on the other hand, exhibits narrow downflow lanes broad upflow regions.
-Furthermore, the \emph{entropy} gradient is flattened by convection rather than the temperature gradient, which
-means that even in the presence of perfectly efficient convection a significant component of the flux can be
+disappear.  Highly stratified convection exhibits narrow downflow lanes and broad upflow regions.
+Furthermore, the \emph{entropy} gradient is negated by convection rather than the temperature gradient, such
+that in the presence of perfectly efficient convection a significant component of the flux can be
 carried by conduction.
@@
 buoyant driving to diffusive damping, and the Prandtl number (Pr), the ratio of viscous to thermal
-diffusivity.  Along with the aspect ratio of the physical domain, these two numbers entirely control the
+diffusivity.  These numbers couple with the aspect ratio of the physical domain and the boundary conditions
+to entirely control the
 dynamics of the convection.  In stratified atmospheres, in addition to specifying the equation of state and
@@
 In this letter we study the behavior of convective heat transport, quantified by
-the Nusselt number (Nu), in polytropically stratified atmospheres.  
+the Nusselt number (Nu), in plane-parallel two-dimensional polytropically stratified atmospheres.  
 We vary $\epsilon$ and Ra while holding \nrho and Pr
-constant across all simulations and convective structures which arise in a domain with an aspect ratio of 4.  In section 
+constant across all simulations.  We study domains with an aspect ratio of 4.  In section 
 \ref{sec:experiment}, we describe the construction of atmospheres, our equations, and our method for
@@
 In order to compare our results with previous studies and in an effort to examine a simplest case,
-we study a fluid composed of monatomic ideal gas particles, with an adiabatic index of $\gamma = 5/3$ and
+we study a fluid composed of monatomic ideal gas particles with an adiabatic index of $\gamma = 5/3$ and
 whose equation of state is $P = R^*\rho T$. 
@@
 We specify the number of density scale heights the atmosphere spans, $n_\rho$, to determine $L_{z}$. Throughout
-this letter, we set $n_{\rho} = 3$ such that the density at the bottom of the atmosphere is larger
-than at the top by a factor of 20.
+this letter, we set $n_{\rho} = 3$ such that the density varies by a factor of 20.
 Thermodynamic variables are nondimensionalized at the top of the atmosphere as 
@@
 The subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$.  
-The characteristic timescale of such an
+The characteristic timescale of the
 atmosphere is related to the characteristic atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$.
@@
 $\nu \equiv \mu/\rho$ and $\chi \equiv \kappa/\rho$.  As a result, $\text{Ra} \propto (\nu\chi)^{-1} \propto
-\rho^2$, such that for our atmospheres with $n_{\rho} = 3$, the Rayleigh number increases by a factor of
-400 across the domain.  This formulation leaves Pr
+\rho^2$.  The atmospheres studied here with $n_{\rho} = 3$ experience an increase in the Rayleigh number 
+by a factor of 400 across the domain.  This formulation leaves Pr
 constant throughout the depth of the atmosphere, and in this letter we impose $\text{Pr} = 1$.
@@
 is reflected in the evolved values of these fluctuations, which follow the scaling of
-Ma$^{1/2} \propto T_1/T_0 \propto \rho_{1}/\rho_{0} \propto \epsilon$, and which scale as roughly $Ra^{0.25}$,
+Ma$^{1/2} \propto T_1/T_0 \propto \rho_{1}/\rho_{0} \propto \epsilon$ for low values of $\epsilon$,
 as in Fig. \ref{fig:ma_v_eps}.
@@
 &\begin{aligned}
-\frac{D T}{D t} = &-(\gamma-1)T\Div{\bm{u}} + \frac{\chi}{c_V}\grad^2 T + \\
-&\grad T \cdot \grad\chi + \chi\grad T \cdot\grad\ln\rho +\nu\left(\lilstressT\cdot\nabla\right)\cdot\bm{u} 
+\frac{D T}{D t} = -&(\gamma-1)T\Div{\bm{u}} + \frac{1}{c_V}\left\{ \chi\grad^2 T + \grad T \cdot \grad\chi  \right. \\ \
+&+ \chi\grad T \cdot\grad\ln\rho +\nu\left(\lilstressT\cdot\nabla\right)\cdot\bm{u}\left.\right\} 
 	\label{eqn:energy_eqn}
@@
 
-In such stratified systems, the total convective flux can be defined as
+In such stratified systems, the total convective flux is
 \begin{equation}
@@
 \frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
-\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{rad}}} = 0
+\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0
 	\label{eqn:energy_eqn_full}
 \end{equation}
-where $\bm{F}_{\text{rad}} = -\kappa \grad T$.  An understanding of the flux terms is essential to characterizing
+where $\bm{F}_{\text{cond}} = -\kappa \grad T$.  An understanding of the flux terms is essential to characterizing
 the convective heat transport in our systems.
 
-The atmosphere is bounded above
-and below by impenetrable, stress free, fixed temperature boundary conditions such that
-\begin{equation}
-w = \partial_z u = T_1 = 0
-\end{equation}
-at the boundaries.
-
-\textbf{Using a linear eigenvalue solve, we found the critical Ra number to be blahblahblah}
-
-We utilize the novel Dedalus pseudospectral framework (http://dedalus-project.org/) to time-evolve Eqs. 
+The atmosphere is contained between two impenetrable, stress free, fixed temperature boundaries at
+the top and bottom of the domain such that $w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. The domain
+is periodic in the horizontal.We utilize the novel Dedalus pseudospectral framework (http://dedalus-project.org/) to time-evolve Eqs. 
 \ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn} using an implicit-explicit third-order four-step 
@@
 Variables are time-evolved on a dealiased Chebyshev (vertical)
-and Fourier (horizontal, periodic) domain in which the
+and Fourier (horizontal) domain in which the
 physical grid dimensions are 3/2 the size of the coefficient grid.  Our physical grid sizes range from
@@
 \begin{equation}
-Nu \equiv \frac{F_{\text{conv, z}} + F_{\text{rad, z}} - F_A}{F_{\text{ref}} - F_A},
+\text{Nu} \equiv \frac{F_{\text{conv, z}} + F_{\text{cond, z}} - F_A}{F_{\text{ref}} - F_A},
 \label{eqn:nusselt}
 \end{equation}
-where $F_{\text{conv, z}}$ and $F_{\text{rad, z}}$ are the z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{rad}}$,
+where $F_{\text{conv, z}}$ and $F_{\text{cond, z}}$ are the z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
 respectively.  $F_A$ is the adiabatic conductive flux, defined as $F_A = -\kappa \partial_z T_{\text{ad}}$.  For an
-ideal gas atmosphere in hydrostatic equilibrium, $\partial_z T_{\text{ad}} \equiv - g / c_{P}$.
+ideal gas in hydrostatic equilibrium, $\partial_z T_{\text{ad}} \equiv - g / c_{P}$.
 $F_{\text{ref}} = \Delta T / L_z$ , where $\Delta T = T_{u} - T_{\ell}$, is the conductive flux of a linear profile connecting the upper
@@
 such that $\grad S \rightarrow 0$ only when $\grad T \rightarrow 0$.  Thus, for RB convection, 
-$\grad T_{\text{ad}} \equiv 0$ and the familiar form of $Nu$ is retrieved.  In the case of stratified convection,
+$\grad T_{\text{ad}} \equiv 0$ and the familiar form of Nu is retrieved.  In the case of stratified convection,
 as $\epsilon \rightarrow m_{ad} + 1$, $\grad P \propto g \rightarrow 0$ and
-the resulting $\grad T_{\text{ad}} \rightarrow 0$.  In such a case, $F_A \rightarrow 0$ and the familiar
-definition of the RB Nusselt number is appropriate to use, as convection carries all of the
-atmospheric flux in such a case \cite{brandenburg&all2005}. As $\epsilon \rightarrow 0$, 
+the resulting $\grad T_{\text{ad}} \rightarrow 0$.  In such a case, $F_A \rightarrow 0$ and the
+definition of the RB Nu is appropriate to use, as convection carries all of the
+flux \cite{brandenburg&all2005}. As $\epsilon \rightarrow 0$, 
 $\grad T_{\text{ad}}\rightarrow \grad T_0$, the atmospheric initial temperature profile.  This causes increasingly
@@
 
-We solved initial value problems which start in hydrostatic and thermal equilibrium and experienced infinitesimal 
-kicks compared to $\epsilon$ in $T_1$.  Solutions were time-evolved until a long-time average of $Nu$ showed little
-dependence on height. At
-high values of $\epsilon$, shock systems form in the upper atmosphere near downflow lanes 
-(see e.g. Fig. \ref{fig:entropy_snapshots}a) and propagate towards upflow lanes.  Such systems were reported in
-both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
-It is unsurprising that \cite{cattaneo&all1990} discovered that as $\gamma \rightarrow 1$, shocks are easier to
-find and produce, as in such a regime $m_{ad} \rightarrow \infty$ and, as a result, $\epsilon \rightarrow \infty$.
-Low mach number flows, such as those in an $\epsilon = 10^{-4}$ atmosphere (e.g. Fig. \ref{fig:entropy_snapshots}b)
-have similar bulk thermodynamic structure but lack the complicating dynamics of shock heating. This is interesting
-in light of the current literature, as low Mach number flows are in pressure equilibrium with the background and
-so pressure forces can no longer be the cause of narrow downflow lanes and broad upflow regions, as suggested
-by \cite{hurlburt&all1984}.  As Ra is
-increased to very large values (e.g. Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
-break up into small packets which traverse through the domain many
-times before diffusing rather than spanning the whole domain.  
-The complicated nature of high Ra dynamics, especially in the low Ma regime where
-shocks are absent, has barred us from sufficiently converging any solutions in the regime of $Ra > 10^6$
-at low $\epsilon$.
-
-\begin{figure}[t]
+\begin{figure}[b]
 \includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
@@
 
-At high values of Ra, the heat transport properties of the systems become increasingly complex and time-dependent.
-Large $\epsilon$ flows exhibit two local maxima in the enthalpy flux and kinetic energy flux: one in the upper 
-atmosphere caused by the shocks, and one in the lower atmosphere caused by the deep mixing of convective motions.
-At low $\epsilon$, only the deep maximum is present.  Furthermore, for low values of $\epsilon$, the presence
-of fixed-temperature boundary conditions allows the flux at the boundaries to vary.  Many runs at $Ra > 10^5$,
-$\epsilon = 10^{-4}$ exhibit time-dependent states of stratified convection (such as those shown in 
-Fig. \ref{fig:entropy_snapshots}), in which the flux entering the system at the bottom of the atmosphere exceeds
-that at the top.  These states are punctuated by states of vigorous shearing which flatten the bottom temperature
-gradient towards adiabatic, allowing the excess energy to exit through the upper boundary.  These shearing
-states will be covered in more detail in a future paper.  Regardless, a proper long-term average over shearing
-and non-shearing states retrieves an invariant flux profile (and therefore Nu profile) throughout the depth
-of the atmosphere (\textbf{After about 24 more hours, it'll be flat!  I don't have enough data at the parameters
-shown in Fig. \ref{flux_profiles} yet}).
+We solved initial value problems which start in hydrostatic and thermal equilibrium and experienced infinitesimal 
+kicks compared to $\epsilon$ in $T_1$.  Solutions were time-evolved until a long-time average of Nu showed little
+dependence on depth. By performing a linear stability analysis, we determined that the onset of convection
+occurs at Ra$_c$ $= \{10, 11, 11\}$ (\textbf{need exact}) for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  We study Rayleigh
+numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$, $10^5$Ra$_c$ for $\epsilon = 10^{-4}$,
+and $10^4$Ra$_c$ for $\epsilon = 10^{-7}$.  At
+high values of $\epsilon$, shock systems form in the upper atmosphere near downflow lanes 
+(see e.g. Fig. \ref{fig:entropy_snapshots}a) and propagate towards upflow lanes.  Such systems were reported in
+both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
+In the context of Fig \ref{fig:ma_v_eps}, it is unsurprising that as $\gamma \rightarrow 1$, systems in which shocks
+form are easier to produce \cite{cattaneo&all1990}.  In such a limit, $m_{ad} \rightarrow \infty$ 
+and therefore $\epsilon \rightarrow \infty$.
+Low mach number flows, such as those in an $\epsilon = 10^{-4}$ atmosphere (e.g. Fig. \ref{fig:entropy_snapshots}b)
+have similar bulk thermodynamic structure but lack the complicating dynamics of shock heating. This is interesting
+in light of the current literature, as low Mach number flows are in pressure equilibrium with the background and
+pressure forces cannot be the cause of narrow downflow lanes and broad upflow regions, as has been suggested
+\cite{hurlburt&all1984}.  As Ra is
+increased to very large values (e.g. Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
+break up into small packets which traverse through the domain many
+times before diffusing rather than spanning the whole domain.  
+The complicated nature of high Ra dynamics, especially in the low Ma regime where
+shocks are absent, has barred us from sufficiently converging any solutions in the regime of 
+$\text{Ra }> 10^5\text{Ra}_c$ at low $\epsilon$.
 
@@
 \includegraphics[width=3.4375in]{./figs/fluxes_fig.png}
-\caption{Time-averaged flux profiles for low (top) and high (bottom) Mach number flows at $Ra = 10^6$.  
+\caption{Time-averaged flux profiles for high (top) and low (bottom) Mach number flows at $Ra = 10^6$.  
 The dashed lines correpond to the
@@
 \end{figure}
+
+At high values of Ra, the heat transport properties of the systems become increasingly complex and time-dependent.
+Large $\epsilon$ flows exhibit two local maxima in the enthalpy flux and kinetic energy flux: one in the upper 
+atmosphere caused by the shocks, and one in the lower atmosphere caused by the deep mixing of convective motions
+(see Fig. \ref{fig:flux_profiles}a).
+At low $\epsilon$, only the deep maximum is present (Fig. \ref{fig:flux_profiles}b).  
+Furthermore, the presence
+of fixed-temperature boundary conditions allows the flux at the boundaries to vary.  Many runs at $Ra > 10^5$ and
+$\epsilon = 10^{-4}$ exhibit time-dependent states of stratified convection (such as those shown in 
+Fig. \ref{fig:entropy_snapshots}b\&c), in which the flux entering the system at the bottom of the atmosphere exceeds
+that at the top.  These states are punctuated by states of vigorous shearing, similar to those previouslyl
+reported in two-dimensional RB convection (\textbf{cite goluskin?}).  These shearing states flatten the bottom temperature
+gradient towards adiabatic, allowing the excess energy to exit through the upper boundary.  These shearing
+states will be covered in more detail in a future paper.  Regardless, a proper long-term average over shearing
+and non-shearing states retrieves an invariant flux profile (and therefore Nu profile) throughout the depth
+of the atmosphere (\textbf{After about 24 more hours, it'll be flat!  I don't have enough data at the parameters
+shown in Fig. \ref{fig:flux_profiles} yet}).
 
@@
 of Nu with Ra.  In the low $\epsilon$ regime Nu vs. Ra scalings collapse onto a similar line which is
-reminiscent of RB scalings \cite{johnston&doering2009}.
+reminiscent of RB scalings \cite{johnston&doering2009}.  Error bars represent one standard deviation
+of a long-time averaged Nu sampled throughout the depth of the domain.
 \label{fig:nu_v_ra} }
@@
 Here we have presented a non-dimensional construction of polytropic atmospheres and the control parameters 
-which determine flow characteristics in such systems.  We argue that such systems are the natural extension
+which determine flow characteristics in such systems.  We argue that these atmospheres are the natural extension
 of the RB problem to stratified systems, and should be used to understand the basic properties of stratified
-convection.  We have argued that the traditional definition of the Nusselt number in stratified atmospheres
+convection.  The striking similarity between the growth of Nu with Ra at low Ma and in RB convection suggests
+that low Ma polytropic convection shares many properties with RB convection but includes the complicating
+effect of stratification. We have argued that the traditional definition of the Nusselt number in stratified atmospheres
 \cite{graham1975} is the correct one, and shown how it extends in extreme cases.
@@
 Furthermore, we have demonstrated that low Ma flows exhibit the same broad-upflow / narrow downflow dynamics
-as are observed in high Mach number flows \cite{hurlburt&all1984}.  However, unlike at high Ma, pressure perturbations
-are no longer responsible this effect; rather, high temperature, low density upflows and low temperature,
-high density upflows causing appropriately signed entropy perturbations are responsible for the entirely
-buoyantly-driven flow.  It is possible that at low Ma, these flows begin to feel the pressure response of the
+as are observed in high Mach number flows \cite{hurlburt&all1984}.  However, pressure perturbations
+cannot be responsible for this effect; rather, high temperature, low density upflows and low temperature,
+high density upflows causing appropriately signed entropy perturbations which buoyantly rise or fall accordingly.
+It is possible that at low Ma, these flows begin to feel the pressure response of the
 top and bottom walls which leads them to deflect at the far boundary in a way that high Ma flows do not.
@@
 convection compared to RB convection \cite{johnston&doering2009}, it will be informative to study the low 
-Mach number systems presented here in three dimensions and in atmospheres bounded by stable regions.
+Mach number systems presented here in three dimensions and in atmospheres bounded by stable regions
+\cite{hurlburt&all1986}.
 

### 2016-10-08 tex/nusselt_paper.tex
incorporates most of Ben's comments, will clean up later

@@
 %\documentclass[iop]{emulateapj}
-\documentclass[aps, prl, twocolumn, groupedaddress, amsfonts, amssymb, amsmath]{revtex4-1}
+\documentclass[aps, prl, twocolumn, nofootinbib, groupedaddress, amsfonts, amssymb, amsmath]{revtex4-1}
 \usepackage{graphicx}
@@
 
-Some of the earliest numerical experiments on stratified convection
-were performed in two \cite{graham1975, chan&all1982,
-hurlburt&all1984, cattaneo&all1990} and three \cite{cattaneo&all1991, brummell&all1996} dimensions and
+Early numerical experiments on stratified convection
+in two \cite{graham1975, chan&all1982,
+hurlburt&all1984, cattaneo&all1990} and three \cite{cattaneo&all1991, brummell&all1996} dimensions
 revealed a number of basic properties in the moderate-to-high Mach number regime.
@@
 Furthermore, the \emph{entropy} gradient is negated by convection rather than the temperature gradient, such
-that in the presence of perfectly efficient convection a significant component of the flux can be
+that in the presence of perfectly efficient convection a significant component of the flux is still
 carried by conduction.
@@
 we study a fluid composed of monatomic ideal gas particles with an adiabatic index of $\gamma = 5/3$ and
-whose equation of state is $P = R^*\rho T$. 
+whose equation of state is $P = R\rho T$. 
 The initial stratification is polytropic and the gravitational
@@
 \rho_0(z) &= \rho_{00}(z_0 - z)^m \\
-T_0(z)    &= T_{00}(z_0 - z),
+T_0(z)    &= T_{00}(z_0 - z).
 \label{eqn:polytrope}
@@
 \end{equation}
-where $z$ increases upwards within the bounds $z =\{0, L_{z}\}$.
-We specify the number of density scale heights the atmosphere spans, $n_\rho$, to determine $L_{z}$. Throughout
-this letter, we set $n_{\rho} = 3$ such that the density varies by a factor of 20.
 Thermodynamic variables are nondimensionalized at the top of the atmosphere as 
-$P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, requiring $z_0 \equiv L_z + 1$ and $R^* = T_{00} = \rho_{00} = 1$.  
-The polytropic index is set by the adiabatic index and the
-superadiabatic excess, $\epsilon$, such that $m = m_{ad} - \epsilon$
-where $m_{ad} \equiv (\gamma-1)^{-1}$ is the adiabatic polytropic index.
+$P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, requiring $z_0 \equiv L_z + 1$ and $R = T_{00} = \rho_{00} = 1$.
+By this choice, the non-dimensional length scale is the inverse temperature gradient scale and
+the timescale is the isothermal sound crossing time of this unit length.
+$z$ increases upwards within the bounds $z =[0, L_{z}]$, where $L_{z} = e^{n_{\rho}/m} - 1$ is
+determined by the number of density scale heights the atmosphere spans, $n_\rho$.
+Throughout this letter, we set $n_{\rho} = 3$ such that the density varies by a factor of 20.
+The polytropic index is such that $m = m_{ad} - \epsilon$
+where $m_{ad} \equiv (\gamma-1)^{-1}$ is the adiabatic polytropic index and $\epsilon$ is the
+superadiabatic excess.
 The subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$.  
-The characteristic timescale of the
-atmosphere is related to the characteristic atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$.
+The characteristic timescale of convective dynamics
+is related to the atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$, with $g = (m+1)$.
 We will utilize buoyancy time units throughout this letter.
 
-Atmospheric diffusivities are set by the Rayleigh number and the Prandtl number.  We define the
-non-dimensional Rayleigh number as
+Atmospheric diffusivities are specified by the Rayleigh number and the Prandtl number.  The
+non-dimensional Rayleigh number is
 \begin{equation}
@@
 where $\Delta S_0$ is the entropy difference between the top and bottom of the atmosphere, 
+$c_P = R\gamma(\gamma-1)^{-1}$ is the specific heat at constant pressure,
 $\nu$ is the kinematic viscosity (viscous diffusivity), and $\chi$ is the thermal dififusivity.  
@@
 constant throughout the depth of the atmosphere, and in this letter we impose $\text{Pr} = 1$.
+Throughout this letter, we specify Ra at the top of the atmosphere.
 
@@
 is reflected in the evolved values of these fluctuations, which follow the scaling of
-Ma$^{1/2} \propto T_1/T_0 \propto \rho_{1}/\rho_{0} \propto \epsilon$ for low values of $\epsilon$,
+$T_1/T_0 \propto \rho_{1}/\rho_{0} \propto$ Ma$^{1/2} \propto epsilon$ for low values of $\epsilon$,
 as in Fig. \ref{fig:ma_v_eps}.
@@
 \includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
-\caption{(a) Characteristic horizontally averaged maximum Mach numbers which have been
-time averaged for over 100$t_{b}$ starting roughly 50$t_{b}$ after the start of simulations. For $\epsilon \leq 0.1$,
-an evident scaling of $Ma \propto \{\epsilon^{0.5015}, \epsilon^{0.5130}\}$ 
+\caption{(a) Characteristic horizontally averaged maximum Mach numbers have been
+time averaged for over $\geq 100t_{b}$ beginning roughly 50$t_{b}$ after the start of simulations. For $\epsilon \leq 0.1$,
+an evident scaling of $Ma \propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
 at Ra = $\{10^2, 10^5\}$ is retrieved.
-When $\epsilon \rightarrow m_{ad}$, large deviations from this power law are seen and the system quickly
-approaches Ma the supersonic regime.  
-(b) At high epsilon, $Ma$ scales as $Ra^{0.2606}$ until it reaches the supersonic regime, at which point it turns
-over and follows a power law of $Ra^{-0.1042}$.  At low epsilon, consistent power laws are achieved throughout all
-values of $Ra$ studied, where $Ma \propto \{Ra^{0.2606}, Ra^{0.2165}\}$ for $\epsilon = \{10^{-4}, 10^{-7}\}$. All
-error bars are negligible.  To study dynamics in the regime of deep solar convection ($Ma \approx 10^{-4}, 
-Ra \approx 10^{20}$), a superadiabatic excess of $\epsilon \approx 10^{-17}$ is appropriate.
-\label{fig:ma_v_eps} }
+When $\epsilon \rightarrow m_{ad}$, large deviations from this power law are seen and the systems display
+supersonic dynamics.  
+(b) At high epsilon, Ma scales as Ra$^{0.26}$ until it reaches the supersonic regime, at which point it turns
+over and follows a power law of Ra$^{-0.10}$.  At low epsilon, consistent power laws are achieved throughout all
+values of $Ra$ studied, where Ma $\propto$ \{Ra$^{0.26}$, Ra$^{0.22}$\} for $\epsilon = \{10^{-4}, 10^{-7}\}$. All
+error bars are negligible.  \label{fig:ma_v_eps} }
 \end{figure}
@@
 &\begin{aligned}
-\frac{D T}{D t} = -&(\gamma-1)T\Div{\bm{u}} + \frac{1}{c_V}\left\{ \chi\grad^2 T + \grad T \cdot \grad\chi  \right. \\ \
-&+ \chi\grad T \cdot\grad\ln\rho +\nu\left(\lilstressT\cdot\nabla\right)\cdot\bm{u}\left.\right\} 
+\frac{D T}{D t} = -&(\gamma-1)T\Div{\bm{u}} + \frac{1}{c_V}\left( \chi\grad^2 T + \grad T \cdot \grad\chi  \right. \\ \
+&+ \chi\grad T \cdot\grad\ln\rho +\nu\left[\lilstressT\cdot\nabla\right]\cdot\bm{u}\left.\right) 
 	\label{eqn:energy_eqn}
@@
 the top and bottom of the domain such that $w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. The domain
-is periodic in the horizontal.We utilize the novel Dedalus pseudospectral framework (http://dedalus-project.org/) to time-evolve Eqs. 
+is periodic in the horizontal. We utilize the novel Dedalus\footnote{http://dedalus-project.org/} pseudospectral framework 
+ to time-evolve Eqs. 
 \ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn} using an implicit-explicit third-order four-step 
@@
 96x384 grid points at the lowest values of Ra to 1152x4608 grid points at Ra $\geq 10^{7}$. 
-By using IMEX timestepping, we are able to study flows at moderate ($Ma \approx 1$) and very low ($Ma \approx 10^{-4}$)
+By using IMEX timestepping, we can implicity step the stiff linear acoustic wave contribution and we are able to
+efficiently study flows at moderate ($Ma \approx 1$) and very low ($Ma \approx 10^{-4}$)
 Mach number (Fig. \ref{fig:ma_v_eps}b).
@@
 ideal gas in hydrostatic equilibrium, $\partial_z T_{\text{ad}} \equiv - g / c_{P}$.
-$F_{\text{ref}} = \Delta T / L_z$ , where $\Delta T = T_{u} - T_{\ell}$, is the conductive flux of a linear profile connecting the upper
-and lower plates.
+$F_{\text{ref}} = \Delta T / L_z$ , where $\Delta T = T(L_z) - T(0)$, is the conductive flux of a linear profile connecting the upper
+and lower plates, which is constant for the choice of fixed-temperature boundaries.
 
@@
 \includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
-\caption{Characteristic entropy. The time- and horizontally-
+\caption{Characteristic entropy fluctuations in evolved flows. The time- and horizontally-
 averaged profile is removed in all cases.  At high
@@
 dependence on depth. By performing a linear stability analysis, we determined that the onset of convection
-occurs at Ra$_c$ $= \{10, 11, 11\}$ (\textbf{need exact}) for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  We study Rayleigh
+occurs at Ra$_c$ $= \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  We study Rayleigh
 numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$, $10^5$Ra$_c$ for $\epsilon = 10^{-4}$,
@@
 high values of $\epsilon$, shock systems form in the upper atmosphere near downflow lanes 
-(see e.g. Fig. \ref{fig:entropy_snapshots}a) and propagate towards upflow lanes.  Such systems were reported in
+(Fig. \ref{fig:entropy_snapshots}a) and propagate towards upflow lanes.  
+These shocks heat downflowing material which reduces the efficiency of convective transport.
+Such systems were reported in
 both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
@@
 and therefore $\epsilon \rightarrow \infty$.
-Low mach number flows, such as those in an $\epsilon = 10^{-4}$ atmosphere (e.g. Fig. \ref{fig:entropy_snapshots}b)
+
+Low mach number flows, such as those in an $\epsilon = 10^{-4}$ atmosphere (Fig. \ref{fig:entropy_snapshots}b)
 have similar bulk thermodynamic structure but lack the complicating dynamics of shock heating. This is interesting
@@
 \cite{hurlburt&all1984}.  As Ra is
-increased to very large values (e.g. Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
+increased to very large values (Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
 break up into small packets which traverse through the domain many
@@
 enthalpy flux (orange, positive) and kinetic energy flux (purple, negative).  The grey dash-dot line is the
-viscous flux, and the green dotted line is the radiative flux with the adiabatic radiative flux removed. All
+viscous flux, the blue dash-dot-dot line is the potential energy flux, 
+and the green dotted line is the radiative flux with the adiabatic radiative flux removed. All
 fluxes are normalized by $F_{ref} - F_A$, as in the calculation of the Nusselt number.  The solid black line is
@@
 that at the top.  These states are punctuated by states of vigorous shearing, similar to those previouslyl
-reported in two-dimensional RB convection (\textbf{cite goluskin?}).  These shearing states flatten the bottom temperature
+reported in two-dimensional RB convection \cite{goluskin&all2014}.  These shearing states flatten the bottom temperature
 gradient towards adiabatic, allowing the excess energy to exit through the upper boundary.  These shearing
@@
 and non-shearing states retrieves an invariant flux profile (and therefore Nu profile) throughout the depth
-of the atmosphere (\textbf{After about 24 more hours, it'll be flat!  I don't have enough data at the parameters
-shown in Fig. \ref{fig:flux_profiles} yet}).
+of the atmosphere.
 
@@
 all simulations at low and high Ma are plotted in Fig. \ref{fig:nu_v_ra}.  At $\epsilon = \{10^{-4}, 10^{-7}\}$,
-scaling laws of $Nu \propto Nu^{\{0.3090, 0.3087\}}$ are retrieved.  At $\epsilon = 0.5$, in the near-sonic
-regime ($Ra \leq 10^4$), the scaling of $Nu$ with $Ra$ is inflated, with $Nu \propto Ra^{0.4489}$.  As simulations
+scaling laws of $Nu \propto Nu^{\{0.31, 0.31\}}$ are retrieved.  At $\epsilon = 0.5$, in the near-sonic
+regime ($Ra \leq 10^4$), the scaling of $Nu$ with $Ra$ is inflated, with $Nu \propto Ra^{0.45}$.  As simulations
 pass into the supersonic regime and shocks start to form near the downflows, propoelling warm fluid deep
-into the atmosphere, that scaling drops to $Nu \propto Ra^{0.1936}$.  Error on all power law scalings is
+into the atmosphere, that scaling drops to $Nu \propto Ra^{0.19}$.  Error on all power law scalings is
 negligible.
@@
 \label{sec:discussion}
-Here we have presented a non-dimensional construction of polytropic atmospheres and the control parameters 
-which determine flow characteristics in such systems.  We argue that these atmospheres are the natural extension
+In this letter we have studied fundamental heat transport by stratified convection in simplified 2-D polytropic
+atmospheres at low and high Mach number.  Out atmospheres here are specified by two parameters, \nrho 
+and $\epsilon$.  We argue that these atmospheres are the natural extension
 of the RB problem to stratified systems, and should be used to understand the basic properties of stratified
@@
 Furthermore, we have demonstrated that low Ma flows exhibit the same broad-upflow / narrow downflow dynamics
-as are observed in high Mach number flows \cite{hurlburt&all1984}.  However, pressure perturbations
-cannot be responsible for this effect; rather, high temperature, low density upflows and low temperature,
-high density upflows causing appropriately signed entropy perturbations which buoyantly rise or fall accordingly.
+as are observed in high Mach number flows \cite{hurlburt&all1984}.  At low Ma, flows are in pressure equilibrium
+with their surroundings, so cold parcels must also be low density parcels, both of which are negative
+entropy contributions.  As there is no thermodynamic variable causing additional breaking or acceleration, it
+is simply the effects of stratification which lead downflows to be narrow and upflows to be broad.
 It is possible that at low Ma, these flows begin to feel the pressure response of the
@@
 Time-dependent oscillating shear states have developed spontaneously, as seen before in RB convection
-(\textbf{citation}).  Future work will aim to better understand the mechanisms of shearing states and
+\cite{goluskin&all2014}.  Future work will aim to better understand the mechanisms of shearing states and
 whether or not these states are attainable in three-dimensional, non-rotating atmospheres.  While the
@@
 \cite{hurlburt&all1986}.
+
+The similarity between the scaling of Nu in RB convection and in these stratified polytropes suggests that
+a similar Prandtl-Blausius or Grossmann-Lohse boundary layer theory could be developed for fully compressible
+convection in these systems \cite{ahlers&all2009}.  If our scalings of Ma and $\epsilon$ hold up, then under
+solar conditions (Ra $\approx 10^{20}$, Ma $\approx 10^{-4}$), we expect that $\epsilon \approx 10^{20}$ and
+Nu $\approx 10^{6}$.  Solar conditions are of course more complicated, as there $\kappa$ is set by the
+radiative opacity and depend on both $T$ and $\rho$.  Our studies here set the groundwork for studying transport
+under conditions with more realistic $\kappa$.
 

### 2016-10-11 tex/nusselt_paper.tex
fixes sign on viscous terms

@@
 &-\grad T - T\grad\ln\rho + \bm{g} \\
-&\,\,\,\,-\nu\Div{\lilstressT} - \lilstressT\cdot\grad\nu - \nu\lilstressT\cdot\grad\ln\rho
+&\,\,\,\,+\nu\Div{\lilstressT} + \lilstressT\cdot\grad\nu + \nu\lilstressT\cdot\grad\ln\rho
 \label{eqn:momentum_eqn}
@@
 where $\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$ is the enthalpy flux, $\bm{F}_{\text{KE}} \equiv 
-\rho|\bm{u}|^2\bm{u}$ is the kinetic energy flux, $\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ is the potential
+\rho|\bm{u}|^2\bm{u}/2$ is the kinetic energy flux, $\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ is the potential
 energy flux (with $\phi \equiv -gz$), 

### 2016-10-13 tex/nusselt_paper.tex
shapes up the discussion a bit

@@
 supersonic dynamics.  
-(b) At high epsilon, Ma scales as Ra$^{0.26}$ until it reaches the supersonic regime, at which point it turns
+(b) At high epsilon, Ma scales as Ra$^{0.28}$ until it reaches the supersonic regime, at which point it turns
 over and follows a power law of Ra$^{-0.10}$.  At low epsilon, consistent power laws are achieved throughout all
@@
 regime ($Ra \leq 10^4$), the scaling of $Nu$ with $Ra$ is inflated, with $Nu \propto Ra^{0.45}$.  As simulations
-pass into the supersonic regime and shocks start to form near the downflows, propoelling warm fluid deep
+pass into the supersonic regime and shocks start to form near the downflows, propelling warm fluid deep
 into the atmosphere, that scaling drops to $Nu \propto Ra^{0.19}$.  Error on all power law scalings is
@@
 In this letter we have studied fundamental heat transport by stratified convection in simplified 2-D polytropic
-atmospheres at low and high Mach number.  Out atmospheres here are specified by two parameters, \nrho 
+atmospheres at low and high Mach number.  Our atmospheres here are specified by two parameters, \nrho 
 and $\epsilon$.  We argue that these atmospheres are the natural extension
 of the RB problem to stratified systems, and should be used to understand the basic properties of stratified
-convection.  The striking similarity between the growth of Nu with Ra at low Ma and in RB convection suggests
-that low Ma polytropic convection shares many properties with RB convection but includes the complicating
-effect of stratification. We have argued that the traditional definition of the Nusselt number in stratified atmospheres
-\cite{graham1975} is the correct one, and shown how it extends in extreme cases.
+convection.  The similarity between the scaling of Nu in RB convection and in these stratified polytropes suggests that
+a boundary layer theory such as the Prandtl-Blausius or Grossmann-Lohse theories for incompressible flows
+could be developed for fully compressible
+convection in these systems \cite{ahlers&all2009}.
 
-Furthermore, we have demonstrated that low Ma flows exhibit the same broad-upflow / narrow downflow dynamics
-as are observed in high Mach number flows \cite{hurlburt&all1984}.  At low Ma, flows are in pressure equilibrium
-with their surroundings, so cold parcels must also be low density parcels, both of which are negative
-entropy contributions.  As there is no thermodynamic variable causing additional breaking or acceleration, it
-is simply the effects of stratification which lead downflows to be narrow and upflows to be broad.
-It is possible that at low Ma, these flows begin to feel the pressure response of the
-top and bottom walls which leads them to deflect at the far boundary in a way that high Ma flows do not.
+Furthermore, we have demonstrated that low Ma flows exhibit the same pattern of broad upflows and narrow downflows
+observed in high Ma flows \cite{hurlburt&all1984}.  At low Ma, flows are often in pressure equilibrium
+with their surroundings, so cooling parcels increases their density, and both of these effects reduce
+entropy.  Neither of the two free thermodynamic variables can cause breaking in warm upflow regions, 
+so stratification effects must cause the observed flow asymmetry.
+While not studied in this work, it is possible that at low Ma, flows feel the pressure response of the
+boundaries, causing deflection in a manner unseen at high Ma.
 
@@
 Time-dependent oscillating shear states have developed spontaneously, as seen before in RB convection
-\cite{goluskin&all2014}.  Future work will aim to better understand the mechanisms of shearing states and
-whether or not these states are attainable in three-dimensional, non-rotating atmospheres.  While the
-two-dimensional work studied here offers a basis for comparing the heat transport abilities of stratified
-convection compared to RB convection \cite{johnston&doering2009}, it will be informative to study the low 
-Mach number systems presented here in three dimensions and in atmospheres bounded by stable regions
-\cite{hurlburt&all1986}.
+\cite{goluskin&all2014}.  While computationally difficult, the highest values of Ra and the lowest value
+of $\epsilon$ studied here are far below the values found in nature.  If the scalings of Nu and Ma
+presented here hold, then under solar conditions ($\text{Ra }\approx 10^{20}$, $\text{Ma }\approx 10^{-4}$), we expect that $\epsilon \approx 10^{20}$ and
+$\text{Nu }\approx 10^{6}$.
 
-The similarity between the scaling of Nu in RB convection and in these stratified polytropes suggests that
-a similar Prandtl-Blausius or Grossmann-Lohse boundary layer theory could be developed for fully compressible
-convection in these systems \cite{ahlers&all2009}.  If our scalings of Ma and $\epsilon$ hold up, then under
-solar conditions (Ra $\approx 10^{20}$, Ma $\approx 10^{-4}$), we expect that $\epsilon \approx 10^{20}$ and
-Nu $\approx 10^{6}$.  Solar conditions are of course more complicated, as there $\kappa$ is set by the
-radiative opacity and depend on both $T$ and $\rho$.  Our studies here set the groundwork for studying transport
-under conditions with more realistic $\kappa$.
+Future work will aim to better understand the mechanisms of shearing states and
+whether or not these states are attainable in three-dimensional, non-rotating atmospheres.  Our studies
+here have set the groundwork for understanding and comparing heat transport in stratified convection
+to that in RB convection \cite{johnston&doering2009}, and for future studies of transport in stratified
+convection in more realistic systems, such as those bounded by stable regions \cite{hurlburt&all2009} or 
+using more realistic profiles of $\kappa$.
 

### 2016-10-13 tex/nusselt_paper.tex
Adding grant and allocation info; may edit depending on response from NAS.

@@
 \subsection{acknowledgements}
-This work was supported by the CU/NSO George Ellery Hale Graduate Fellowship,
-Juri's allocation and Ben's allocation.
+This work was supported by the CU/NSO George Ellery Hale Graduate Fellowship
+and supported by NASA LWS grant number NNX16AC92G.  Computations were conducted 
+with support by the NASA High End Computing (HEC) Program through the NASA 
+Advanced Supercomputing (NAS) Division at Ames Research Center
+with allocations (GID s1647, PI Brown; GID g26133, PI Toomre).
 We thank Axel Brandenburg, Mark Rast, and Jeff Oishi for many useful discussions.

### 2016-10-13 tex/nusselt_paper.tex
Minor typo (epsilon, sign error) & spelling fixes.

@@
 $c_P = R\gamma(\gamma-1)^{-1}$ is the specific heat at constant pressure,
-$\nu$ is the kinematic viscosity (viscous diffusivity), and $\chi$ is the thermal dififusivity.  
+$\nu$ is the kinematic viscosity (viscous diffusivity), and $\chi$ is the thermal diffusivity.  
 The relationship between the thermal and viscous diffusivities is
@@
 96x384 grid points at the lowest values of Ra to 1152x4608 grid points at Ra $\geq 10^{7}$. 
-By using IMEX timestepping, we can implicity step the stiff linear acoustic wave contribution and we are able to
+By using IMEX timestepping, we can implicitly step the stiff linear acoustic wave contribution and we are able to
 efficiently study flows at moderate ($Ma \approx 1$) and very low ($Ma \approx 10^{-4}$)
@@
 \caption{Time-averaged flux profiles for high (top) and low (bottom) Mach number flows at $Ra = 10^6$.  
-The dashed lines correpond to the
+The dashed lines correspond to the
 enthalpy flux (orange, positive) and kinetic energy flux (purple, negative).  The grey dash-dot line is the
@@
 Fig. \ref{fig:entropy_snapshots}b\&c), in which the flux entering the system at the bottom of the atmosphere exceeds
-that at the top.  These states are punctuated by states of vigorous shearing, similar to those previouslyl
+that at the top.  These states are punctuated by states of vigorous shearing, similar to those previously
 reported in two-dimensional RB convection \cite{goluskin&all2014}.  These shearing states flatten the bottom temperature
@@
 of $\epsilon$ studied here are far below the values found in nature.  If the scalings of Nu and Ma
-presented here hold, then under solar conditions ($\text{Ra }\approx 10^{20}$, $\text{Ma }\approx 10^{-4}$), we expect that $\epsilon \approx 10^{20}$ and
+presented here hold, then under solar conditions ($\text{Ra }\approx 10^{20}$, $\text{Ma }\approx 10^{-4}$), we expect that $\epsilon \approx 10^{-20}$ and
 $\text{Nu }\approx 10^{6}$.

### 2016-10-13 tex/nusselt_paper.tex
Adding refs to Lecoanet (check MNRAS formatting for PRL) in IMEX section.

@@
 \newcommand{\appropto}{\mathpalette\approptoinn\relax}
+
+\newcommand\mnras{{MNRAS}}%
+          % Monthly Notices of the RAS
 
@@
 \ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn} using an implicit-explicit third-order four-step 
-Runge-Kutta timestepping scheme \cite{ascher&all1997}.  
+Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
 Variables are time-evolved on a dealiased Chebyshev (vertical)
@@
 96x384 grid points at the lowest values of Ra to 1152x4608 grid points at Ra $\geq 10^{7}$. 
-By using IMEX timestepping, we can implicitly step the stiff linear acoustic wave contribution and we are able to
+By using IMEX timestepping, we implicitly step the stiff linear acoustic wave contribution and we are able to
 efficiently study flows at moderate ($Ma \approx 1$) and very low ($Ma \approx 10^{-4}$)
-Mach number (Fig. \ref{fig:ma_v_eps}b).
+Mach number (Fig. \ref{fig:ma_v_eps}b).  Our equations take the form
+of the FC equations in \cite{lecoanet&all2014}, extended to include variable
+$\nu$ and $\chi$, and we follow the approach there; this IMEX approach has been successfully 
+tested against a nonlinear benchmark  of the compressible Kelvin-Helmholtz instability \cite{Lecoanet_et_al_2016_KH}.
 

### 2016-10-13 tex/nusselt_paper.tex
Fixing two typos: epsilon -> \epsilon, Ma^{1/2} -> Ma^{2}

@@
 is reflected in the evolved values of these fluctuations, which follow the scaling of
-$T_1/T_0 \propto \rho_{1}/\rho_{0} \propto$ Ma$^{1/2} \propto epsilon$ for low values of $\epsilon$,
+$T_1/T_0 \propto \rho_{1}/\rho_{0} \propto$ Ma$^{2} \propto \epsilon$ for low values of $\epsilon$,
 as in Fig. \ref{fig:ma_v_eps}.

### 2016-10-13 tex/nusselt_paper.tex
Not sure the comment on \epsilon -> \inf is correct or critical to our argument; here's a possible replacement.  Is the shock heating significant?
Adding back in solar kappa sentence.

@@
 both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
-In the context of Fig \ref{fig:ma_v_eps}, it is unsurprising that as $\gamma \rightarrow 1$, systems in which shocks
-form are easier to produce \cite{cattaneo&all1990}.  In such a limit, $m_{ad} \rightarrow \infty$ 
-and therefore $\epsilon \rightarrow \infty$.
+These shocks heat material entering the downflows, reducing both the
+buoyant driving and the efficiency of convective transport.
 
@@
 $\text{Nu }\approx 10^{6}$.  
+Solar conditions are of course more complicated, as there $\kappa$ is
+set by the radiative opacity, which depends on both $\rho$ and $T$.
 

### 2016-10-14 tex/nusselt_paper.tex
comments out a couple of unecessary sections; revamps lots of sentences all over

@@
 Here we study stratified convection in the context of 
-plane-parallel polytropically stratified atmospheres. 
+plane-parallel, polytropically stratified atmospheres. 
 We hold the density stratification (\nrho) and Prandtl number (Pr) constant while varying the
@@
 which quantifies the efficiency of convective heat transport.
-As Ra increases and $\text{Ma} \rightarrow 1$, a scaling of Nu $\appropto$ Ra$^{0.45}$ is observed.  
+As Ra increases and $\text{Ma} \rightarrow 1$, a scaling of Nu $\propto$ Ra$^{0.45}$ is observed.  
 As Ra increases to a regime where Ma $\geq 1$,
-this scaling gives way to a weaker Nu $\appropto$ Ra$^{0.20}$.  In the regime of Ma $\ll 1$, a consistent
-Nu $\appropto$ Ra$^{0.3}$ is retrieved,  reminiscent of the Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
+this scaling gives way to a weaker Nu $\propto$ Ra$^{0.19}$.  In the regime of Ma $\ll 1$, a consistent
+Nu $\propto$ Ra$^{0.31}$ is retrieved,  reminiscent of the Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
 \end{abstract}
@@
 In this letter we study the behavior of convective heat transport, quantified by
-the Nusselt number (Nu), in plane-parallel two-dimensional polytropically stratified atmospheres.  
-We vary $\epsilon$ and Ra while holding \nrho and Pr
-constant across all simulations.  We study domains with an aspect ratio of 4.  In section 
-\ref{sec:experiment}, we describe the construction of atmospheres, our equations, and our method for
-numerical time evolution.  We describe our findings in section \ref{sec:results} and discuss
-implications in section \ref{sec:discussion}.
+the Nusselt number (Nu), in plane-parallel, two-dimensional, polytropically stratified atmospheres.  
+$\epsilon$ and Ra are varied  while $\nrho$, Pr, and the aspect ratio are held
+constant.  In section 
+\ref{sec:experiment}, the construction of atmospheres, equations, and numerical methods are discussed.  
+Results are described in section \ref{sec:results} and their implications are discussed
+in section \ref{sec:discussion}.
 
@@
 by a factor of 400 across the domain.  This formulation leaves Pr
-constant throughout the depth of the atmosphere, and in this letter we impose $\text{Pr} = 1$.
-Throughout this letter, we specify Ra at the top of the atmosphere.
+constant throughout the depth of the atmosphere. In this letter we impose $\text{Pr} = 1$ and
+specify Ra at $z = L_z$.  We study atmospheres with an aspect ratio of 4.
 
@@
 \includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
-\caption{(a) Characteristic horizontally averaged maximum Mach numbers have been
-time averaged for over $\geq 100t_{b}$ beginning roughly 50$t_{b}$ after the start of simulations. For $\epsilon \leq 0.1$,
-an evident scaling of $Ma \propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
-at Ra = $\{10^2, 10^5\}$ is retrieved.
-When $\epsilon \rightarrow m_{ad}$, large deviations from this power law are seen and the systems display
-supersonic dynamics.  
-(b) At high epsilon, Ma scales as Ra$^{0.28}$ until it reaches the supersonic regime, at which point it turns
-over and follows a power law of Ra$^{-0.10}$.  At low epsilon, consistent power laws are achieved throughout all
-values of $Ra$ studied, where Ma $\propto$ \{Ra$^{0.26}$, Ra$^{0.22}$\} for $\epsilon = \{10^{-4}, 10^{-7}\}$. All
+\caption{The maximum value of Ma which has been horizontally averaged and time averaged for $\geq 100 t_b$, 
+beginning roughly $50t_b$ after
+the start of simulations.  (a) For $\epsilon \leq 0.1$,
+a scaling of $\text{Ma }\propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
+at $\text{Ra }= \{10^2, 10^5\}$ exists.
+When $\epsilon \rightarrow m_{ad}$, large deviations from this power law are seen.  
+(b) At high $\epsilon$, Ma scales as Ra$^{0.28}$ until it reaches the supersonic regime, at which point it
+follows a power law of Ra$^{-0.10}$.  At low $\epsilon$, consistent power laws are achieved throughout all
+values of Ra studied, where $\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
+for $\epsilon = \{10^{-4}, 10^{-7}\}$. All
 error bars are negligible.  \label{fig:ma_v_eps} }
@@
 
-We evolve the Fully Compressible Navier-Stokes equations,
-which take the form:
+The Fully Compressible Navier-Stokes equations,
 \begin{align}
 &\begin{aligned}
-&\frac{D \ln\rho}{D t} = -\Div{\bm{u}}
+&\frac{\partial \ln\rho}{\partial t} + \Div{\bm{u}} = -\bm{u}\cdot\grad\rho,
 	\label{eqn:continuity_eqn}
@@
 &\begin{aligned}
-\frac{D\bm{u}}{D t}=
-&-\grad T - T\grad\ln\rho + \bm{g} \\
-&\,\,\,\,+\nu\Div{\lilstressT} + \lilstressT\cdot\grad\nu + \nu\lilstressT\cdot\grad\ln\rho
+\frac{\partial\bm{u}}{\partial t} + \grad T - &\nu\Div{\lilstressT} - \lilstressT\cdot\grad\nu = \\
+&-\bm{u}\cdot\grad\bm{u} - T\grad\ln\rho + \bm{g} + \nu\lilstressT\cdot\grad\ln\rho,
 \label{eqn:momentum_eqn}
@@
 &\begin{aligned}
-\frac{D T}{D t} = -&(\gamma-1)T\Div{\bm{u}} + \frac{1}{c_V}\left( \chi\grad^2 T + \grad T \cdot \grad\chi  \right. \\ \
-&+ \chi\grad T \cdot\grad\ln\rho +\nu\left[\lilstressT\cdot\nabla\right]\cdot\bm{u}\left.\right) 
+\frac{\partial T}{\partial t} -\frac{1}{c_V}\left(\right.\chi&\left.\grad^2 T + \grad T\cdot\grad\chi\right) = \\
+	&-\bm{u}\cdot\grad T - (\gamma-1)T\Div{\bm{u}} \\
+	&+ \frac{1}{c_V}\left(\chi\grad T \cdot\grad\ln\rho +\nu\left[\lilstressT\cdot\nabla\right]\cdot\bm{u}\right), 
 	\label{eqn:energy_eqn}
@@
 \end{align}
-where $D/Dt \equiv \partial_t + \bm{u}\cdot\grad$ and the viscous stress tensor is defined as
+are evolved with a viscous stress tensor defined as
 \begin{equation}
@@
 \end{equation}
-
-In such stratified systems, the total convective flux is
+These equations carry a total convective flux of
 \begin{equation}
@@
 energy flux (with $\phi \equiv -gz$), 
-and $\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$ is the viscous flux.  Taking an inner product of
-Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
-Eq. \ref{eqn:energy_eqn}, the full energy equation in conservation form is retrieved,
-\begin{equation}
-\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
-\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0
-	\label{eqn:energy_eqn_full}
-\end{equation}
-where $\bm{F}_{\text{cond}} = -\kappa \grad T$.  An understanding of the flux terms is essential to characterizing
-the convective heat transport in our systems.
+and $\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$ is the viscous flux. 
+%Taking an inner product of
+%Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
+%Eq. \ref{eqn:energy_eqn}, the full energy equation in conservation form is retrieved,
+%\begin{equation}
+%\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
+%\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0,
+%	\label{eqn:energy_eqn_full}
+%\end{equation}
+%where $\bm{F}_{\text{cond}} = -\kappa \grad T$.  
+Understanding these flux terms and how they interact with the conductive flux, 
+$\bm{F}_{\text{cond}} = -\kappa \grad T$, is crucial in characterizing
+convective heat transport.
 
@@
 the top and bottom of the domain such that $w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. The domain
-is periodic in the horizontal. We utilize the novel Dedalus\footnote{http://dedalus-project.org/} pseudospectral framework 
+is horizontally periodic. We utilize the novel Dedalus\footnote{http://dedalus-project.org/} pseudospectral framework 
  to time-evolve Eqs. 
-\ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn} using an implicit-explicit third-order four-step 
+\ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn} using an implicit-explicit, third-order, four-step 
 Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
@@
 and Fourier (horizontal) domain in which the
-physical grid dimensions are 3/2 the size of the coefficient grid.  Our physical grid sizes range from
+physical grid dimensions are 3/2 the size of the coefficient grid.  Physical grid sizes range from
 96x384 grid points at the lowest values of Ra to 1152x4608 grid points at Ra $\geq 10^{7}$. 
 By using IMEX timestepping, we implicitly step the stiff linear acoustic wave contribution and we are able to
-efficiently study flows at moderate ($Ma \approx 1$) and very low ($Ma \approx 10^{-4}$)
+efficiently study flows at moderate ($\text{Ma } \approx 1$) and very low ($\text{Ma } \approx 10^{-4}$)
 Mach number (Fig. \ref{fig:ma_v_eps}b).  Our equations take the form
@@
 The efficiency of convection is quantified by the Nusselt number.  
-While the Nusselt number is well-defined in RB convection
-as the amount of total flux divided by the steady-state background conductive flux 
-\cite{johnston&doering2009, otero&all2002},
-a well-defined Nusselt number is more elusive in stratified convection.  A traditional definition of the Nusselt
-number in stratified convection is \cite{graham1975,hurlburt&all1984}
+Nu is well-defined in RB convection
+as total flux normalized by the steady-state background conductive flux 
+\cite{johnston&doering2009, otero&all2002}.
+In stratified convection Nu is more difficulut to define, but one of the earliest definitions used
+was \cite{graham1975,hurlburt&all1984}
 \begin{equation}
-\text{Nu} \equiv \frac{F_{\text{conv, z}} + F_{\text{cond, z}} - F_A}{F_{\text{ref}} - F_A},
+\text{Nu} \equiv \frac{F_{\text{conv, z}} + F_{\text{cond, z}} - F_{\text{A}}}{F_{\text{ref}} - F_{\text{A}}},
 \label{eqn:nusselt}
@@
 where $F_{\text{conv, z}}$ and $F_{\text{cond, z}}$ are the z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
-respectively.  $F_A$ is the adiabatic conductive flux, defined as $F_A = -\kappa \partial_z T_{\text{ad}}$.  For an
-ideal gas in hydrostatic equilibrium, $\partial_z T_{\text{ad}} \equiv - g / c_{P}$.
-$F_{\text{ref}} = \Delta T / L_z$ , where $\Delta T = T(L_z) - T(0)$, is the conductive flux of a linear profile connecting the upper
+respectively.  $F_{\text{A}} \equiv -\kappa \partial_z T_{\text{ad}}$ is the adiabatic conductive flux, and
+$\partial_z T_{\text{ad}} \equiv - g / c_{P}$ for an ideal gas in hydrostatic equilibrium.
+$F_{\text{ref}} \equiv \Delta T / L_z$, where $\Delta T \equiv T(L_z) - T(0)$ is the 
+conductive flux of a linear profile connecting the upper
 and lower plates, which is constant for the choice of fixed-temperature boundaries.
 
-We contend that this is the general form of the Nusselt number.  To illustrate this, we consider a few limiting
+We contend that this is the general form of the Nusselt number and illustrate this with a few limiting
 cases. Convection works to
 suppress entropy stratification and create isentropic atmospheres.  Under the Boussinesq approximation,
-density variations are ignored and entropy stratification is directly proportional to temperature stratification,
-such that $\grad S \rightarrow 0$ only when $\grad T \rightarrow 0$.  Thus, for RB convection, 
-$\grad T_{\text{ad}} \equiv 0$ and the familiar form of Nu is retrieved.  In the case of stratified convection,
-as $\epsilon \rightarrow m_{ad} + 1$, $\grad P \propto g \rightarrow 0$ and
-the resulting $\grad T_{\text{ad}} \rightarrow 0$.  In such a case, $F_A \rightarrow 0$ and the
+in which density variations are ignored, entropy stratification is directly proportional to temperature stratification,
+such that $\grad S \rightarrow 0$ when $\grad T \rightarrow 0$.  Thus, for RB convection, the familiar Nu is
+retrieved from Eq. \ref{eqn:nusselt} because $\grad T_{\text{ad}} = 0$.  
+In the case of polytropic convection,
+as $\epsilon \rightarrow m_{ad} + 1$, $g \rightarrow 0$, so
+$\grad T_{\text{ad}} \rightarrow 0$.  In such a case, $F_{\text{A}} \rightarrow 0$ and the
 definition of the RB Nu is appropriate to use, as convection carries all of the
 flux \cite{brandenburg&all2005}. As $\epsilon \rightarrow 0$, 
-$\grad T_{\text{ad}}\rightarrow \grad T_0$, the atmospheric initial temperature profile.  This causes increasingly
-smaller velocity, and thermodynamic perturbations (e.g. Fig. \ref{fig:ma_v_eps}), but the removal of the 
-O(1) background term in the numerator and denominator of Eq. \ref{eqn:nusselt}, makes the numerator and
-denominator both O($\epsilon$).
+$\grad T_{\text{ad}}\rightarrow \grad T_0$, and increasingly
+smaller velocity and thermodynamic perturbations are needed to achieve $\grad S = 0$ (Fig. \ref{fig:ma_v_eps}a).
+Here, the removal of $F_{\text{A}}$ in the numerator and denominator of Eq. \ref{eqn:nusselt} makes them both
+O($\epsilon$), so the overall Nu is sensible.
 
@@
 
-We solved initial value problems which start in hydrostatic and thermal equilibrium and experienced infinitesimal 
-kicks compared to $\epsilon$ in $T_1$.  Solutions were time-evolved until a long-time average of Nu showed little
-dependence on depth. By performing a linear stability analysis, we determined that the onset of convection
-occurs at Ra$_c$ $= \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  We study Rayleigh
+Initial value problems were solved in which $T_1$ experienced an infinitesimal kick compared to $\epsilon$
+away from hydrostatic and thermal equilibrium.
+Solutions were time-evolved until a long average of Nu showed little
+dependence on depth. A linear stability analysis determined that the onset of convection
+occurs at $\text{Ra}_c = \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  Rayleigh
 numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$, $10^5$Ra$_c$ for $\epsilon = 10^{-4}$,
-and $10^4$Ra$_c$ for $\epsilon = 10^{-7}$.  At
-high values of $\epsilon$, shock systems form in the upper atmosphere near downflow lanes 
-(Fig. \ref{fig:entropy_snapshots}a) and propagate towards upflow lanes.  
-These shocks heat downflowing material which reduces the efficiency of convective transport.
+and $10^3$Ra$_c$ for $\epsilon = 10^{-7}$ were studied.
+
+At large $\epsilon$ (0.5), shock systems form in the upper atmosphere near downflow lanes 
+(Fig. \ref{fig:entropy_snapshots}a) and propagate toward upflow lanes.  
 Such systems were reported in
@@
 
-Low mach number flows, such as those in an $\epsilon = 10^{-4}$ atmosphere (Fig. \ref{fig:entropy_snapshots}b)
-have similar bulk thermodynamic structure but lack the complicating dynamics of shock heating. This is interesting
-in light of the current literature, as low Mach number flows are in pressure equilibrium with the background and
-pressure forces cannot be the cause of narrow downflow lanes and broad upflow regions, as has been suggested
-\cite{hurlburt&all1984}.  As Ra is
-increased to very large values (Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
-break up into small packets which traverse through the domain many
-times before diffusing rather than spanning the whole domain.  
-The complicated nature of high Ra dynamics, especially in the low Ma regime where
-shocks are absent, has barred us from sufficiently converging any solutions in the regime of 
+Low Mach number flows, such as those in an $\epsilon = 10^{-4}$ atmosphere (Fig. \ref{fig:entropy_snapshots}b)
+have similar bulk thermodynamic structure but lack the complicating dynamics of shock heating. 
+Low Ma flows are in pressure equilibrium with their suroundings, so
+pressure forces are unlikely to be the sole cause of symmetry breaking in up- and downflows, as has been suggested
+\cite{hurlburt&all1984};  it is more likely that these flows are responding to 
+the effects of density stratification.
+As Ra is increased to large values (Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
+no longer span the whole domain but rather break up into small packets which traverse the domain multiple
+times before diffusing.  
+The complicated nature of high Ra dynamics, especially in the low Ma regime,
+has prevented the convergence of solutions in the regime of 
 $\text{Ra }> 10^5\text{Ra}_c$ at low $\epsilon$.
@@
 \includegraphics[width=3.4375in]{./figs/fluxes_fig.png}
-\caption{Time-averaged flux profiles for high (top) and low (bottom) Mach number flows at $Ra = 10^6$.  
+\caption{Time-averaged flux profiles for high (top) and low (bottom) Ma flows at $\text{Ra }= 10^6$.  
 The dashed lines correspond to the
@@
 and the green dotted line is the radiative flux with the adiabatic radiative flux removed. All
-fluxes are normalized by $F_{ref} - F_A$, as in the calculation of the Nusselt number.  The solid black line is
-the properly normalized sum of all the fluxes, and under this normalization its height-averaged value is the
-Nusselt number.
-\label{fig:flux_profiles} }
+fluxes are normalized by $F_{\text{ref}} - F_{\text{A}}$, as in Eq. \ref{eqn:nusselt}.  The solid black line is
+Nu, the properly normalized sum of all the fluxes \label{fig:flux_profiles} }
 \end{figure}
 
-At high values of Ra, the heat transport properties of the systems become increasingly complex and time-dependent.
+At large Ra, the heat transport properties of the systems become increasingly complex and time-dependent.
 Large $\epsilon$ flows exhibit two local maxima in the enthalpy flux and kinetic energy flux: one in the upper 
 atmosphere caused by the shocks, and one in the lower atmosphere caused by the deep mixing of convective motions
-(see Fig. \ref{fig:flux_profiles}a).
+(Fig. \ref{fig:flux_profiles}a).
 At low $\epsilon$, only the deep maximum is present (Fig. \ref{fig:flux_profiles}b).  
-Furthermore, the presence
-of fixed-temperature boundary conditions allows the flux at the boundaries to vary.  Many runs at $Ra > 10^5$ and
-$\epsilon = 10^{-4}$ exhibit time-dependent states of stratified convection (such as those shown in 
-Fig. \ref{fig:entropy_snapshots}b\&c), in which the flux entering the system at the bottom of the atmosphere exceeds
-that at the top.  These states are punctuated by states of vigorous shearing, similar to those previously
-reported in two-dimensional RB convection \cite{goluskin&all2014}.  These shearing states flatten the bottom temperature
+Fixed-temperature boundary conditions allow the flux at the boundaries to vary, so many runs at $\text{Ra }> 10^5$
+and $\epsilon = 10^{-4}$ exhibit states in which the flux entering the system at the bottom of the atmosphere 
+exceeds that which leaves at the top.  
+These states are punctuated by states of vigorous shearing, similar to those previously
+reported in two-dimensional RB convection \cite{goluskin&all2014}.  These shearing states push the bottom temperature
 gradient towards adiabatic, allowing the excess energy to exit through the upper boundary.  These shearing
 states will be covered in more detail in a future paper.  Regardless, a proper long-term average over shearing
-and non-shearing states retrieves an invariant flux profile (and therefore Nu profile) throughout the depth
+and non-shearing states retrieves an invariant flux (and Nu) profile throughout the depth
 of the atmosphere.
 
-After appropriately time-averaging the fluxes, a sensible Nusselt number is retrieved.  Nusselt numbers for
+After appropriately time-averaging the fluxes, a sensible Nu is retrieved.  Nusselt numbers for
 all simulations at low and high Ma are plotted in Fig. \ref{fig:nu_v_ra}.  At $\epsilon = \{10^{-4}, 10^{-7}\}$,
@@
 regime ($Ra \leq 10^4$), the scaling of $Nu$ with $Ra$ is inflated, with $Nu \propto Ra^{0.45}$.  As simulations
-pass into the supersonic regime and shocks start to form near the downflows, propelling warm fluid deep
-into the atmosphere, that scaling drops to $Nu \propto Ra^{0.19}$.  Error on all power law scalings is
-negligible.
+pass into the supersonic regime and shocks start to form near the downflows,
+that scaling drops to $Nu \propto Ra^{0.19}$.  Error on all power law scalings is negligible.
 
@@
 \includegraphics[width=3.4375in]{./figs/nu_v_ra.png}
-\caption{Variation of $Nu$ as $Ra$ increases is shown for $\epsilon = \{10^{-7}, 10^{-4}, 0.5\}$. 
+\caption{Variation of Nu as Ra increases at low and high Ma. 
 At high $\epsilon$, a clear transition from the subsonic to supersonic regime is evident in the scaling
-of Nu with Ra.  In the low $\epsilon$ regime Nu vs. Ra scalings collapse onto a similar line which is
-reminiscent of RB scalings \cite{johnston&doering2009}.  Error bars represent one standard deviation
-of a long-time averaged Nu sampled throughout the depth of the domain.
+of Nu with Ra.  In the low $\epsilon$ regime, Nu scalings collapse onto a similar line which is
+reminiscent of RB scalings \cite{johnston&doering2009}.  Error bars represent the square root of
+the variance of Nu with depth.
 \label{fig:nu_v_ra} }
@@
 In this letter we have studied fundamental heat transport by stratified convection in simplified 2-D polytropic
-atmospheres at low and high Mach number.  Our atmospheres here are specified by two parameters, \nrho 
+atmospheres which are specified by two parameters, $\nrho$ 
 and $\epsilon$.  We argue that these atmospheres are the natural extension
 of the RB problem to stratified systems, and should be used to understand the basic properties of stratified
-convection.  The similarity between the scaling of Nu in RB convection and in these stratified polytropes suggests that
-a boundary layer theory such as the Prandtl-Blausius or Grossmann-Lohse theories for incompressible flows
-could be developed for fully compressible
-convection in these systems \cite{ahlers&all2009}.
+convection.  The similarity between the scaling of Nu in RB convection and in low-$\epsilon$ polytropes suggests 
+that a boundary layer theory such as the Grossmann-Lohse theory for incompressible flows
+could be developed for fully compressible convection in these systems \cite{ahlers&all2009}.
 
-Furthermore, we have demonstrated that low Ma flows exhibit the same pattern of broad upflows and narrow downflows
-observed in high Ma flows \cite{hurlburt&all1984}.  At low Ma, flows are often in pressure equilibrium
-with their surroundings, so cooling parcels increases their density, and both of these effects reduce
-entropy.  Neither of the two free thermodynamic variables can cause breaking in warm upflow regions, 
-so stratification effects must cause the observed flow asymmetry.
-While not studied in this work, it is possible that at low Ma, flows feel the pressure response of the
-boundaries, causing deflection in a manner unseen at high Ma.
+%Furthermore, we have demonstrated that low Ma flows exhibit the same pattern of broad upflows and narrow downflows
+%observed in high Ma flows \cite{hurlburt&all1984}.  At low Ma, flows are often in pressure equilibrium
+%with their surroundings, so cooling parcels increases their density, and both of these effects reduce
+%entropy.  Neither of the two free thermodynamic variables can cause breaking in warm upflow regions, 
+%so stratification effects must cause the observed flow asymmetry.
+%While not studied in this work, it is possible that at low Ma, flows feel the pressure response of the
+%boundaries, causing deflection in a manner unseen at high Ma.
 
@@
 \cite{goluskin&all2014}.  While computationally difficult, the highest values of Ra and the lowest value
-of $\epsilon$ studied here are far below the values found in nature.  If the scalings of Nu and Ma
-presented here hold, then under solar conditions ($\text{Ra }\approx 10^{20}$, $\text{Ma }\approx 10^{-4}$), we expect that $\epsilon \approx 10^{-20}$ and
+of $\epsilon$ studied here are far from values found in nature.  If the scalings of Nu and Ma
+presented here (Figs.
+\ref{fig:ma_v_eps} \& \ref{fig:nu_v_ra}) hold, then under solar conditions ($\text{Ra }\approx 10^{20}$, $\text{Ma }\approx 10^{-4}$), we expect that $\epsilon \approx 10^{-20}$ and
 $\text{Nu }\approx 10^{6}$.  
@@
 to that in RB convection \cite{johnston&doering2009}, and for future studies of transport in stratified
-convection in more realistic systems, such as those bounded by stable regions \cite{hurlburt&all2009} or 
+convection in more realistic systems, such as those bounded by stable regions \cite{hurlburt&all1986} or 
 using more realistic profiles of $\kappa$.

### 2016-10-26 tex/nusselt_paper.tex
start adding Jeff's notes

@@
 plane-parallel, polytropically stratified atmospheres. 
-We hold the density stratification (\nrho) and Prandtl number (Pr) constant while varying the
-Mach number (Ma) and the Rayleigh number (Ra) to determine the behavior of the Nusselt number (Nu), 
+We hold the density stratification (\nrho) and Prandtl 
+number (Pr) constant while varying the
+Mach number (Ma) and the Rayleigh number (Ra) to determine 
+the behavior of the Nusselt number (Nu), 
 which quantifies the efficiency of convective heat transport.
-As Ra increases and $\text{Ma} \rightarrow 1$, a scaling of Nu $\propto$ Ra$^{0.45}$ is observed.  
+As Ra increases and $\text{Ma} \rightarrow 1$, a scaling 
+of Nu $\propto$ Ra$^{0.45}$ is observed.  
 As Ra increases to a regime where Ma $\geq 1$,
-this scaling gives way to a weaker Nu $\propto$ Ra$^{0.19}$.  In the regime of Ma $\ll 1$, a consistent
-Nu $\propto$ Ra$^{0.31}$ is retrieved,  reminiscent of the Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
+this scaling gives way to a weaker Nu $\propto$ Ra$^{0.19}$. 
+In the regime of Ma $\ll 1$, a consistent
+Nu $\propto$ Ra$^{0.31}$ is retrieved,  reminiscent of the 
+Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
 \end{abstract}
@@
 \label{sec:intro}
-Convection is essential to heat transport in the cores of high mass stars, the
-envelopes of low mass stars, and the atmospheres of terrestrial and jovian planets. In such systems, convection
-occurs in the presence of the atmospheric stratification which can be small but extends up to 
+Convection is essential to heat transport in the cores of high mass stars,
+the envelopes of low mass stars, and the atmospheres of terrestrial and 
+jovian planets.  The convective dynamics are influenced by the atmospheric 
+stratification, which is small in some systems but extends up to 
 14 density scale heights in the Sun's convective envelope.
-A basic understanding of the
-properties of compressible convection in stratified media is important to understanding systems in astrophysics
-and planetary sciences.  Numerical constraints have often restricted studies of stratified convection to
-moderately high Mach numbers, appropriate to regions near the Sun's surface.  As such, we know few
-fundamental properties of the low-Mach number stratified convection which occurs in the deep solar interior.
+Understanding the fundamental
+properties of compressible convection in stratified media is essential
+to characterizing systems in astrophysics and planetary sciences.  
+Numerical constraints have often restricted studies of compressible
+convection to moderately high Mach number (Ma), appropriate to regions near 
+the Sun's surface.  Few fundamental properties of the 
+low-Ma stratified convection which occurs in the deep solar interior are known.
 
@@
 in two \cite{graham1975, chan&all1982,
-hurlburt&all1984, cattaneo&all1990} and three \cite{cattaneo&all1991, brummell&all1996} dimensions
-revealed a number of basic properties in the moderate-to-high Mach number regime.
-In the widely-studied \RB (hereafter RB) problem, upflows and downflows are symmetrical and
-the temperature gradient approaches zero in the convective interior causing the conductive flux to similarly 
-disappear.  Highly stratified convection exhibits narrow downflow lanes and broad upflow regions.
-Furthermore, the \emph{entropy} gradient is negated by convection rather than the temperature gradient, such
-that in the presence of perfectly efficient convection a significant component of the flux is still
-carried by conduction.
+hurlburt&all1984, cattaneo&all1990} and three 
+\cite{cattaneo&all1991, brummell&all1996} dimensions
+revealed a number of basic properties in the moderate-to-high 
+Ma regime. In the widely-studied \RB (hereafter RB) problem, 
+upflows and downflows are symmetrical and
+the temperature gradient approaches zero in the convective interior 
+causing the conductive flux to similarly 
+disappear.  Highly stratified convection exhibits narrow downflow 
+lanes and broad upflow regions.
+Furthermore, the \emph{entropy} gradient is negated by convection 
+rather than the temperature gradient, such
+that in the presence of perfectly efficient convection a significant 
+component of the flux is still carried by conduction.
 
-In RB convection, there exist two primary control parameters: the Rayleigh number (Ra), the ratio of
-buoyant driving to diffusive damping, and the Prandtl number (Pr), the ratio of viscous to thermal
-diffusivity.  These numbers couple with the aspect ratio of the physical domain and the boundary conditions
-to entirely control the
-dynamics of the convection.  In stratified atmospheres, in addition to specifying the equation of state and
-fundamental properties of the gas, the two control parameters of RB convection are joined by the degree of
-stratification across the domain and the characteristic Mach number (Ma) of the convective flows.  
-Polytropically stratified atmospheres, such as those used in early studies, are an ideal extension of
-RB convection into the stratified realm as the two additional control parameters are directly linked to
-basic properties of the atmosphere.  The density stratification is set by the number of density scale heights
-the atmosphere spans (\nrho), and Ma is controlled by the superadiabatic excess ($\epsilon$),
-the deviation of the polytropic index from the adiabatic polytropic index \cite{graham1975}.
+In RB convection, there exist two primary control parameters: 
+the Rayleigh number (Ra, the ratio of
+buoyant driving to diffusive damping) and the Prandtl number 
+(Pr, the ratio of viscous to thermal
+diffusivity).  These numbers coupled with the aspect ratio of 
+the physical domain and the boundary conditions
+determine the dynamics of the convection.  In stratified atmospheres, 
+in addition to specifying the equation of state and
+fundamental properties of the gas, the two control parameters of 
+RB convection are joined by the degree of
+stratification across the domain and the characteristic 
+Ma of the convective flows.  
+Polytropically stratified atmospheres, such as those used in 
+early studies, are an ideal extension of
+RB convection into the stratified realm as the two additional 
+control parameters are directly linked to
+basic properties of the atmosphere.  The density stratification is 
+set by the number of density scale heights
+the atmosphere spans (\nrho), and Ma is controlled 
+by the superadiabatic excess ($\epsilon$,
+the deviation of the polytropic index from the adiabatic polytropic 
+index \cite{graham1975}).
 
@@
 we study a fluid composed of monatomic ideal gas particles with an adiabatic index of $\gamma = 5/3$ and
-whose equation of state is $P = R\rho T$. 
-The initial stratification is polytropic and the gravitational
-acceleration and conductive heat flux are invariant throughout the depth of the atmosphere. We specify that both 
-the thermal conductivity, $\kappa$, and the temperature gradient, $\grad T_0$, are constant while constructing
-our atmosphere such that $\bm{F}_{\text{cond,0}} = -\kappa \grad T_0 = \text{constant}$.
-Under these assumptions, solving the equation of hydrostatic equilibrium produces an atmosphere defined by
+whose equation of state is $P = R\rho T$. In constructing an initial atmosphere, we assume
+that the gravitational
+acceleration and conductive heat flux do not vary with depth. Both 
+the thermal conductivity, $\kappa$, and the temperature gradient, $\grad T_0$, are constant,
+such that $\bm{F}_{\text{cond,0}} = -\kappa \grad T_0 = \text{constant}$.
+Under these assumptions, satisfying hydrostatic equilibrium produces an atmosphere defined by
 \begin{equation}
 \begin{split}
-\rho_0(z) &= \rho_{00}(z_0 - z)^m \\
-T_0(z)    &= T_{00}(z_0 - z).
+\rho_0(z) &= \rho_{t}(z_0 - z)^m \\
+T_0(z)    &= T_{t}(z_0 - z).
 \label{eqn:polytrope}
@@
 \end{equation}
-Thermodynamic variables are nondimensionalized at the top of the atmosphere as 
-$P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, requiring $z_0 \equiv L_z + 1$ and $R = T_{00} = \rho_{00} = 1$.
-By this choice, the non-dimensional length scale is the inverse temperature gradient scale and
-the timescale is the isothermal sound crossing time of this unit length.
-$z$ increases upwards within the bounds $z =[0, L_{z}]$, where $L_{z} = e^{n_{\rho}/m} - 1$ is
-determined by the number of density scale heights the atmosphere spans, $n_\rho$.
-Throughout this letter, we set $n_{\rho} = 3$ such that the density varies by a factor of 20.
-The polytropic index is such that $m = m_{ad} - \epsilon$
+The polytropic index is $m = m_{ad} - \epsilon$
 where $m_{ad} \equiv (\gamma-1)^{-1}$ is the adiabatic polytropic index and $\epsilon$ is the
@@
 The subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$. 
+Thermodynamic variables are nondimensionalized at the top of the atmosphere as 
+$P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, requiring $z_0 \equiv L_z + 1$ and $R = T_{t} = \rho_{t} = 1$.
+By this choice, the non-dimensional length scale is the inverse temperature gradient scale and
+the timescale is the isothermal sound crossing time of this unit length.
+$z$ increases upwards within $[0, L_{z}]$, where $L_{z} = e^{n_{\rho}/m} - 1$ is
+determined by the number of density scale heights the atmosphere spans, $n_\rho$.
+Throughout this letter, we set $n_{\rho} = 3$ such that the density varies by a factor of 20.
 The characteristic timescale of convective dynamics
 is related to the atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$, with $g = (m+1)$.
-We will utilize buoyancy time units throughout this letter.
+We use buoyancy time units in this letter.
 

### 2016-10-27 tex/nusselt_paper.tex
Jeff's comments are bolded to be taken care of in the future

@@
 values of Ra studied, where $\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
-for $\epsilon = \{10^{-4}, 10^{-7}\}$. All
-error bars are negligible.  \label{fig:ma_v_eps} }
+for $\epsilon = \{10^{-4}, 10^{-7}\}$. \textbf{All
+error bars are negligible.}  \label{fig:ma_v_eps} }
 \end{figure}
@@
 
-Initial value problems were solved in which $T_1$ experienced an infinitesimal kick compared to $\epsilon$
-away from hydrostatic and thermal equilibrium.
+\textbf{Initial value problems were solved in which $T_1$ experienced an infinitesimal kick compared to $\epsilon$
+away from hydrostatic and thermal equilibrium}.
 Solutions were time-evolved until a long average of Nu showed little
-dependence on depth. A linear stability analysis determined that the onset of convection
+dependence on depth. \textbf{A linear stability analysis determined that} the onset of convection
 occurs at $\text{Ra}_c = \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  Rayleigh
@@
 
-After appropriately time-averaging the fluxes, a sensible Nu is retrieved.  Nusselt numbers for
+\textbf{After appropriately time-averaging the fluxes,} a sensible Nu is retrieved.  Nusselt numbers for
 all simulations at low and high Ma are plotted in Fig. \ref{fig:nu_v_ra}.  At $\epsilon = \{10^{-4}, 10^{-7}\}$,
@@
 of Nu with Ra.  In the low $\epsilon$ regime, Nu scalings collapse onto a similar line which is
-reminiscent of RB scalings \cite{johnston&doering2009}.  Error bars represent the square root of
-the variance of Nu with depth.
+\textbf{reminiscent} of RB scalings \cite{johnston&doering2009}.  Error bars represent the square root of
+the variance of Nu with depth. \textbf{Identify power law fits on plot, add 2/7 law?}
 \label{fig:nu_v_ra} }

### 2016-10-27 tex/nusselt_paper.tex
reworks experiment section.  Cleans it up?

@@
 we study a fluid composed of monatomic ideal gas particles with an adiabatic index of $\gamma = 5/3$ and
-whose equation of state is $P = R\rho T$. In constructing an initial atmosphere, we assume
-that the gravitational
-acceleration and conductive heat flux do not vary with depth. Both 
-the thermal conductivity, $\kappa$, and the temperature gradient, $\grad T_0$, are constant,
-such that $\bm{F}_{\text{cond,0}} = -\kappa \grad T_0 = \text{constant}$.
-Under these assumptions, satisfying hydrostatic equilibrium produces an atmosphere defined by
+whose equation of state is $P = R\rho T$. 
+The initial atmosphere is a plane-parallel polytrope in which the gravitational acceleration
+and conductive flux, $\bm{F}_{\text{cond,0}} = -\kappa \grad T_0$, do not vary with depth. To
+achieve the latter condition, both $\kappa$ and $\grad T_0$ are constant.
+Under these assumptions, satisfying hydrostatic equilibrium produces a stratification of
 \begin{equation}
 \begin{split}
-\rho_0(z) &= \rho_{t}(z_0 - z)^m \\
-T_0(z)    &= T_{t}(z_0 - z).
+\rho_0(z) &= \rho_{t}(z_0 - z)^m, \\
+T_0(z)    &= T_{t}(z_0 - z),
 \label{eqn:polytrope}
@@
 \end{equation}
-The polytropic index is $m = m_{ad} - \epsilon$
-where $m_{ad} \equiv (\gamma-1)^{-1}$ is the adiabatic polytropic index and $\epsilon$ is the
-superadiabatic excess.
-The subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$. 
+where $m = m_{ad} - \epsilon$ is the polytropic index.
+The adiabatic polytropic index is $m_{ad} \equiv (\gamma-1)^{-1}$ and
+the superadiabatic excess is $\epsilon$ which sets the scale 
+of the entropy gradient, $\grad S_0 \propto -\epsilon$.
 Thermodynamic variables are nondimensionalized at the top of the atmosphere as 
@@
 $z$ increases upwards within $[0, L_{z}]$, where $L_{z} = e^{n_{\rho}/m} - 1$ is
-determined by the number of density scale heights the atmosphere spans, $n_\rho$.
-Throughout this letter, we set $n_{\rho} = 3$ such that the density varies by a factor of 20.
+determined by $n_\rho$, the number of density scale heights the atmosphere spans.
 The characteristic timescale of convective dynamics
 is related to the atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$, with $g = (m+1)$.
-We use buoyancy time units in this letter.
+Throughout this letter, buoyancy time units are used and 
+$n_{\rho} = 3$ such that the initial density varies by a factor of 20.
+All atmospheres studied here have an aspect ratio of 4, such that $L_x = 4L_z$.
 
@@
 The relationship between the thermal and viscous diffusivities is
-set by the Prandtl number, Pr$ = \nu/\chi$.   We relate the dynamic viscosity, $\mu$, and the thermal conductivity,
+set by the Prandtl number, $\text{Pr} = \nu/\chi$.   We relate the dynamic viscosity, $\mu$, and the thermal conductivity,
 $\kappa$, to their corresponding diffusivities such that 
@@
 constant throughout the depth of the atmosphere. In this letter we impose $\text{Pr} = 1$ and
-specify Ra at $z = L_z$.  We study atmospheres with an aspect ratio of 4.
+specify Ra at $z = L_z$.
 
@@
 \end{equation}
-These equations carry a total convective flux of
-\begin{equation}
-\bm{F}_{\text{conv}} \equiv \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}},
-\end{equation}
-where $\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$ is the enthalpy flux, $\bm{F}_{\text{KE}} \equiv 
-\rho|\bm{u}|^2\bm{u}/2$ is the kinetic energy flux, $\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ is the potential
-energy flux (with $\phi \equiv -gz$), 
-and $\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$ is the viscous flux. 
+These equations carry a total convective flux of the form
+%\begin{equation}
+$
+\bm{F}_{\text{conv}} \equiv \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}}.
+$
+%\end{equation}
+Contributions from the enthalpy flux, $\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$;
+the kinetic energy flux, $\bm{F}_{\text{KE}} \equiv \rho|\bm{u}|^2\bm{u}/2$;
+the potential energy flux, $\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ (with $\phi \equiv -gz$);
+and the viscous flux, $\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$, must all be considered. 
 %Taking an inner product of
@@
 96x384 grid points at the lowest values of Ra to 1152x4608 grid points at Ra $\geq 10^{7}$. 
-By using IMEX timestepping, we implicitly step the stiff linear acoustic wave contribution and we are able to
-efficiently study flows at moderate ($\text{Ma } \approx 1$) and very low ($\text{Ma } \approx 10^{-4}$)
-Mach number (Fig. \ref{fig:ma_v_eps}b).  Our equations take the form
+By using IMEX timestepping, we implicitly step the stiff linear acoustic wave contribution and are able to
+efficiently study flows at moderate ($\approx 1$) and very low ($\approx 10^{-4}$)
+Ma (Fig. \ref{fig:ma_v_eps}b).  Our equations take the form
 of the FC equations in \cite{lecoanet&all2014}, extended to include variable

### 2016-10-28 tex/nusselt_paper.tex
improvements throughout

@@
 beginning roughly $50t_b$ after
-the start of simulations.  (a) For $\epsilon \leq 0.1$,
+the start of simulations.  This time average is long enough that the profile is well converged
+and error bars are negligible. (a) For $\epsilon \leq 0.1$,
 a scaling of $\text{Ma }\propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
@@
 values of Ra studied, where $\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
-for $\epsilon = \{10^{-4}, 10^{-7}\}$. \textbf{All
-error bars are negligible.}  \label{fig:ma_v_eps} }
+for $\epsilon = \{10^{-4}, 10^{-7}\}$. 
+\label{fig:ma_v_eps} }
 \end{figure}
@@
 \end{equation}
-These equations carry a total convective flux of the form
-%\begin{equation}
+
+Taking an inner product of
+Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
+Eq. \ref{eqn:energy_eqn} reveals the full energy equation,
+\begin{equation}
+\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
+\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0.
+	\label{eqn:energy_eqn_full}
+\end{equation}
+The convective flux is
 $
@@
 $
-%\end{equation}
 Contributions from the enthalpy flux, $\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$;
@@
 and the viscous flux, $\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$, must all be considered. 
-%Taking an inner product of
-%Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
-%Eq. \ref{eqn:energy_eqn}, the full energy equation in conservation form is retrieved,
-%\begin{equation}
-%\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
-%\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0,
-%	\label{eqn:energy_eqn_full}
-%\end{equation}
 %where $\bm{F}_{\text{cond}} = -\kappa \grad T$.  
@@
 Nu is well-defined in RB convection
-as total flux normalized by the steady-state background conductive flux 
+as the total flux normalized by the steady-stateconductive flux 
 \cite{johnston&doering2009, otero&all2002}.
-In stratified convection Nu is more difficulut to define, but one of the earliest definitions used
+In stratified convection Nu is more difficult to define, but one of the earliest definitions used
 was \cite{graham1975,hurlburt&all1984}
@@
 where $F_{\text{conv, z}}$ and $F_{\text{cond, z}}$ are the z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
-respectively.  $F_{\text{A}} \equiv -\kappa \partial_z T_{\text{ad}}$ is the adiabatic conductive flux, and
+respectively.  $F_{\text{A}} \equiv -\kappa \partial_z T_{\text{ad}}$ is the adiabatic conductive flux and
 $\partial_z T_{\text{ad}} \equiv - g / c_{P}$ for an ideal gas in hydrostatic equilibrium.
-$F_{\text{ref}} \equiv \Delta T / L_z$, where $\Delta T \equiv T(L_z) - T(0)$ is the 
+$F_{\text{ref}} \equiv \Delta T / L_z$, where $\Delta T \equiv T(L_z) - T(0)$, is the 
 conductive flux of a linear profile connecting the upper
@@
 We contend that this is the general form of the Nusselt number and illustrate this with a few limiting
-cases. Convection works to
-suppress entropy stratification and create isentropic atmospheres.  Under the Boussinesq approximation,
-in which density variations are ignored, entropy stratification is directly proportional to temperature stratification,
-such that $\grad S \rightarrow 0$ when $\grad T \rightarrow 0$.  Thus, for RB convection, the familiar Nu is
-retrieved from Eq. \ref{eqn:nusselt} because $\grad T_{\text{ad}} = 0$.  
-In the case of polytropic convection,
-as $\epsilon \rightarrow m_{ad} + 1$, $g \rightarrow 0$, so
-$\grad T_{\text{ad}} \rightarrow 0$.  In such a case, $F_{\text{A}} \rightarrow 0$ and the
+cases. Convection eliminates
+entropy stratification.  Under the Boussinesq approximation,
+in which density variations are ignored, entropy stratification is directly proportional to temperature stratification
+such that $\grad S \rightarrow 0$ when $\grad T \rightarrow 0$.  The familiar Nu in the RB problem is
+therefore retrieved from Eq. \ref{eqn:nusselt} because $\grad T_{\text{ad}} = 0$.  
+In the case of polytropic convection,  $g \rightarrow 0$
+as $\epsilon \rightarrow m_{ad} + 1$.
+In this limit, $F_{\text{A}} \rightarrow 0$ and the
 definition of the RB Nu is appropriate to use, as convection carries all of the
-flux \cite{brandenburg&all2005}. As $\epsilon \rightarrow 0$, 
-$\grad T_{\text{ad}}\rightarrow \grad T_0$, and increasingly
+flux \cite{brandenburg&all2005}. 
+However, as $\epsilon \rightarrow 0$, 
+$\grad T_{\text{ad}}\rightarrow \grad T_0$ and increasingly
 smaller velocity and thermodynamic perturbations are needed to achieve $\grad S = 0$ (Fig. \ref{fig:ma_v_eps}a).
-Here, the removal of $F_{\text{A}}$ in the numerator and denominator of Eq. \ref{eqn:nusselt} makes them both
-O($\epsilon$), so the overall Nu is sensible.
+These perturbations carry what little flux exists in excess of the adiabatic, so the removal of 
+$F_{\text{A}}$ in the numerator and denominator of Eq. \ref{eqn:nusselt} is essential for a reasonable Nu measurement.
 
@@
 
-\textbf{Initial value problems were solved in which $T_1$ experienced an infinitesimal kick compared to $\epsilon$
-away from hydrostatic and thermal equilibrium}.
+Initial value problems were solved in which $T_1$ 
+was filled with infinitesimal, random noise compared to $T_0$ and $\epsilon$.
 Solutions were time-evolved until a long average of Nu showed little
-dependence on depth. \textbf{A linear stability analysis determined that} the onset of convection
-occurs at $\text{Ra}_c = \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  Rayleigh
+variance with depth. By performing a linear stability analysis, we determined that the onset of convection
+occurs at $\text{Ra}_c = \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  
+We studied Rayleigh
 numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$, $10^5$Ra$_c$ for $\epsilon = 10^{-4}$,
-and $10^3$Ra$_c$ for $\epsilon = 10^{-7}$ were studied.
+and $10^3$Ra$_c$ for $\epsilon = 10^{-7}$.
 
-At large $\epsilon$ (0.5), shock systems form in the upper atmosphere near downflow lanes 
+At large Ma ($\epsilon = 0.5$), shock systems form in the upper atmosphere near downflow lanes 
 (Fig. \ref{fig:entropy_snapshots}a) and propagate toward upflow lanes.  
@@
 both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
-These shocks heat material entering the downflows, reducing both the
-buoyant driving and the efficiency of convective transport.
+These shocks heat material entering the downflows, affecting the dynamics and heat transport
+of these systems.
 
-Low Mach number flows, such as those in an $\epsilon = 10^{-4}$ atmosphere (Fig. \ref{fig:entropy_snapshots}b)
-have similar bulk thermodynamic structure but lack the complicating dynamics of shock heating. 
-Low Ma flows are in pressure equilibrium with their suroundings, so
-pressure forces are unlikely to be the sole cause of symmetry breaking in up- and downflows, as has been suggested
-\cite{hurlburt&all1984};  it is more likely that these flows are responding to 
-the effects of density stratification.
+Low Ma flows ($\epsilon = 10^{-4}$)
+have similar bulk thermodynamic structures (Fig. \ref{fig:entropy_snapshots}b).
 As Ra is increased to large values (Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
@@
 times before diffusing.  
-The complicated nature of high Ra dynamics, especially in the low Ma regime,
-has prevented the convergence of solutions in the regime of 
-$\text{Ra }> 10^5\text{Ra}_c$ at low $\epsilon$.
+While it has been suggested that pressure forces cause symmetry breaking in up- and downflows,
+\cite{hurlburt&all1984}, this effect seems to be secondary to flows obeying mass conservation as they traverse
+the stratified medium.  We observe low Ma cases where the double-roll systems such as those in
+Fig. \ref{fig:entropy_snapshots}b contain one roll of increased pressure and one roll of decreased pressure
+where the up- and downflows bound these regions of pressure disequilibrium.
 
@@
 \includegraphics[width=3.4375in]{./figs/fluxes_fig.png}
-\caption{Time-averaged flux profiles for high (top) and low (bottom) Ma flows at $\text{Ra }= 10^6$.  
+\caption{Time-averaged flux profiles for high (a) and low (b) Ma flows at $\text{Ra }= 10^6$.  
 The dashed lines correspond to the
@@
 viscous flux, the blue dash-dot-dot line is the potential energy flux, 
-and the green dotted line is the radiative flux with the adiabatic radiative flux removed. All
+and the green dotted line is the radiative flux with the adiabatic radiative flux removed. Viscous and
+potential energy fluxes are negligible in (a) and are not shown.  All
 fluxes are normalized by $F_{\text{ref}} - F_{\text{A}}$, as in Eq. \ref{eqn:nusselt}.  The solid black line is
@@
 
-At large Ra, the heat transport properties of the systems become increasingly complex and time-dependent.
-Large $\epsilon$ flows exhibit two local maxima in the enthalpy flux and kinetic energy flux: one in the upper 
-atmosphere caused by the shocks, and one in the lower atmosphere caused by the deep mixing of convective motions
-(Fig. \ref{fig:flux_profiles}a).
-At low $\epsilon$, only the deep maximum is present (Fig. \ref{fig:flux_profiles}b).  
+%At large Ra, the heat transport properties of the systems become increasingly complex and time-dependent.
+at large values of Ra in which shocks form, high Ma flows exhibit two 
+local maxima in the enthalpy flux and kinetic energy flux (Fig. \ref{fig:flux_profiles}a).
+Shock-heated fluid parcels sometimes spin-up as they are pushed into the lower atmosphere, creating deep,
+rapidly-rotating regions
+of mixing which persist for many overturn times.  These ``spinners'' sit inside of larger rolls created by their
+neighboring up- and downflows and greatly influence the dynamics.
+At low Ma, only the deep maximum is present (Fig. \ref{fig:flux_profiles}b).  
 Fixed-temperature boundary conditions allow the flux at the boundaries to vary, so many runs at $\text{Ra }> 10^5$
@@
 These states are punctuated by states of vigorous shearing, similar to those previously
-reported in two-dimensional RB convection \cite{goluskin&all2014}.  These shearing states push the bottom temperature
+reported in two-dimensional RB convection \cite{goluskin&all2014}.  
+These shearing states push the bottom temperature
 gradient towards adiabatic, allowing the excess energy to exit through the upper boundary.  These shearing
@@
 
-\textbf{After appropriately time-averaging the fluxes,} a sensible Nu is retrieved.  Nusselt numbers for
+After appropriately time-averaging the fluxes for $\geq 200 t_b$, a sensible Nu is retrieved.  
+Nusselt numbers for
 all simulations at low and high Ma are plotted in Fig. \ref{fig:nu_v_ra}.  At $\epsilon = \{10^{-4}, 10^{-7}\}$,
@@
 pass into the supersonic regime and shocks start to form near the downflows,
-that scaling drops to $Nu \propto Ra^{0.19}$.  Error on all power law scalings is negligible.
+that scaling drops to $Nu \propto Ra^{0.19}$.
 
@@
 \caption{Variation of Nu as Ra increases at low and high Ma. 
-At high $\epsilon$, a clear transition from the subsonic to supersonic regime is evident in the scaling
-of Nu with Ra.  In the low $\epsilon$ regime, Nu scalings collapse onto a similar line which is
-\textbf{reminiscent} of RB scalings \cite{johnston&doering2009}.  Error bars represent the square root of
-the variance of Nu with depth. \textbf{Identify power law fits on plot, add 2/7 law?}
+At high $\epsilon$ (purple circles), 
+a clear transition from the subsonic to supersonic regime is evident in the scaling
+of Nu with Ra.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
+Nu scalings collapse onto a similar line which is
+\textbf{consistent with RB scalings?} \cite{johnston&doering2009}.  Error bars are determined
+ by the square root of the variance of Nu with depth and indicate whether or not a solution is well-converged.
 \label{fig:nu_v_ra} }
@@
 \subsection{acknowledgements}
-This work was supported by the CU/NSO George Ellery Hale Graduate Fellowship
-and supported by NASA LWS grant number NNX16AC92G.  Computations were conducted 
+EHA acknowledges the support of the University of Colorado’s George 
+Ellery Hale Graduate Student Fellowship.
+This work was supported by  NASA LWS grant number NNX16AC92G.  
+Computations were conducted 
 with support by the NASA High End Computing (HEC) Program through the NASA 

### 2016-10-31 tex/nusselt_paper.tex
updates to figures and minor text fixes

@@
 
-After appropriately time-averaging the fluxes for $\geq 200 t_b$, a sensible Nu is retrieved.  
+After appropriately time-averaging the fluxes for $\geq 200 t_b$, a sensible flux average is retrieved.  
 Nusselt numbers for
-all simulations at low and high Ma are plotted in Fig. \ref{fig:nu_v_ra}.  At $\epsilon = \{10^{-4}, 10^{-7}\}$,
-scaling laws of $Nu \propto Nu^{\{0.31, 0.31\}}$ are retrieved.  At $\epsilon = 0.5$, in the near-sonic
-regime ($Ra \leq 10^4$), the scaling of $Nu$ with $Ra$ is inflated, with $Nu \propto Ra^{0.45}$.  As simulations
+all simulations at low and high Ma are plotted as a function of Ra in Fig. \ref{fig:nu_v_ra}.  
+At $\epsilon = \{10^{-4}, 10^{-7}\}$,
+scaling laws of $\text{Nu} \propto \text{Ra}^{\{0.31, 0.31\}}$ are retrieved.  At $\epsilon = 0.5$, in the near-sonic
+regime ($\text{Ra} \leq 10^4$), the scaling of Nu with Ra is inflated, with $\text{Nu} \propto \text{Ra}^{0.45}$.  As simulations
 pass into the supersonic regime and shocks start to form near the downflows,
-that scaling drops to $Nu \propto Ra^{0.19}$.
+that scaling drops to $\text{Nu} \propto \text{Ra}^{0.19}$.
 
@@
 \subsection{acknowledgements}
-EHA acknowledges the support of the University of Colorado’s George 
+EHA acknowledges the support of the University of Colorado's George 
 Ellery Hale Graduate Student Fellowship.

### 2016-10-31 tex/nusselt_paper.tex
hacked and slashed, part almost done

@@
 \begin{abstract}
+Convection in astrophysical systems is stratified and
+often occurs at high Rayleigh number (Ra) and low
+Mach number (Ma).
 Here we study stratified convection in the context of 
@@
 We hold the density stratification (\nrho) and Prandtl 
-number (Pr) constant while varying the
-Mach number (Ma) and the Rayleigh number (Ra) to determine 
+number (Pr) constant while varying
+Ma and Ra to determine 
 the behavior of the Nusselt number (Nu), 
@@
 the envelopes of low mass stars, and the atmospheres of terrestrial and 
-jovian planets.  The convective dynamics are influenced by the atmospheric 
-stratification, which is small in some systems but extends up to 
+jovian planets.  The convective dynamics in these astrophysical objects
+are influenced by the atmospheric 
+stratification, which is small in some systems (e.g. massive star cores)
+but spans about
 14 density scale heights in the Sun's convective envelope.
@@
 the Sun's surface.  Few fundamental properties of the 
-low-Ma stratified convection which occurs in the deep solar interior are known.
+low-Ma stratified convection, which occurs in the deep solar interior, are known.
 
@@
 causing the conductive flux to similarly 
-disappear.  Highly stratified convection exhibits narrow downflow 
-lanes and broad upflow regions.
+disappear.  These two hallmark characteristics of RB convection change
+significantly when stratification is included.  Stratified convection 
+exhibits narrow downflow lanes and broad upflow regions.
 Furthermore, the \emph{entropy} gradient is negated by convection 
@@
 Polytropically stratified atmospheres, such as those used in 
-early studies, are an ideal extension of
+early studies \cite{graham1975, chan&all1982, hurlburt&all1984, 
+cattaneo&all1990, cattaneo&all1991, brummell&all1996} are an ideal extension of
 RB convection into the stratified realm as the two additional 
@@
 basic properties of the atmosphere.  The density stratification is 
-set by the number of density scale heights
-the atmosphere spans (\nrho), and Ma is controlled 
-by the superadiabatic excess ($\epsilon$,
+set by the number of density scale heights (\nrho)
+the atmosphere spans, and Ma is controlled 
+by the superadiabatic excess ($\epsilon$),
 the deviation of the polytropic index from the adiabatic polytropic 
-index \cite{graham1975}).
+index \cite{graham1975}.
 
-In this letter we study the behavior of convective heat transport, quantified by
-the Nusselt number (Nu), in plane-parallel, two-dimensional, polytropically stratified atmospheres.  
-$\epsilon$ and Ra are varied  while $\nrho$, Pr, and the aspect ratio are held
-constant.  In section 
-\ref{sec:experiment}, the construction of atmospheres, equations, and numerical methods are discussed.  
+In this letter we study the behavior of convective heat transport, 
+quantified by the Nusselt number (Nu), in plane-parallel, 
+two-dimensional, polytropically stratified atmospheres.  
+We vary $\epsilon$ and Ra while holding $\nrho$, Pr, and the aspect ratio
+constant.  We describe experimental methods in section 
+\ref{sec:experiment}, including the construction of atmospheres, equations, and numerical methods.  
 Results are described in section \ref{sec:results} and their implications are discussed
@@
 \label{sec:experiment}
-In order to compare our results with previous studies and in an effort to examine a simplest case,
-we study a fluid composed of monatomic ideal gas particles with an adiabatic index of $\gamma = 5/3$ and
-whose equation of state is $P = R\rho T$. 
-The initial atmosphere is a plane-parallel polytrope in which the gravitational acceleration
-and conductive flux, $\bm{F}_{\text{cond,0}} = -\kappa \grad T_0$, do not vary with depth. To
+We exmine the simplist stratified extension of RB by studying a
+fluid composed of monatomic ideal gas particles with an adiabatic 
+index of $\gamma = 5/3$ and whose equation of state is $P = R\rho T$. 
+This is consistent with the approach used in earlier work.
+The initial atmosphere is a plane-parallel polytrope in which 
+the gravitational acceleration and conductive flux, 
+$\bm{F}_{\text{cond,0}} = -\kappa \grad T_0$, do not vary with depth. To
 achieve the latter condition, both $\kappa$ and $\grad T_0$ are constant.
-Under these assumptions, satisfying hydrostatic equilibrium produces a stratification of
+Under these assumptions, satisfying hydrostatic 
+equilibrium produces a stratification of
 \begin{equation}
@@
 \end{equation}
-where $m = m_{ad} - \epsilon$ is the polytropic index.
-The adiabatic polytropic index is $m_{ad} \equiv (\gamma-1)^{-1}$ and
+where $m = m_{\text{ad}} - \epsilon$ is the polytropic index.
+The adiabatic polytropic index is $m_{\text{ad}} \equiv (\gamma-1)^{-1}$ and
 the superadiabatic excess is $\epsilon$ which sets the scale 
-of the entropy gradient, $\grad S_0 \propto -\epsilon$.
-Thermodynamic variables are nondimensionalized at the top of the atmosphere as 
-$P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, requiring $z_0 \equiv L_z + 1$ and $R = T_{t} = \rho_{t} = 1$.
-By this choice, the non-dimensional length scale is the inverse temperature gradient scale and
-the timescale is the isothermal sound crossing time of this unit length.
-$z$ increases upwards within $[0, L_{z}]$, where $L_{z} = e^{n_{\rho}/m} - 1$ is
-determined by $n_\rho$, the number of density scale heights the atmosphere spans.
+of the entropy gradient ($\grad S_0 \propto -\epsilon$).
+A significant advance of this work is the ability to study large 
+and small values of $\epsilon$, as will be discussed.
+Thermodynamic variables are nondimensionalized at the 
+top of the atmosphere as  $P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, 
+requiring $z_0 \equiv L_z + 1$ and $R = T_{t} = \rho_{t} = 1$.
+By this choice, the non-dimensional length scale is the inverse 
+temperature gradient scale and the timescale is the isothermal 
+sound crossing time of this unit length.
+The height $z$ increases upwards within $[0, L_{z}]$, 
+where $L_{z} = e^{n_{\rho}/m} - 1$ is
+determined by $n_\rho$ and $\epsilon$.
 The characteristic timescale of convective dynamics
-is related to the atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$, with $g = (m+1)$.
-Throughout this letter, buoyancy time units are used and 
-$n_{\rho} = 3$ such that the initial density varies by a factor of 20.
-All atmospheres studied here have an aspect ratio of 4, such that $L_x = 4L_z$.
+is related to the atmospheric buoyancy time, 
+$t_{\text{b}} = \sqrt{L_z/g\epsilon}$, with $g = (m+1)$.
+Throughout this letter, we use buoyancy time units and 
+choose $n_{\rho} = 3$ such that the 
+initial density varies by a factor of 20.
+All atmospheres studied here have an aspect ratio of 4, 
+such that $L_x = 4L_z$.
 
-Atmospheric diffusivities are specified by the Rayleigh number and the Prandtl number.  The
+Atmospheric diffusivities are specified by the Rayleigh number
+and the Prandtl number.  The
 non-dimensional Rayleigh number is
@@
 \end{equation}
-where $\Delta S_0$ is the entropy difference between the top and bottom of the atmosphere, 
-$c_P = R\gamma(\gamma-1)^{-1}$ is the specific heat at constant pressure,
-$\nu$ is the kinematic viscosity (viscous diffusivity), and $\chi$ is the thermal diffusivity.  
+where $\Delta S_0 = \epsilon\ln z_0$ is the entropy difference 
+between the top and bottom of the atmosphere, 
+$c_P = R\gamma(\gamma-1)^{-1}$ is the specific heat 
+at constant pressure, $\nu$ is the kinematic viscosity 
+(the viscous diffusivity), and $\chi$ is the thermal diffusivity.  
 The relationship between the thermal and viscous diffusivities is
-set by the Prandtl number, $\text{Pr} = \nu/\chi$.   We relate the dynamic viscosity, $\mu$, and the thermal conductivity,
-$\kappa$, to their corresponding diffusivities such that 
-$\nu \equiv \mu/\rho$ and $\chi \equiv \kappa/\rho$.  As a result, $\text{Ra} \propto (\nu\chi)^{-1} \propto
-\rho^2$.  The atmospheres studied here with $n_{\rho} = 3$ experience an increase in the Rayleigh number 
+set by the Prandtl number, $\text{Pr} = \nu/\chi$.   
+The dynamic viscosity, $\mu$, and the thermal conductivity,
+$\kappa$, relate to their corresponding diffusivities such that 
+$\nu \equiv \mu/\rho$ and $\chi \equiv \kappa/\rho$.  We take
+$\mu$ and $\kappa$ to be constant with height.
+As a result, $\text{Ra} \propto (\nu\chi)^{-1} \propto
+\rho^2$.  The atmospheres studied here with $n_{\rho} = 3$ 
+experience an increase in the Rayleigh number 
 by a factor of 400 across the domain.  This formulation leaves Pr
-constant throughout the depth of the atmosphere. In this letter we impose $\text{Pr} = 1$ and
-specify Ra at $z = L_z$.
+constant throughout the depth of the atmosphere. 
+In this letter we impose $\text{Pr} = 1$ and specify Ra at 
+the top of the domain ($z = L_z$).
 
-At the constant values of $n_\rho$ and Pr used, the primary control parameters of convection are $\epsilon$
-and Ra.  We decompose our atmosphere into the background polytrope ($\ln\rho_{0}, T_{0}$) and the fluctuations
-about that background ($\bm{u}, \ln\rho_{1}, T_{1}$).  The scaling of the entropy gradient with $\epsilon$
-is reflected in the evolved values of these fluctuations, which follow the scaling of
-$T_1/T_0 \propto \rho_{1}/\rho_{0} \propto$ Ma$^{2} \propto \epsilon$ for low values of $\epsilon$,
+At the constant values of $n_\rho$ and Pr used, 
+the primary control parameters of convection are $\epsilon$
+and Ra.  We decompose our atmosphere into the background 
+polytrope ($\ln\rho_{0}, T_{0}$) and the fluctuations
+about that background ($\bm{u}, \ln\rho_{1}, T_{1}$),
+which can be large.
+The scaling of the entropy gradient with $\epsilon$
+is reflected in the evolved values of these fluctuations, 
+which follow the scaling of
+$T_1/T_0 \propto \rho_{1}/\rho_{0} \propto$ Ma$^{2} \propto \epsilon$ 
+for low values of $\epsilon$,
 as in Fig. \ref{fig:ma_v_eps}.
@@
 \includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
-\caption{The maximum value of Ma which has been horizontally averaged and time averaged for $\geq 100 t_b$, 
+\caption{The maximum value of Ma which has been horizontally 
+averaged and time averaged for $\geq 100 t_b$, 
 beginning roughly $50t_b$ after
-the start of simulations.  This time average is long enough that the profile is well converged
+the start of simulations.  This time average is long 
+enough that the profile is well converged
 and error bars are negligible. (a) For $\epsilon \leq 0.1$,
@@
 at $\text{Ra }= \{10^2, 10^5\}$ exists.
-When $\epsilon \rightarrow m_{ad}$, large deviations from this power law are seen.  
-(b) At high $\epsilon$, Ma scales as Ra$^{0.28}$ until it reaches the supersonic regime, at which point it
-follows a power law of Ra$^{-0.10}$.  At low $\epsilon$, consistent power laws are achieved throughout all
-values of Ra studied, where $\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
+When $\epsilon \rightarrow m_{\text{ad}}$, 
+large deviations from this power law are seen.  
+(b) At high $\epsilon$, Ma scales as Ra$^{0.28}$ 
+until it reaches the supersonic regime, at which point it
+follows a power law of Ra$^{-0.10}$.  At low $\epsilon$, 
+consistent power laws are achieved throughout all
+values of Ra studied, where 
+$\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
 for $\epsilon = \{10^{-4}, 10^{-7}\}$. 
@@
 
-The Fully Compressible Navier-Stokes equations,
+We evolve the Fully Compressible Navier-Stokes equations,
 \begin{align}
 &\begin{aligned}
-&\frac{\partial \ln\rho}{\partial t} + \Div{\bm{u}} = -\bm{u}\cdot\grad\rho,
+&\frac{\partial \ln\rho}{\partial t} + \grad\cdot\bm{u} 
+    = -\bm{u}\cdot\grad\rho,
 	\label{eqn:continuity_eqn}
@@
 &\begin{aligned}
-\frac{\partial\bm{u}}{\partial t} + \grad T - &\nu\Div{\lilstressT} - \lilstressT\cdot\grad\nu = \\
-&-\bm{u}\cdot\grad\bm{u} - T\grad\ln\rho + \bm{g} + \nu\lilstressT\cdot\grad\ln\rho,
+\frac{\partial\bm{u}}{\partial t} + \grad T - 
+&\nu\grad\cdot\lilstressT - \lilstressT\cdot\grad\nu = \\
+&-\bm{u}\cdot\grad\bm{u} - T\grad\ln\rho + \bm{g} + 
+\nu\lilstressT\cdot\grad\ln\rho,
 \label{eqn:momentum_eqn}
@@
 &\begin{aligned}
-\frac{\partial T}{\partial t} -\frac{1}{c_V}\left(\right.\chi&\left.\grad^2 T + \grad T\cdot\grad\chi\right) = \\
-	&-\bm{u}\cdot\grad T - (\gamma-1)T\Div{\bm{u}} \\
-	&+ \frac{1}{c_V}\left(\chi\grad T \cdot\grad\ln\rho +\nu\left[\lilstressT\cdot\nabla\right]\cdot\bm{u}\right), 
+\frac{\partial T}{\partial t} -\frac{1}{c_V}\left(\right.\chi&\left.
+    \grad^2 T + \grad T\cdot\grad\chi\right) = \\
+	&-\bm{u}\cdot\grad T - (\gamma-1)T\grad\cdot{\bm{u}} \\
+	&+ \frac{1}{c_V}\left(\chi\grad T \cdot\grad\ln\rho +
+	\nu\left[\lilstressT\cdot\nabla\right]\cdot\bm{u}\right), 
 	\label{eqn:energy_eqn}
@@
 \end{align}
-are evolved with a viscous stress tensor defined as
+with the viscous stress tensor given by
 \begin{equation}
-\sigma_{ij} \equiv \left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\Div{\bm{u}}\right).
+\sigma_{ij} \equiv \left(\frac{\partial u_i}{\partial x_j} + 
+\frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\grad\cdot\bm{u}\right).
 	\label{eqn:stress_tensor}
 \end{equation}
-
 Taking an inner product of
-Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
-Eq. \ref{eqn:energy_eqn} reveals the full energy equation,
+(\ref{eqn:momentum_eqn}) with $\bm{u}$ and adding it to 
+(\ref{eqn:energy_eqn}) reveals the full energy equation,
 \begin{equation}
 \frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
-\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0.
+\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0,
 	\label{eqn:energy_eqn_full}
 \end{equation}
-The convective flux is
+where the convective flux is
 $
-\bm{F}_{\text{conv}} \equiv \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}}.
+\bm{F}_{\text{conv}} \equiv \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}}
 $
-Contributions from the enthalpy flux, $\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$;
-the kinetic energy flux, $\bm{F}_{\text{KE}} \equiv \rho|\bm{u}|^2\bm{u}/2$;
-the potential energy flux, $\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ (with $\phi \equiv -gz$);
-and the viscous flux, $\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$, must all be considered. 
-%where $\bm{F}_{\text{cond}} = -\kappa \grad T$.  
-Understanding these flux terms and how they interact with the conductive flux, 
-$\bm{F}_{\text{cond}} = -\kappa \grad T$, is crucial in characterizing
-convective heat transport.
+and the condcutve flux is $\bm{F}_{\text{cond}} = -\kappa \grad T$.
+The individual contributions to $\bm{F}_{\text{conv}}$ are the enthalpy flux, 
+$\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$;
+the kinetic energy flux, 
+$\bm{F}_{\text{KE}} \equiv \rho|\bm{u}|^2\bm{u}/2$;
+the potential energy flux,
+$\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ (with $\phi \equiv -gz$);
+and the viscous flux, 
+$\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$, and all four
+must all be considered. 
+Understanding how these flux interact  
+is crucial in characterizing convective heat transport.
 
-The atmosphere is contained between two impenetrable, stress free, fixed temperature boundaries at
-the top and bottom of the domain such that $w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. The domain
-is horizontally periodic. We utilize the novel Dedalus\footnote{http://dedalus-project.org/} pseudospectral framework 
- to time-evolve Eqs. 
-\ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn} using an implicit-explicit, third-order, four-step 
+The atmosphere is contained between two 
+impenetrable, stress free, fixed temperature boundaries at
+the top and bottom of the domain such that 
+$w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. The domain
+is horizontally periodic. We utilize the 
+Dedalus\footnote{http://dedalus-project.org/} \cite{burns&all2016} pseudospectral framework 
+ to time-evolve  
+(\ref{eqn:continuity_eqn})-(\ref{eqn:energy_eqn}) 
+using an implicit-explicit, third-order, four-step 
 Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
@@
 and Fourier (horizontal) domain in which the
-physical grid dimensions are 3/2 the size of the coefficient grid.  Physical grid sizes range from
-96x384 grid points at the lowest values of Ra to 1152x4608 grid points at Ra $\geq 10^{7}$. 
-By using IMEX timestepping, we implicitly step the stiff linear acoustic wave contribution and are able to
+physical grid dimensions are 3/2 the size of the coefficient grid.  
+Physical grid sizes range from
+96x384 grid points at the lowest values of 
+Ra to 1152x4608 grid points at Ra $\geq 10^{7}$. 
+By using IMEX timestepping, we implicitly step the 
+stiff linear acoustic wave contribution and are able to
 efficiently study flows at moderate ($\approx 1$) and very low ($\approx 10^{-4}$)
@@
 of the FC equations in \cite{lecoanet&all2014}, extended to include variable
-$\nu$ and $\chi$, and we follow the approach there; this IMEX approach has been successfully 
-tested against a nonlinear benchmark  of the compressible Kelvin-Helmholtz instability \cite{Lecoanet_et_al_2016_KH}.
+$\nu$ and $\chi$, and we follow the approach there; 
+this IMEX approach has been successfully 
+tested against a nonlinear benchmark  of the compressible 
+Kelvin-Helmholtz instability \cite{Lecoanet_et_al_2016_KH}.
 
@@
 \end{equation}
-where $F_{\text{conv, z}}$ and $F_{\text{cond, z}}$ are the z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
-respectively.  $F_{\text{A}} \equiv -\kappa \partial_z T_{\text{ad}}$ is the adiabatic conductive flux and
-$\partial_z T_{\text{ad}} \equiv - g / c_{P}$ for an ideal gas in hydrostatic equilibrium.
-$F_{\text{ref}} \equiv \Delta T / L_z$, where $\Delta T \equiv T(L_z) - T(0)$, is the 
+where $F_{\text{conv, z}}$ and $F_{\text{cond, z}}$ are the 
+z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
+respectively.  $F_{\text{A}} \equiv -\kappa \partial_z T_{\text{ad}}$ 
+is the adiabatic conductive flux and
+$\partial_z T_{\text{ad}} \equiv - g / c_{P}$ 
+for an ideal gas in hydrostatic equilibrium.
+$F_{\text{ref}} \equiv \Delta T / L_z$, 
+where $\Delta T \equiv T(L_z) - T(0)$, is the 
 conductive flux of a linear profile connecting the upper
-and lower plates, which is constant for the choice of fixed-temperature boundaries.
+and lower plates, which is constant for 
+the choice of fixed-temperature boundaries.
 
-We contend that this is the general form of the Nusselt number and illustrate this with a few limiting
+We contend that this is the general form of the Nusselt number
+and illustrate this with a few limiting
 cases. Convection eliminates
 entropy stratification.  Under the Boussinesq approximation,
-in which density variations are ignored, entropy stratification is directly proportional to temperature stratification
-such that $\grad S \rightarrow 0$ when $\grad T \rightarrow 0$.  The familiar Nu in the RB problem is
-therefore retrieved from Eq. \ref{eqn:nusselt} because $\grad T_{\text{ad}} = 0$.  
+in which density variations are ignored, entropy stratification 
+is directly proportional to temperature stratification
+such that $\grad S \rightarrow 0$ when $\grad T \rightarrow 0$.  
+The familiar Nu in the RB problem is
+therefore retrieved from (\ref{eqn:nusselt}) because $\grad T_{\text{ad}} = 0$.  
 In the case of polytropic convection,  $g \rightarrow 0$
-as $\epsilon \rightarrow m_{ad} + 1$.
-In this limit, $F_{\text{A}} \rightarrow 0$ and the
+as $\epsilon \rightarrow m_{\text{ad}} + 1$.
+In this limit, $\grad T_{\text{ad}} \rightarrow 0$ as well and the
 definition of the RB Nu is appropriate to use, as convection carries all of the
@@
 $\grad T_{\text{ad}}\rightarrow \grad T_0$ and increasingly
-smaller velocity and thermodynamic perturbations are needed to achieve $\grad S = 0$ (Fig. \ref{fig:ma_v_eps}a).
-These perturbations carry what little flux exists in excess of the adiabatic, so the removal of 
-$F_{\text{A}}$ in the numerator and denominator of Eq. \ref{eqn:nusselt} is essential for a reasonable Nu measurement.
+smaller velocity and thermodynamic perturbations are needed to 
+achieve $\grad S = 0$ (Fig. \ref{fig:ma_v_eps}a).
+These perturbations carry what little flux exists in 
+excess of the adiabatic, so the removal of 
+$F_{\text{A}}$ in the numerator and denominator of 
+(\ref{eqn:nusselt}) is essential for a reasonable Nu measurement.
 
@@
 \includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
-\caption{Characteristic entropy fluctuations in evolved flows. The time- and horizontally-
-averaged profile is removed in all cases.  At high
-$\epsilon$ (a), shock systems form near the upper downflow lanes and propel shock-heated material deep within
-the atmosphere at sufficiently high Ra.  At low $\epsilon$ but at the same Ra (b), shock systems are absent, 
-but otherwise the dynamics are similar.  As Ra is increased (c), downflow lanes no longer span
-the entirety of the domain and individual small blobs are responsible for carrying the flux.
+\caption{Characteristic entropy fluctuations in evolved flows. 
+The time- and horizontally-averaged profile is removed in all cases.  (a) At high
+$\epsilon$, shock systems form near the upper downflow lanes ($x \approx 45, z \approx 15-19$)
+at sufficiently high Ra.
+Shock-heated fluid then flows into the downflows as the shocks propagate across upflows.
+(b) At low $\epsilon$ but at the same Ra, shock systems are absent, 
+but otherwise the dynamics are similar.  (c) As Ra is increased, downflows no longer span
+the entirety of the domain and individual small eddies are responsible for carrying the flux.
 \label{fig:entropy_snapshots} }
@@
 
-Initial value problems were solved in which $T_1$ 
-was filled with infinitesimal, random noise compared to $T_0$ and $\epsilon$.
+We evolve initial value problems in which $T_1$ is
+filled with infinitesimal, random white noise compared to $T_0$ and $\epsilon$.
+We filter the noise spectrum in coefficient space, such that 25\% of the coefficients
+have power.
 Solutions were time-evolved until a long average of Nu showed little
-variance with depth. By performing a linear stability analysis, we determined that the onset of convection
-occurs at $\text{Ra}_c = \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  
+variance with depth. By performing a linear stability analysis, 
+we determined that the onset of convection
+occurs at $\text{Ra}_c = \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$ respectively.  
 We studied Rayleigh
-numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$, $10^5$Ra$_c$ for $\epsilon = 10^{-4}$,
-and $10^3$Ra$_c$ for $\epsilon = 10^{-7}$.
+numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$ and for $\epsilon = 10^{-4}$
+and up to $10^3$Ra$_c$ for $\epsilon = 10^{-7}$.
 
 At large Ma ($\epsilon = 0.5$), shock systems form in the upper atmosphere near downflow lanes 
-(Fig. \ref{fig:entropy_snapshots}a) and propagate toward upflow lanes.  
+(Fig. \ref{fig:entropy_snapshots}a) once Ra is sufficiently large.
+These shocks propagate through upflow upflow regions.  
 Such systems were reported in
@@
 Low Ma flows ($\epsilon = 10^{-4}$)
-have similar bulk thermodynamic structures (Fig. \ref{fig:entropy_snapshots}b).
-As Ra is increased to large values (Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
-no longer span the whole domain but rather break up into small packets which traverse the domain multiple
+have similar bulk thermodynamic structures (Fig. \ref{fig:entropy_snapshots}b)
+to high Ma flows.
+As Ra is increased to large values 
+(Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
+no longer span the whole domain but rather break up into 
+small eddies which traverse the domain multiple
 times before diffusing.  
-While it has been suggested that pressure forces cause symmetry breaking in up- and downflows,
-\cite{hurlburt&all1984}, this effect seems to be secondary to flows obeying mass conservation as they traverse
-the stratified medium.  We observe low Ma cases where the double-roll systems such as those in
-Fig. \ref{fig:entropy_snapshots}b contain one roll of increased pressure and one roll of decreased pressure
-where the up- and downflows bound these regions of pressure disequilibrium.
+While it has been suggested that pressure forces 
+cause symmetry breaking in up- and downflows
+\cite{hurlburt&all1984}, at low $\epsilon$ this 
+effect seems to be secondary to flows obeying mass conservation as they traverse
+the stratified medium.
 
@@
 \includegraphics[width=3.4375in]{./figs/fluxes_fig.png}
-\caption{Time-averaged flux profiles for high (a) and low (b) Ma flows at $\text{Ra }= 10^6$.  
+\caption{Time-averaged vertical flux profiles ($F_{\text{z}}$)
+for (a) high and (b) low Ma flows at $\text{Ra }= 10^6$.  
+All fluxes are defined as in (\ref{eqn:energy_eqn_full}) and 
+normalized by $F_{\text{ref}} - F_{\text{A}}$, as in (\ref{eqn:nusselt}).
 The dashed lines correspond to the
-enthalpy flux (orange, positive) and kinetic energy flux (purple, negative).  The grey dash-dot line is the
-viscous flux, the blue dash-dot-dot line is the potential energy flux, 
-and the green dotted line is the radiative flux with the adiabatic radiative flux removed. Viscous and
-potential energy fluxes are negligible in (a) and are not shown.  All
-fluxes are normalized by $F_{\text{ref}} - F_{\text{A}}$, as in Eq. \ref{eqn:nusselt}.  The solid black line is
+enthalpy flux (orange, positive) and kinetic energy flux (purple, negative).  
+The grey dash-dot line is the
+viscous flux and the green dotted line is the conductive flux with the 
+adiabatic contribution removed. Viscous and
+potential energy fluxes are negligible in (a) and are not shown.    
+The solid black line is
 Nu, the properly normalized sum of all the fluxes \label{fig:flux_profiles} }
@@
 
-%At large Ra, the heat transport properties of the systems become increasingly complex and time-dependent.
-at large values of Ra in which shocks form, high Ma flows exhibit two 
+High Ma flows at large values of Ra, in which shocks form, exhibit two 
 local maxima in the enthalpy flux and kinetic energy flux (Fig. \ref{fig:flux_profiles}a).
-Shock-heated fluid parcels sometimes spin-up as they are pushed into the lower atmosphere, creating deep,
-rapidly-rotating regions
-of mixing which persist for many overturn times.  These ``spinners'' sit inside of larger rolls created by their
-neighboring up- and downflows and greatly influence the dynamics.
+Shock-heated fluid parcels sometimes gain vorticity
+they sink into the lower atmosphere.
+This creates deep, rapidly-rotating regions
+of mixing which persist for many overturn times. These ``spinners'' appear to
+influence the dynamics, but their contributions are unclear.
 At low Ma, only the deep maximum is present (Fig. \ref{fig:flux_profiles}b).  
-Fixed-temperature boundary conditions allow the flux at the boundaries to vary, so many runs at $\text{Ra }> 10^5$
-and $\epsilon = 10^{-4}$ exhibit states in which the flux entering the system at the bottom of the atmosphere 
+Fixed-temperature boundary conditions allow the flux at the 
+boundaries to vary, so many runs at $\text{Ra }> 10^5$
+and $\epsilon = 10^{-4}$ exhibit states in which the flux 
+entering the system at the bottom of the atmosphere 
 exceeds that which leaves at the top.  
-These states are punctuated by states of vigorous shearing, similar to those previously
+These systems are punctuated by states of vigorous shearing, similar to those previously
 reported in two-dimensional RB convection \cite{goluskin&all2014}.  
-These shearing states push the bottom temperature
-gradient towards adiabatic, allowing the excess energy to exit through the upper boundary.  These shearing
-states will be covered in more detail in a future paper.  Regardless, a proper long-term average over shearing
+In these shearing states, the bottom temperature
+gradient approaches adiabatic, 
+allowing the excess energy to exit through the upper boundary.  
+During shearing states, convective transport is suppressed and Nu diminishes.
+A proper long-term average over shearing
 and non-shearing states retrieves an invariant flux (and Nu) profile throughout the depth
 of the atmosphere. 
+These shearing states will be covered in more detail in a future paper.
 
-After appropriately time-averaging the fluxes for $\geq 200 t_b$, a sensible flux average is retrieved.  
-Nusselt numbers for
+After appropriately time-averaging the fluxes for $\geq 200 t_b$, 
+a sensible flux average is retrieved.  Nusselt numbers for
 all simulations at low and high Ma are plotted as a function of Ra in Fig. \ref{fig:nu_v_ra}.  
-At $\epsilon = \{10^{-4}, 10^{-7}\}$,
-scaling laws of $\text{Nu} \propto \text{Ra}^{\{0.31, 0.31\}}$ are retrieved.  At $\epsilon = 0.5$, in the near-sonic
-regime ($\text{Ra} \leq 10^4$), the scaling of Nu with Ra is inflated, with $\text{Nu} \propto \text{Ra}^{0.45}$.  As simulations
+At $\epsilon = 0.5$, in the near-sonic
+regime ($\text{Ra} \leq 10^4$), the scaling of Nu with Ra is inflated,
+with $\text{Nu} \propto \text{Ra}^{0.45}$, similar to that expected in the
+ultimate regime of RB \cite{ahlers&all2009}.  As simulations
 pass into the supersonic regime and shocks start to form near the downflows,
 that scaling drops to $\text{Nu} \propto \text{Ra}^{0.19}$.  
+At $\epsilon = \{10^{-4}, 10^{-7}\}$,
+scaling laws of $\text{Nu} \propto \text{Ra}^{\{0.31, 0.31\}}$ are retrieved. 
+This scaling is indistringuishable from the $\text{Ra}^{2/7}$ found in RB
+convection.
 
@@
 \includegraphics[width=3.4375in]{./figs/nu_v_ra.png}
-\caption{Variation of Nu as Ra increases at low and high Ma. 
+\caption{Variation of Nu as Ra increases at high and low $\epsilon$. 
 At high $\epsilon$ (purple circles), 
 a clear transition from the subsonic to supersonic regime is evident in the scaling
-of Nu with Ra.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
-Nu scalings collapse onto a similar line which is
-\textbf{consistent with RB scalings?} \cite{johnston&doering2009}.  Error bars are determined
- by the square root of the variance of Nu with depth and indicate whether or not a solution is well-converged.
+of Nu with Ra At $\text{Ra} \approx 10^4$.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
+our observed Nu scalings collapse onto a similar line which is
+indistinguishable from an $\text{Ra}^{2/7}$ scaling, 
+as observed in RB convection \cite{johnston&doering2009}.  Error bars are determined
+ by the square root of the variance of the time-averaged Nu profile with depth and 
+ indicate whether or not a solution is well-converged.
 \label{fig:nu_v_ra} }
@@
 \label{sec:discussion}
-In this letter we have studied fundamental heat transport by stratified convection in simplified 2-D polytropic
-atmospheres which are specified by two parameters, $\nrho$ 
+In this letter we have studied fundamental heat transport by 
+stratified convection in simplified 2-D polytropic
+atmospheres which are specified by two additional parameters, $\nrho$ 
 and $\epsilon$.  We argue that these atmospheres are the natural extension
-of the RB problem to stratified systems, and should be used to understand the basic properties of stratified
-convection.  The similarity between the scaling of Nu in RB convection and in low-$\epsilon$ polytropes suggests 
+of the RB problem to stratified systems, 
+and are an ideal laboratory for understanding the basic properties of stratified
+convection.  The similarity between the scaling of Nu in RB 
+convection and in our low-$\epsilon$ polytropes suggests 
 that a boundary layer theory such as the Grossmann-Lohse theory for incompressible flows
-could be developed for fully compressible convection in these systems \cite{ahlers&all2009}.
+could be developed for fully compressible 
+convection in these stratified systems \cite{ahlers&all2009}.
 
-%Furthermore, we have demonstrated that low Ma flows exhibit the same pattern of broad upflows and narrow downflows
-%observed in high Ma flows \cite{hurlburt&all1984}.  At low Ma, flows are often in pressure equilibrium
-%with their surroundings, so cooling parcels increases their density, and both of these effects reduce
-%entropy.  Neither of the two free thermodynamic variables can cause breaking in warm upflow regions, 
-%so stratification effects must cause the observed flow asymmetry.
-%While not studied in this work, it is possible that at low Ma, flows feel the pressure response of the
-%boundaries, causing deflection in a manner unseen at high Ma.
-
-The dynamics of these polytropic solutions are complex and highly time-dependent, even in two dimensions.
+The dynamics of these polytropic solutions are complex and time-dependent, even in two dimensions.
 Time-dependent oscillating shear states have developed spontaneously, as seen before in RB convection
@@
 Ellery Hale Graduate Student Fellowship.
-This work was supported by  NASA LWS grant number NNX16AC92G.  
+This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
 Computations were conducted 
 with support by the NASA High End Computing (HEC) Program through the NASA 
-Advanced Supercomputing (NAS) Division at Ames Research Center
-with allocations (GID s1647, PI Brown; GID g26133, PI Toomre).
+Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
+with allocations GID s1647 and GID g26133.
 We thank Axel Brandenburg, Mark Rast, and Jeff Oishi for many useful discussions.

### 2016-11-01 tex/nusselt_paper.tex
SUBMISSION DRAFT NUMERO UNO

@@
 jovian planets.  The convective dynamics in these astrophysical objects
-are influenced by the atmospheric 
+are influenced by atmospheric 
 stratification, which is small in some systems (e.g. massive star cores)
@@
 convection to moderately high Mach number (Ma), appropriate to regions near 
-the Sun's surface.  Few fundamental properties of the 
-low-Ma stratified convection, which occurs in the deep solar interior, are known.
+the Sun's surface.  Few fundamental properties of
+low Ma convection, which occurs in the deep solar interior, are known.
 
@@
 Furthermore, the \emph{entropy} gradient is negated by convection 
-rather than the temperature gradient, such
-that in the presence of perfectly efficient convection a significant 
-component of the flux is still carried by conduction.
+rather than the temperature gradient, and
+a significant conductive flux can exist in the presence of
+efficient convection.
 
@@
 early studies \cite{graham1975, chan&all1982, hurlburt&all1984, 
-cattaneo&all1990, cattaneo&all1991, brummell&all1996} are an ideal extension of
+cattaneo&all1990, cattaneo&all1991, brummell&all1996}, are an ideal extension of
 RB convection into the stratified realm as the two additional 
@@
 \label{sec:experiment}
-We exmine the simplist stratified extension of RB by studying a
+We exmine the simplest stratified extension of RB by studying a
 fluid composed of monatomic ideal gas particles with an adiabatic 
@@
 
-Atmospheric diffusivities are specified by the Rayleigh number
-and the Prandtl number.  The
-non-dimensional Rayleigh number is
+The atmospheric diffusivities are primarily controlled by
+the non-dimensional Rayleigh number,
 \begin{equation}
@@
 where $\Delta S_0 = \epsilon\ln z_0$ is the entropy difference 
-between the top and bottom of the atmosphere, 
+between the top and bottom boundaries, 
 $c_P = R\gamma(\gamma-1)^{-1}$ is the specific heat 
@@
 \rho^2$.  The atmospheres studied here with $n_{\rho} = 3$ 
-experience an increase in the Rayleigh number 
+experience an increase in Ra 
 by a factor of 400 across the domain.  This formulation leaves Pr
@@
 
-At the constant values of $n_\rho$ and Pr used, 
+While holding $n_\rho$ and Pr constant, 
 the primary control parameters of convection are $\epsilon$
@@
 \end{equation}
-where the convective flux is
+where
 $
@@
 $
-and the condcutve flux is $\bm{F}_{\text{cond}} = -\kappa \grad T$.
+is the convective flux and $\bm{F}_{\text{cond}} = -\kappa \grad T$
+is the conductive flux.
 The individual contributions to $\bm{F}_{\text{conv}}$ are the enthalpy flux, 
@@
 must all be considered. 
-Understanding how these flux interact  
+Understanding how these fluxes interact  
 is crucial in characterizing convective heat transport.
@@
 Nu is well-defined in RB convection
-as the total flux normalized by the steady-stateconductive flux 
+as the total flux normalized by the steady-state conductive flux 
 \cite{johnston&doering2009, otero&all2002}.
@@
 is directly proportional to temperature stratification
-such that $\grad S \rightarrow 0$ when $\grad T \rightarrow 0$.  
+and $\partial_z S \rightarrow 0$ when $\partial_z T \rightarrow 0$.  
 The familiar Nu in the RB problem is
-therefore retrieved from (\ref{eqn:nusselt}) because $\grad T_{\text{ad}} = 0$.  
+therefore retrieved from (\ref{eqn:nusselt}) because $\partial_z T_{\text{ad}} = 0$.  
 In the case of polytropic convection,  $g \rightarrow 0$
 as $\epsilon \rightarrow m_{\text{ad}} + 1$.
-In this limit, $\grad T_{\text{ad}} \rightarrow 0$ as well and the
-definition of the RB Nu is appropriate to use, as convection carries all of the
-flux \cite{brandenburg&all2005}. 
+In this limit, $\partial_z T_{\text{ad}} \rightarrow 0$ and the
+definition of the RB Nu is appropriate to use \cite{brandenburg&all2005}. 
 However, as $\epsilon \rightarrow 0$, 
-$\grad T_{\text{ad}}\rightarrow \grad T_0$ and increasingly
-smaller velocity and thermodynamic perturbations are needed to 
-achieve $\grad S = 0$ (Fig. \ref{fig:ma_v_eps}a).
+$\partial_z T_{0}\rightarrow \partial_z T_{\text{ad}}$ and increasingly
+smaller velocity and thermodynamic perturbations 
+achieve $\partial_z S = 0$ (Fig. \ref{fig:ma_v_eps}a).
 These perturbations carry what little flux exists in 
@@
 We studied Rayleigh
-numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$ and for $\epsilon = 10^{-4}$
+numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = \{0.5, 10^{-4}\}$ 
 and up to $10^3$Ra$_c$ for $\epsilon = 10^{-7}$.
@@
 (Fig. \ref{fig:entropy_snapshots}a) once Ra is sufficiently large.
-These shocks propagate through upflow upflow regions.  
+These shocks propagate through upflow regions.  
 Such systems were reported in
@@
 viscous flux and the green dotted line is the conductive flux with the 
-adiabatic contribution removed. Viscous and
-potential energy fluxes are negligible in (a) and are not shown.    
-The solid black line is
+adiabatic contribution removed. The potential energy flux is negligible and is not shown.
+In (a), the viscous flux is negligible and is not shown.  The solid black line is
 Nu, the properly normalized sum of all the fluxes \label{fig:flux_profiles} }
@@
 
-High Ma flows at large values of Ra, in which shocks form, exhibit two 
-local maxima in the enthalpy flux and kinetic energy flux (Fig. \ref{fig:flux_profiles}a).
-Shock-heated fluid parcels sometimes gain vorticity
+High Ma flows exhibit two 
+local maxima in the enthalpy flux and kinetic energy flux (Fig. \ref{fig:flux_profiles}a)
+at large enough values of Ra for shocks to form.
+Shock-heated fluid parcels sometimes gain vorticity as
 they sink into the lower atmosphere.
@@
 influence the dynamics, but their contributions are unclear.
-At low Ma, only the deep maximum is present (Fig. \ref{fig:flux_profiles}b).  
-Fixed-temperature boundary conditions allow the flux at the 
+
+At low Ma, only the deep maximum in enthalpy and kinetic energy fluxes
+is present (Fig. \ref{fig:flux_profiles}b).  
+Our choice of fixed-temperature boundary conditions allows the flux at the 
 boundaries to vary, so many runs at $\text{Ra }> 10^5$
@@
 reported in two-dimensional RB convection \cite{goluskin&all2014}.  
-In these shearing states, the bottom temperature
-gradient approaches adiabatic, 
-allowing the excess energy to exit through the upper boundary.  
-During shearing states, convective transport is suppressed and Nu diminishes.
+%In these shearing states, flux entering the lower atmosphere approaches $F_\text{A}$,
+%allowing excess energy to escape through the upper boundary.  
+During shearing states, convective transport is suppressed and Nu diminishes while
+excess energy exits the system through the upper boundary.
 A proper long-term average over shearing
-and non-shearing states retrieves an invariant flux (and Nu) profile throughout the depth
+and non-shearing states retrieves an invariant Nu profile throughout the depth
 of the atmosphere. 
@@
 with $\text{Nu} \propto \text{Ra}^{0.45}$, similar to that expected in the
-ultimate regime of RB \cite{ahlers&all2009}.  As simulations
+ultimate regime of RB convection \cite{ahlers&all2009}.  As simulations
 pass into the supersonic regime and shocks start to form near the downflows,
@@
 scaling laws of $\text{Nu} \propto \text{Ra}^{\{0.31, 0.31\}}$ are retrieved. 
-This scaling is indistringuishable from the $\text{Ra}^{2/7}$ found in RB
+This scaling is indistinguishable from the $\text{Ra}^{2/7}$ found in RB
 convection.
@@
 our observed Nu scalings collapse onto a similar line which is
-indistinguishable from an $\text{Ra}^{2/7}$ scaling, 
+indistinguishable from a $\text{Ra}^{2/7}$ scaling, 
 as observed in RB convection \cite{johnston&doering2009}.  Error bars are determined

### 2016-11-17 tex/nusselt_paper.tex
fixes eqn 3 to have ln rho
changes RB sentence in second paragraph of intro

@@
 upflows and downflows are symmetrical and
-the temperature gradient approaches zero in the convective interior 
-causing the conductive flux to similarly 
-disappear.  These two hallmark characteristics of RB convection change
+the conductive flux approaches zero in the convective interior.
+These two hallmark characteristics of RB convection change
 significantly when stratification is included.  Stratified convection 
@@
 &\frac{\partial \ln\rho}{\partial t} + \grad\cdot\bm{u} 
-    = -\bm{u}\cdot\grad\rho,
+    = -\bm{u}\cdot\grad\ln\rho,
 	\label{eqn:continuity_eqn}

### 2016-11-17 tex/nusselt_paper.tex
as-->because, grad-->partial_z, extra comma

@@
 cattaneo&all1990, cattaneo&all1991, brummell&all1996}, are an ideal extension of
-RB convection into the stratified realm as the two additional 
+RB convection into the stratified realm because the two additional 
 control parameters are directly linked to
@@
 the gravitational acceleration and conductive flux, 
-$\bm{F}_{\text{cond,0}} = -\kappa \grad T_0$, do not vary with depth. To
-achieve the latter condition, both $\kappa$ and $\grad T_0$ are constant.
+$\bm{F}_{\text{cond,0}} = -\kappa \partial_z T_0$, do not vary with depth. To
+achieve the latter condition, both $\kappa$ and $\partial_z T_0$ are constant.
 Under these assumptions, satisfying hydrostatic 
@@
 where $m = m_{\text{ad}} - \epsilon$ is the polytropic index.
-The adiabatic polytropic index is $m_{\text{ad}} \equiv (\gamma-1)^{-1}$ and
+The adiabatic polytropic index is $m_{\text{ad}} \equiv (\gamma-1)^{-1}$, and
 the superadiabatic excess is $\epsilon$ which sets the scale 
-of the entropy gradient ($\grad S_0 \propto -\epsilon$).
+of the entropy gradient ($\partial_z S_0 \propto -\epsilon$).
 A significant advance of this work is the ability to study large 

### 2016-11-17 tex/nusselt_paper.tex
small changes near FC eqns

@@
 The scaling of the entropy gradient with $\epsilon$
-is reflected in the evolved values of these fluctuations, 
-which follow the scaling of
-$T_1/T_0 \propto \rho_{1}/\rho_{0} \propto$ Ma$^{2} \propto \epsilon$ 
-for low values of $\epsilon$,
-as in Fig. \ref{fig:ma_v_eps}.
+is reflected in the evolved values of these fluctuations.  For small $\epsilon$,
+evolved values scale as
+$T_1/T_0 \propto \rho_{1}/\rho_{0} \propto$ Ma$^{2} \propto \epsilon$,
+as shown in Fig. \ref{fig:ma_v_eps}.
 
@@
 and the viscous flux, 
-$\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$, and all four
-must all be considered. 
+$\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$, and each 
+must be considered. 
 Understanding how these fluxes interact  

### 2016-11-17 tex/nusselt_paper.tex
fixes a few things in results section for easier reading.

@@
 for an ideal gas in hydrostatic equilibrium.
-$F_{\text{ref}} \equiv \Delta T / L_z$, 
-where $\Delta T \equiv T(L_z) - T(0)$, is the 
-conductive flux of a linear profile connecting the upper
-and lower plates, which is constant for 
+The conductive flux of a linear profile connecting the upper
+and lower plates
+is $F_{\text{ref}} \equiv \Delta T / L_z$, 
+where $\Delta T \equiv T(L_z) - T(0)$.  $F_{\text{ref}}$ is constant for 
 the choice of fixed-temperature boundaries.
@@
 
-High Ma flows exhibit two 
-local maxima in the enthalpy flux and kinetic energy flux (Fig. \ref{fig:flux_profiles}a)
-at large enough values of Ra for shocks to form.
+At large enough values of Ra for shocks to form,
+high Ma flows exhibit two 
+local maxima in the enthalpy flux and kinetic energy flux (Fig. \ref{fig:flux_profiles}a).
 Shock-heated fluid parcels sometimes gain vorticity as
@@
 a clear transition from the subsonic to supersonic regime is evident in the scaling
-of Nu with Ra At $\text{Ra} \approx 10^4$.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
+of Nu with Ra at $\text{Ra} \approx 10^4$.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
 our observed Nu scalings collapse onto a similar line which is

### 2016-11-17 tex/nusselt_paper.tex
reworks last sentence to cite keith

@@
 whether or not these states are attainable in three-dimensional, non-rotating atmospheres.  Our studies
-here have set the groundwork for understanding and comparing heat transport in stratified convection
+here will serve as a foundation both for understanding and comparing heat transport in stratified convection
 to that in RB convection \cite{johnston&doering2009}, and for future studies of transport in stratified
-convection in more realistic systems, such as those bounded by stable regions \cite{hurlburt&all1986} or 
-using more realistic profiles of $\kappa$.
+convection in more realistic systems, such as rapidly rotating atmospheres \cite{julien&all2016},
+atmospheres bounded by stable regions \cite{hurlburt&all1986}, 
+or regions with realistic profiles of $\kappa$.
 

### 2016-11-17 tex/nusselt_paper.tex
changes from julien 2016-->2012

--- 2016-11-17 tex/nusselt_paper.tex
@@
 whether or not these states are attainable in three-dimensional, non-rotating atmospheres.  Our studies
-here have set the groundwork for understanding and comparing heat transport in stratified convection
+here will serve as a foundation both for understanding and comparing heat transport in stratified convection
 to that in RB convection \cite{johnston&doering2009}, and for future studies of transport in stratified
-convection in more realistic systems, such as those bounded by stable regions \cite{hurlburt&all1986} or 
-using more realistic profiles of $\kappa$.
+convection in more realistic systems, such as rapidly rotating atmospheres \cite{julien&all2012},
+atmospheres bounded by stable regions \cite{hurlburt&all1986}, 
+or regions with realistic profiles of $\kappa$.
 

### 2017-02-15 code/FC_poly.py
chi_l and chi_r etc in 3d

@@ -75,7 +75,7 @@ def FC_polytrope(  Rayleigh=1e4, Prandtl=1, aspect_ratio=4,\
     
     if threeD:
         atmosphere = equations.FC_polytrope_3d(nx=nx, ny=ny, nz=nz, mesh=mesh, constant_kappa=const_kappa, constant_mu=const_mu,\
-                                        epsilon=epsilon, n_rho_cz=n_rho_cz, Lx=Lx, aspect_ratio=aspect_ratio,\
+                                        epsilon=epsilon, n_rho_cz=n_rho_cz, aspect_ratio=aspect_ratio,\
                                         fig_dir='./FC_poly_atmosphere/')
     else:
         atmosphere = equations.FC_polytrope_2d(nx=nx, nz=nz, constant_kappa=const_kappa, constant_mu=const_mu,\
@@ -118,7 +118,7 @@ def FC_polytrope(  Rayleigh=1e4, Prandtl=1, aspect_ratio=4,\
     atmosphere.check_atmosphere(make_plots = False, rho=atmosphere.get_full_rho(solver), T=atmosphere.get_full_T(solver))
 
     #Set up timestep defaults
-    max_dt = atmosphere.buoyancy_time*0.05
+    max_dt = atmosphere.buoyancy_time*0.25
     dt = max_dt/5
     if epsilon < 1e-5:
         max_dt = atmosphere.buoyancy_time*0.05
@@ -180,7 +180,7 @@ def FC_polytrope(  Rayleigh=1e4, Prandtl=1, aspect_ratio=4,\
         solver.stop_sim_time    = 100*atmosphere.thermal_time
     
     from numpy import inf
-    solver.stop_iteration   = 100#inf
+    solver.stop_iteration   = inf
     solver.stop_wall_time   = run_time*3600
     report_cadence = 1
     output_time_cadence = out_cadence*atmosphere.buoyancy_time

### 2017-02-15 code/equations.py

@@ -619,7 +619,7 @@ class Polytrope(Atmosphere):
         else:
             if self.constant_kappa:
                 self.rho0.set_scales(1, keep_data=True)
-                if self.poly_m == 1:
+                if np.round(self.poly_m*1e10)/1e10 == 1:
                     chi_l = chi_top/(self.rho0['g'])
                     chi_r = 0
                 else:
@@ -633,7 +633,7 @@ class Polytrope(Atmosphere):
             if self.constant_mu:
                 self.rho0.set_scales(1, keep_data=True)
                 nu_l  = nu_top/(self.z0 - self.z)
-                if self.poly_m == 1:
+                if np.round(self.poly_m*1e10)/1e10 == 1:
                     nu_l  = nu_top/(self.rho0['g'])
                     nu_r = 0
                 else:
@@ -1225,38 +1225,74 @@ class FC_equations_3d(FC_equations):
  
         self._set_subs()
         
+        self.viscous_term_u_l = " nu_l*(Lap(u, u_z) + 1/3*Div(dx(u), dx(v), dx(w_z)))"
+        self.viscous_term_v_l = " nu_l*(Lap(v, v_z) + 1/3*Div(dy(u), dy(v), dy(w_z)))"
+        self.viscous_term_w_l = " nu_l*(Lap(w, w_z) + 1/3*Div(  u_z, v_z, dz(w_z)))"
+        self.viscous_term_u_r = " nu_r*(Lap(u, u_z) + 1/3*Div(dx(u), dx(v), dx(w_z)))"
+        self.viscous_term_v_r = " nu_r*(Lap(v, v_z) + 1/3*Div(dy(u), dy(v), dy(w_z)))"
+        self.viscous_term_w_r = " nu_r*(Lap(w, w_z) + 1/3*Div(  u_z, v_z, dz(w_z)))"
         # here, nu and chi are constants        
-        self.viscous_term_u = " nu*(Lap(u, u_z) + 1/3*Div(dx(u), dx(v), dx(w_z)))"
-        self.viscous_term_v = " nu*(Lap(v, v_z) + 1/3*Div(dy(u), dy(v), dy(w_z)))"
-        self.viscous_term_w = " nu*(Lap(w, w_z) + 1/3*Div(  u_z,   v_z, dz(w_z)))"
[…]

### 2017-02-17 code/FC_poly.py
lots of small tweaks/fixes

@@ -118,7 +118,7 @@ def FC_polytrope(  Rayleigh=1e4, Prandtl=1, aspect_ratio=4,\
     atmosphere.check_atmosphere(make_plots = False, rho=atmosphere.get_full_rho(solver), T=atmosphere.get_full_T(solver))
 
     #Set up timestep defaults
-    max_dt = atmosphere.buoyancy_time*0.25
+    max_dt = atmosphere.buoyancy_time*0.05
     dt = max_dt/5
     if epsilon < 1e-5:
         max_dt = atmosphere.buoyancy_time*0.05

### 2017-02-17 code/equations.py

@@ -34,6 +34,7 @@ class Atmosphere:
                           ny=256, Ly=4,
                           nz=128, Lz=1,
                           grid_dtype=np.float64, comm=MPI.COMM_WORLD, mesh=None):
+        self.mesh=mesh
 
         z_basis = de.Chebyshev('z', nz, interval=[0., Lz], dealias=3/2)
         if self.dimensions > 1:
@@ -1402,7 +1403,7 @@ class FC_polytrope_2d(FC_equations_2d, Polytrope):
                 elif key == 'nu_l':
                     array = self.problem.parameters[key]['g'][0,:] +\
                             self.problem.parameters['nu_r']['g'][0,:]
-                if key == 'del_chi_l':
+                elif key == 'del_chi_l':
                     array = self.problem.parameters[key]['g'][0,:] +\
                             self.problem.parameters['del_chi_r']['g'][0,:]
                 elif key == 'del_nu_l':
@@ -1465,4 +1466,81 @@ class FC_polytrope_3d(FC_equations_3d, Polytrope):
                                                         easy_rho_energy   = easy_rho_energy,
                                                         **kwargs)
         self.test_hydrostatic_balance(T=self.T0, rho=self.rho0)
+
+    def initialize_output(self, solver, data_dir, *args, **kwargs):
+        #Need to think about this more
+        super(FC_polytrope_3d, self).initialize_output(solver, data_dir, *args, **kwargs)
+#        import h5py
+#        import os
+#        from dedalus.core.field import Field
+#        dir = data_dir + '/atmosphere/'
+#        file = dir + 'atmosphere.h5'
+#        if self.domain.dist.comm_cart.rank == 0:
+#            if not os.path.exists('{:s}'.format(dir)):
+#                os.mkdir('{:s}'.format(dir))
+#        if self.domain.dist.comm_cart.rank == 0:
+#            f = h5py.File('{:s}'.format(file), 'w')
+#        for key in self.problem.parameters.keys():
+#            if 'scale' in key:
+#                continue
+#            if type(self.problem.parameters[key]) == Field:
+#                if key == 'chi_l':
+#                    array = self.problem.parameters[key]['g'][0,0,:] +\
+#                            self.problem.parameters['chi_r']['g'][0,0,:]
+#                elif key == 'nu_l':
+#                    array = self.problem.parameters[key]['g'][0,0,:] +\
+#                            self.problem.parameters['nu_r']['g'][0,0,:]
+#                if key == 'del_chi_l':
[…]

### 2017-02-17 code/plotting/base/movie_buddy.py

@@ -174,15 +174,15 @@ class MovieBuddy(PlotBuddy):
 
         local_counts  = np.zeros(1, np.int16)
         global_counts = np.zeros(1, np.int16)
-        local_sum     = np.zeros(1, np.float64)
-        global_sum    = np.zeros(1, np.float64)
 
 
         local_counts[0] = field.shape[0]
 
-        collapsed_profile = np.mean(field, axis=1)
-        collapsed_profile = np.sum(collapsed_profile, axis=0)
-        local_sum[0] = collapsed_profile[0]
+        collapsed_profile   = np.mean(field, axis=1)
+        collapsed_profile   = np.sum(collapsed_profile, axis=0)
+        local_sum           = np.zeros(collapsed_profile.shape, dtype=np.float64)
+        local_sum[:]      = collapsed_profile[:]
+        global_sum          = np.zeros(local_sum.shape, dtype=np.float64)
 
         self.comm.Allreduce(local_counts, global_counts, op=MPI.SUM)
         self.comm.Allreduce(local_sum, global_sum, op=MPI.SUM)

### 2017-02-17 code/plotting/base/plot_buddy_base.py

@@ -141,9 +141,10 @@ class PlotBuddy:
                     np.exp(self.atmosphere['n_rho_cz'])
             self.atmosphere['t_buoy']           = np.sqrt(self.atmosphere['Lz']/\
                     (self.atmosphere['g']*self.atmosphere['epsilon']))
-#            self.atmosphere['t_therm']          = 2*self.atmosphere['Lz']**2 /\
-#                    (self.atmosphere['chi'][int(self.atmosphere['chi'].shape[0]/2)-1]+\
-#                            self.atmosphere['chi'][int(self.atmosphere['chi'].shape[0]/2)])
+            self.atmosphere['t_therm']          = 2*self.atmosphere['Lz']**2 /\
+                    (self.atmosphere['chi'][int(self.atmosphere['chi'].shape[0]/2)-1]+\
+                            self.atmosphere['chi'][int(self.atmosphere['chi'].shape[0]/2)])
+
 
     def _read_atmosphere(self):
         '''
@@ -157,6 +158,12 @@ class PlotBuddy:
                 self.atmosphere[key] = f[key].value
             else:
                 self.atmosphere[key] = f[key][:]
+        nu_top = np.sqrt(self.atmosphere['prandtl']*(self.atmosphere['Lz']**3 * \
+                        np.abs(self.atmosphere['delta_s_atm']/self.atmosphere['Cp'])*\
+                            self.atmosphere['g'])/self.atmosphere['rayleigh'])
+        chi_top = nu_top/self.atmosphere['prandtl']
+        self.atmosphere['chi'] = chi_top/self.atmosphere['rho0']
+        self.atmosphere['nu'] = nu_top/self.atmosphere['rho0']
 
     def _get_all_files(self):
         '''

### 2017-02-17 code/plotting/base/profile_buddy.py

@@ -279,6 +279,114 @@ class ProfileBuddy(PlotBuddy):
                 f2.write(key + '_mean \n')
                 f2.write(key + '_stdev \n')
 
+            if  'enthalpy_flux_z' in self.full_average_profiles.keys() and  \
+                'KE_flux_z' in self.full_average_profiles.keys() and        \
+                'PE_flux_z' in self.full_average_profiles.keys() and        \
+                'viscous_flux_z' in self.full_average_profiles.keys() and   \
+                'kappa_flux_fluc_z' in self.full_average_profiles.keys() and     \
+                'ln_rho1' in self.full_average_profiles.keys() and         \
+                'T1' in self.full_average_profiles.keys():
+                new_nu, means, stdevs = [], [], []
+
+                for i in range(self.full_average_profiles['enthalpy_flux_z'].shape[0]):
+                    T_full = self.full_average_profiles['T1'][i,:]+self.atmosphere['T0']
+                    ln_rho = self.full_average_profiles['ln_rho1'][i,:]+np.log(self.atmosphere['rho0'])
+                    kappa_flux_mean = self.atmosphere['rho0']*self.atmosphere['chi']
+                    rho_full = np.exp(ln_rho)
+                    
+                    
+#                    current_field.set_scales(1, keep_data=False)
+#                    current_field['g'] = ln_rho
+#                    current_field.differentiate('z', out=work_field)
+#                    work_field.set_scales(1, keep_data=True)
+#                    grad_ln_rho = work_field['g']
+
+
+                    F_conv = self.full_average_profiles['enthalpy_flux_z'][i,:]+ \
+                             self.full_average_profiles['KE_flux_z'][i,:]+       \
+                             self.full_average_profiles['PE_flux_z'][i,:]+       \
+                             self.full_average_profiles['viscous_flux_z'][i,:]
+                    F_cond = self.full_average_profiles['kappa_flux_fluc_z'][i,:] + kappa_flux_mean
+
+                    #better to interpolate rho at the edge, but good first start.
+                    rho_t0   = self.atmosphere['rho0'][-1]
+                    rho_ad   = 1#rho_full[-1]
+                    work_field.set_scales(1, keep_data=True)
+                    work_field['g'] = rho_full*self.atmosphere['chi']
+                    work_field.antidifferentiate('z', ('left', 0), out=current_field)
[…]

### 2017-02-17 code/plotting/base/profile_buddy.py
adding script to make parameter space plots

@@ -379,8 +379,8 @@ class ProfileBuddy(PlotBuddy):
                 for i in range(self.full_average_profiles['rho_full'].shape[0]):
                     current_field.set_scales(1, keep_data=False)
                     current_field['g'] = self.full_average_profiles['rho_full'][i,:]
-                    density_contrasts.append( current_field.interpolate(z=self.atmosphere['Lz'])['g'][0]/\
-                                              current_field.interpolate(z=0)['g'][0])
+                    density_contrasts.append( current_field.interpolate(z=0)['g'][0]/\
+                                              current_field.interpolate(z=self.atmosphere['Lz'])['g'][0])
                 f['density_contrasts'] = np.array(density_contrasts, dtype=np.float32)
                     
                     

### 2017-02-17 code/plotting/parameter_space_plots.py

@@ -1,0 +1,237 @@
+"""
+Script for plotting a parameter space study of Nu v Ra.
+
+Usage:
+    parameter_space_plots.py --calculate
+    parameter_space_plots.py
+
+Options:
+    --calculate     If flagged, touch dedalus output files and do time averages.  If not, use post-processed data from before
+"""
+
+
+import matplotlib   
+matplotlib.use('Agg')
+matplotlib.rcParams.update({'font.size': 11})
+import matplotlib.pyplot as plt
+from base.plot_buddy import ProfileBuddy, COLORS
+import os
+import numpy as np
+import glob
+
+COLORS=['orange', 'green', 'indigo']
+MARKERS=['s', 'd', 'o']
+
+golden_ratio=1.618
+FIGWIDTH=3+7.0/16
+FIGHEIGHT=(FIGWIDTH/golden_ratio)*2.25 #2 plots, with padding for x-label.
+
+#MARKERS=['s', 'o', '*']
+
+from mpi4py import MPI
+
+comm = MPI.COMM_WORLD
+
+root_dir='/nobackup/eanders/sp2017/fc_poly_hydro/'
+dirs = []
+
+start_file=50
+n_files=1000
+
+#change to 5
+param_keys = ['Ra', 'eps', 'nrhocz', 'Pr', 'dims']
+keys = ['Nusselt', 'Nusselt_2', 'Nusselt_3', 'Nusselt_4', 'Nusselt_5', 'Nusselt_6', 'Nusselt_7', 'norm_5_kappa_flux_z',  'Re_rms', 'Ma_ad', 'ln_rho1', 'T1',\
+    'rho_full', 'T_full', 'kappa_flux_z', 'enthalpy_flux_z', 'PE_flux_z', 'KE_flux_z', 'viscous_flux_z', 'kappa_flux_fluc_z']
+out_dir_name = '/parameter_profiles/'
+out_file_name= 'parameter'
+
+#Get all of the directories and get info on them.
+
+for i, dir in enumerate(glob.glob('{:s}/*/'.format(root_dir))):
+    tag = dir.split(root_dir)[-1]
+    info = dict()
+    for stem in tag.split('_'):
+        if 'eps' in stem:
+            info['eps'] = float(stem.split('eps')[-1])
+        if 'Ra' in stem:
+            info['Ra']  = float(stem.split('Ra')[-1])
+        if 'nrhocz' in stem:
[…]

### 2017-02-17 tex/nusselt_paper.tex
fixes ascl for dedalus (ben/geoff switch)
fixes the definition of Nu

@@
 \cite{johnston&doering2009, otero&all2002}.
-In stratified convection Nu is more difficult to define, but one of the earliest definitions used
-was \cite{graham1975,hurlburt&all1984}
+In stratified convection Nu is more difficult to define, and we use
+a modified version of a traditional stratified Nusselt number \cite{graham1975,hurlburt&all1984},
 \begin{equation}
-\text{Nu} \equiv \frac{F_{\text{conv, z}} + F_{\text{cond, z}} - F_{\text{A}}}{F_{\text{ref}} - F_{\text{A}}},
+\text{Nu} \equiv \frac{\langle F_{\text{conv, z}} + F_{\text{cond, z}} - F_{\text{A}}\rangle}
+{\langle F_{\text{cond, z}} - F_{\text{A}}\rangle} 
+= 1 + \frac{\langle F_{\text{conv, z}}\rangle}{\langle F_{\text{cond, z}} - F_{\text{A}} \rangle}
 \label{eqn:nusselt}
@@
 z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
-respectively.  $F_{\text{A}} \equiv -\kappa \partial_z T_{\text{ad}}$ 
+respectively and $\langle \rangle$ implies a volume average.  
+$F_{\text{A}} \equiv -\langle\kappa\rangle \partial_z T_{\text{ad}}$ 
 is the adiabatic conductive flux and
 $\partial_z T_{\text{ad}} \equiv - g / c_{P}$ 
-for an ideal gas in hydrostatic equilibrium.
-The conductive flux of a linear profile connecting the upper
-and lower plates
-is $F_{\text{ref}} \equiv \Delta T / L_z$, 
-where $\Delta T \equiv T(L_z) - T(0)$.  $F_{\text{ref}}$ is constant for 
-the choice of fixed-temperature boundaries.
+for an ideal gas in hydrostatic equilibrium.  Here we specify
+$\langle \kappa \rangle = \langle (\rho_{1}/\rho_{0})\kappa_0 \rangle$.
+At large values of $\epsilon$, $\kappa$ evolves significantly as the
+density profile evolves.  At low $\epsilon$, $\langle\kappa\rangle \approx \kappa_0$.
 
@@
 with allocations GID s1647 and GID g26133.
-We thank Axel Brandenburg, Mark Rast, and Jeff Oishi for many useful discussions.
+We thank Axel Brandenburg, Keith Julien, Mark Rast, and Jeff Oishi for many useful discussions.
 

### 2017-02-17 tex/nusselt_paper.tex
adds Re, modifies abstract

@@
 plane-parallel, polytropically stratified atmospheres. 
-We hold the density stratification (\nrho) and Prandtl 
-number (Pr) constant while varying
-Ma and Ra to determine 
+We hold the density stratification ($n_{\rho}$) and Prandtl 
+number (Pr) constant while varying the superadiabaticity
+and Ra.  We find that Ma is primarily controlled by the
+superadiabaticity of the atmosphere.  We also examine
 the behavior of the Nusselt number (Nu), 
-which quantifies the efficiency of convective heat transport.
-As Ra increases and $\text{Ma} \rightarrow 1$, a scaling 
-of Nu $\propto$ Ra$^{0.45}$ is observed.  
-As Ra increases to a regime where Ma $\geq 1$,
-this scaling gives way to a weaker Nu $\propto$ Ra$^{0.19}$. 
-In the regime of Ma $\ll 1$, a consistent
-Nu $\propto$ Ra$^{0.31}$ is retrieved,  reminiscent of the 
-Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
+which quantifies the efficiency of convective heat transport,
+and the Reynolds number (Re), which quantifies how turbulent our
+solutions are.
+%As Ra increases and $\text{Ma} \rightarrow 1$, a scaling 
+%of Nu $\propto$ Ra$^{0.45}$ is observed.  
+%As Ra increases to a regime where Ma $\geq 1$,
+%this scaling gives way to a weaker Nu $\propto$ Ra$^{0.19}$. 
+%In the regime of Ma $\ll 1$, a consistent
+%Nu $\propto$ Ra$^{0.31}$ is retrieved,  reminiscent of the 
+%Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
 \end{abstract}
@@
 \label{sec:intro}
-Convection is essential to heat transport in the cores of high mass stars,
+Convective heat transport is essential
+in the cores of high mass stars,
 the envelopes of low mass stars, and the atmospheres of terrestrial and 
-jovian planets.  The convective dynamics in these astrophysical objects
-are influenced by atmospheric 
-stratification, which is small in some systems (e.g. massive star cores)
-but spans about
-14 density scale heights in the Sun's convective envelope.
+jovian planets.  These astrophysical systems have density stratifications
+ranging from a few density scale heights (e.g. massive star cores)
+up to 14 density scale heights in the convective envelopes of low
+mass stars such as the Sun.
+Atmospheric stratification presumably modifies the fundamental
+dynamics and heat transport mechanisms of these atmospheres.
 Understanding the fundamental
@@
 density profile evolves.  At low $\epsilon$, $\langle\kappa\rangle \approx \kappa_0$.
+In the Boussinesq approximation, under which $\grad S = 0$ only when 
+$\grad T = 0$, this definition reduces the the traditional definition
+of the Nusselt number \cite{otero&all2002, johnston&doering2009}.
 
-We contend that this is the general form of the Nusselt number
-and illustrate this with a few limiting
-cases. Convection eliminates
-entropy stratification.  Under the Boussinesq approximation,
-in which density variations are ignored, entropy stratification 
-is directly proportional to temperature stratification
-and $\partial_z S \rightarrow 0$ when $\partial_z T \rightarrow 0$.  
-The familiar Nu in the RB problem is
-therefore retrieved from (\ref{eqn:nusselt}) because $\partial_z T_{\text{ad}} = 0$.  
-In the case of polytropic convection,  $g \rightarrow 0$
-as $\epsilon \rightarrow m_{\text{ad}} + 1$.
-In this limit, $\partial_z T_{\text{ad}} \rightarrow 0$ and the
-definition of the RB Nu is appropriate to use \cite{brandenburg&all2005}. 
-However, as $\epsilon \rightarrow 0$, 
-$\partial_z T_{0}\rightarrow \partial_z T_{\text{ad}}$ and increasingly
-smaller velocity and thermodynamic perturbations 
-achieve $\partial_z S = 0$ (Fig. \ref{fig:ma_v_eps}a).
-These perturbations carry what little flux exists in 
-excess of the adiabatic, so the removal of 
-$F_{\text{A}}$ in the numerator and denominator of 
-(\ref{eqn:nusselt}) is essential for a reasonable Nu measurement.
+The Reynolds number and Peclet number,
+\begin{equation}
+\text{Re} = \frac{|\bm{u}| L_z}{\nu};\,\,\,\,\text{Pe} = \text{Pr}\,\text{Re},
+\end{equation}
+quantify the importance of advection to diffusion in the evolved
+convective state.  Our choice of $\{\nu,\chi\}\propto \rho_0^{-1}$ drastically changes
+the value of Re between the top and bottom of the atmosphere.  We report values of
+Re at the midplane ($z=L_z/2$) of the atmosphere.
 
@@
 Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
-with allocations GID s1647 and GID g26133.
+with allocations GID s1647 and GID g26133 (\textbf{AND ALSO THE NEW ONE AS OF 2017}).
 We thank Axel Brandenburg, Keith Julien, Mark Rast, and Jeff Oishi for many useful discussions.

### 2017-02-18 code/plotting/parameter_space_plots.py
parameter space plots up and working for all pictures

@@ -18,9 +18,13 @@ from base.plot_buddy import ProfileBuddy, COLORS
 import os
 import numpy as np
 import glob
+from docopt import docopt
 
-COLORS=['orange', 'green', 'indigo']
-MARKERS=['s', 'd', 'o']
+import dedalus.public as de
+
+
+COLORS=['orange', 'green', 'indigo', 'black']
+MARKERS=['s', 'd', '*', 'o']
 
 golden_ratio=1.618
 FIGWIDTH=3+7.0/16
@@ -33,64 +37,69 @@ from mpi4py import MPI
 comm = MPI.COMM_WORLD
 
 root_dir='/nobackup/eanders/sp2017/fc_poly_hydro/'
-dirs = []
+mach_dir='/nobackup/eanders/sp2017/mach_eps/'
 
 start_file=50
 n_files=1000
 
 #change to 5
 param_keys = ['Ra', 'eps', 'nrhocz', 'Pr', 'dims']
-keys = ['Nusselt', 'Nusselt_2', 'Nusselt_3', 'Nusselt_4', 'Nusselt_5', 'Nusselt_6', 'Nusselt_7', 'norm_5_kappa_flux_z',  'Re_rms', 'Ma_ad', 'ln_rho1', 'T1',\
+keys = ['Nusselt', 'Nusselt_5', 'Nusselt_6', 'norm_5_kappa_flux_z',  'Re_rms', 'Ma_ad', 'Ma_iso', 'ln_rho1', 'T1', 'vel_rms',\
     'rho_full', 'T_full', 'kappa_flux_z', 'enthalpy_flux_z', 'PE_flux_z', 'KE_flux_z', 'viscous_flux_z', 'kappa_flux_fluc_z']
 out_dir_name = '/parameter_profiles/'
 out_file_name= 'parameter'
 
-#Get all of the directories and get info on them.
+def get_info(start_dir, keys, out_dir_name, out_file_name):
+    #Get all of the directories and get info on them.
+    dirs = []
 
-for i, dir in enumerate(glob.glob('{:s}/*/'.format(root_dir))):
-    tag = dir.split(root_dir)[-1]
-    info = dict()
-    for stem in tag.split('_'):
-        if 'eps' in stem:
-            info['eps'] = float(stem.split('eps')[-1])
-        if 'Ra' in stem:
-            info['Ra']  = float(stem.split('Ra')[-1])
-        if 'nrhocz' in stem:
-            info['nrhocz'] = float(stem.split('nrhocz')[-1])
[…]

### 2017-02-21 code/equations.py
improvements to diffusivity decomposition (adds flag), improvements to parameter space plots

@@ -566,8 +566,8 @@ class Polytrope(Atmosphere):
             # consider whether to scale nccs involving chi differently (e.g., energy equation)
             self.scale['g']            = (self.z0 - self.z)
             self.scale_continuity['g'] = (self.z0 - self.z)
-            self.scale_momentum['g']   = (self.z0 - self.z)#**np.floor(self.m_cz)
-            self.scale_energy['g']     = (self.z0 - self.z)#**np.floor(self.m_cz)
+            self.scale_momentum['g']   = (self.z0 - self.z)**(1)#**np.floor(self.m_cz)
+            self.scale_energy['g']     = (self.z0 - self.z)**(1)#**np.floor(self.m_cz)
 
         # choose a particular gauge for phi (g*z0); and -grad(phi)=g_vec=-g*z_hat
         # double negative is correct.
@@ -600,7 +600,7 @@ class Polytrope(Atmosphere):
         logger.info("   min_BV_time = {:g}, freefall_time = {:g}, buoyancy_time = {:g}".format(atmosphere.min_BV_time,
                                                                                                atmosphere.freefall_time,
                                                                                                atmosphere.buoyancy_time))
-    def _set_diffusivities(self, Rayleigh=1e6, Prandtl=1):
+    def _set_diffusivities(self, Rayleigh=1e6, Prandtl=1, split_diffusivities=False):
         
         logger.info("problem parameters:")
         logger.info("   Ra = {:g}, Pr = {:g}".format(Rayleigh, Prandtl))
@@ -620,7 +620,7 @@ class Polytrope(Atmosphere):
         else:
             if self.constant_kappa:
                 self.rho0.set_scales(1, keep_data=True)
-                if np.round(self.poly_m*1e10)/1e10 == 1:
+                if not split_diffusivities:
                     chi_l = chi_top/(self.rho0['g'])
                     chi_r = 0
                 else:
@@ -633,8 +633,7 @@ class Polytrope(Atmosphere):
                 logger.info('using constant chi')
             if self.constant_mu:
                 self.rho0.set_scales(1, keep_data=True)
[…]

### 2017-02-21 code/plotting/parameter_space_plots.py

@@ -300,8 +300,8 @@ for label in ax1.get_yticklabels():
 
 fig.savefig('./figs/density_v_ra.png', dpi=1200, bbox_inches='tight')
 
-#for dir in dirs_root:
-#    print('ra: {}, eps: {}'.format(dir[2], dir[1]))
-#    for key in dir[-1].keys():
-#        print(key, dir[-1][key])
-#    
+for dir in dirs_root:
+    print('ra: {}, eps: {}'.format(dir[2], dir[1]))
+    for key in dir[-1].keys():
+        print(key, dir[-1][key])
+    

### 2017-02-21 code/equations.py
makes nu/chi decomposition work at eps = 1

@@ -566,8 +566,8 @@ class Polytrope(Atmosphere):
             # consider whether to scale nccs involving chi differently (e.g., energy equation)
             self.scale['g']            = (self.z0 - self.z)
             self.scale_continuity['g'] = (self.z0 - self.z)
-            self.scale_momentum['g']   = (self.z0 - self.z)**(1)#**np.floor(self.m_cz)
-            self.scale_energy['g']     = (self.z0 - self.z)**(1)#**np.floor(self.m_cz)
+            self.scale_momentum['g']   = (self.z0 - self.z)#**np.floor(self.m_cz)
+            self.scale_energy['g']     = (self.z0 - self.z)#**np.floor(self.m_cz)
 
         # choose a particular gauge for phi (g*z0); and -grad(phi)=g_vec=-g*z_hat
         # double negative is correct.
@@ -624,7 +624,10 @@ class Polytrope(Atmosphere):
                     chi_l = chi_top/(self.rho0['g'])
                     chi_r = 0
                 else:
-                    chi_l = chi_top/(self.z0 - self.z)
+                    if self.poly_m < 1:
+                        chi_l = np.exp(self.n_rho_cz)*chi_top/(self.z0 - self.z)
+                    else:
+                        chi_l = chi_top/(self.z0 - self.z)
                     chi_r = chi_top/(self.rho0['g']) - chi_l
                 logger.info('using constant kappa')
             else:
@@ -637,11 +640,15 @@ class Polytrope(Atmosphere):
                     nu_l  = nu_top/(self.rho0['g'])
                     nu_r = 0
                 else:
-                    nu_l  = nu_top/(self.z0 - self.z)
+                    if self.poly_m < 1:
+                        nu_l  = np.exp(self.n_rho_cz)*nu_top/(self.z0 - self.z)
+                    else:
+                        nu_l  = nu_top/(self.z0 - self.z)
                     nu_r  = nu_top/(self.rho0['g']) - nu_l
                 logger.info('using constant mu')
             else:
                 nu_l  = nu_top
+                nu_r = 0
                 logger.info('using constant nu')
 
       

### 2017-02-22 tex/nusselt_paper.tex
slots new figures into the paper, does not change any of the text

@@
 \begin{figure}[t]
-\includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
+\includegraphics[width=3.4375in]{./figs/ma_v_Ra.png}
 \caption{The maximum value of Ma which has been horizontally 
@@
 \begin{figure}[t]
-\includegraphics[width=3.4375in]{./figs/fluxes_fig.png}
+\includegraphics[width=3.4375in]{./figs/re_and_nu_v_Ra.png}
 \caption{Time-averaged vertical flux profiles ($F_{\text{z}}$)
@@
 In (a), the viscous flux is negligible and is not shown.  The solid black line is
-Nu, the properly normalized sum of all the fluxes \label{fig:flux_profiles} }
+Nu, the properly normalized sum of all the fluxes \label{fig:re_and_nu_v_Ra} }
 \end{figure}
@@
 \begin{figure}[t]
-\includegraphics[width=3.4375in]{./figs/nu_v_ra.png}
+\includegraphics[width=3.4375in]{./figs/density_v_ra.png}
 \caption{Variation of Nu as Ra increases at high and low $\epsilon$. 
@@
  indicate whether or not a solution is well-converged.
-\label{fig:nu_v_ra} }
+\label{fig:nrho_v_ra} }
 \end{figure}

### 2017-02-23 tex/nusselt_paper.tex
fig 3 (re/nu) is now ~finalized (other than calculating the last few data points).  Intro reworked but rough.

@@
 \label{sec:intro}
-Convective heat transport is essential
-in the cores of high mass stars,
-the envelopes of low mass stars, and the atmospheres of terrestrial and 
-jovian planets.  These astrophysical systems have density stratifications
-ranging from a few density scale heights (e.g. massive star cores)
-up to 14 density scale heights in the convective envelopes of low
-mass stars such as the Sun.
-Atmospheric stratification presumably modifies the fundamental
-dynamics and heat transport mechanisms of these atmospheres.
-Understanding the fundamental
-properties of compressible convection in stratified media is essential
-to characterizing systems in astrophysics and planetary sciences.  
-Numerical constraints have often restricted studies of compressible
-convection to moderately high Mach number (Ma), appropriate to regions near 
-the Sun's surface.  Few fundamental properties of
-low Ma convection, which occurs in the deep solar interior, are known.
+Convective dynamics transport energy in stellar and planetary atmospheres.
+In these objects, flows are compressible and
+feel the atmospheric stratification.  While in some systems this stratification is
+negligible, it is significant in regions such as
+the convective envelope of the Sun, which spans 14 density scale heights.
+In the bulk of these systems, flows are at very low Mach Number (Ma), but numerical
+constrainst have restricted most studies of compressible convection to high Ma.
+These studies provide important insight to low temperature, high Ma regions
+near the Sun's surface, but few fundamental
+properties of low Ma convection which characterize deeper motions
+are known.
 
-Early numerical experiments on stratified convection
+%Convective heat transport is essential
+%in the cores of high mass stars,
+%the envelopes of low mass stars, and the atmospheres of terrestrial and 
+%jovian planets.  These astrophysical systems have density stratifications
+%ranging from a few density scale heights (e.g. massive star cores)
+%up to 14 density scale heights in the convective envelopes of low
+%mass stars such as the Sun.
+%Atmospheric stratification presumably modifies the fundamental
+%dynamics and heat transport mechanisms of these atmospheres.
+%Understanding the fundamental
+%properties of compressible convection in stratified media is essential
+%to characterizing systems in astrophysics and planetary sciences.  
+%Numerical constraints have often restricted studies of compressible
+%convection to moderately high Mach number (Ma), appropriate to regions near 
+%the Sun's surface.  Few fundamental properties of
+%low Ma convection, which occurs in the deep solar interior, are known.
+
+In the widely-studied \RB (RB) problem of Boussinesq convection, 
+upflows and downflows are symmetrical and
+the conductive flux ($\propto \grad T$) approaches zero in the convective interior.
+Early numerical experiments of moderate-to-high Ma compressible convection
 in two \cite{graham1975, chan&all1982,
@@
 \cite{cattaneo&all1991, brummell&all1996} dimensions
-revealed a number of basic properties in the moderate-to-high 
-Ma regime. In the widely-studied \RB (hereafter RB) problem, 
-upflows and downflows are symmetrical and
-the conductive flux approaches zero in the convective interior.
-These two hallmark characteristics of RB convection change
-significantly when stratification is included.  Stratified convection 
-exhibits narrow downflow lanes and broad upflow regions.
+revealed that these two hallmark characteristics of RB convection change
+significantly when stratification is included.  Downflow lanes
+become fast and narrow, and upflow lanes turn into broad, slow upwellings.
 Furthermore, the \emph{entropy} gradient is negated by convection 
@@
 
-In RB convection, there exist two primary control parameters: 
+In RB convection, there exist two primary dynamical control parameters: 
 the Rayleigh number (Ra, the ratio of
@@
 (Pr, the ratio of viscous to thermal
-diffusivity).  These numbers coupled with the aspect ratio of 
-the physical domain and the boundary conditions
-determine the dynamics of the convection.  In stratified atmospheres, 
-in addition to specifying the equation of state and
-fundamental properties of the gas, the two control parameters of 
-RB convection are joined by the degree of
-stratification across the domain and the characteristic 
-Ma of the convective flows.  
-Polytropically stratified atmospheres, such as those used in 
-early studies \cite{graham1975, chan&all1982, hurlburt&all1984, 
-cattaneo&all1990, cattaneo&all1991, brummell&all1996}, are an ideal extension of
-RB convection into the stratified realm because the two additional 
-control parameters are directly linked to
-basic properties of the atmosphere.  The density stratification is 
-set by the number of density scale heights (\nrho)
-the atmosphere spans, and Ma is controlled 
-by the superadiabatic excess ($\epsilon$),
-the deviation of the polytropic index from the adiabatic polytropic 
-index \cite{graham1975}.
+diffusivity). These numbers control two useful
+measures of turbulence in the evolved solution:
+the Reynolds
+number (Re, the strength of advection to viscous diffusion)
+and the Peclet number (Pe = Re Pr).  Stratified atmospheres
+with negative entropy gradients are unstable to convection,
+and the magnitude of that entropy gradient, or the superadiabaticity,
+joins Ra and Pr as an important control parameter.  The
+Ma of the evolved solution is primarily controlled by 
+the \emph{superadiabatic excess}, $\epsilon$, which 
+sets the scale of the atmospheric entropy gradient \cite{graham1975}.
+
+%In RB convection, there exist two primary control parameters: 
+%the Rayleigh number (Ra, the ratio of
+%buoyant driving to diffusive damping) and the Prandtl number 
+%(Pr, the ratio of viscous to thermal
+%diffusivity).  These numbers coupled with the aspect ratio of 
+%the physical domain and the boundary conditions
+%determine the dynamics of the convection.  In stratified atmospheres, 
+%in addition to specifying the equation of state and
+%fundamental properties of the gas, the two control parameters of 
+%RB convection are joined by the degree of
+%stratification across the domain and the characteristic 
+%Ma of the convective flows.  
+%Polytropically stratified atmospheres, such as those used in 
+%early studies \cite{graham1975, chan&all1982, hurlburt&all1984, 
+%cattaneo&all1990, cattaneo&all1991, brummell&all1996}, are an ideal extension of
+%RB convection into the stratified realm because the two additional 
+%control parameters are directly linked to
+%basic properties of the atmosphere.  The density stratification is 
+%set by the number of density scale heights (\nrho)
+%the atmosphere spans, and Ma is controlled 
+%by the superadiabatic excess ($\epsilon$),
+%the deviation of the polytropic index from the adiabatic polytropic 
+%index \cite{graham1975}.
 
@@
 two-dimensional, polytropically stratified atmospheres.  
-We vary $\epsilon$ and Ra while holding $\nrho$, Pr, and the aspect ratio
+We vary $\epsilon$ and Ra while holding Pr, aspect ratio, boundary conditions,
+and initial atmospheric stratification
 constant.  We describe experimental methods in section 
@@
 \label{sec:experiment}
-We exmine the simplest stratified extension of RB by studying a
+We examine the simplest stratified extension of RB by studying a
 fluid composed of monatomic ideal gas particles with an adiabatic 

### 2017-02-24 tex/nusselt_paper.tex
restructures experiment and results, need to finalize plots and put them in.

@@
 constrainst have restricted most studies of compressible convection to high Ma.
-These studies provide important insight to low temperature, high Ma regions
+These studies have provided important insight into the low temperature, high Ma region
 near the Sun's surface, but few fundamental
@@
 and the Peclet number (Pe = Re Pr).  Stratified atmospheres
-with negative entropy gradients are unstable to convection,
-and the magnitude of that entropy gradient, or the superadiabaticity,
-joins Ra and Pr as an important control parameter.  The
-Ma of the evolved solution is primarily controlled by 
-the \emph{superadiabatic excess}, $\epsilon$, which 
-sets the scale of the atmospheric entropy gradient \cite{graham1975}.
+with negative entropy gradients are unstable to convection.
+The magnitude of the unstable entropy gradient, or the superadiabaticity,
+joins Ra and Pr as an important control parameter.  This 
+\emph{superadiabatic excess} \cite{graham1975}, $\epsilon$, which 
+sets the scale of the atmospheric entropy gradient
+primarily controls the Ma of the evolved solution.
 
@@
 \label{sec:experiment}
-We examine the simplest stratified extension of RB by studying a
-fluid composed of monatomic ideal gas particles with an adiabatic 
-index of $\gamma = 5/3$ and whose equation of state is $P = R\rho T$. 
-This is consistent with the approach used in earlier work.
-The initial atmosphere is a plane-parallel polytrope in which 
-the gravitational acceleration and conductive flux, 
-$\bm{F}_{\text{cond,0}} = -\kappa \partial_z T_0$, do not vary with depth. To
-achieve the latter condition, both $\kappa$ and $\partial_z T_0$ are constant.
-Under these assumptions, satisfying hydrostatic 
-equilibrium produces a stratification of
+We examine a monatomic ideal gas with an adiabatic index of
+$\gamma = 5/3$ whose equation of state is $P = R\rho T$.
+This is consistent with the approach used in earlier work
+and is the simplest stratified extension of RB.
+We study atmospheres which are initially polytropically stratified,
 \begin{equation}
 \begin{split}
-\rho_0(z) &= \rho_{t}(z_0 - z)^m, \\
-T_0(z)    &= T_{t}(z_0 - z),
+\rho_0(z) &= \rho_{t}(1 + L_z - z)^m, \\
+T_0(z)    &= T_{t}(1 + L_z - z),
 \label{eqn:polytrope}
@@
 \end{equation}
-where $m = m_{\text{ad}} - \epsilon$ is the polytropic index.
-The adiabatic polytropic index is $m_{\text{ad}} \equiv (\gamma-1)^{-1}$, and
-the superadiabatic excess is $\epsilon$ which sets the scale 
-of the entropy gradient ($\partial_z S_0 \propto -\epsilon$).
-A significant advance of this work is the ability to study large 
-and small values of $\epsilon$, as will be discussed.
-Thermodynamic variables are nondimensionalized at the 
-top of the atmosphere as  $P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, 
-requiring $z_0 \equiv L_z + 1$ and $R = T_{t} = \rho_{t} = 1$.
-By this choice, the non-dimensional length scale is the inverse 
-temperature gradient scale and the timescale is the isothermal 
-sound crossing time of this unit length.
-The height $z$ increases upwards within $[0, L_{z}]$, 
-where $L_{z} = e^{n_{\rho}/m} - 1$ is
-determined by $n_\rho$ and $\epsilon$.
-The characteristic timescale of convective dynamics
-is related to the atmospheric buoyancy time, 
-$t_{\text{b}} = \sqrt{L_z/g\epsilon}$, with $g = (m+1)$.
-Throughout this letter, we use buoyancy time units and 
-choose $n_{\rho} = 3$ such that the 
-initial density varies by a factor of 20.
-All atmospheres studied here have an aspect ratio of 4, 
-such that $L_x = 4L_z$.
+where $m$ is the polytropic index and $L_z$ is the depth of the atmosphere.
+The height coordinate, $z$, increases upwards in the range $[0, L_z]$.  We
+specify the depth of the atmosphere, $L_z = e^{n_{\rho}/m} - 1$, by choosing
+the number of density scale heights, $n_{\rho}$, it spans.
+Throughout this letter we set $n_{\rho} = 3$.  Satisfying hydrostatic
+equilibrium sets the value of gravity, $g = R T_t (m + 1)$, which is
+constant with depth.  We study two-dimensional atmospheres with aspect
+ratios of 4 where the $x$ coordinate has the range $[0, 4L_z]$.
 
-The atmospheric diffusivities are primarily controlled by
-the non-dimensional Rayleigh number,
+%
+%We examine the simplest stratified extension of RB by studying a
+%fluid composed of monatomic ideal gas particles with an adiabatic 
+%index of $\gamma = 5/3$ and whose equation of state is $P = R\rho T$. 
+%This is consistent with the approach used in earlier work.
+%The initial atmosphere is a plane-parallel polytrope in which 
+%the gravitational acceleration and conductive flux, 
+%$\bm{F}_{\text{cond,0}} = -\kappa \partial_z T_0$, do not vary with depth. To
+%achieve the latter condition, both $\kappa$ and $\partial_z T_0$ are constant.
+%Under these assumptions, satisfying hydrostatic 
+%equilibrium produces a stratification of
+%\begin{equation}
+%\begin{split}
+%\rho_0(z) &= \rho_{t}(z_0 - z)^m, \\
+%T_0(z)    &= T_{t}(z_0 - z),
+%\label{eqn:polytrope}
+%\end{split}
+%\end{equation}
+%where $m = m_{\text{ad}} - \epsilon$ is the polytropic index.
+%The adiabatic polytropic index is $m_{\text{ad}} \equiv (\gamma-1)^{-1}$, and
+%the superadiabatic excess is $\epsilon$ which sets the scale 
+%of the entropy gradient ($\partial_z S_0 \propto -\epsilon$).
+%A significant advance of this work is the ability to study large 
+%and small values of $\epsilon$, as will be discussed.
+%Thermodynamic variables are nondimensionalized at the 
+%top of the atmosphere as  $P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, 
+%requiring $z_0 \equiv L_z + 1$ and $R = T_{t} = \rho_{t} = 1$.
+%By this choice, the non-dimensional length scale is the inverse 
+%temperature gradient scale and the timescale is the isothermal 
+%sound crossing time of this unit length.
+%The height $z$ increases upwards within $[0, L_{z}]$, 
+%where $L_{z} = e^{n_{\rho}/m} - 1$ is
+%determined by $n_\rho$ and $\epsilon$.
+%The characteristic timescale of convective dynamics
+%is related to the atmospheric buoyancy time, 
+%$t_{\text{b}} = \sqrt{L_z/g\epsilon}$, with $g = (m+1)$.
+%Throughout this letter, we use buoyancy time units and 
+%choose $n_{\rho} = 3$ such that the 
+%initial density varies by a factor of 20.
+%All atmospheres studied here have an aspect ratio of 4, 
+%such that $L_x = 4L_z$.
+%
+
+Convective dynamics are controlled by the superadiabaticity
+of the atmospheres as well as the atmospheric diffusivities.
+The superadiabaticity, or the magnitude of the (negative) 
+entropy gradient, is set by 
+the superadiabatic excess, $\epsilon = m_{ad} - m$, where 
+$m_{ad} = (\gamma - 1)^{-1}$.
+The atmospheric thermal diffusivity, $\chi$,
+and kinematic viscosity (or viscous diffusivity), $\nu$,
+are determined by the Rayleigh number (Ra) and the Prandtl
+number (Pr).  We set $\text{Pr } = \nu/\chi = 1$ throughout
+this work. The polytropic initial conditions are in
+thermal equilibrium, $\kappa_0 \partial_z T_0 =$ const,
+so $\kappa_0 = \chi \rho_0$ must be constant. To keep
+Pr constant with height, we set $\chi = \chi_t/\rho_0$
+and $\nu = \nu_t/\rho_0$.  Under these constraints, the
+diffusivity profiles are specified by choosing Ra
+at the top of the domain,
 \begin{equation}
-\text{Ra} = \frac{g L_z^3 (\Delta S_0 / c_P)}{\nu\chi},
+\text{Ra}_{\text{top}} = \frac{g L_z^3 (\Delta S_0 / c_P)}{\nu_t\chi_t},
 \end{equation}
 where $\Delta S_0 = \epsilon\ln z_0$ is the entropy difference 
-between the top and bottom boundaries, 
+between the top and bottom boundaries and
 $c_P = R\gamma(\gamma-1)^{-1}$ is the specific heat 
-at constant pressure, $\nu$ is the kinematic viscosity 
-(the viscous diffusivity), and $\chi$ is the thermal diffusivity.  
-The relationship between the thermal and viscous diffusivities is
-set by the Prandtl number, $\text{Pr} = \nu/\chi$.   
-The dynamic viscosity, $\mu$, and the thermal conductivity,
-$\kappa$, relate to their corresponding diffusivities such that 
-$\nu \equiv \mu/\rho$ and $\chi \equiv \kappa/\rho$.  We take
-$\mu$ and $\kappa$ to be constant with height.
-As a result, $\text{Ra} \propto (\nu\chi)^{-1} \propto
-\rho^2$.  The atmospheres studied here with $n_{\rho} = 3$ 
-experience an increase in Ra 
-by a factor of 400 across the domain.  This formulation leaves Pr
-constant throughout the depth of the atmosphere. 
-In this letter we impose $\text{Pr} = 1$ and specify Ra at 
-the top of the domain ($z = L_z$).
+at constant pressure. The profiles of $\nu$ and $\chi$ are constant with
+time, and Ra at the bottom of the atmosphere is greater than Ra$_{\text{top}}$
+by a factor of $e^{2n_{\rho}}$.  This formulation leaves
+the thermal conductivity, $\kappa = \rho\chi$ and
+the dynamic viscosity, $\mu = \rho\chi$, free to evolve
+as the density profile changes.
 
-While holding $n_\rho$ and Pr constant, 
-the primary control parameters of convection are $\epsilon$
-and Ra.  We decompose our atmosphere into the background 
-polytrope ($\ln\rho_{0}, T_{0}$) and the fluctuations
-about that background ($\bm{u}, \ln\rho_{1}, T_{1}$),
-which can be large.
-The scaling of the entropy gradient with $\epsilon$
-is reflected in the evolved values of these fluctuations.  For small $\epsilon$,
-evolved values scale as
-$T_1/T_0 \propto \rho_{1}/\rho_{0} \propto$ Ma$^{2} \propto \epsilon$,
-as shown in Fig. \ref{fig:ma_v_eps}.
-
-\begin{figure}[t]
-\includegraphics[width=3.4375in]{./figs/ma_v_Ra.png}
-\caption{The maximum value of Ma which has been horizontally 
-averaged and time averaged for $\geq 100 t_b$, 
-beginning roughly $50t_b$ after
-the start of simulations.  This time average is long 
-enough that the profile is well converged
-and error bars are negligible. (a) For $\epsilon \leq 0.1$,
-a scaling of $\text{Ma }\propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
-at $\text{Ra }= \{10^2, 10^5\}$ exists.
-When $\epsilon \rightarrow m_{\text{ad}}$, 
-large deviations from this power law are seen.  
-(b) At high $\epsilon$, Ma scales as Ra$^{0.28}$ 
-until it reaches the supersonic regime, at which point it
-follows a power law of Ra$^{-0.10}$.  At low $\epsilon$, 
-consistent power laws are achieved throughout all
-values of Ra studied, where 
-$\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
-for $\epsilon = \{10^{-4}, 10^{-7}\}$. 
-\label{fig:ma_v_eps} }
-\end{figure}
-
-We evolve the Fully Compressible Navier-Stokes equations,
+We decompose our thermodynamic variables such that $T = T_0 + T_1$ and
+$\ln\rho = (\ln\rho)_0 + (\ln\rho)_1$, and the velocity $\bm{u}$ has no
+background component.    We evolve the Fully Compressible Navier-Stokes equations,
 \begin{align}
@@
 
-The atmosphere is contained between two 
-impenetrable, stress free, fixed temperature boundaries at
-the top and bottom of the domain such that 
-$w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. The domain
-is horizontally periodic. We utilize the 
+We utilize the 
 Dedalus\footnote{http://dedalus-project.org/} \cite{burns&all2016} pseudospectral framework 
@@
 (\ref{eqn:continuity_eqn})-(\ref{eqn:energy_eqn}) 
-using an implicit-explicit, third-order, four-step 
+using an implicit-explicit (IMEX), third-order, four-step 
 Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
 Variables are time-evolved on a dealiased Chebyshev (vertical)
-and Fourier (horizontal) domain in which the
+and Fourier (horizontal, periodic) domain in which the
 physical grid dimensions are 3/2 the size of the coefficient grid.  
@@
 96x384 grid points at the lowest values of 
-Ra to 1152x4608 grid points at Ra $\geq 10^{7}$. 
+Ra to 1536x6144 grid points at Ra $> 10^{7}$. 
 By using IMEX timestepping, we implicitly step the 
@@
 efficiently study flows at moderate ($\approx 1$) and very low ($\approx 10^{-4}$)
-Ma (Fig. \ref{fig:ma_v_eps}b).  Our equations take the form
-of the FC equations in \cite{lecoanet&all2014}, extended to include variable
-$\nu$ and $\chi$, and we follow the approach there; 
-this IMEX approach has been successfully 
+Ma.  Our equations take the form
+of the FC equations in \cite{lecoanet&all2014}, extended to include
+$\nu$ and $\chi$ which vary with depth, and we follow the approach there.
+This IMEX approach has been successfully 
 tested against a nonlinear benchmark  of the compressible 
 Kelvin-Helmholtz instability \cite{Lecoanet_et_al_2016_KH}.
+
+We impose
+impenetrable, stress free, fixed temperature boundary conditions at
+the top and bottom of the domain such that 
+$w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. 
+$T_1$ is initially filled with
+random white noise whose magnitude is infinitesimal
+compared to $T_0$ and $\epsilon$.
+We filter this noise spectrum in coefficient space, such that 25\% of the coefficients
+have power. We non-dimensionalize our computational domains by setting
+all thermodynamic variables to unity at $z = L_z$ and
+$R = T_t = \rho_t = 1$.  By this choice, the non-dimensional
+grid length scale is the inverse temperature gradient scale and the 
+simulation timescale is the isothermal sound crossing time, $\tau_I$ of this unit length.
+Meaningful convective dynamics occur on timescales of the atmospheric buoyancy time,
+$t_b = \tau_I \sqrt{L_z/g\epsilon}$, and we will report our results in terms of
+buoyancy times.
 
@@
 
-The efficiency of convection is quantified by the Nusselt number.  
+The efficiency of convection is quantified by the Nusselt number (Nu).  
 Nu is well-defined in RB convection
@@
 \begin{equation}
-\text{Nu} \equiv \frac{\langle F_{\text{conv, z}} + F_{\text{cond, z}} - F_{\text{A}}\rangle}
-{\langle F_{\text{cond, z}} - F_{\text{A}}\rangle} 
-= 1 + \frac{\langle F_{\text{conv, z}}\rangle}{\langle F_{\text{cond, z}} - F_{\text{A}} \rangle}
+\text{Nu} \equiv \frac{\langle F_{\text{conv,z}} + F_{\text{cond,z}} - F_{\text{A}}\rangle}
+{\langle F_{\text{cond,z}} - F_{\text{A}}\rangle} 
+= 1 + \frac{\langle F_{\text{conv,z}}\rangle}{\langle F_{\text{cond,z}} - F_{\text{A}} \rangle}
 \label{eqn:nusselt}
@@
 for an ideal gas in hydrostatic equilibrium.  Here we specify
-$\langle \kappa \rangle = \langle (\rho_{1}/\rho_{0})\kappa_0 \rangle$.
-At large values of $\epsilon$, $\kappa$ evolves significantly as the
-density profile evolves.  At low $\epsilon$, $\langle\kappa\rangle \approx \kappa_0$.
+$\langle \kappa \rangle = \langle \rho\chi \rangle$, which is nearly
+$\kappa_0$ when $\epsilon$ is small but can change appreciably for large
+values of $\epsilon$.
 In the Boussinesq approximation, under which $\grad S = 0$ only when 
@@
 
-The Reynolds number and Peclet number,
-\begin{equation}
-\text{Re} = \frac{|\bm{u}| L_z}{\nu};\,\,\,\,\text{Pe} = \text{Pr}\,\text{Re},
-\end{equation}
-quantify the importance of advection to diffusion in the evolved
-convective state.  Our choice of $\{\nu,\chi\}\propto \rho_0^{-1}$ drastically changes
-the value of Re between the top and bottom of the atmosphere.  We report values of
-Re at the midplane ($z=L_z/2$) of the atmosphere.
+\begin{figure}[t]
+\includegraphics[width=3.4375in]{./figs/ma_v_Ra.png}
+\caption{The maximum value of Ma which has been horizontally 
+averaged and time averaged for $\geq 100 t_b$, 
+beginning roughly $50t_b$ after
+the start of simulations.  This time average is long 
+enough that the profile is well converged
+and error bars are negligible. (a) For $\epsilon \leq 0.1$,
+a scaling of $\text{Ma }\propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
+at $\text{Ra }= \{10^2, 10^5\}$ exists.
+When $\epsilon \rightarrow m_{\text{ad}}$, 
+large deviations from this power law are seen.  
+(b) At high $\epsilon$, Ma scales as Ra$^{0.28}$ 
+until it reaches the supersonic regime, at which point it
+follows a power law of Ra$^{-0.10}$.  At low $\epsilon$, 
+consistent power laws are achieved throughout all
+values of Ra studied, where 
+$\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
+for $\epsilon = \{10^{-4}, 10^{-7}\}$. 
+\label{fig:ma_v_eps} }
+\end{figure}
 
-\begin{figure}[b]
+Solutions were time-evolved until a long time average of the fluxes
+showed little
+variance with depth. By performing a linear stability analysis, 
+we determined that the onset of convection
+occurs at $\text{Ra}_c = \{11.15, 10.06, 10.97, 10.97\}$ for $\epsilon = \{1.0, 0.5, 10^{-4}, 10^{-7}\}$ respectively.  
+We studied Rayleigh
+numbers from values at onset to values $\geq 10^6$Ra$_c$ for $\epsilon = 0.5$, up to
+roughly $10^5$Ra$_c$ at $\epsilon = 10^{-4}$, and 
+up to $10^3$Ra$_c$ for $\epsilon = \{1, 10^{-7}\}$.
+
+We find that the Mach number is a strong function of $\epsilon$ and a weak function of 
+Ra, as can be seen in Fig. \ref{fig:ma_v_eps}.  We find that Ma $\propto \epsilon^{1/2}$,
+which we expect at low $\epsilon$ but which seems to persist even as $\epsilon \rightarrow m_{ad}$.
+Furthermore, the evolved thermodynamic variables, $T_1/T_0, \rho_1/\rho_0 \propto \epsilon$,
+are very small for low Ma flows, but are order 1 when $\epsilon$ and Ma approach 1.
+
+\begin{figure}[t]
 \includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
@@
 
-We evolve initial value problems in which $T_1$ is
-filled with infinitesimal, random white noise compared to $T_0$ and $\epsilon$.
-We filter the noise spectrum in coefficient space, such that 25\% of the coefficients
-have power.
-Solutions were time-evolved until a long average of Nu showed little
-variance with depth. By performing a linear stability analysis, 
-we determined that the onset of convection
-occurs at $\text{Ra}_c = \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$ respectively.  
-We studied Rayleigh
-numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = \{0.5, 10^{-4}\}$ 
-and up to $10^3$Ra$_c$ for $\epsilon = 10^{-7}$.
-
 At large Ma ($\epsilon = 0.5$), shock systems form in the upper atmosphere near downflow lanes 
-(Fig. \ref{fig:entropy_snapshots}a) once Ra is sufficiently large.
+(Fig. \ref{fig:entropy_snapshots}b,c) once Ra is sufficiently large.
 These shocks propagate through upflow regions.  
@@
 These shocks heat material entering the downflows, affecting the dynamics and heat transport
-of these systems.
-
-Low Ma flows ($\epsilon = 10^{-4}$)
-have similar bulk thermodynamic structures (Fig. \ref{fig:entropy_snapshots}b)
-to high Ma flows.
-As Ra is increased to large values 
+of these systems.  As Ra is increased to large values 
 (Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
@@
 times before diffusing.
+
+Low Ma flows ($\epsilon = 10^{-4}$)
+have similar bulk thermodynamic structures (Fig. \ref{fig:entropy_snapshots}a)
+to high Ma flows.
 While it has been suggested that pressure forces 
@@
 the stratified medium.  
+Our choice of fixed-temperature boundary conditions allows the flux at the 
+boundaries to vary, so many runs at $\text{Ra }> 10^4$
+and $\epsilon = 10^{-4}$ exhibit long-term states of
+flux disequilibrium.  Roll solutions such as those pictured in Fig. \ref{fig:entropy_snapshots}a
+are punctuated are punctuated by states of vigorous shearing, similar to those previously
+reported in two-dimensional RB convection \cite{goluskin&all2014}.  
+During the roll states, the flux at the lower boundary exceeds that at the upper boundary
+and energy is stored in the system.
+During shearing states, convective transport is suppressed and Nu diminishes while
+the flux at the upper boundary is higher than the flux at the lower boundary.  Long term
+averages over these shearing and non-shearing states produce a flat flux profile which
+can be sensibly analyzed.
 
@@
 \includegraphics[width=3.4375in]{./figs/re_and_nu_v_Ra.png}
-\caption{Time-averaged vertical flux profiles ($F_{\text{z}}$)
-for (a) high and (b) low Ma flows at $\text{Ra }= 10^6$.  
-All fluxes are defined as in (\ref{eqn:energy_eqn_full}) and 
-normalized by $F_{\text{ref}} - F_{\text{A}}$, as in (\ref{eqn:nusselt}).
-The dashed lines correspond to the
-enthalpy flux (orange, positive) and kinetic energy flux (purple, negative).  
-The grey dash-dot line is the
-viscous flux and the green dotted line is the conductive flux with the 
-adiabatic contribution removed. The potential energy flux is negligible and is not shown.
-In (a), the viscous flux is negligible and is not shown.  The solid black line is
-Nu, the properly normalized sum of all the fluxes \label{fig:re_and_nu_v_Ra} }
+\caption{
+Variation of Nu as Ra increases at high and low $\epsilon$. 
+At high $\epsilon$ (purple circles), 
+a clear transition from the subsonic to supersonic regime is evident in the scaling
+of Nu with Ra at $\text{Ra} \approx 10^4$.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
+our observed Nu scalings collapse onto a similar line which is
+indistinguishable from a $\text{Ra}^{2/7}$ scaling, 
+as observed in RB convection \cite{johnston&doering2009}.  Error bars are determined
+ by the square root of the variance of the time-averaged Nu profile with depth and 
+ indicate whether or not a solution is well-converged.
+}
 \end{figure}
 
-At large enough values of Ra for shocks to form,
-high Ma flows exhibit two 
-local maxima in the enthalpy flux and kinetic energy flux (Fig. \ref{fig:flux_profiles}a).
-Shock-heated fluid parcels sometimes gain vorticity as
-they sink into the lower atmosphere.
-This creates deep, rapidly-rotating regions
-of mixing which persist for many overturn times. These ``spinners'' appear to
-influence the dynamics, but their contributions are unclear.
-
-At low Ma, only the deep maximum in enthalpy and kinetic energy fluxes
-is present (Fig. \ref{fig:flux_profiles}b).  
-Our choice of fixed-temperature boundary conditions allows the flux at the 
-boundaries to vary, so many runs at $\text{Ra }> 10^5$
-and $\epsilon = 10^{-4}$ exhibit states in which the flux 
-entering the system at the bottom of the atmosphere 
-exceeds that which leaves at the top.  
-These systems are punctuated by states of vigorous shearing, similar to those previously
-reported in two-dimensional RB convection \cite{goluskin&all2014}.  
-%In these shearing states, flux entering the lower atmosphere approaches $F_\text{A}$,
-%allowing excess energy to escape through the upper boundary.  
-During shearing states, convective transport is suppressed and Nu diminishes while
-excess energy exits the system through the upper boundary.
-A proper long-term average over shearing
-and non-shearing states retrieves an invariant Nu profile throughout the depth
-of the atmosphere. 
-These shearing states will be covered in more detail in a future paper.
+The Reynolds number and Peclet number,
+\begin{equation}
+\text{Re} = \frac{|\bm{u}| L_z}{\nu};\,\,\,\,\text{Pe} = \text{Pr}\,\text{Re},
+\end{equation}
+quantify the importance of advection to diffusion in the evolved
+convective state.  Our choice of $\{\nu,\chi\}\propto \rho_0^{-1}$ drastically changes
+the value of Re between the top and bottom of the atmosphere.  We report values of
+Re at the midplane ($z=L_z/2$) of the atmosphere.
 
@@
 \includegraphics[width=3.4375in]{./figs/density_v_ra.png}
-\caption{Variation of Nu as Ra increases at high and low $\epsilon$. 
-At high $\epsilon$ (purple circles), 
-a clear transition from the subsonic to supersonic regime is evident in the scaling
-of Nu with Ra at $\text{Ra} \approx 10^4$.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
-our observed Nu scalings collapse onto a similar line which is
-indistinguishable from a $\text{Ra}^{2/7}$ scaling, 
-as observed in RB convection \cite{johnston&doering2009}.  Error bars are determined
- by the square root of the variance of the time-averaged Nu profile with depth and 
- indicate whether or not a solution is well-converged.
-\label{fig:nrho_v_ra} }
+\caption{\label{fig:nrho_v_ra} Here's how density stratification changes.}
 \end{figure}

### 2017-02-24 tex/nusselt_paper.tex
pushing up edited version for Ben, the discussion is a mess still.

@@
 \label{sec:intro}
-Convective dynamics transport energy in stellar and planetary atmospheres.
+Convection transports energy in stellar and planetary atmospheres.
 In these objects, flows are compressible and
@@
 \emph{superadiabatic excess} \cite{graham1975}, $\epsilon$, which 
-sets the scale of the atmospheric entropy gradient
+sets the scale of the atmospheric entropy gradient,
 primarily controls the Ma of the evolved solution.
@@
 by a factor of $e^{2n_{\rho}}$.  This formulation leaves
-the thermal conductivity, $\kappa = \rho\chi$ and
+the thermal conductivity, $\kappa = \rho\chi$, and
 the dynamic viscosity, $\mu = \rho\chi$, free to evolve
@@
 We decompose our thermodynamic variables such that $T = T_0 + T_1$ and
-$\ln\rho = (\ln\rho)_0 + (\ln\rho)_1$, and the velocity $\bm{u}$ has no
+$\ln\rho = (\ln\rho)_0 + (\ln\rho)_1$, and the velocity $\bm{u} = u\hat{x} + w\hat{z}$ has no
 background component.    We evolve the Fully Compressible Navier-Stokes equations,
@@
 96x384 grid points at the lowest values of 
-Ra to 1536x6144 grid points at Ra $> 10^{7}$. 
+Ra to 1536x6144 grid points at Ra$_{\text{top}} > 10^{7}$. 
 By using IMEX timestepping, we implicitly step the 
@@
 have power. We non-dimensionalize our computational domains by setting
-all thermodynamic variables to unity at $z = L_z$ and
+all thermodynamic variables to unity at $z = L_z$ by choosing
 $R = T_t = \rho_t = 1$.  By this choice, the non-dimensional
 grid length scale is the inverse temperature gradient scale and the 
-simulation timescale is the isothermal sound crossing time, $\tau_I$ of this unit length.
+simulation timescale is the isothermal sound crossing time, $\tau_I$, of this unit length.
 Meaningful convective dynamics occur on timescales of the atmospheric buoyancy time,
-$t_b = \tau_I \sqrt{L_z/g\epsilon}$, and we will report our results in terms of
-buoyancy times.
+$t_b = \tau_I \sqrt{L_z/g\epsilon}$, and all reported results are taken from time averages
+over many buoyancy times starting 100$t_b$ after the start of our simulations in order to
+assure our results are not biased by the convective transient.
 
@@
 
-The efficiency of convection is quantified by the Nusselt number (Nu).  
-Nu is well-defined in RB convection
-as the total flux normalized by the steady-state conductive flux 
-\cite{johnston&doering2009, otero&all2002}.
-In stratified convection Nu is more difficult to define, and we use
-a modified version of a traditional stratified Nusselt number \cite{graham1975,hurlburt&all1984},
-\begin{equation}
-\text{Nu} \equiv \frac{\langle F_{\text{conv,z}} + F_{\text{cond,z}} - F_{\text{A}}\rangle}
-{\langle F_{\text{cond,z}} - F_{\text{A}}\rangle} 
-= 1 + \frac{\langle F_{\text{conv,z}}\rangle}{\langle F_{\text{cond,z}} - F_{\text{A}} \rangle}
-\label{eqn:nusselt}
-\end{equation}
-where $F_{\text{conv, z}}$ and $F_{\text{cond, z}}$ are the 
-z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
-respectively and $\langle \rangle$ implies a volume average.  
-$F_{\text{A}} \equiv -\langle\kappa\rangle \partial_z T_{\text{ad}}$ 
-is the adiabatic conductive flux and
-$\partial_z T_{\text{ad}} \equiv - g / c_{P}$ 
-for an ideal gas in hydrostatic equilibrium.  Here we specify
-$\langle \kappa \rangle = \langle \rho\chi \rangle$, which is nearly
-$\kappa_0$ when $\epsilon$ is small but can change appreciably for large
-values of $\epsilon$.
-In the Boussinesq approximation, under which $\grad S = 0$ only when 
-$\grad T = 0$, this definition reduces the the traditional definition
-of the Nusselt number \cite{otero&all2002, johnston&doering2009}.
-
 \begin{figure}[t]
 \includegraphics[width=3.4375in]{./figs/ma_v_Ra.png}
-\caption{The maximum value of Ma which has been horizontally 
-averaged and time averaged for $\geq 100 t_b$, 
-beginning roughly $50t_b$ after
-the start of simulations.  This time average is long 
-enough that the profile is well converged
-and error bars are negligible. (a) For $\epsilon \leq 0.1$,
-a scaling of $\text{Ma }\propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
-at $\text{Ra }= \{10^2, 10^5\}$ exists.
-When $\epsilon \rightarrow m_{\text{ad}}$, 
-large deviations from this power law are seen.  
-(b) At high $\epsilon$, Ma scales as Ra$^{0.28}$ 
-until it reaches the supersonic regime, at which point it
-follows a power law of Ra$^{-0.10}$.  At low $\epsilon$, 
-consistent power laws are achieved throughout all
-values of Ra studied, where 
-$\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
-for $\epsilon = \{10^{-4}, 10^{-7}\}$. 
+\caption{The mean adiabatic Mach number of long-time-averaged profiles
+is shown.  Error bars show the full range of Ma over the depth of the
+atmosphere.
+(a) When $Ma < 1$ (below the black horizontal line), Ma $\propto \epsilon^{1/2}$.
+at low ($10^2$) and moderate ($10^5$) values of Ra.
+(b) When Ra is small, Ma $\propto Ra^{1/2}$ (dashed lines).
+Once the mean Ma reaches 1 ($\epsilon = \{0.5, 1\}$), this scaling breaks down
+and nearly all flows in the atmosphere are at Ma = 1.
+At low $\epsilon$, a consistent power law of Ma $\propto Ra^{1/4}$ is retrieved.
 \label{fig:ma_v_eps} }
@@
 we determined that the onset of convection
-occurs at $\text{Ra}_c = \{11.15, 10.06, 10.97, 10.97\}$ for $\epsilon = \{1.0, 0.5, 10^{-4}, 10^{-7}\}$ respectively.  
+occurs at $\text{Ra}_{\text{c,top}} = \{11.15, 10.06, 10.97, 10.97\}$ for $\epsilon = \{1.0, 0.5, 10^{-4}, 10^{-7}\}$ respectively.  
 We studied Rayleigh
-numbers from values at onset to values $\geq 10^6$Ra$_c$ for $\epsilon = 0.5$, up to
-roughly $10^5$Ra$_c$ at $\epsilon = 10^{-4}$, and 
-up to $10^3$Ra$_c$ for $\epsilon = \{1, 10^{-7}\}$.
+numbers from values at onset to values $\geq 10^6$Ra$_{\text{c,top}}$ for $\epsilon = 0.5$, up to
+roughly $10^5$Ra$_{\text{c,top}}$ at $\epsilon = 10^{-4}$, and 
+up to $10^3$Ra$_{\text{c,top}}$ for $\epsilon = \{1, 10^{-7}\}$.
 
 We find that the Mach number is a strong function of $\epsilon$ and a weak function of 
-Ra, as can be seen in Fig. \ref{fig:ma_v_eps}.  We find that Ma $\propto \epsilon^{1/2}$,
-which we expect at low $\epsilon$ but which seems to persist even as $\epsilon \rightarrow m_{ad}$.
+Ra.  When Ma $< 1$, Ma $\propto \epsilon^{1/2}$, but this relation break down as the mean
+Ma approaches 1 and the flows become supersonic (see Fig. \ref{fig:ma_v_eps}a).  At low
+Ra (Ra$_{\text{c,top}} \lesssim 10^4$), Ma $\propto$ Ra$^{1/4}$.  At high epsilon
+($\epsilon = 0.5$, this scaling breaks down near Ra = $10^4$ where the flows become primarily
+supersonic.  The scaling of Ra$^{1/4}$ appears to break down for Ra $\gtrsim 10^5$ at
+$\epsilon = 10^{-4}$, but computational constraints made it restrictively difficult to converge
+many runs in this region of parameter space.
 Furthermore, the evolved thermodynamic variables, $T_1/T_0, \rho_1/\rho_0 \propto \epsilon$,
@@
 
-At large Ma ($\epsilon = 0.5$), shock systems form in the upper atmosphere near downflow lanes 
-(Fig. \ref{fig:entropy_snapshots}b,c) once Ra is sufficiently large.
-These shocks propagate through upflow regions.  
-Such systems were reported in
-both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
-These shocks heat material entering the downflows, affecting the dynamics and heat transport
-of these systems.  As Ra is increased to large values 
-(Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
-no longer span the whole domain but rather break up into 
-small eddies which traverse the domain multiple
-times before diffusing.
-
 Low Ma flows ($\epsilon = 10^{-4}$)
-have similar bulk thermodynamic structures (Fig. \ref{fig:entropy_snapshots}a)
-to high Ma flows.
+display the classic narrow downflow and broad upflow lanes of stratified
+convection (Fig. \ref{fig:entropy_snapshots}a).
 While it has been suggested that pressure forces 
@@
 Our choice of fixed-temperature boundary conditions allows the flux at the 
-boundaries to vary, so many runs at $\text{Ra }> 10^4$
+boundaries to vary, and runs at $\text{Ra }> 10^4$
 and $\epsilon = 10^{-4}$ exhibit long-term states of
 flux disequilibrium.  Roll solutions such as those pictured in Fig. \ref{fig:entropy_snapshots}a
-are punctuated are punctuated by states of vigorous shearing, similar to those previously
+are punctuated by states of vigorous shearing, similar to those previously
 reported in two-dimensional RB convection \cite{goluskin&all2014}.  
@@
 During shearing states, convective transport is suppressed and Nu diminishes while
-the flux at the upper boundary is higher than the flux at the lower boundary.  Long term
-averages over these shearing and non-shearing states produce a flat flux profile which
+the flux at the upper boundary exceeds that at the lower boundary.  Long term
+averages over both of these states produce flat flux profiles which
 can be sensibly analyzed.
+
+At large Ma ($\epsilon = 0.5$), bulk thermodynamic structures are similar but
+shock systems form in the upper atmosphere near downflow lanes 
+(Fig. \ref{fig:entropy_snapshots}b,c) once Ra is sufficiently large.
+Similar shock phenomena were reported in
+both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
+As Ra is increased to large values 
+(Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
+no longer span the whole domain but rather break up into 
+small eddies which traverse the domain multiple
+times before diffusing.
 
@@
 a clear transition from the subsonic to supersonic regime is evident in the scaling
-of Nu with Ra at $\text{Ra} \approx 10^4$.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
+of Nu with Ra at $\text{Ra}_{\text{top}} \approx 10^4$.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
 our observed Nu scalings collapse onto a similar line which is
-indistinguishable from a $\text{Ra}^{2/7}$ scaling, 
+indistinguishable from a $\text{Ra}_{\text{top}}^{2/7}$ scaling, 
 as observed in RB convection \cite{johnston&doering2009}.  Error bars are determined
@@
  indicate whether or not a solution is well-converged.
+ \label{fig:re_and_nu_v_ra}.
 }
 \end{figure}
+
+The efficiency of convection is quantified by the Nusselt number (Nu).  
+Nu is well-defined in RB convection
+as the total flux normalized by the steady-state conductive flux 
+\cite{johnston&doering2009, otero&all2002}.
+In stratified convection Nu is more difficult to define, and we use
+a modified version of a traditional stratified Nusselt number \cite{graham1975,hurlburt&all1984},
+\begin{equation}
+\text{Nu} \equiv \frac{\langle F_{\text{conv,z}} + F_{\text{cond,z}} - F_{\text{A}}\rangle}
+{\langle F_{\text{cond,z}} - F_{\text{A}}\rangle} 
+= 1 + \frac{\langle F_{\text{conv,z}}\rangle}{\langle F_{\text{cond,z}} - F_{\text{A}} \rangle}
+\label{eqn:nusselt}
+\end{equation}
+where $F_{\text{conv,z}}$ and $F_{\text{cond,z}}$ are the 
+z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
+respectively and $\langle \rangle$ are volume averages.  
+$F_{\text{A}} \equiv -\langle\kappa\rangle \partial_z T_{\text{ad}}$ 
+is the conductive flux of the proper corresponding adiabatic atmosphere
+with $\partial_z T_{\text{ad}} \equiv - g / c_{P}$ 
+for an ideal gas in hydrostatic equilibrium.  Here we specify
+$\langle \kappa \rangle = \langle \rho\chi \rangle$, which is nearly
+$\kappa_0$ when $\epsilon$ is small but can change appreciably for large
+values of $\epsilon$.
+In the Boussinesq approximation, under which $\grad S = 0$ only when 
+$\grad T = 0$, this definition reduces the the traditional definition
+of the Nusselt number \cite{otero&all2002, johnston&doering2009}.
+
+The variation of Nu with Ra$_{\text{top}}$ is shown in Fig. \ref{fig:re_and_nu_v_ra}a.
+At low to moderate Ra, Nu $\propto$ Ra$_{\text{top}}^{1/3}$ regardless of $\epsilon$ (NEED TO CITE A
+RB PAPER WITH A 1/3 POWER LAW \cite{ahlers&all2009} maybe?).  At large Ra$_{\text{top}}$, Nu $\propto$ Ra$_{\text{top}}^{1/5}$ at $\epsilon = 0.5$.
+The scaling of Nu with Ra is unclear at low $\epsilon$ (so I'll try to fill in that space with
+data from comps...time to fish it out of Lou and do post-processing hell).
 
@@
 quantify the importance of advection to diffusion in the evolved
-convective state.  Our choice of $\{\nu,\chi\}\propto \rho_0^{-1}$ drastically changes
+convective state.  For Pr = 1, such as in this work, Pe = Re.  
+Our choice of $\{\nu,\chi\}\propto \rho_0^{-1}$ drastically changes
 the value of Re between the top and bottom of the atmosphere.  We report values of
-Re at the midplane ($z=L_z/2$) of the atmosphere.
-
-After appropriately time-averaging the fluxes for $\geq 200 t_b$, 
-a sensible flux average is retrieved.  Nusselt numbers for
-all simulations at low and high Ma are plotted as a function of Ra in Fig. \ref{fig:nu_v_ra}.  
-At $\epsilon = 0.5$, in the near-sonic
-regime ($\text{Ra} \leq 10^4$), the scaling of Nu with Ra is inflated,
-with $\text{Nu} \propto \text{Ra}^{0.45}$, similar to that expected in the
-ultimate regime of RB convection \cite{ahlers&all2009}.  As simulations
-pass into the supersonic regime and shocks start to form near the downflows,
-that scaling drops to $\text{Nu} \propto \text{Ra}^{0.19}$.  
-At $\epsilon = \{10^{-4}, 10^{-7}\}$,
-scaling laws of $\text{Nu} \propto \text{Ra}^{\{0.31, 0.31\}}$ are retrieved. 
-This scaling is indistinguishable from the $\text{Ra}^{2/7}$ found in RB
-convection.
+Re at the midplane ($z=L_z/2$) of the atmosphere in Fig. \ref{fig:re_and_nu_v_ra}b.
+At low Ra$_{\text{top}}$, Re $\propto$ Ra$_{\text{top}}^{3/4}$, but at high Ra$_{\text{top}}$
+where Ma $\geq 1$ for $\epsilon = 0.5$, this scaling gives way to a Re $\propto$ Ra$_{\text{top}}^{1/2}$.
 
@@
 \includegraphics[width=3.4375in]{./figs/density_v_ra.png}
-\caption{\label{fig:nrho_v_ra} Here's how density stratification changes.}
+\caption{\label{fig:nrho_v_ra} We measure the stratification of evolved solutions
+in two ways.  The solid symbols show $\ln(\rho(0)/\rho(L_z))$, or the density contrast
+as measured at the upper and lower boundary.  The empty symbols show 
+$\ln(\text{max}(\rho)/\text{min}(\rho))$. Unsurprisingly, at low $\epsilon$ the evolved
+$n_{\rho}$ is not different from the initial conditions to first order.  At high $\epsilon$,
+the density contrast shrinks, and once the mean Ma approaches 1 the two methods of
+measuring the density stratification bifurcate as density inversions form within the thermal
+boundary layers.}
 \end{figure}
+
+As these simulations evolve and the thermodynamic variables evolve, the density
+profile evolves while remaining in hydrostatic equilibrium to zeroth order.  In 
+Fig. \ref{fig:nrho_v_ra} we show the number of density scale heights present in the
+evolved solution using two measures.  We find that once the average Ma of the domain
+becomes approximately one, large density inversions begin to form in the boundary layers,
+as was reported by \cite{brandenburg&all2005}.  The Regardless, the agreement of Nu
+across $\epsilon$ despite the different effective stratifications felt in the simulations
+is striking.
 
@@
 In this letter we have studied fundamental heat transport by 
-stratified convection in simplified 2-D polytropic
-atmospheres which are specified by two additional parameters, $\nrho$ 
-and $\epsilon$.  We argue that these atmospheres are the natural extension
+stratified convection in simplified 2-D polytropic atmospheres.
+We argue that these atmospheres are the natural extension
 of the RB problem to stratified systems, 
 and are an ideal laboratory for understanding the basic properties of stratified
-convection.  The similarity between the scaling of Nu in RB 
-convection and in our low-$\epsilon$ polytropes suggests 
-that a boundary layer theory such as the Grossmann-Lohse theory for incompressible flows
-could be developed for fully compressible 
-convection in these stratified systems \cite{ahlers&all2009}.
+convection.
 
-The dynamics of these polytropic solutions are complex and time-dependent, even in two dimensions.
 Time-dependent oscillating shear states have developed spontaneously, as seen before in RB convection
 \cite{goluskin&all2014}.  While computationally difficult, the highest values of Ra and the lowest value
-of $\epsilon$ studied here are far from values found in nature.  If the scalings of Nu and Ma
-presented here (Figs.
-\ref{fig:ma_v_eps} \& \ref{fig:nu_v_ra}) hold, then under solar conditions ($\text{Ra }\approx 10^{20}$, $\text{Ma }\approx 10^{-4}$), we expect that $\epsilon \approx 10^{-20}$ and
-$\text{Nu }\approx 10^{6}$.  
-Solar conditions are of course more complicated, as there $\kappa$ is
-set by the radiative opacity, which depends on both $\rho$ and $T$.
+of $\epsilon$ studied here are far from values found in nature.  Future work will aim to better understand the mechanisms of shearing states and
+whether or not these states are attainable in three-dimensional, non-rotating atmospheres.
 
-Future work will aim to better understand the mechanisms of shearing states and
-whether or not these states are attainable in three-dimensional, non-rotating atmospheres.  Our studies
-here will serve as a foundation both for understanding and comparing heat transport in stratified convection
-to that in RB convection \cite{johnston&doering2009}, and for future studies of transport in stratified
-convection in more realistic systems, such as rapidly rotating atmospheres \cite{julien&all2012},
+Furthermore, we have found that the stratification of these atmospheres evolves in a complex
+manner, and future work should aim to understand the importance of changing stratification on
+convective heat transport. Our studies
+here will serve as a foundation both for understanding and 
+comparing heat transport in stratified convection
+to that in RB convection \cite{johnston&doering2009}, 
+and for future studies of transport in stratified
+convection,  both in determining the utility of simplified equation sets (such as the
+anelastic equations) and in coming to understand more realistic systems, 
+such as rapidly rotating atmospheres \cite{julien&all2012},
 atmospheres bounded by stable regions \cite{hurlburt&all1986}, 

### 2017-03-03 code/FC_poly.py
improves parameter space plotting -- bugs still there

@@ -189,7 +189,10 @@ def FC_polytrope(  Rayleigh=1e4, Prandtl=1, aspect_ratio=4,\
     solver.stop_wall_time   = run_time*3600
     report_cadence = 1
     output_time_cadence = out_cadence*atmosphere.buoyancy_time
-    Hermitian_cadence = 100
+    if threeD:
+        Hermitian_cadence = 10
+    else:
+        Hermitian_cadence = 100
     
     logger.info("stopping after {:g} time units".format(solver.stop_sim_time))
     logger.info("output cadence = {:g}".format(output_time_cadence))

### 2017-03-03 code/equations.py

@@ -831,8 +831,10 @@ class FC_equations(Equations):
         # thermal boundary conditions
         if fixed_flux:
             logger.info("Thermal BC: fixed flux (full form)")
-            self.problem.add_bc( "left(T1_z + ln_rho1*T0_z)  =  left((exp(-ln_rho1)-1+ln_rho1)*T0_z)")
-            self.problem.add_bc("right(T1_z + ln_rho1*T0_z)  = right((exp(-ln_rho1)-1+ln_rho1)*T0_z)")
+#            self.problem.add_bc( "left(T1_z + ln_rho1*T0_z)  =  left((exp(-ln_rho1)-1+ln_rho1)*T0_z)")
+            self.problem.add_bc( "left(T1_z) + left(ln_rho1)*left(T0_z)  =  (exp(-left(ln_rho1))-1+left(ln_rho1))*left(T0_z)")
+#            self.problem.add_bc("right(T1_z + ln_rho1*T0_z)  = right((exp(-ln_rho1)-1+ln_rho1)*T0_z)")
+            self.problem.add_bc( "right(T1_z) + right(ln_rho1)*right(T0_z)  =  (exp(-right(ln_rho1))-1+right(ln_rho1))*right(T0_z)")
             self.dirichlet_set.append('T1_z')
             self.dirichlet_set.append('ln_rho1')
         elif fixed_temperature:

### 2017-03-03 code/plotting/base/parameter_space_buddy.py

@@ -1,0 +1,252 @@
+"""
+Script for plotting a parameter space study of Nu v Ra.
+
+Usage:
+    parameter_space_plots.py --calculate
+    parameter_space_plots.py
+
+Options:
+    --calculate     If flagged, touch dedalus output files and do time averages.  If not, use post-processed data from before
+"""
+
+
+import matplotlib   
+matplotlib.use('Agg')
+matplotlib.rcParams.update({'font.size': 11})
+import matplotlib.pyplot as plt
+from profile_buddy import ProfileBuddy, COLORS
+import os
+import numpy as np
+import glob
+from docopt import docopt
+from mpi4py import MPI
+comm_world = MPI.COMM_WORLD
+
+
+import dedalus.public as de
+
+EPSILON_ORDER=[1e-7, 1e0, 1e-4, 5e-1]
+FORCE_WRITE=False
+
+COLORS=['orange', 'red', 'green', 'indigo']
+MARKERS=['s', 'o', 'd', '*']
+MARKERSIZE=[5,4,5,7]
+
+MARKERS_2=['p', '^', '8']
+COLORS_2=['gold', 'peru', 'teal']
+MARKERSIZE_2=[5,5,5]
+
+
+
+
+class ParameterSpaceBuddy():
+    
+    def __init__(self, top_dir, parameters=['eps', 'ra', 'nrhocz', 'pr', 'a'], out_dir_name='/parameter_profiles/', out_file_name='parameter.h5' ):
+        self.top_dir = top_dir
+        for i in range(len(parameters)):
+            parameters[i] = parameters[i].lower()
+        self.parameters = parameters
+        self.out_dir_name = out_dir_name
+        self.out_file_name = out_file_name
+
+
+    def get_info(self):
+        #Get all of the directories and get info on them.
+        dirs = []
+
+        for i, dir in enumerate(glob.glob('{:s}/*/'.format(self.top_dir))):
+            tag = dir.split(self.top_dir)[-1]
+            info = dict()
+            current_info = [dir,]
+            break_loop = False
+            for stem in tag.split('_'):
+                for parameter in self.parameters:
+                    if parameter in stem.lower():
+                        info[parameter] = float(stem.lower().split(parameter)[-1])
+            for parameter in self.parameters:
+                try:
+                    current_info.append(info[parameter])
+                except:
+                    current_info.append(None)
+                    break_loop = True
+                    if comm_world.rank == 0:
[…]

### 2017-03-03 code/plotting/base/plot_buddy_base.py

@@ -4,6 +4,7 @@ import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 from mpl_toolkits.axes_grid1 import make_axes_locatable
+from parameter_space_buddy import *
 
 import numpy as np
 from scipy import stats

### 2017-03-03 code/plotting/base/profile_buddy.py

@@ -287,18 +287,33 @@ class ProfileBuddy(PlotBuddy):
                 'ln_rho1' in self.full_average_profiles.keys() and         \
                 'T1' in self.full_average_profiles.keys() and               \
                 'vel_rms' in self.full_average_profiles.keys():
-                ma_ad_post, means, stdevs = [], [], []
+                ma_ad_post, ma_means, ma_stdevs = [], [], []
+                nu_6_post, nu_6_means, nu_6_stdevs = [], [], []
 
                 for i in range(self.full_average_profiles['enthalpy_flux_z'].shape[0]):
                     T_full = self.full_average_profiles['T1'][i,:]+self.atmosphere['T0']
                     ln_rho = self.full_average_profiles['ln_rho1'][i,:]+np.log(self.atmosphere['rho0'])
-                    kappa_flux_mean = self.atmosphere['rho0']*self.atmosphere['chi']
                     rho_full = np.exp(ln_rho)
+                    kappa_flux_mean = self.atmosphere['rho0']*self.atmosphere['chi']
+                    kappa_ad = self.atmosphere['chi']*rho_full
+                    current_field.set_scales(1, keep_data=False)
+                    current_field['g'] = kappa_ad
+                    current_field.antidifferentiate('z', ('left', 0), out=work_field)
+                    kappa_ad_mean = work_field.interpolate(z=self.atmosphere['Lz'])['g'][0]/self.atmosphere['Lz']
+                    grad_t_ad = self.atmosphere['g']/self.atmosphere['Cp']
+
                     F_conv = self.full_average_profiles['enthalpy_flux_z'][i,:]+ \
                              self.full_average_profiles['KE_flux_z'][i,:]+       \
                              self.full_average_profiles['PE_flux_z'][i,:]+       \
                              self.full_average_profiles['viscous_flux_z'][i,:]
                     F_cond = self.full_average_profiles['kappa_flux_fluc_z'][i,:] + kappa_flux_mean
+
+                    current_field.set_scales(1, keep_data=False)
+                    current_field['g'] = F_cond - kappa_ad_mean*grad_t_ad
+                    current_field.antidifferentiate('z', ('left', 0), out=work_field)
+                    nu_bottom = work_field.interpolate(z=self.atmosphere['Lz'])['g'][0]/self.atmosphere['Lz']
+
+                    Nu_6 = (F_conv + F_cond - kappa_ad_mean*grad_t_ad)/(nu_bottom)
 
[…]

### 2017-03-03 code/plotting/parameter_space_plots.py

@@ -14,7 +14,7 @@ import matplotlib
 matplotlib.use('Agg')
 matplotlib.rcParams.update({'font.size': 11})
 import matplotlib.pyplot as plt
-from base.plot_buddy import ProfileBuddy, COLORS
+from base.plot_buddy import ParameterSpaceBuddy, ProfileBuddy, COLORS
 import os
 import numpy as np
 import glob
@@ -22,84 +22,65 @@ from docopt import docopt
 
 import dedalus.public as de
 
+EPSILON_ORDER=[1e-7, 1e0, 1e-4, 5e-1]
+FORCE_WRITE=False
 
-COLORS=['orange', 'green', 'indigo', 'black']
-MARKERS=['s', 'd', '*', 'o']
-
+def line_leastsq(x, y, y_uncert):
+    x = np.copy(x)
+    min_x = np.min(x)
+    max_x = np.max(x)
+    x_sub = 0
+    if min_x != 0:
+        if y_uncert[0] > y_uncert[-1]:
+            x_sub = max_x
+        else:
+            x_sub = min_x
+        x -= x_sub
+    s = np.sum(1/y_uncert**2)#/max_y_u**2
+    sx = np.sum(x / y_uncert**2)#/max_y_u**2
+    sy = np.sum(y / y_uncert**2)#/max_y_u
+    sx2 = np.sum(x**2 / y_uncert**2)#/max_y_u**2
+    sxy = np.sum(x*y / y_uncert**2)#/max_y_u
+    
+    Delta = (s*sx2 - sx**2) 
+    slope = (s * sxy - sx * sy) / Delta 
+    intercept = (sx2*sy - sx*sxy) / Delta - x_sub*slope
+    p = np.array((slope, intercept))
+    covar = np.array(((s, -sx),(-sx, sx2)))/Delta
+    return p, covar
+START_FILE=50
+N_FILES=1000
 golden_ratio=1.618
 FIGWIDTH=3+7.0/16
 FIGHEIGHT=(FIGWIDTH/golden_ratio)*2.25 #2 plots, with padding for x-label.
 
-#MARKERS=['s', 'o', '*']
 
 from mpi4py import MPI
-
 comm = MPI.COMM_WORLD
 
+
+#root_dir='/nobackup/eanders/sp2017/comps_data/'
 root_dir='/nobackup/eanders/sp2017/fc_poly_hydro/'
[…]

### 2017-03-03 tex/nusselt_paper.tex

@@
 shock systems form in the upper atmosphere near downflow lanes 
-(Fig. \ref{fig:entropy_snapshots}b,c) once Ra is sufficiently large.
+once Ra is sufficiently large  (Fig. \ref{fig:entropy_snapshots}b,c).
 Similar shock phenomena were reported in
@@
 In the Boussinesq approximation, under which $\grad S = 0$ only when 
-$\grad T = 0$, this definition reduces the the traditional definition
+$\grad T = 0$, this definition reduces to the traditional definition
 of the Nusselt number \cite{otero&all2002, johnston&doering2009}.
@@
 The variation of Nu with Ra$_{\text{top}}$ is shown in Fig. \ref{fig:re_and_nu_v_ra}a.
-At low to moderate Ra, Nu $\propto$ Ra$_{\text{top}}^{1/3}$ regardless of $\epsilon$ (NEED TO CITE A
+At low to moderate Ra$_{\text{top}}$, Nu $\propto$ Ra$_{\text{top}}^{1/3}$ regardless of $\epsilon$ (NEED TO CITE A
 RB PAPER WITH A 1/3 POWER LAW \cite{ahlers&all2009} maybe?).  At large Ra$_{\text{top}}$, Nu $\propto$ Ra$_{\text{top}}^{1/5}$ at $\epsilon = 0.5$.
-The scaling of Nu with Ra is unclear at low $\epsilon$ (so I'll try to fill in that space with
+The scaling of Nu with Ra$_{\text{top}}$ is unclear at low $\epsilon$ (so I'll try to fill in that space with
 data from comps...time to fish it out of Lou and do post-processing hell).
@@
 At low Ra$_{\text{top}}$, Re $\propto$ Ra$_{\text{top}}^{3/4}$, but at high Ra$_{\text{top}}$
-where Ma $\geq 1$ for $\epsilon = 0.5$, this scaling gives way to a Re $\propto$ Ra$_{\text{top}}^{1/2}$.
+where the average Ma $\approx 1$ for $\epsilon = 0.5$, this scaling gives way to a Re $\propto$ Ra$_{\text{top}}^{1/2}$.
 
@@
 
-As these simulations evolve and the thermodynamic variables evolve, the density
+As the thermodynamic variables converge to their steady state values, the density
 profile evolves while remaining in hydrostatic equilibrium to zeroth order.  In 
@@
 
+At low Ra and Ma, the scaling of Nu with Ra is reminiscent of RB convection.  However,
+at high Ra and Ma, the scaling breaks down to a Ra$^{1/5}$ scaling unlike what is seen
+in Boussinesq convection.  Similarly, the Reynolds number switches from a Ra$^{3/4}$ to
+a Ra$^{1/2}$ scaling in this regime shift.  It is interesting that both of these
+scaling laws turn over by roughly a factor of 2/3.
+
 Time-dependent oscillating shear states have developed spontaneously, as seen before in RB convection
@@
 and for future studies of transport in stratified
-convection,  both in determining the utility of simplified equation sets (such as the
-anelastic equations) and in coming to understand more realistic systems, 
+convection.  These results can be used to determine if simplified equation sets, 
+such as the anelastic equations, carry heat in the same manner as the FC equations.
+This work will also be useful in coming to understand more realistic systems, 
 such as rapidly rotating atmospheres \cite{julien&all2012},

### 2017-03-03 code/equations.py
fixed parameter space plotting, woot

@@ -1513,14 +1513,24 @@ class FC_polytrope_3d(FC_equations_3d, Polytrope):
 #                self.problem.parameters[key].set_scales(1, keep_data=True)
 #                this_chunk      = np.zeros(self.nz)
 #                global_chunk    = np.zeros(self.nz)
+#                comm = None
 #                if self.mesh != None:
-#                    n_per_cpu       = int(self.nz/self.mesh[-1])
+#                    comm = self.domain.dist.comm_cart.Create(self.domain.dist.comm_cart.Get_group().Incl(np.arange(self.mesh[-1])))
+#                    n_per_cpu       = int(np.floor(self.nz/self.mesh[-1]))
 #                else:
-#                    n_per_cpu       = int(self.nz/self.domain.dist.comm_cart.size)
-#                this_chunk[ self.domain.dist.comm_cart.rank*(n_per_cpu):\
-#                            (self.domain.dist.comm_cart.rank+1)*(n_per_cpu)] = \
-#                                    self.problem.parameters[key]['g'][0,0,:]
-#                self.domain.dist.comm_cart.Allreduce(this_chunk, global_chunk, op=MPI.SUM)
+#                    comm = self.domain.dist.comm_cart
+#                    n_per_cpu       = int(np.floor(self.nz/self.domain.dist.comm_cart.size))
+#                extra_prev = 0
+#                if comm.rank < comm.size:
+#                    if np.mod(self.nz, n_per_cpu) > comm.rank:
+#                        n_per_cpu += 1
+#                    else:
+#                        extra_prev += np.mod(self.nz, n_per_cpu)
+#
+#                    this_chunk[ comm.rank*(n_per_cpu)+extra_prev:\
+#                                (comm.rank+1)*(n_per_cpu)+extra_prev] = \
+#                                        self.problem.parameters[key]['g'][0,0,:]
+#                    comm.Allreduce(this_chunk, global_chunk, op=MPI.SUM)
 #                if self.domain.dist.comm_cart.rank == 0:
 #                    if key != 'chi_l' and key != 'nu_l' and key != 'del_chi_l' and key != 'del_nu_l':
 #                        f[key] = global_chunk

### 2017-03-03 code/plotting/base/parameter_space_buddy.py

@@ -54,11 +54,12 @@ class ParameterSpaceBuddy():
         #Get all of the directories and get info on them.
         dirs = []
 
-        for i, dir in enumerate(glob.glob('{:s}/*/'.format(self.top_dir))):
+        for i, dir in enumerate(glob.glob('{:s}/FC*/'.format(self.top_dir))):
             tag = dir.split(self.top_dir)[-1]
             info = dict()
             current_info = [dir,]
             break_loop = False
+            print(tag)
             for stem in tag.split('_'):
                 for parameter in self.parameters:
                     if parameter in stem.lower():
@@ -93,7 +94,7 @@ class ParameterSpaceBuddy():
         base_n_files = n_files
 
         for i, dir in enumerate(important_dirs):
-            if np.mod(i, comm.size) != comm.rank:
+            if np.mod(i, comm_world.size) != comm_world.rank:
                 continue
             try:
                 comm_new = comm.Create(comm.Get_group().Incl(np.ones(1)*comm.rank))
@@ -162,7 +163,6 @@ class ParameterSpaceBuddy():
         data = self.dir_info
 
         index = self.parameters.index(grouping.lower())+1
-        print(grouping, index)
         if grouping == 'eps':
             groups = np.unique(np.array(data)[:,index])
             groups = EPSILON_ORDER
@@ -185,13 +185,11 @@ class ParameterSpaceBuddy():
         plot_points = dict()
 
         for i, group in enumerate(groups):
-            print(group, 'here')
             x_vals = []
             x_err  = []
             y_vals = []
             y_err  = []
             for dir in data:
-                print(group, dir[index])
                 if group != dir[index] or dir[-1] == {}:
                     continue
                 x_vals.append(dir[x_key])
@@ -199,7 +197,6 @@ class ParameterSpaceBuddy():
 
                 y_vals.append(dir[-1][y_key][0])
                 y_err.append((dir[-1][y_key][1], dir[-1][y_key][2]))
-            print(x_vals, x_err)
             if len(x_vals) == 0:
                 continue
             x_vals, x_err, y_vals, y_err = zip(*sorted(zip(x_vals, x_err, y_vals, y_err)))
@@ -244,7 +241,6 @@ class ParameterSpaceBuddy():
                 kwargs['markerfacecolor'] = 'None'
                 kwargs['markeredgecolor'] = colors[i]
[…]

### 2017-03-03 code/plotting/parameter_space_plots.py

@@ -96,6 +96,7 @@ for dir in root_buddy.dir_info:
     print('ra: {}, eps: {}'.format(dir[2], dir[1]))
     for key in dir[-1].keys():
         print(key, dir[-1][key])
+    print('  ')
 
 dirs_root = root_buddy.dir_info
 dirs_mach = mach_buddy.dir_info
@@ -108,7 +109,6 @@ ax2 = fig.add_subplot(2,1,2)
 ax1.grid(which='major')
 ax1, data, groups = root_buddy.plot_parameter_space_comparison(ax1, 'Ra', 'Nusselt_6', grouping='eps')
 
-print(ax1, data, groups)
 x1s = np.logspace(1.5, 4, 100)
 x1s_long = np.logspace(2, 8, 100)
 y1s = (3/5)*x1s**(1/3)

### 2017-03-07 tex/nusselt_paper.tex
makes tex file mostly fit into an 80-column terminal.  Adds King&all ref

@@
 In these objects, flows are compressible and
-feel the atmospheric stratification.  While in some systems this stratification is
-negligible, it is significant in regions such as
+feel the atmospheric stratification.  While in some systems this stratification 
+is negligible, it is significant in regions such as
 the convective envelope of the Sun, which spans 14 density scale heights.
-In the bulk of these systems, flows are at very low Mach Number (Ma), but numerical
-constrainst have restricted most studies of compressible convection to high Ma.
-These studies have provided important insight into the low temperature, high Ma region
-near the Sun's surface, but few fundamental
+In the bulk of these systems, flows are at very low Mach Number (Ma), 
+but numerical constraints have restricted most studies of 
+compressible convection to high Ma.
+These studies have provided important insight into the low temperature, 
+high Ma region near the Sun's surface, but few fundamental
 properties of low Ma convection which characterize deeper motions
@@
 upflows and downflows are symmetrical and
-the conductive flux ($\propto \grad T$) approaches zero in the convective interior.
+the conductive flux ($\propto \grad T$) approaches 
+zero in the convective interior.
 Early numerical experiments of moderate-to-high Ma compressible convection
@@
 constant.  We describe experimental methods in section 
-\ref{sec:experiment}, including the construction of atmospheres, equations, and numerical methods.  
-Results are described in section \ref{sec:results} and their implications are discussed
+\ref{sec:experiment}, including the construction of atmospheres, 
+equations, and numerical methods.  
+Results are described in section \ref{sec:results} 
+and their implications are discussed
 in section \ref{sec:discussion}.
@@
 We decompose our thermodynamic variables such that $T = T_0 + T_1$ and
-$\ln\rho = (\ln\rho)_0 + (\ln\rho)_1$, and the velocity $\bm{u} = u\hat{x} + w\hat{z}$ has no
-background component.    We evolve the Fully Compressible Navier-Stokes equations,
+$\ln\rho = (\ln\rho)_0 + (\ln\rho)_1$, 
+and the velocity $\bm{u} = u\hat{x} + w\hat{z}$ 
+has no background component.    
+We evolve the Fully Compressible Navier-Stokes equations,
 \begin{align}
@@
 We utilize the 
-Dedalus\footnote{http://dedalus-project.org/} \cite{burns&all2016} pseudospectral framework 
- to time-evolve  
+Dedalus\footnote{http://dedalus-project.org/} \cite{burns&all2016} 
+pseudospectral framework to time-evolve  
 (\ref{eqn:continuity_eqn})-(\ref{eqn:energy_eqn}) 
@@
 stiff linear acoustic wave contribution and are able to
-efficiently study flows at moderate ($\approx 1$) and very low ($\approx 10^{-4}$)
-Ma.  Our equations take the form
+efficiently study flows at moderate ($\approx 1$) 
+and very low ($\approx 10^{-4}$) Ma.  Our equations take the form
 of the FC equations in \cite{lecoanet&all2014}, extended to include
@@
 
-We impose
-impenetrable, stress free, fixed temperature boundary conditions at
+We impose impenetrable, stress free, fixed temperature boundary conditions at
 the top and bottom of the domain such that 
@@
 compared to $T_0$ and $\epsilon$.
-We filter this noise spectrum in coefficient space, such that 25\% of the coefficients
+We filter this noise spectrum in coefficient space, 
+such that 25\% of the coefficients
 have power. We non-dimensionalize our computational domains by setting
@@
 grid length scale is the inverse temperature gradient scale and the 
-simulation timescale is the isothermal sound crossing time, $\tau_I$, of this unit length.
-Meaningful convective dynamics occur on timescales of the atmospheric buoyancy time,
-$t_b = \tau_I \sqrt{L_z/g\epsilon}$, and all reported results are taken from time averages
-over many buoyancy times starting 100$t_b$ after the start of our simulations in order to
+simulation timescale is the isothermal sound crossing time, 
+$\tau_I$, of this unit length.
+Meaningful convective dynamics occur on 
+timescales of the atmospheric buoyancy time,
+$t_b = \tau_I \sqrt{L_z/g\epsilon}$, 
+and all reported results are taken from time averages
+over many buoyancy times starting 100$t_b$ 
+after the start of our simulations in order to
 assure our results are not biased by the convective transient.
@@
 atmosphere.
-(a) When $Ma < 1$ (below the black horizontal line), Ma $\propto \epsilon^{1/2}$.
-at low ($10^2$) and moderate ($10^5$) values of Ra.
+(a) When $Ma < 1$ (below the black horizontal line), 
+Ma $\propto \epsilon^{1/2}$.
+t low ($10^2$) and moderate ($10^5$) values of Ra.
 (b) When Ra is small, Ma $\propto Ra^{1/2}$ (dashed lines).
@@
 we determined that the onset of convection
-occurs at $\text{Ra}_{\text{c,top}} = \{11.15, 10.06, 10.97, 10.97\}$ for $\epsilon = \{1.0, 0.5, 10^{-4}, 10^{-7}\}$ respectively.  
+occurs at $\text{Ra}_{\text{c,top}} = \{11.15, 10.06, 10.97, 10.97\}$ 
+for $\epsilon = \{1.0, 0.5, 10^{-4}, 10^{-7}\}$ respectively.  
 We studied Rayleigh
-numbers from values at onset to values $\geq 10^6$Ra$_{\text{c,top}}$ for $\epsilon = 0.5$, up to
+numbers from values at onset to values $\geq 10^6$Ra$_{\text{c,top}}$ 
+for $\epsilon = 0.5$, up to
 roughly $10^5$Ra$_{\text{c,top}}$ at $\epsilon = 10^{-4}$, and 
@@
 
-We find that the Mach number is a strong function of $\epsilon$ and a weak function of 
-Ra.  When Ma $< 1$, Ma $\propto \epsilon^{1/2}$, but this relation break down as the mean
+We find that the Mach number is a strong function of 
+$\epsilon$ and a weak function of Ra.  
+When Ma $< 1$, Ma $\propto \epsilon^{1/2}$, 
+but this relation break down as the mean
 Ma approaches 1 and the flows become supersonic (see Fig. \ref{fig:ma_v_eps}a).  At low
-Ra (Ra$_{\text{c,top}} \lesssim 10^4$), Ma $\propto$ Ra$^{1/4}$.  At high epsilon
-($\epsilon = 0.5$, this scaling breaks down near Ra = $10^4$ where the flows become primarily
-supersonic.  The scaling of Ra$^{1/4}$ appears to break down for Ra $\gtrsim 10^5$ at
-$\epsilon = 10^{-4}$, but computational constraints made it restrictively difficult to converge
+Ra (Ra$_{\text{c,top}} \lesssim 10^4$), 
+Ma $\propto$ Ra$^{1/4}$.  At high epsilon
+($\epsilon = 0.5$, this scaling breaks down near 
+Ra = $10^4$ where the flows become primarily
+supersonic.  The scaling of 
+Ra$^{1/4}$ appears to break down for Ra $\gtrsim 10^5$ at
+$\epsilon = 10^{-4}$, 
+but computational constraints made it restrictively difficult to converge
 many runs in this region of parameter space.
-Furthermore, the evolved thermodynamic variables, $T_1/T_0, \rho_1/\rho_0 \propto \epsilon$,
-are very small for low Ma flows, but are order 1 when $\epsilon$ and Ma approach 1.
+Furthermore, the evolved thermodynamic variables, 
+$T_1/T_0, \rho_1/\rho_0 \propto \epsilon$,
+are very small for low Ma flows, 
+but are order 1 when $\epsilon$ and Ma approach 1.
 
@@
 \caption{Characteristic entropy fluctuations in evolved flows. 
-The time- and horizontally-averaged profile is removed in all cases.  (a) At high
-$\epsilon$, shock systems form near the upper downflow lanes ($x \approx 45, z \approx 15-19$)
-at sufficiently high Ra.
+The time- and horizontally-averaged profile is removed in all cases.  
+(a) At high $\epsilon$, shock systems form near the upper downflow lanes 
+($x \approx 45, z \approx 15-19$) at sufficiently high Ra.
 Shock-heated fluid then flows into the downflows as the shocks propagate across upflows.
 (b) At low $\epsilon$ but at the same Ra, shock systems are absent, 
-but otherwise the dynamics are similar.  (c) As Ra is increased, downflows no longer span
-the entirety of the domain and individual small eddies are responsible for carrying the flux.
+but otherwise the dynamics are similar.  
+(c) As Ra is increased, downflows no longer span
+the entirety of the domain and individual 
+small eddies are responsible for carrying the flux.
 \label{fig:entropy_snapshots} }
@@
 and $\epsilon = 10^{-4}$ exhibit long-term states of
-flux disequilibrium.  Roll solutions such as those pictured in Fig. \ref{fig:entropy_snapshots}a
+flux disequilibrium.  
+Roll solutions such as those pictured in Fig. \ref{fig:entropy_snapshots}a
 are punctuated by states of vigorous shearing, similar to those previously
 reported in two-dimensional RB convection \cite{goluskin&all2014}.  
-During the roll states, the flux at the lower boundary exceeds that at the upper boundary
+During the roll states, 
+the flux at the lower boundary exceeds that at the upper boundary
 and energy is stored in the system.
-During shearing states, convective transport is suppressed and Nu diminishes while
+During shearing states, 
+convective transport is suppressed and Nu diminishes while
 the flux at the upper boundary exceeds that at the lower boundary.  Long term
@@
 Similar shock phenomena were reported in
-both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
+both two \cite{cattaneo&all1990} and 
+three \cite{malagoli&all1990} dimensional polytropic simulations previously.
 As Ra is increased to large values 
@@
 At high $\epsilon$ (purple circles), 
-a clear transition from the subsonic to supersonic regime is evident in the scaling
-of Nu with Ra at $\text{Ra}_{\text{top}} \approx 10^4$.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
+a clear transition from the subsonic to supersonic regime 
+is evident in the scaling
+of Nu with Ra at $\text{Ra}_{\text{top}} \approx 10^4$.  
+In the low $\epsilon$ regime (green diamonds and yellow squares), 
 our observed Nu scalings collapse onto a similar line which is
 indistinguishable from a $\text{Ra}_{\text{top}}^{2/7}$ scaling, 
-as observed in RB convection \cite{johnston&doering2009}.  Error bars are determined
- by the square root of the variance of the time-averaged Nu profile with depth and 
- indicate whether or not a solution is well-converged.
+as observed in RB convection \cite{johnston&doering2009}.  
+Errors bars indicate the properly normalized range of the
+value of Nu as a function of depth and
+large error bars indicate a poorly converged solution.
  \label{fig:re_and_nu_v_ra}.
@@
 In stratified convection Nu is more difficult to define, and we use
-a modified version of a traditional stratified Nusselt number \cite{graham1975,hurlburt&all1984},
+a modified version of a traditional stratified Nusselt number 
+\cite{graham1975,hurlburt&all1984},
 \begin{equation}
@@
 
-The variation of Nu with Ra$_{\text{top}}$ is shown in Fig. \ref{fig:re_and_nu_v_ra}a.
-At low to moderate Ra$_{\text{top}}$, Nu $\propto$ Ra$_{\text{top}}^{1/3}$ regardless of $\epsilon$ (NEED TO CITE A
-RB PAPER WITH A 1/3 POWER LAW \cite{ahlers&all2009} maybe?).  At large Ra$_{\text{top}}$, Nu $\propto$ Ra$_{\text{top}}^{1/5}$ at $\epsilon = 0.5$.
-The scaling of Nu with Ra$_{\text{top}}$ is unclear at low $\epsilon$ (so I'll try to fill in that space with
+The variation of Nu with Ra$_{\text{top}}$ is shown in 
+Fig. \ref{fig:re_and_nu_v_ra}a.
+At low to moderate Ra$_{\text{top}}$, 
+Nu $\propto$ Ra$_{\text{top}}^{1/3}$ regardless of $\epsilon$,
+as predicted by classical \RB theory \cite{king&all2012}.
+At large Ra$_{\text{top}}$, Nu $\propto$ Ra$_{\text{top}}^{1/5}$ 
+at $\epsilon = 0.5$.
+The scaling of Nu with Ra$_{\text{top}}$ 
+is unclear at low $\epsilon$ (so I'll try to fill in that space with
 data from comps...time to fish it out of Lou and do post-processing hell).
@@
 the value of Re between the top and bottom of the atmosphere.  We report values of
-Re at the midplane ($z=L_z/2$) of the atmosphere in Fig. \ref{fig:re_and_nu_v_ra}b.
-At low Ra$_{\text{top}}$, Re $\propto$ Ra$_{\text{top}}^{3/4}$, but at high Ra$_{\text{top}}$
-where the average Ma $\approx 1$ for $\epsilon = 0.5$, this scaling gives way to a Re $\propto$ Ra$_{\text{top}}^{1/2}$.
+Re at the midplane ($z=L_z/2$) of the atmosphere in
+Fig. \ref{fig:re_and_nu_v_ra}b.
+At low Ra$_{\text{top}}$, Re $\propto$ Ra$_{\text{top}}^{3/4}$, but at high 
+Ra$_{\text{top}}$ where the average Ma $\approx 1$ for $\epsilon = 0.5$, 
+this scaling gives way to a Re $\propto$ Ra$_{\text{top}}^{1/2}$.
 
@@
 \includegraphics[width=3.4375in]{./figs/density_v_ra.png}
-\caption{\label{fig:nrho_v_ra} We measure the stratification of evolved solutions
-in two ways.  The solid symbols show $\ln(\rho(0)/\rho(L_z))$, or the density contrast
+\caption{\label{fig:nrho_v_ra} We measure the stratification of 
+evolved solutions
+in two ways.  The solid symbols show $\ln(\rho(0)/\rho(L_z))$, 
+or the density contrast
 as measured at the upper and lower boundary.  The empty symbols show 
-$\ln(\text{max}(\rho)/\text{min}(\rho))$. Unsurprisingly, at low $\epsilon$ the evolved
-$n_{\rho}$ is not different from the initial conditions to first order.  At high $\epsilon$,
-the density contrast shrinks, and once the mean Ma approaches 1 the two methods of
-measuring the density stratification bifurcate as density inversions form within the thermal
+$\ln(\text{max}(\rho)/\text{min}(\rho))$. 
+Unsurprisingly, at low $\epsilon$ the evolved
+$n_{\rho}$ is not different from the initial conditions to first order.  
+At high $\epsilon$,
+the density contrast shrinks, and once the mean 
+Ma approaches 1 the two methods of
+measuring the density stratification bifurcate as density 
+inversions form within the thermal
 boundary layers.}
@@
 
-As the thermodynamic variables converge to their steady state values, the density
-profile evolves while remaining in hydrostatic equilibrium to zeroth order.  In 
-Fig. \ref{fig:nrho_v_ra} we show the number of density scale heights present in the
-evolved solution using two measures.  We find that once the average Ma of the domain
-becomes approximately one, large density inversions begin to form in the boundary layers,
-as was reported by \cite{brandenburg&all2005}.  The Regardless, the agreement of Nu
-across $\epsilon$ despite the different effective stratifications felt in the simulations
-is striking.
+As the thermodynamic variables converge to their steady state values, 
+the density profile evolves while remaining in hydrostatic equilibrium 
+to zeroth order.  In Fig. \ref{fig:nrho_v_ra} we show the number of density 
+scale heights present in the evolved solution using two measures.  
+We find that once the average Ma of the domain
+becomes approximately one, large density inversions begin to 
+form in the boundary layers, as was reported by \cite{brandenburg&all2005}.  
+Regardless, the agreement of Nu across $\epsilon$, particularly at
+low Ra, despite the difference in effective stratifications is striking.
 
@@
 of the RB problem to stratified systems, 
-and are an ideal laboratory for understanding the basic properties of stratified
-convection.
+and are an ideal laboratory for understanding the basic 
+properties of stratified convection.
 
-At low Ra and Ma, the scaling of Nu with Ra is reminiscent of RB convection.  However,
-at high Ra and Ma, the scaling breaks down to a Ra$^{1/5}$ scaling unlike what is seen
-in Boussinesq convection.  Similarly, the Reynolds number switches from a Ra$^{3/4}$ to
-a Ra$^{1/2}$ scaling in this regime shift.  It is interesting that both of these
+At low Ra and Ma, the scaling of Nu with Ra is reminiscent of RB convection.  
+However, at high Ra and Ma, the scaling breaks down to a Ra$^{1/5}$ 
+scaling unlike what is seen in Boussinesq convection.  
+Similarly, the Reynolds number switches from a Ra$^{3/4}$ to
+a Ra$^{1/2}$ scaling in this regime shift.  
+It is interesting that both of these
 scaling laws turn over by roughly a factor of 2/3.
 
-Time-dependent oscillating shear states have developed spontaneously, as seen before in RB convection
-\cite{goluskin&all2014}.  While computationally difficult, the highest values of Ra and the lowest value
-of $\epsilon$ studied here are far from values found in nature.  Future work will aim to better understand the mechanisms of shearing states and
-whether or not these states are attainable in three-dimensional, non-rotating atmospheres.
+Time-dependent oscillating shear states have developed spontaneously, 
+as seen before in RB convection \cite{goluskin&all2014}.  
+While computationally difficult, 
+the highest values of Ra and the lowest value
+of $\epsilon$ studied here are far from values found in nature.  
+Future work will aim to better understand the mechanisms of shearing states and
+whether or not these states are attainable in 
+three-dimensional, non-rotating atmospheres.
 
-Furthermore, we have found that the stratification of these atmospheres evolves in a complex
-manner, and future work should aim to understand the importance of changing stratification on
+Furthermore, we have found that the stratification of 
+these atmospheres evolves in a complex
+manner, and future work should aim to 
+understand the importance of changing stratification on
 convective heat transport. Our studies
@@
 to that in RB convection \cite{johnston&doering2009}, 
-and for future studies of transport in stratified
-convection.  These results can be used to determine if simplified equation sets, 
-such as the anelastic equations, carry heat in the same manner as the FC equations.
+and for future studies of transport in stratified convection.  
+These results can be used to determine if simplified equation sets, 
+such as the anelastic equations, carry heat in the same manner as the 
+FC equations.
 This work will also be useful in coming to understand more realistic systems, 
@@
 Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
-with allocations GID s1647 and GID g26133 (\textbf{AND ALSO THE NEW ONE AS OF 2017}).
-We thank Axel Brandenburg, Keith Julien, Mark Rast, and Jeff Oishi for many useful discussions.
+with allocations GID s1647 and GID g26133.
+We thank Jon Aurnou, Axel Brandenburg, Keith Julien, Mark Rast, and Jeff Oishi 
+for many useful discussions.
 

### 2017-03-09 tex/nusselt_paper.tex
adds note about 3D in discussion
fixes spiegel & veronis thing

@@
 with $\partial_z T_{\text{ad}} \equiv - g / c_{P}$ 
-for an ideal gas in hydrostatic equilibrium.  Here we specify
+for a compressible ideal gas in hydrostatic equilibrium \cite{spiegel&veronis1960}.  Here we specify
 $\langle \kappa \rangle = \langle \rho\chi \rangle$, which is nearly
@@
 values of $\epsilon$.
-In the Boussinesq approximation, under which $\grad S = 0$ only when 
+In incompressible Boussinesq convection, where $\grad S = 0$ only when 
 $\grad T = 0$, this definition reduces to the traditional definition
@@
 properties of stratified convection. 
+We see little difference between
+the properties of our 2D and 3D results, which aligns with expectations
+of Boussinesq theory and DNS results at values of Pr $\geq$ 1 \cite{ahlers&all2009}.
 
@@
 We thank Jon Aurnou, Axel Brandenburg, Keith Julien, Mark Rast, and Jeff Oishi 
-for many useful discussions.
+for many useful discussions. We also thank the two anonymous referees whose
+critical comments greatly improved the quality of this letter.
 

### 2017-03-09 referee_process/first_submission/referee_response.tex
adds rough draft of referee letter #1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional Formal Letter
% LaTeX Template
% Version 2.0 (12/2/17)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Brian Moses
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[aps, 11pt, singlecolumn]{revtex4-1} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\usepackage{natbib}
\bibliographystyle{apsrev}
\usepackage{setspace}

\begin{document}
%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\noindent
Dear Editor,
$\,$\newline

\begin{singlespace}
We have returned the revised version of our paper, 
``Convective heat transport in stratified atmospheres at low and high
Mach number,'' in which we have addressed the concerns of the referees.
We hope this version of the document is acceptable for publication.  We
have adjusted the text to address the criticism of the referee reports,
with a detailed description of our changes below.

We are grateful for the careful reading and responses of the referees.  
We thank referee A, whose
comments pushed us to undertake our first 3D runs in which we found the
transport results were nearly identical to the 2D results.
Upon reflecting on the
comments of referee B, we realized that the old definition of the
Nusselt number (Nu) that we were using was flawed, and have since defined
a slightly modified, more appropriate Nu.  This new definition better unifies
the results at low and high Mach number (Ma) and makes it easier to understand
the changes between the low and high Ma regimes.  Furthermore, 
the comments of referee B drove us to better analyze all properties of our evolved
atmospheres, and we have come to better understand how the Reynolds scales with
the Rayleigh number and the structure of the evolved atmosphere compared to the
initial atmosphere.

We apologize for the three month delay between receiving the referee reports
and the return of the revised draft.  In these months we have
recomputed all solutions, designed and tested our 3D implementation, and
thought carefully about the proper definition of Nu.  Through this
process we have gained a greater understanding of the fundamental
fluid properties in our simulations and how they change coherently
across parameter space.  We have removed the previous figure 3 from our
draft, as we feel it did not share any important information (the sum of
the fluxes adds up to a flat line in an equilibrated solution, and this
is well known).  The previous figure 4 has now become figure 3, and in addition
to showing the scaling of Nu with Ra, we now also show the scaling of the
Reynolds number, Re, with Ra.  We have added a new figure 4, in which we
find that the density contrast across the domain at high $\epsilon$ appreciably
shrinks in the evolved state compared to the initial state.  Furthermore, we
find that density inversions form near the boundary layers of these atmospheres
once the mean atmospheric Mach number approaches one, and show that this density
inversion becomes significant at high Ra and high $\epsilon$.
%\end{singlespace}

$\,$
\newline
$\,$
\newline

\textbf{Detailed response to referee report A:}

\begin{quotation}
The refereed paper is a reasonable step forward in an extremely
difficult and very important for understanding of fundamental physics
in planetary and star atmospheres problem of heat transfer in
convection of compressible, stratified media at moderately high Mach
numbers.

Authors expended previous studies to wider region of parameters, which
control an efficiency of the convection, and reported observation of
three regimes of convection with different scaling of the convection
efficiency (Nusselt number) vs. temperature gradient (Rayleigh number)
with a complicated time-space behavior of velocity, density and
temperature fluctuations.

Authors attacked this problem using high-end computer facilities of
NASA and efficient well justified numerical schemes. Nevertheless, to
be able to perform the direct numerical simulations of fully
compressible Navier-Stokes equations coupled with an equation for the
temperature transport, they restricted themselves by considering
two-dimensional version of the problem. Unfortunately, they did not
clarified, in which respect the two-dimensional simulations reflect
the real features of the three-dimensional physics. There is a well
known example (incompressible hydrodynamic turbulence, governed by the
Euler equation), in which an additional integral of motion in
two-dimensional case completely changes the basic physics of the
problem, including the direction of the energy flux over scales.
\end{quotation}

We have run and analyzed select 3D cases at both low and high $\epsilon$
at select values of the Rayleigh number.  These simulations have shown
us that the density profile, Mach number, and Reynolds number of the
evolved 3D state are nearly identical to the 2D simulations.  The Nusselt
number appears to change slightly between the 2D and 3D cases at low $\epsilon$, 
but the high $\epsilon$ results agree almost perfectly.  These results are shown
in Figs. 1, 3, and 4, and the agreement suggests that 2D cases
represent the bulk properties of the 3D dynamics well.

\begin{quotation}
The Letter is clearly written with a well balanced general
introduction to the field, a formulation of particular simplifications
of basic equations of motion and a presentation of the results of
numerical simulations. According to my understanding, the paper should
be interesting for non-experts in the field. I tend to recommend this
manuscript for publication in PRL, after detailed clarification of the
relations between two- and three-dimensional description on the basics
of Rayleigh-Bernard convection and on their generalization to the
compressible case.
\end{quotation}

Boussinesq theory and DNS results have shown that the scaling of Nu with Ra
is nearly the same in 2D and 3D for fluids with Pr $\geq$ 1 \cite{ahlers&all2009}.
We have shown that this is true in our results, and have mentioned this connection
to Boussinesq convection in the first paragraph of our discussion section.

$\,$
\newline
$\,$
\newline

\textbf{Detailed response to referee report A:}

\begin{quotation}
This paper essentially examines the heat transport in compressible
convection as as function of Rayleigh number and Mach number for fixed
density stratification and Prandtl number via 2D simulations The major
results cited are the scalings of the heat transport (measured by a
Nusselt number) with the Rayleigh number.

This paper has one substantial result and hints at another with
limited investigation. The major interesting result is that as flows
become supersonic, then the heat transport characteristics change
dramatically due to shock heating transported into the downflows. The
other aspect that is hinted at but not really elucidated, is that
compressible convection at high and low superadiabaticity is
substantially different.

The result regarding the heat transport characteristics and scaling
are sufficiently difficult to obtain and sufficiently interesting to
warrant publication. However, this paper is presented in a very
mysterious way that significantly confuses these interesting results.
The description of the modelling used is perplexing and misleading,
and the major results are buried. I will try to explain my issues
below. Overall, my feeling is that this paper needs substantial
re-writing to be publishable.
\end{quotation}
We thank referee B for their honesty regarding the confusing
structure of the paper.  We have tried to restructure the text in
a more sequential and hopefully less confusing way.

\begin{quotation}
My first and major issue is that this paper presents the model as
though the Mach number is a parameter. The Mach number is a diagnostic
of compressible convection. Compressible convection is governed by 4
parameters: a measure of the density stratification, a measure of the
superadiabaticity, and two measures of the diffusivities (viscous and
thermal). These can all be considered as timescales. Since there is a
further timescale (the sound crossing time) available, these 4
parameters can be non-dimensionalised. Some of these
non-dimensionalisations can be cast in terms of a Rayleigh number and
a Prandtl number for convenience of comparison with Boussinesq models,
for example. The Mach number, on the other hand, is a derived,
diagnostic quantity that depends on the choice of these 4 parameters.
This is easily seen from the results in the paper, e.g. Figure 1. Here
the Mach number is a measured quantity plotted as a function of (a)
the Rayleigh number, and then (b) the superadiabaticity. The paper
here is therefore confusing because it casts the results in terms of
`low or high Mach number', as if this were a parameter. There
are many examples of this throughout the paper, but see the abstract,
and, for instance, in the introduction ` the two control parameters
of RB convection are joined by the degree of stratification, $n_\rho$,
across the domain and the characteristic Ma of the convective
flows'. What the authors generally mean in their writeup is that
they are either choosing a small or large superadiabaticity (epsilon)
at fixed Ra, or small or large Ra at fixed epsilon. The former is used
for most of the results section.  ...
\end{quotation}
It is true that $\epsilon$ is the primary control parameter we are
referring to when we mentioned ``high'' or ``low'' Mach number. This
is because Ma is a very strong function of $\epsilon$, and a weaker
function of Ra, as shown in Fig. 1.  At the ranges of Ra which we are
reasonable to examine via DNS (up to nearly $10^7$Ra$_{\text{crit}}$),
the Ma increases by less than a factor of 100 from simulations at
onset to simulations near the state-of-the-art.  Thus, the choice of
very low $\epsilon$ ($10^{-4}$, $10^{-7}$) forces all simulations at
that parameter into the Ma $\ll 1$ regime, regardless of Ra.  Whereas the
choice of $\epsilon \approx 1$ forces all simulations into the Ma $\approx 1$
regime.

This being said, it is understandable that the manner in which we presented
Ma and $\epsilon$ was somewhat confusing.  We have changed the text to try
to more explicitly state that $\epsilon$ is the control parameter, and that
setting $\epsilon$ to be very small allows us to study low Ma convection,
whereas setting $\epsilon$ near 1 allows us to study high Ma convection.  We
have chosen to retain the title of the letter while adding clarification to
the text.

\begin{quotation}
...However, it is true that the
interesting change in transport results appear when the flow becomes
supersonic, but this could mean high superadiabaticity (epsilon) *or*
high Ra (for fixed Pr). The results should all really be cast as
`at high enough Ra or high enough superadiabaticity, a high Ma flow
results and this changes the transport characteristics'.
Ultimately, the scaling results exhibited are in terms of Ra, and this
makes perfect sense, although these results are only confined to a
small paragraph at the end of the results section without much
elaboration or explanation. I personally would like a much more causal
relationship explained between the shock heating and `spinners'
and the heat transport results.

Beyond this main issue, there are a lot of small things that I don't
understand, which I will try and list here, in chronological order.

Introduction

'Numerical constraints ... to moderately high Ma': What is the
numerical constraint of low Ma flow?
\end{quotation}
When the convection is low Ma, the convective dynamics are much slower
than the linear acoustic waves.  By stepping this linear component
implicitly, we bypass the high Ma component of these waves and timestep
on the order of the convective dynamics.

\begin{quotation}
'RB' By `Rayleigh-Benard problem' here I assume that the
authors are referring to Boussinesq dynamics? It might be a good idea
to make this clear.
\end{quotation}
We have reworded this sentence at the beginning of paragraph 3 to make it
clear that we are referring to Boussinesq convection.

\begin{quotation}
'the Ma is controlled by the superadiabatic excess': It is clear
from Fig 1 that this is not a complete statement.
\end{quotation}
We have removed this sentence from the introduction, and mentioned that
the superadiabaticity is the important control parameter.

\begin{quotation}
Experiment

Eqn (1): Better define co-ordinates, especially $z$ and $z_0$
\end{quotation}
$z_0$ was confusing and has been removed.  We define $z$ shortly
below the eqn (1).

\begin{quotation}
The non-dimensionalization is very confusingly written. Can you write
out the non-dimensionalised polytope? This section also says that the
`timescale is the isothermal sound crossing time of the layer'
and then two sentences later says that `we use buoyancy time
units', so which is it? The definition of the latter does look like
the sqrt(epsilon) so maybe these are the same?
\end{quotation}
Ben, what is he asking us to write out?
In our numerical simulations, one time unit is the isothermal sound
crossing time at the top of the layer.  However, convective dynamics
have a typical overturn time which can be a few simulation time units
(at high $\epsilon$) or it can have an overturn time of many simulation
time units (at low $\epsilon$).  The buoyancy time allows us to estimate this.

\begin{quotation}
'The scaling of the entropy gradient with epsilon ... evolved
values ': I really have no idea what these two sentences mean,
sorry!
\end{quotation}
The initial entropy gradient of the polytrope is $\nabla S \propto -\epsilon$,
and as a result evolved variables are $O(\epsilon)$.  We have removed this
sentence, as it is confusing, and said this in the results section.

\begin{quotation}
Eqns: I don't understand why these equations are formulated with
gradients of nu when mu is constant. The stress tensor only depends on
mu and so this can be pulled out of all derivatives. Or am I missing
something? The case of constant nu and therefore variable mu is much
harder. Similarly for the formulation in terms of chi and not the
thermal conductivity; variable thermal conductivity is hard but
variable chi is easy. Why not write in terms of mu and k not nu and
chi?
\end{quotation}
$\mu$ is initially constant, which means that $\mu = \nu\rho_0$
must be constant.  Since we are in a stratified atmosphere, this
means that $\nu \propto 1/\rho_0$.  A similar relation between
$\kappa$ and $\chi$ exists.  Thus the gradients of $\nu$ and $\chi$
are present.  $\mu$ and $\kappa$ are allowed to evolve with the
density profile, and we have discussed this more clearly in section X.

\begin{quotation}
'IMEX': I am assuming this acronym stands for implicit-explicit?
Maybe write out?
\end{quotation}
We have spelled this out in the paragraph after the paragraph
containing Eq. 7.

\begin{quotation}
'extended to include variable nu and chi' : see above. This seems
very unnecessary!
\end{quotation}
See above discussion

\begin{quotation}
Results

$d_z T_{ad} = 0$: This is only true for liquids not gases. See Speigel and
Veronis 1960.
\end{quotation}
This is a good point that we had not appreciated.  Most of the studies of Boussinesq
convection with which we are familiar make the assumption that the fluid is incompressible.
It is true that in an ideal gas which is compressible but barely stratified, the
adiabatic temperature gradient is what we found and what is reported by
Spiegel and Veronis, $\partial_z T_{ad} = -g/c_P$, \cite{spiegel&veronis1960}.
We have updated the text following eqn 8 to reflect this.

\begin{quotation}
'While it has been suggested that pressure forces...': I do not
understand the discussion here. Do the authors regard the breakup of
the down flows as an extreme version of asymmetry?
\end{quotation}
We are merely stating that at low Ma, pressure fluctuations are small and
tend to not be positive in the upper atmosphere and negative in the lower atmosphere
regardless of whether we are observing an upflow or a downflow.  The classical argument
\cite{hurlburt&all1984} of ``buoyancy breaking accelerates downflows and deccelerates
upflows'' seems to break down when the Mach number is small from the cases we've studied.

\begin{quotation}
'exhibit states in which the flux entering...': Surely in a
stationary state the flux in has to equal the flux out. Are the
authors saying that this is not a stationary state?
\end{quotation}
We are saying this is a non-stationary state.  The combination of fixed-temperature
boundary conditions and no-slip boundary conditions allows the system to fluctuate between
roll states of convection and shear states of convection.  These states persist over long
time scales (hundreds of buoyancy times) and the atmosphere is in flux disequilibrium in both states.
We have tried to update the text to make this clearer.

\begin{quotation}
Discussion

Can the authors demonstrate the basic principles of whatever balance
is described by the Grossman-Lohse theory?
\end{quotation}
The Grossman-Lohse theory for Boussinesq dynamics models the energy dissipation rate of both
kinetic and potential energies, and separates these rates within the boundary layers and
the bulk flow.  Stratified, compressible convection must also deal with potential energy,
and as the Mach number becomes large and density inversions begin to occur (such as in our new
Fig. 4), a more complex theory involving dissipation rates of all three energies could
in practice be developed.  In the low Ma case in which the flows are small and density 
gradients monitonically point downwards, it is likely that a simplified version of the
Grossman-Lohse theory could be developed in the context of polytropically stratified atmospheres.
Here, the density profile would mean that the upper and lower boundary layers become
asymmetrical.

Unfortunately, we are not experts in boundary layer theory and will need to educate ourselves
further on how the Grossman-Lohse theory was developed and applied before we can say anything
with certainty in stratified convection. In keeping with this, we have removed this nod from
the Discussion section and made suggestions towards further experiments which we are certain our
work can inform.

\begin{quotation}
'under solar conditions ... we expect that epsilon  $\approx 10^{-20}$
...': Is this small epsilon a reflection of efficient mixing of
convection in the ultimate nonlinear state or of the initial linear
convective driving?
\end{quotation}
These approximations in the initial letter were a representation of the choices of
parameters necessary to achieve the desired Mach number and Rayleigh number of convective
motions in the deep solar interior.  There, Ma $\approx 10^{-4}$ and Ra $\approx 10^{20}$,
and due to the scaling of Mach number with $\epsilon$ and Ra, we made a best-guess estimate
based on our scaling laws in fig. 1 for what $\epsilon$ could describe that low Ma at such
extreme values of Ra.

\end{singlespace}

\noindent
Sincerely,

Evan H. Anders \& Benjamin P. Brown

\bibliography{../../biblio.bib}
\end{document}

### 2017-03-09 referee_process/first_submission/structure.tex
adds rough draft of referee letter #1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional Formal Letter
% Structure Specification File
% Version 1.0 (12/2/17)
%
% This file originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Brian Moses
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\usepackage{graphicx} % Required for including pictures

\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage{gfsdidot} % Use the GFS Didot font: http://www.tug.dk/FontCatalogue/gfsdidot/
\usepackage{microtype} % Improves typography

\pagestyle{empty} % Suppress headers and footers

\setlength\parindent{0.5cm} % Paragraph indentation

% Create a new command for the horizontal rule in the document which allows thickness specification
\makeatletter
\newcommand{\vhrulefill}[1]{\leavevmode\leaders\hrule\@height#1\hfill \kern\z@}
\makeatother

%----------------------------------------------------------------------------------------
%	DOCUMENT MARGINS
%----------------------------------------------------------------------------------------

\usepackage{geometry} % Required for adjusting page dimensions

\geometry{
	top=1cm, % Top margin
	bottom=1.5cm, % Bottom margin
	left=2cm, % Left margin
	right=2cm, % Right margin
	%showframe, % Uncomment to show how the type block is set on the page
}

%----------------------------------------------------------------------------------------
%	DEFINE CUSTOM COMMANDS
%----------------------------------------------------------------------------------------

\newcommand{\logo}[1]{\renewcommand{\logo}{#1}}

\newcommand{\Who}[1]{\renewcommand{\Who}{#1}}
\newcommand{\Title}[1]{\renewcommand{\Title}{#1}}

\newcommand{\headerlineone}[1]{\renewcommand{\headerlineone}{#1}}
\newcommand{\headerlinetwo}[1]{\renewcommand{\headerlinetwo}{#1}}

\newcommand{\authordetails}[1]{\renewcommand{\authordetails}{#1}}

%----------------------------------------------------------------------------------------
%	AUTHOR DETAILS STRUCTURE
%----------------------------------------------------------------------------------------

\newcommand{\authordetailsblock}{
	\hspace{\fill} % Move the author details to the far right
	\parbox[t]{0.48\textwidth}{ % Box holding the author details; width value specifies where it starts and ends, increase to move details left
		\footnotesize % Use a smaller font size for the details
		\Who\\ % Author name
		\textit{\authordetails} % The author details text, all italicised
	}
}

%----------------------------------------------------------------------------------------
%	HEADER STRUCTURE
%----------------------------------------------------------------------------------------

\address{
	\includegraphics[width=1in]{\logo} % Include the logo of author institution
	\hspace{0.82\textwidth} % Position of the institution logo, increase to move left, decrease to move right
	\vskip -0.1\textheight~\\ % Position of the large header text in relation to the institution logo, increase to move down, decrease to move up
	\Large\hspace{0.2\textwidth}\headerlineone\hfill ~\\[0.006\textheight] % First line of institution name, adjust hspace if your logo is wide
	\hspace{0.2\textwidth}\headerlinetwo\hfill \normalsize % Second line of institution name, adjust hspace if your logo is wide
	\makebox[0ex][r]{\textbf{\Who\Title}}\hspace{0.01\textwidth} % Print author name and title with a little whitespace to the right
	~\\[-0.01\textheight] % Reduce the whitespace above the horizontal rule
	\hspace{0.2\textwidth}\vhrulefill{1pt} \\ % Horizontal rule, adjust hspace if your logo is wide and \vhrulefill for the thickness of the rule
	\authordetailsblock % Include the letter author's details on the right side of the page under the horizontal rule
	\hspace{-0.25\textwidth} % Horizontal position of the author details block, increase to move left, decrease to move right
	\vspace{-0.1\textheight} % Move the date and letter content up for a more compact look
}

%----------------------------------------------------------------------------------------
%	COMPOSE THE ENTIRE HEADER
%----------------------------------------------------------------------------------------

\renewcommand{\opening}[1]{{}{}
%	{\centering\fromaddress\vspace{0.05\textheight} \par$\,$\newline\par} % Print today's date, remove \today to not display it
%	{} % Print the to name and address
	\vspace{1cm} % White space after the to address
	\noindent #1 % Print the opening line
}

%----------------------------------------------------------------------------------------
%	SIGNATURE STRUCTURE
%----------------------------------------------------------------------------------------

\signature{\Who\Title} % The signature is a combination of the author's name and title

\renewcommand{\closing}[1]{
	\vspace{2.5mm} % Some whitespace after the letter content and before the signature
	\noindent % Stop paragraph indentation
	\hspace*{\longindentation} % Move the signature right to the value of \longindentation
	\parbox{\indentedwidth}{
		\raggedright
		#1 % Print the signature text
		\vskip 1.65cm % Whitespace between the closing text and author's name for a physical signature
		\fromsig % Prints the value of \signature{}, i.e. author name and title
	}
}

### 2017-03-09 tex/nusselt_paper.tex
fixes a couple things in results

@@
 variance with depth. By performing a linear stability analysis, 
-we determined that the onset of convection
+we determined that the onset of convection in 2D
 occurs at $\text{Ra}_{\text{c,top}} = \{11.15, 10.06, 10.97, 10.97\}$ 
@@
 for $\epsilon = 0.5$, up to
-roughly $10^5$Ra$_{\text{c,top}}$ at $\epsilon = 10^{-4}$, and 
-up to $10^3$Ra$_{\text{c,top}}$ for $\epsilon = \{1, 10^{-7}\}$.
+$\sim 10^5$Ra$_{\text{c,top}}$ at $\epsilon = 10^{-4}$, 
+up to $\sim 10^4$Ra$_{\text{c,top}}$ for $\epsilon = 1$,
+and up to $\sim 10^3$Ra$_{\text{c,top}}$ for $\epsilon = 10^{-7}$.
 
@@
 but this relation break down as the mean
-Ma approaches 1 and the flows become supersonic (see Fig. \ref{fig:ma_v_eps}a).  At low
-Ra (Ra$_{\text{c,top}} \lesssim 10^4$), 
-Ma $\propto$ Ra$^{1/4}$.  At high epsilon
-($\epsilon = 0.5$, this scaling breaks down near 
-Ra = $10^4$ where the flows become primarily
-supersonic.  The scaling of 
-Ra$^{1/4}$ appears to break down for Ra $\gtrsim 10^5$ at
-$\epsilon = 10^{-4}$, 
-but computational constraints made it restrictively difficult to converge
-many runs in this region of parameter space.
-Furthermore, the evolved thermodynamic variables, 
-$T_1/T_0, \rho_1/\rho_0 \propto \epsilon$,
+Ma approaches 1 and the flows become supersonic (see Fig. \ref{fig:ma_v_eps}a).  
+When Ma is small,
+Ma $\propto$ Ra$^{1/4}$.  At high epsilon, 
+this scaling breaks down once the mean atmospheric Ma reaches 1.
+Furthermore, the value of $\epsilon$ sets the size of the
+evolved thermodynamic variables, 
+$T_1/T_0, \rho_1/\rho_0 \propto \epsilon$.  Thus, fluctuations
 are very small for low Ma flows, 

### 2017-03-09 tex/nusselt_paper.tex
adds some 3D generalization

@@
 ratios of 4 where the $x$ coordinate has the range $[0, 4L_z]$.
+Select cases have been run in three dimensions with $y$ in the range
+$[0, 4L_z]$.
 
@@
 $\ln\rho = (\ln\rho)_0 + (\ln\rho)_1$, 
-and the velocity $\bm{u} = u\hat{x} + w\hat{z}$ 
-has no background component.    
+and the velocity $\bm{u} = u\hat{x} + v\hat{y} +  w\hat{z}$ 
+has no background component, and that $v = 0$ in our 2D runs..    
 We evolve the Fully Compressible Navier-Stokes equations,
@@
 Physical grid sizes range from
-96x384 grid points at the lowest values of 
-Ra to 1536x6144 grid points at Ra$_{\text{top}} > 10^{7}$. 
+64x256 coefficient points at the lowest values of 
+Ra to 1024x4096 coefficient points at Ra$_{\text{top}} > 10^{7}$ in 2D,
+and 64x128$^2$ to  128x256$^2$ in 3D. 
 By using IMEX timestepping, we implicitly step the 
@@
 occurs at $\text{Ra}_{\text{c,top}} = \{11.15, 10.06, 10.97, 10.97\}$ 
-for $\epsilon = \{1.0, 0.5, 10^{-4}, 10^{-7}\}$ respectively.  
+for $\epsilon = \{1.0, 0.5, 10^{-4}, 10^{-7}\}$ respectively.  Results
+in 3D appear to be consistent with our 2D onset values.
 We studied Rayleigh

### 2017-03-09 tex/nusselt_paper.tex
gets all of the ideas into the discussion

@@
 Ra to 1024x4096 coefficient points at Ra$_{\text{top}} > 10^{7}$ in 2D,
-and 64x128$^2$ to  128x256$^2$ in 3D. 
+and 64x128$^2$ to  256x512$^2$ in 3D. 
 By using IMEX timestepping, we implicitly step the 
@@
 atmosphere.
-(a) When $Ma < 1$ (below the black horizontal line), 
-Ma $\propto \epsilon^{1/2}$.
-t low ($10^2$) and moderate ($10^5$) values of Ra.
-(b) When Ra is small, Ma $\propto Ra^{1/2}$ (dashed lines).
-Once the mean Ma reaches 1 ($\epsilon = \{0.5, 1\}$), this scaling breaks down
-and nearly all flows in the atmosphere are at Ma = 1.
-At low $\epsilon$, a consistent power law of Ma $\propto Ra^{1/4}$ is retrieved.
+(a) Ma is plotted as a function of $\epsilon$, the superadiabatic excess,
+at various values of Ra.
+(b) Ma is plotted as a function of Ra at various values of $\epsilon$.
+Larger symbols with white dots designate 3D runs.
 \label{fig:ma_v_eps} }
@@
 the stratified medium.  
-Our choice of fixed-temperature boundary conditions allows the flux at the 
-boundaries to vary, and runs at $\text{Ra }> 10^4$
+Our choice of fixed-temperature, stress free boundary conditions 
+allows the flux at the boundaries to vary, while also allowing
+for large-scale ``axisymmetric'' horizontal velocities.
+Runs at $\text{Ra }> 10^4$
 and $\epsilon = 10^{-4}$ exhibit long-term states of
-flux disequilibrium.  
-Roll solutions such as those pictured in Fig. \ref{fig:entropy_snapshots}a
-are punctuated by states of vigorous shearing, similar to those previously
+flux disequilibrium, in which roll solutions such as those pictured in 
+Fig. \ref{fig:entropy_snapshots}a
+are punctuated by shearing states similar to those previously
 reported in two-dimensional RB convection \cite{goluskin&all2014}.  
-During the roll states, 
-the flux at the lower boundary exceeds that at the upper boundary
-and energy is stored in the system.
-During shearing states, 
-convective transport is suppressed and Nu diminishes while
-the flux at the upper boundary exceeds that at the lower boundary.  Long term
-averages over both of these states produce flat flux profiles which
-can be sensibly analyzed.
+During both of these states, the system is in flux disequilibrium.
+A long time average
+over both of these states produce flat flux profiles which
+can be sensibly analyzed, but the presence of these time-dependent states
+makes it difficult to measure fluid quantities in these cases.
 
@@
 \caption{
-Variation of Nu as Ra increases at high and low $\epsilon$. 
-At high $\epsilon$ (purple circles), 
-a clear transition from the subsonic to supersonic regime 
-is evident in the scaling
-of Nu with Ra at $\text{Ra}_{\text{top}} \approx 10^4$.  
-In the low $\epsilon$ regime (green diamonds and yellow squares), 
-our observed Nu scalings collapse onto a similar line which is
-indistinguishable from a $\text{Ra}_{\text{top}}^{2/7}$ scaling, 
-as observed in RB convection \cite{johnston&doering2009}.  
+(a) Variation of Nu as Ra increases at high and low $\epsilon$. 
 Errors bars indicate the properly normalized range of the
@@
 large error bars indicate a poorly converged solution.
+(b) Variation of Re as Ra increases at high and low $\epsilon$.
+Re is measured at the midplane of the atmosphere.
+Larger symbols with white dots designate 3D runs.
  \label{fig:re_and_nu_v_ra}.
@@
 The scaling of Nu with Ra$_{\text{top}}$ 
-is unclear at low $\epsilon$ (so I'll try to fill in that space with
-data from comps...time to fish it out of Lou and do post-processing hell).
+is unclear at low $\epsilon$ once Ra is sufficiently large
+for shearing states to occur.  It would be beneficial to study
+low $\epsilon$ flows with fixed-flux boundary conditions or
+no-slip boundary conditions that disallow these large scale
+structures.
 
@@
 this scaling gives way to a Re $\propto$ Ra$_{\text{top}}^{1/2}$.
+For large values of Ra but at low $\epsilon$, there appears to be a scaling
+of Re $\propto$ Ra$^{2/3}$.
 
@@
 \includegraphics[width=3.4375in]{./figs/density_v_ra.png}
-\caption{\label{fig:nrho_v_ra} We measure the stratification of 
-evolved solutions
-in two ways.  The solid symbols show $\ln(\rho(0)/\rho(L_z))$, 
-or the density contrast
+\caption{\label{fig:nrho_v_ra} The stratification of 
+evolved solutions is measured
+in two ways.  Solid symbols show $\ln(\rho(z=0)/\rho(z=L_z))$, 
+the density contrast
 as measured at the upper and lower boundary.  The empty symbols show 
@@
 the density contrast shrinks, and once the mean 
-Ma approaches 1 the two methods of
+Ma approaches 1 (as in Fig. \ref{fig:ma_v_eps}b), the two methods of
 measuring the density stratification bifurcate as density 
 inversions form within the thermal
-boundary layers.}
+boundary layers. Larger symbols with white dots represent 3D runs.}
 \end{figure}
@@
 In this letter we have studied fundamental heat transport by 
-stratified convection in simplified 2-D polytropic atmospheres.
+stratified convection in simplified 2D and 3D polytropic atmospheres.
 We argue that these atmospheres are the natural extension
@@
 At low Ra and Ma, the scaling of Nu with Ra is reminiscent of RB convection.  
-However, at high Ra and Ma, the scaling breaks down to a Ra$^{1/5}$ 
-scaling unlike what is seen in Boussinesq convection.  
-Similarly, the Reynolds number switches from a Ra$^{3/4}$ to
-a Ra$^{1/2}$ scaling in this regime shift.  
-It is interesting that both of these
-scaling laws turn over by roughly a factor of 2/3.
+However, at high Ra and Ma, the scaling of Nu becomes weakear, decreasing
+from a 1/3 to a 1/5 power law, a decrease by roughly a factor of 1/3.
+Similarly, the Reynolds number switches from a 3/4 power law to
+a 1/2 scaling in this regime shift, a similar decrease by a factor of 1/3.
+This seems to suggest that a large portion of the scaling of the Nusselt number
+comes from increases in velocity as Ra increases.  Once the velocity reaches
+its natural maximum, heat transport can no longer benefit from increased velocities.
+The same is true of the Reynolds number, which tracks increases in velocities as
+the flows become more turbulent, but which can only scale with the diffusivities
+once the Mach number reaches its maximum value.
 
 Time-dependent oscillating shear states have developed spontaneously, 
-as seen before in RB convection \cite{goluskin&all2014}.  
-While computationally difficult, 
-the highest values of Ra and the lowest value
-of $\epsilon$ studied here are far from values found in nature.  
-Future work will aim to better understand the mechanisms of shearing states and
-whether or not these states are attainable in 
-three-dimensional, non-rotating atmospheres.
+as seen before in RB convection \cite{goluskin&all2014}, and these should
+be studied in more detail.  These states are fundamentally in flux disequilibrium
+and make it very difficult to calculate a meaningful Nusselt number.  It would
+be beneficial for future studies to study solutions with fixed flux or no slip
+boundary conditions to better converge and study cases at high $\epsilon$ and low
+Ra.
 
-Furthermore, we have found that the stratification of 
+Finally, we have found that the stratification of 
 these atmospheres evolves in a complex
-manner, and future work should aim to 
-understand the importance of changing stratification on
-convective heat transport. Our studies
+manner.  Future work should aim to 
+understand the importance of stratification on
+convective heat transport, and the manner in which
+boundary layer density inversions interact with
+thermal plumes.
+
+Our studies
 here will serve as a foundation both for understanding and 

### 2017-03-09 referee_process/first_submission/referee_response.tex
cleans up one section of referee letter a bit.

@@
 Mach number,'' in which we have addressed the concerns of the referees.
-We hope this version of the document is acceptable for publication.  We
-have adjusted the text to address the criticism of the referee reports,
+We hope this version of the document is acceptable for publication.  The text 
+has been adjusted to address the criticism of the referee reports,
 with a detailed description of our changes below.
@@
 comments pushed us to undertake our first 3D runs in which we found the
-transport results were nearly identical to the 2D results.
+transport results were nearly identical to our 2D results.
 Upon reflecting on the
@@
 the comments of referee B drove us to better analyze all properties of our evolved
-atmospheres, and we have come to better understand how the Reynolds scales with
-the Rayleigh number and the structure of the evolved atmosphere compared to the
-initial atmosphere.
+atmospheres, and we have come to better understand how the Reynolds number scales with
+the Rayleigh number, and also how the structure of the evolved atmospheric density
+compares to the initial atmosphere.
 
@@
 \end{quotation}
-The Grossman-Lohse theory for Boussinesq dynamics models the energy dissipation rate of both
-kinetic and potential energies, and separates these rates within the boundary layers and
-the bulk flow.  Stratified, compressible convection must also deal with potential energy,
-and as the Mach number becomes large and density inversions begin to occur (such as in our new
-Fig. 4), a more complex theory involving dissipation rates of all three energies could
-in practice be developed.  In the low Ma case in which the flows are small and density 
-gradients monitonically point downwards, it is likely that a simplified version of the
-Grossman-Lohse theory could be developed in the context of polytropically stratified atmospheres.
-Here, the density profile would mean that the upper and lower boundary layers become
-asymmetrical.
-
-Unfortunately, we are not experts in boundary layer theory and will need to educate ourselves
+We believe that the Grossman-Lohse theory, which models the energy dissipation rate of both
+kinetic and potential energies, could be extended to stratified, compresible flows which also
+have potential energy.  At low $\epsilon$, where the density profile is simple and very similar
+to the initial polytrope in the evolved state, it seems that this extension would be easier to
+develop.  However, we are inexperienced in applying boundary layer theory and 
+will need to educate ourselves
 further on how the Grossman-Lohse theory was developed and applied before we can say anything
-with certainty in stratified convection. In keeping with this, we have removed this nod from
+with certainty regarding how to expand this theory to stratified convection. 
+We have removed this suggestion from
 the Discussion section and made suggestions towards further experiments which we are certain our

### 2017-03-10 referee_process/first_submission/referee_response.tex
minor cleanups, adds some to abstract

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Professional Formal Letter
-% LaTeX Template
-% Version 2.0 (12/2/17)
-%
-% This template originates from:
-% http://www.LaTeXTemplates.com
-%
-% Authors:
-% Brian Moses
-% Vel (vel@LaTeXTemplates.com)
-%
-% License:
-% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %----------------------------------------------------------------------------------------
@@
 $\,$\newline
+
+\newenvironment{myquotation}{
+\begin{quotation}
+\itshape
+}{ 
+\end{quotation}
+}
 
@@
 
-\begin{quotation}
+\begin{myquotation}
 The refereed paper is a reasonable step forward in an extremely
@@
 problem, including the direction of the energy flux over scales.
-\end{quotation}
+\end{myquotation}
 
@@
 
-\begin{quotation}
+\begin{myquotation}
 The Letter is clearly written with a well balanced general
@@
 compressible case.
-\end{quotation}
+\end{myquotation}
 
@@
 
-\begin{quotation}
+\begin{myquotation}
 This paper essentially examines the heat transport in compressible
@@
 re-writing to be publishable.
-\end{quotation}
+\end{myquotation}
 We thank referee B for their honesty regarding the confusing
 structure of the paper.  We have tried to restructure the text in
-a more sequential and hopefully less confusing way.
+a more sequential and thoughtful manner.
 
-\begin{quotation}
+\begin{myquotation}
 My first and major issue is that this paper presents the model as
@@
 for most of the results section.  ...
-\end{quotation}
+\end{myquotation}
 It is true that $\epsilon$ is the primary control parameter we are
@@
 
-\begin{quotation}
+\begin{myquotation}
 ...However, it is true that the
@@
 and the heat transport results.
+\end{myquotation}
+It appears that the ``spinners'' are not the primary cause of the change
+of the Nu scaling at about Ma = 1.  We see a similar change in the scaling
+of the Reynolds number, and this suggests that a large fraction of the
+increase in energy transport with Ra is caused by increasing velocities.
+Once the mean flow speed is at Ma = 1, the convective transport
+can no longer benefit from increases in velocities, and only changes in
+the size of thermodynamic variables or changes in the strength of the
+diffusivity are left to increase the Nusselt Number.  This is
+mentioned in the second paragraph of the Discussion section.
 
+\begin{myquotation}
 Beyond this main issue, there are a lot of small things that I don't
@@
 numerical constraint of low Ma flow?
-\end{quotation}
+\end{myquotation}
 When the convection is low Ma, the convective dynamics are much slower
@@
 implicitly, we bypass the high Ma component of these waves and timestep
-on the order of the convective dynamics.
+on the order of the convective dynamics.  This is noted in the second to
+last paragraph of the Experiment section.
 
-\begin{quotation}
+\begin{myquotation}
 'RB' By `Rayleigh-Benard problem' here I assume that the
@@
 to make this clear.
-\end{quotation}
-We have reworded this sentence at the beginning of paragraph 3 to make it
-clear that we are referring to Boussinesq convection.
+\end{myquotation}
+We have reworded this sentence at the beginning of the second paragraph of the
+Introduction to clarify that we are referring to Boussinesq convection.
 
-\begin{quotation}
+\begin{myquotation}
 'the Ma is controlled by the superadiabatic excess': It is clear
 from Fig 1 that this is not a complete statement.
-\end{quotation}
-We have removed this sentence from the introduction, and mentioned that
-the superadiabaticity is the important control parameter.
+\end{myquotation}
+The third paragraph of the introduction has been restructured.  We note
+that $\epsilon$ is a control parameter whose primary job is to modify
+the Ma of the resulting solution.
 
-\begin{quotation}
+\begin{myquotation}
 Experiment
@@
 Eqn (1): Better define co-ordinates, especially $z$ and $z_0$
-\end{quotation}
-$z_0$ was confusing and has been removed.  We define $z$ shortly
-below the eqn (1).
+\end{myquotation}
+$z_0 = L_z + 1$ was confusing notation and has been removed.  
+We define $z$ shortly below Eqn (1).
 
-\begin{quotation}
+\begin{myquotation}
 The non-dimensionalization is very confusingly written. Can you write
@@
 the sqrt(epsilon) so maybe these are the same?
-\end{quotation}
+\end{myquotation}
 Ben, what is he asking us to write out?
@@
 
-\begin{quotation}
+\begin{myquotation}
 'The scaling of the entropy gradient with epsilon ... evolved
@@
 sorry!
-\end{quotation}
+\end{myquotation}
 The initial entropy gradient of the polytrope is $\nabla S \propto -\epsilon$,
 and as a result evolved variables are $O(\epsilon)$.  We have removed this
-sentence, as it is confusing, and said this in the results section.
+sentence, as it is confusing, and mentioned the scaling of thermodynamic variables
+with $\epsilon$ in the second paragraph of the Results section, where we now describe
+Fig. 1.
 
-\begin{quotation}
+\begin{myquotation}
 Eqns: I don't understand why these equations are formulated with
@@
 chi?
-\end{quotation}
+\end{myquotation}
 $\mu$ is initially constant, which means that $\mu = \nu\rho_0$
@@
 means that $\nu \propto 1/\rho_0$.  A similar relation between
-$\kappa$ and $\chi$ exists.  Thus the gradients of $\nu$ and $\chi$
-are present.  $\mu$ and $\kappa$ are allowed to evolve with the
-density profile, and we have discussed this more clearly in section X.
+$\kappa$ and $\chi$ exists.  Thus, while $\nu$ and $\chi$ are constant
+in time, they are \emph{not} constant with height, and their
+gradients must be included in the equation set.
+$\mu$ and $\kappa$ are allowed to evolve with the
+density profile, and we have discussed this more clearly in the
+second paragraph of the Experiment section.
 
-\begin{quotation}
+\begin{myquotation}
 'IMEX': I am assuming this acronym stands for implicit-explicit?
 Maybe write out?
-\end{quotation}
-We have spelled this out in the paragraph after the paragraph
-containing Eq. 7.
+\end{myquotation}
+We have spelled this out in the second to last paragraph of the Experiment section.
 
-\begin{quotation}
+\begin{myquotation}
 'extended to include variable nu and chi' : see above. This seems
 very unnecessary!
-\end{quotation}
-See above discussion
 
-\begin{quotation}
 Results
@@
 Veronis 1960.
-\end{quotation}
+\end{myquotation}
 This is a good point that we had not appreciated.  Most of the studies of Boussinesq
@@
 Spiegel and Veronis, $\partial_z T_{ad} = -g/c_P$, \cite{spiegel&veronis1960}.
-We have updated the text following eqn 8 to reflect this.
+We have updated the text following Eqn 8 to reflect this.
 
-\begin{quotation}
+\begin{myquotation}
 'While it has been suggested that pressure forces...': I do not
@@
 the down flows as an extreme version of asymmetry?
-\end{quotation}
-We are merely stating that at low Ma, pressure fluctuations are small and
+\end{myquotation}
+In our low Ma simulations, pressure fluctuations are small and
 tend to not be positive in the upper atmosphere and negative in the lower atmosphere
@@
 \cite{hurlburt&all1984} of ``buoyancy breaking accelerates downflows and deccelerates
-upflows'' seems to break down when the Mach number is small from the cases we've studied.
+upflows'' appears to break down at low Ma.
 
-\begin{quotation}
+\begin{myquotation}
 'exhibit states in which the flux entering...': Surely in a
@@
 authors saying that this is not a stationary state?
-\end{quotation}
+\end{myquotation}
 We are saying this is a non-stationary state.  The combination of fixed-temperature
@@
 time scales (hundreds of buoyancy times) and the atmosphere is in flux disequilibrium in both states.
-We have tried to update the text to make this clearer.
+We have updated the text in the third paragraph of the Results section to make this clearer.
 
-\begin{quotation}
+\begin{myquotation}
 Discussion
@@
 is described by the Grossman-Lohse theory?
-\end{quotation}
+\end{myquotation}
 We believe that the Grossman-Lohse theory, which models the energy dissipation rate of both
@@
 will need to educate ourselves
-further on how the Grossman-Lohse theory was developed and applied before we can say anything
-with certainty regarding how to expand this theory to stratified convection. 
+further on the development of the Grossman-Lohse theory before we can say
+with certainty that an expansion of this theory to stratified convection is tractable. 
 We have removed this suggestion from
@@
 
-\begin{quotation}
+\begin{myquotation}
 'under solar conditions ... we expect that epsilon  $\approx 10^{-20}$
@@
 convective driving?
-\end{quotation}
+\end{myquotation}
 These approximations in the initial letter were a representation of the choices of
 parameters necessary to achieve the desired Mach number and Rayleigh number of convective
-motions in the deep solar interior.  There, Ma $\approx 10^{-4}$ and Ra $\approx 10^{20}$,
-and due to the scaling of Mach number with $\epsilon$ and Ra, we made a best-guess estimate
-based on our scaling laws in fig. 1 for what $\epsilon$ could describe that low Ma at such
-extreme values of Ra.
+motions in the deep solar interior.  There, Ma $\approx 10^{-4}$ and Ra $\approx 10^{20}$.
+We made an estimate of what $\epsilon$ would be necessary to achieve low Ma at such large
+values of Ra based on the observed scaling of Mach number with $\epsilon$ and Ra
+in Fig. 1.
+
+$\,$
+\newline
+\noindent
+\textbf{Closing}
+\newline
+$\,$\newline
+We hope that these modifications to the text have sufficiently clarified our work for experts
+in the field while also keeping it broad enough to remain interesting for non-experts.
+Thank you for considering our newly revised manuscript for publication.
 

### 2017-03-10 tex/nusselt_paper.tex
minor cleanups, adds some to abstract

@@
 plane-parallel, polytropically stratified atmospheres. 
-We hold the density stratification ($n_{\rho}$) and Prandtl 
+We hold the density stratification ($n_{\rho}$), aspect
+ratio, and Prandtl 
 number (Pr) constant while varying the superadiabaticity
-and Ra.  We find that Ma is primarily controlled by the
-superadiabaticity of the atmosphere.  We also examine
-the behavior of the Nusselt number (Nu), 
+and Ra.  We find that Ma is a strong function of the superadiabaticity
+and a weak function of the Rayleigh number.
+We also examine the behavior of the Nusselt number (Nu), 
 which quantifies the efficiency of convective heat transport,
 and the Reynolds number (Re), which quantifies how turbulent our
-solutions are.
+solutions are.  Both of these measures experience weaker scaling when
+the evolved solution has an average Ma of one than they do in the
+low Ma regime.
 %As Ra increases and $\text{Ma} \rightarrow 1$, a scaling 
@@
 
-In the widely-studied \RB (RB) problem of Boussinesq convection, 
-upflows and downflows are symmetrical and
+In the widely-studied \RB (RB) problem of incompressible Boussinesq convection, 
+upflows and downflows are symmetrical, and
 the conductive flux ($\propto \grad T$) approaches 
@@
 quantified by the Nusselt number (Nu), in plane-parallel, 
-two-dimensional, polytropically stratified atmospheres.  
+two- and three-dimensional, polytropically stratified atmospheres.  
 We vary $\epsilon$ and Ra while holding Pr, aspect ratio, boundary conditions,

### 2017-03-10 tex/nusselt_paper.tex
removes clunky Ra_top notation

@@
 and initial atmospheric stratification
-constant.  We describe experimental methods in section 
-\ref{sec:experiment}, including the construction of atmospheres, 
-equations, and numerical methods.  
-Results are described in section \ref{sec:results} 
-and their implications are discussed
-in section \ref{sec:discussion}.
+constant.  We also examie the behavior of flow speeds, as quantifed by Ma,
+and the level of turbulence in solutions, as quantified by Re.
+%We describe experimental methods in section 
+%\ref{sec:experiment}, including the construction of atmospheres, 
+%equations, and numerical methods.  
+%Results are described in section \ref{sec:results} 
+%and their implications are discussed
+%in section \ref{sec:discussion}.
 
@@
 equilibrium sets the value of gravity, $g = R T_t (m + 1)$, which is
-constant with depth.  We study two-dimensional atmospheres with aspect
-ratios of 4 where the $x$ coordinate has the range $[0, 4L_z]$.
-Select cases have been run in three dimensions with $y$ in the range
-$[0, 4L_z]$.
+constant with depth.  We study atmospheres with aspect
+ratios of 4 where both the $x$ and $y$ coordinates have the range $[0, 4L_z]$.
+In our 2D cases, we only consider $x$ and $z$.
 
@@
 \end{equation}
-where $\Delta S_0 = \epsilon\ln z_0$ is the entropy difference 
+where $\Delta S_0 = \epsilon\ln (L_z + 1)$ is the entropy difference 
 between the top and bottom boundaries and
@@
 the dynamic viscosity, $\mu = \rho\chi$, free to evolve
-as the density profile changes.
+as the density profile changes.  Throughout this letter,
+when we refer to Ra, we are referring to Ra$_{\text{top}}$.
 
@@
 64x256 coefficient points at the lowest values of 
-Ra to 1024x4096 coefficient points at Ra$_{\text{top}} > 10^{7}$ in 2D,
+Ra to 1024x4096 coefficient points at Ra $> 10^{7}$ in 2D,
 and 64x128$^2$ to  256x512$^2$ in 3D. 
@@
 we determined that the onset of convection in 2D
-occurs at $\text{Ra}_{\text{c,top}} = \{11.15, 10.06, 10.97, 10.97\}$ 
+occurs at $\text{Ra}_{\text{crit}} = \{11.15, 10.06, 10.97, 10.97\}$ 
 for $\epsilon = \{1.0, 0.5, 10^{-4}, 10^{-7}\}$ respectively.  Results
@@
 We studied Rayleigh
-numbers from values at onset to values $\geq 10^6$Ra$_{\text{c,top}}$ 
+numbers from values at onset to values $\geq 10^6$Ra$_{\text{crit}}$ 
 for $\epsilon = 0.5$, up to
-$\sim 10^5$Ra$_{\text{c,top}}$ at $\epsilon = 10^{-4}$, 
-up to $\sim 10^4$Ra$_{\text{c,top}}$ for $\epsilon = 1$,
-and up to $\sim 10^3$Ra$_{\text{c,top}}$ for $\epsilon = 10^{-7}$.
+$\sim 10^5$Ra$_{\text{crit}}$ at $\epsilon = 10^{-4}$, 
+up to $\sim 10^4$Ra$_{\text{crit}}$ for $\epsilon = 1$,
+and up to $\sim 10^3$Ra$_{\text{crit}}$ for $\epsilon = 10^{-7}$.
 
@@
 
-The variation of Nu with Ra$_{\text{top}}$ is shown in 
+The variation of Nu with Ra is shown in 
 Fig. \ref{fig:re_and_nu_v_ra}a.
-At low to moderate Ra$_{\text{top}}$, 
-Nu $\propto$ Ra$_{\text{top}}^{1/3}$ regardless of $\epsilon$,
+At low to moderate Ra, 
+Nu $\propto$ Ra$^{1/3}$ regardless of $\epsilon$,
 as predicted by classical \RB theory \cite{king&all2012}.
-At large Ra$_{\text{top}}$, Nu $\propto$ Ra$_{\text{top}}^{1/5}$ 
+At large Ra, Nu $\propto$ Ra$^{1/5}$ 
 at $\epsilon = 0.5$.
-The scaling of Nu with Ra$_{\text{top}}$ 
+The scaling of Nu with Ra 
 is unclear at low $\epsilon$ once Ra is sufficiently large
@@
 Fig. \ref{fig:re_and_nu_v_ra}b.
-At low Ra$_{\text{top}}$, Re $\propto$ Ra$_{\text{top}}^{3/4}$, but at high 
-Ra$_{\text{top}}$ where the average Ma $\approx 1$ for $\epsilon = 0.5$, 
-this scaling gives way to a Re $\propto$ Ra$_{\text{top}}^{1/2}$.
+At low Ra, Re $\propto$ Ra$^{3/4}$, but at high 
+Ra where the average Ma $\approx 1$ for $\epsilon = 0.5$, 
+this scaling gives way to a Re $\propto$ Ra$^{1/2}$.
 For large values of Ra but at low $\epsilon$, there appears to be a scaling

### 2017-03-10 tex/nusselt_paper.tex
removes clunky Ra_top notation
cleans up experiment section

@@
 as the density profile changes.  Throughout this letter,
-when we refer to Ra, we are referring to Ra$_{\text{top}}$.
+we will use Ra and Ra$_{\text{top}}$ interchangeably.
 
@@
 and the velocity $\bm{u} = u\hat{x} + v\hat{y} +  w\hat{z}$ 
-has no background component, and that $v = 0$ in our 2D runs..    
+has no background component.  In our 2D runs, $v = 0$.
 We evolve the Fully Compressible Navier-Stokes equations,
@@
 physical grid dimensions are 3/2 the size of the coefficient grid.  
-Physical grid sizes range from
+Grid sizes range from
 64x256 coefficient points at the lowest values of 
 Ra to 1024x4096 coefficient points at Ra $> 10^{7}$ in 2D,
-and 64x128$^2$ to  256x512$^2$ in 3D. 
+and from 64x128$^2$ to  256x512$^2$ in 3D. 
 By using IMEX timestepping, we implicitly step the 
@@
 timescales of the atmospheric buoyancy time,
-$t_b = \tau_I \sqrt{L_z/g\epsilon}$, 
-and all reported results are taken from time averages
-over many buoyancy times starting 100$t_b$ 
+$t_b = \tau_I \sqrt{L_z/g\epsilon}$. 
+All reported results are taken from time averages
+over many buoyancy times beginning 100$t_b$ 
 after the start of our simulations in order to

### 2017-03-10 tex/nusselt_paper.tex
finishes draft of paper

@@
 occurs at $\text{Ra}_{\text{crit}} = \{11.15, 10.06, 10.97, 10.97\}$ 
-for $\epsilon = \{1.0, 0.5, 10^{-4}, 10^{-7}\}$ respectively.  Results
-in 3D appear to be consistent with our 2D onset values.
+for $\epsilon = \{1.0, 0.5, 10^{-4}, 10^{-7}\}$, respectively.  These
+onset values hold in 3D.
 We studied Rayleigh
-numbers from values at onset to values $\geq 10^6$Ra$_{\text{crit}}$ 
-for $\epsilon = 0.5$, up to
-$\sim 10^5$Ra$_{\text{crit}}$ at $\epsilon = 10^{-4}$, 
-up to $\sim 10^4$Ra$_{\text{crit}}$ for $\epsilon = 1$,
-and up to $\sim 10^3$Ra$_{\text{crit}}$ for $\epsilon = 10^{-7}$.
+numbers $\lesssim \left\{10^7, 10^5, 10^4, 10^3\right\}$Ra$_{\text{crit}}$ 
+for $\epsilon = \{0.5, 10^{-4}, 1.0, 10^{-7}\}$, respectively.
 
@@
 $\epsilon$ and a weak function of Ra.  
-When Ma $< 1$, Ma $\propto \epsilon^{1/2}$, 
-but this relation break down as the mean
-Ma approaches 1 and the flows become supersonic (see Fig. \ref{fig:ma_v_eps}a).  
-When Ma is small,
-Ma $\propto$ Ra$^{1/4}$.  At high epsilon, 
-this scaling breaks down once the mean atmospheric Ma reaches 1.
+When Ma $< 1$, we observe a scaling law of
+Ma(Ra$, \epsilon) \propto \epsilon^{1/2}$Ra$^{1/4}$, 
+but this relation breaks down as the mean
+Ma approaches 1 and the flows become supersonic (see Fig. \ref{fig:ma_v_eps}).  
 Furthermore, the value of $\epsilon$ sets the size of the
-evolved thermodynamic variables, 
-$T_1/T_0, \rho_1/\rho_0 \propto \epsilon$.  Thus, fluctuations
-are very small for low Ma flows, 
-but are order 1 when $\epsilon$ and Ma approach 1.
+evolved thermodynamic variables, such that
+$T_1/T_0 \propto \epsilon$ and $\rho_1/\rho_0 \propto \epsilon$.  
+These fluctuations are very small when $\epsilon$ and Ma are small,
+but can be O(1) for values of $\epsilon$ near $m_{\text{ad}}$.
 
@@
 
-Low Ma flows ($\epsilon = 10^{-4}$)
+Low Ma flows (e.g. $\epsilon = 10^{-4}$)
 display the classic narrow downflow and broad upflow lanes of stratified
 convection (Fig. \ref{fig:entropy_snapshots}a).
-While it has been suggested that pressure forces 
-cause symmetry breaking in up- and downflows
+While it has been suggested that buoyancy breaking as 
+a result of pressure forces leads to
+the asymmetric nature of up- and downflows
 \cite{hurlburt&all1984}, at low $\epsilon$ this 
-effect seems to be secondary to flows obeying mass conservation as they traverse
+effect seems to be unimportant, and the convective structures form
+as a result of flows obeying mass conservation while traversing
 the stratified medium.  
@@
 allows the flux at the boundaries to vary, while also allowing
-for large-scale ``axisymmetric'' horizontal velocities.
-Runs at $\text{Ra }> 10^4$
+for domain-wide horizontal velocity profiles along the boundaries.
+2D runs at $\text{Ra }> 10^3$Ra$_{\text{crit}}$
 and $\epsilon = 10^{-4}$ exhibit long-term states of
@@
 A long time average
-over both of these states produce flat flux profiles which
+over both of these states produces a flat flux profile which
 can be sensibly analyzed, but the presence of these time-dependent states
-makes it difficult to measure fluid quantities in these cases.
+makes it difficult to measure fluid quantities in these higher-Ra
+cases at low $\epsilon$.
 
-At large Ma ($\epsilon = 0.5$), bulk thermodynamic structures are similar but
+At high Ma (e.g. $\epsilon = 0.5$), bulk thermodynamic structures are similar but
 shock systems form in the upper atmosphere near downflow lanes 
-once Ra is sufficiently large  (Fig. \ref{fig:entropy_snapshots}b,c).
+for sufficiently large values of $\epsilon$ and Ra (Fig. \ref{fig:entropy_snapshots}b,c).
 Similar shock phenomena were reported in
@@
 z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
-respectively and $\langle \rangle$ are volume averages.  
+and $\langle \rangle$ are volume averages.  
 $F_{\text{A}} \equiv -\langle\kappa\rangle \partial_z T_{\text{ad}}$ 
-is the conductive flux of the proper corresponding adiabatic atmosphere
-with $\partial_z T_{\text{ad}} \equiv - g / c_{P}$ 
-for a compressible ideal gas in hydrostatic equilibrium \cite{spiegel&veronis1960}.  Here we specify
+is the conductive flux of the proper corresponding adiabatic atmosphere in
+in thermal equilibrium.
+For a compressible ideal gas in hydrostatic equilibrium,
+$\partial_z T_{\text{ad}} \equiv - g / c_{P}$ \cite{spiegel&veronis1960}.  
+It is important to measure the evolved value of
 $\langle \kappa \rangle = \langle \rho\chi \rangle$, which is nearly
@@
 Nu $\propto$ Ra$^{1/3}$ regardless of $\epsilon$,
-as predicted by classical \RB theory \cite{king&all2012}.
+reminiscent of scaling laws in classical \RB theory \cite{king&all2012}.
 At large Ra, Nu $\propto$ Ra$^{1/5}$ 
@@
 low $\epsilon$ flows with fixed-flux boundary conditions or
-no-slip boundary conditions that disallow these large scale
-structures.
+no-slip boundary conditions that disallow time-dependent shear states.
 
-The Reynolds number and Peclet number,
-\begin{equation}
-\text{Re} = \frac{|\bm{u}| L_z}{\nu};\,\,\,\,\text{Pe} = \text{Pr}\,\text{Re},
-\end{equation}
-quantify the importance of advection to diffusion in the evolved
+The Reynolds number (Re = $|\bm{u}|L_z/\nu$) and Peclet number
+(Pe = Pr Re)
+compare the importance of advection to diffusion in the evolved
 convective state.  For Pr = 1, such as in this work, Pe = Re.  
@@
 Fig. \ref{fig:re_and_nu_v_ra}b.
-At low Ra, Re $\propto$ Ra$^{3/4}$, but at high 
-Ra where the average Ma $\approx 1$ for $\epsilon = 0.5$, 
-this scaling gives way to a Re $\propto$ Ra$^{1/2}$.
+At low Ra, Re $\propto$ Ra$^{3/4}$.  At high Ra and $\epsilon$, 
+where the average Ma $\approx 1$, 
+this scaling gives way to a Re $\propto$ Ra$^{1/2}$,
+where all changes in Re are due to the lowering of the diffusivity
+through raising Ra.
 For large values of Ra but at low $\epsilon$, there appears to be a scaling
-of Re $\propto$ Ra$^{2/3}$.
+of Re $\propto$ Ra$^{2/3}$, but once again the shearing states have made
+these points difficult to measure.
 
@@
 form in the boundary layers, as was reported by \cite{brandenburg&all2005}.  
-Regardless, the agreement of Nu across $\epsilon$, particularly at
-low Ra, despite the difference in effective stratifications is striking.
+The agreement of Nu across $\epsilon$ (Fig. \ref{fig:re_and_nu_v_ra}a), 
+particularly at low Ra in which all four of our cases collapse onto a single
+power law, is striking in light of the vastly different evolved stratifications
+felt by the flows.
 
@@
 the properties of our 2D and 3D results, which aligns with expectations
-of Boussinesq theory and DNS results at values of Pr $\geq$ 1 \cite{ahlers&all2009}.
+of Boussinesq theory and numerical simulation results at 
+values of Pr $\geq$ 1 \cite{ahlers&all2009}.
 
 At low Ra and Ma, the scaling of Nu with Ra is reminiscent of RB convection.  
-However, at high Ra and Ma, the scaling of Nu becomes weakear, decreasing
-from a 1/3 to a 1/5 power law, a decrease by roughly a factor of 1/3.
+However, at high Ra and Ma, the scaling of Nu becomes weaker, changing
+from a 1/3 to a 1/5 power law, a decrease by nearly a factor of 1/3.
 Similarly, the Reynolds number switches from a 3/4 power law to
-a 1/2 scaling in this regime shift, a similar decrease by a factor of 1/3.
+a 1/2 scaling in this regime shift, a similar decrease.
 This seems to suggest that a large portion of the scaling of the Nusselt number
-comes from increases in velocity as Ra increases.  Once the velocity reaches
+and Reynolds number in the low-Ma regime
+comes from increases in velocity.  Once the velocity reaches
 its natural maximum, heat transport can no longer benefit from increased velocities.
-The same is true of the Reynolds number, which tracks increases in velocities as
-the flows become more turbulent, but which can only scale with the diffusivities
+The same is true of the Reynolds number, which scales directly with system diffusivities
 once the Mach number reaches its maximum value.
 
-Time-dependent oscillating shear states have developed spontaneously, 
-as seen before in RB convection \cite{goluskin&all2014}, and these should
+Time-dependent oscillating shear states have developed spontaneously
+at values of $\epsilon=10^{-4}$ and Ra $\gtrsim 10^3$Ra$_{\text{crit}}$ in our 2D simulations.  
+Similar states have been observed in 2D RB convection \cite{goluskin&all2014}, and these should
 be studied in more detail.  These states are fundamentally in flux disequilibrium
-and make it very difficult to calculate a meaningful Nusselt number.  It would
-be beneficial for future studies to study solutions with fixed flux or no slip
-boundary conditions to better converge and study cases at high $\epsilon$ and low
+and last for large time scales (O(100$t_b$)),
+making it very difficult to choose a proper time window over which to calculate a 
+meaningful Nusselt number.  It would
+be beneficial for future studies to examine atmosperes with fixed flux or no slip
+boundary conditions to better converge and study cases at low $\epsilon$ and high
 Ra.
@@
 boundary layer density inversions interact with
-thermal plumes.
+the formation and transport properties of thermal plumes.
 

### 2017-03-10 tex/nusselt_paper.tex
finishes off pre-PDP paper stuff

@@
 \includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
-\caption{Characteristic entropy fluctuations in evolved flows. 
+\caption{Characteristic entropy fluctuations in evolved flows roughly
+140$t_b$ after the start of simulations. 
 The time- and horizontally-averaged profile is removed in all cases.  
-(a) At high $\epsilon$, shock systems form near the upper downflow lanes 
-($x \approx 45, z \approx 15-19$) at sufficiently high Ra.
-Shock-heated fluid then flows into the downflows as the shocks propagate across upflows.
-(b) At low $\epsilon$ but at the same Ra, shock systems are absent, 
-but otherwise the dynamics are similar.  
-(c) As Ra is increased, downflows no longer span
-the entirety of the domain and individual 
-small eddies are responsible for carrying the flux.
+(a) An $\epsilon = 10^{-4}$, low Ma flow. (b) An $\epsilon = 0.5$, flow,
+in which shock systems can be seen in the upper atmosphere (e.g.
+$(x, z) \approx (30, 18-19), (70, 15-19))$.
+(c) A high Ra, $\epsilon = 0.5$ case.  Convective structures become
+much smaller scale, and shock systems can be see near $(x, z) \approx (30, 16-19),
+(65, 17-19)$.
 \label{fig:entropy_snapshots} }
@@
 is unclear at low $\epsilon$ once Ra is sufficiently large
-for shearing states to occur.  It would be beneficial to study
-low $\epsilon$ flows with fixed-flux boundary conditions or
-no-slip boundary conditions that disallow time-dependent shear states.
+for shearing states to occur.  It is also important to note that
+the value of Nu is heavily dependent upon the specific thermodynamic
+structures of the solution, as double roll states will transport
+heat more efficiently than single roll states, and slight changes in
+Ra can result in a solution latching on to one solution or the other.
 

### 2017-03-17 tex/nusselt_paper.tex
pounded in a bunch of words about the 2D v 3D results

@@
 and Ra.  We find that Ma is a strong function of the superadiabaticity
-and a weak function of the Rayleigh number.
-We also examine the behavior of the Nusselt number (Nu), 
-which quantifies the efficiency of convective heat transport,
-and the Reynolds number (Re), which quantifies how turbulent our
-solutions are.  Both of these measures experience weaker scaling when
-the evolved solution has an average Ma of one than they do in the
-low Ma regime.
+in both 2D and 3D simulations, and that it is a 
+weak function of Ra in 2D.
+In 2D simulations, the scaling of the Nusselt Number (Nu) and the Reynolds number (Re)
+with Ra weaken
+once the mean Ma of the solution is unity, but in 3D
+Re and Nu seem to have consistent scaling across Ra.
+We further find that when the superadiabaticity and Ma are large,
+density inversions form in the thermal boundary layers.
 %As Ra increases and $\text{Ma} \rightarrow 1$, a scaling 
@@
 $\epsilon$ and a weak function of Ra.  
-When Ma $< 1$, we observe a scaling law of
+In our 2D runs, when Ma $< 1$ we observe a scaling law of
 Ma(Ra$, \epsilon) \propto \epsilon^{1/2}$Ra$^{1/4}$, 
@@
 Ma approaches 1 and the flows become supersonic (see Fig. \ref{fig:ma_v_eps}).  
+In 3D, Ma appears to be a function of $\epsilon$ alone, with
+Ma $\propto \epsilon^{1/2}$.
 Furthermore, the value of $\epsilon$ sets the size of the
@@
 \includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
-\caption{Characteristic entropy fluctuations in evolved flows roughly
+\caption{Characteristic entropy fluctuations in evolved 2D flows roughly
 140$t_b$ after the start of simulations. 
@@
 Fig. \ref{fig:re_and_nu_v_ra}a.
-At low to moderate Ra, 
+In 2D and at low to moderate Ra, 
 Nu $\propto$ Ra$^{1/3}$ regardless of $\epsilon$,
@@
 Ra can result in a solution latching on to one solution or the other.
+In 3D, it appears that Nu $\propto$ Ra$^{2/7}$, a classic scaling law
+seen in RB studies \cite{johnston&doering2009}.
 
@@
 Fig. \ref{fig:re_and_nu_v_ra}b.
-At low Ra, Re $\propto$ Ra$^{3/4}$.  At high Ra and $\epsilon$, 
+In 2D and at low Ra, Re $\propto$ Ra$^{3/4}$.  At high Ra and $\epsilon$, 
 where the average Ma $\approx 1$, 
@@
 of Re $\propto$ Ra$^{2/3}$, but once again the shearing states have made
-these points difficult to measure.
+these points difficult to measure.  In 3D, the scaling of Re appears to
+consistently be Re $\propto$ Ra$^{1/2}$, consistent with the high-$\epsilon$,
+high Ra results seen in 2D and the lack of scaling of Ma with Ra in Fig. 
+\ref{fig:ma_v_eps}b.
 
@@
 scale heights present in the evolved solution using two measures.  
-We find that once the average Ma of the domain
+We find that in 2D, once the average Ma of the domain
 becomes approximately one, large density inversions begin to 
@@
 power law, is striking in light of the vastly different evolved stratifications
-felt by the flows.
+felt by the flows.  In 3D, despite the Ma not scaling with Ra, we see similar density
+inversions at high $\epsilon$ once Ra is sufficiently large.
 
@@
 properties of stratified convection. 
-We see little difference between
-the properties of our 2D and 3D results, which aligns with expectations
+The primary difference we see between our 2D and 3D results is that the Ma
+is not a function of Ra in 3D, and this has far-reaching consequences.  Otherwise,
+we see only slightly different scaling in Nu(Ra) in 2D and 3D, 
+which aligns with expectations
 of Boussinesq theory and numerical simulation results at 

### 2017-03-21 tex/nusselt_paper.tex
pushes changes made with Ben

@@
 the convective envelope of the Sun, which spans 14 density scale heights.
-In the bulk of these systems, flows are at very low Mach Number (Ma), 
+In the bulk of these systems, flows are at very low Mach number (Ma), 
 but numerical constraints have restricted most studies of 
 compressible convection to high Ma.
-These studies have provided important insight into the low temperature, 
-high Ma region near the Sun's surface, but few fundamental
-properties of low Ma convection which characterize deeper motions
+These prior studies have provided important insight into the low temperature, 
+high Ma region near the Sun's surface. Few fundamental
+properties of low Ma convection, which characterizes deeper motions,
 are known.
 
-%Convective heat transport is essential
-%in the cores of high mass stars,
-%the envelopes of low mass stars, and the atmospheres of terrestrial and 
-%jovian planets.  These astrophysical systems have density stratifications
-%ranging from a few density scale heights (e.g. massive star cores)
-%up to 14 density scale heights in the convective envelopes of low
-%mass stars such as the Sun.
-%Atmospheric stratification presumably modifies the fundamental
-%dynamics and heat transport mechanisms of these atmospheres.
-%Understanding the fundamental
-%properties of compressible convection in stratified media is essential
-%to characterizing systems in astrophysics and planetary sciences.  
-%Numerical constraints have often restricted studies of compressible
-%convection to moderately high Mach number (Ma), appropriate to regions near 
-%the Sun's surface.  Few fundamental properties of
-%low Ma convection, which occurs in the deep solar interior, are known.
-
 In the widely-studied \RB (RB) problem of incompressible Boussinesq convection, 
-upflows and downflows are symmetrical, and
+a negative temperature gradient leads to convective instability.
+In the evolved solution, upflows and downflows are symmetrical, the
+temperature in the interior becomes isothermal and
 the conductive flux ($\propto \grad T$) approaches 
-zero in the convective interior.
+zero there. 
+For compressible convection in a stratified atmosphere, a
+negative entropy gradient leads to convective instability.
 Early numerical experiments of moderate-to-high Ma compressible convection
@@
 \cite{cattaneo&all1991, brummell&all1996} dimensions
-revealed that these two hallmark characteristics of RB convection change
-significantly when stratification is included.  Downflow lanes
+revealed that the evolved state differs from the RB case.
+Downflow lanes
 become fast and narrow, and upflow lanes turn into broad, slow upwellings.
-Furthermore, the \emph{entropy} gradient is negated by convection 
-rather than the temperature gradient, and
-a significant conductive flux can exist in the presence of
+Furthermore, the \emph{entropy} gradient is negated by convection in the interior, and
+a significant temperature gradient and conductive flux persist in the presence of
 efficient convection.
@@
 number (Re, the strength of advection to viscous diffusion)
-and the Peclet number (Pe = Re Pr).  Stratified atmospheres
-with negative entropy gradients are unstable to convection.
-The magnitude of the unstable entropy gradient, or the superadiabaticity,
+and the Peclet number (Pe, advection vs. thermal diffusion).  
+In stratified atmospheres, the magnitude of the unstable entropy gradient, 
 joins Ra and Pr as an important control parameter.  This 
-\emph{superadiabatic excess} \cite{graham1975}, $\epsilon$, which 
-sets the scale of the atmospheric entropy gradient,
-primarily controls the Ma of the evolved solution.
-
-%In RB convection, there exist two primary control parameters: 
-%the Rayleigh number (Ra, the ratio of
-%buoyant driving to diffusive damping) and the Prandtl number 
-%(Pr, the ratio of viscous to thermal
-%diffusivity).  These numbers coupled with the aspect ratio of 
-%the physical domain and the boundary conditions
-%determine the dynamics of the convection.  In stratified atmospheres, 
-%in addition to specifying the equation of state and
-%fundamental properties of the gas, the two control parameters of 
-%RB convection are joined by the degree of
-%stratification across the domain and the characteristic 
-%Ma of the convective flows.  
-%Polytropically stratified atmospheres, such as those used in 
-%early studies \cite{graham1975, chan&all1982, hurlburt&all1984, 
-%cattaneo&all1990, cattaneo&all1991, brummell&all1996}, are an ideal extension of
-%RB convection into the stratified realm because the two additional 
-%control parameters are directly linked to
-%basic properties of the atmosphere.  The density stratification is 
-%set by the number of density scale heights (\nrho)
-%the atmosphere spans, and Ma is controlled 
-%by the superadiabatic excess ($\epsilon$),
-%the deviation of the polytropic index from the adiabatic polytropic 
-%index \cite{graham1975}.
+\emph{superadiabatic excess} \cite{graham1975}, $\epsilon$,
+sets the scale of the atmospheric entropy gradient.
+We find here that $\epsilon$ primarily controls the Ma of the evolved solution.
 
@@
 and initial atmospheric stratification
-constant.  We also examie the behavior of flow speeds, as quantifed by Ma,
-and the level of turbulence in solutions, as quantified by Re.
-%We describe experimental methods in section 
-%\ref{sec:experiment}, including the construction of atmospheres, 
-%equations, and numerical methods.  
-%Results are described in section \ref{sec:results} 
-%and their implications are discussed
-%in section \ref{sec:discussion}.
+constant.  We also examine the behavior of flow properties, as quantifed by Ma and Re.
 
@@
 We examine a monatomic ideal gas with an adiabatic index of
-$\gamma = 5/3$ whose equation of state is $P = R\rho T$.
-This is consistent with the approach used in earlier work
+$\gamma = 5/3$ whose equation of state is $P = R\rho T$. In this
+work we take $R = 1$.
+This is consistent with the approach used in earlier work \cite{graham1975, chan&all1982,
+hurlburt&all1984, cattaneo&all1990, cattaneo&all1991, brummell&all1996} 
 and is the simplest stratified extension of RB.
@@
 where $m$ is the polytropic index and $L_z$ is the depth of the atmosphere.
+Subscript 0 indicates initial conditions and subscript $t$ indicates values
+at $z = L_z$.
 The height coordinate, $z$, increases upwards in the range $[0, L_z]$.  We
 specify the depth of the atmosphere, $L_z = e^{n_{\rho}/m} - 1$, by choosing
-the number of density scale heights, $n_{\rho}$, it spans.
+the number of density scale heights, $n_{\rho}$, it spans initially.
 Throughout this letter we set $n_{\rho} = 3$.  Satisfying hydrostatic
-equilibrium sets the value of gravity, $g = R T_t (m + 1)$, which is
+equilibrium sets the value of gravity, $g = T_t (m + 1)$, which is
 constant with depth.  We study atmospheres with aspect
@@
 The atmospheric thermal diffusivity, $\chi$,
-and kinematic viscosity (or viscous diffusivity), $\nu$,
+and kinematic viscosity (viscous diffusivity), $\nu$,
 are determined by the Rayleigh number (Ra) and the Prandtl
@@
 \end{equation}
-where $\Delta S_0 = \epsilon\ln (L_z + 1)$ is the entropy difference 
-between the top and bottom boundaries and
-$c_P = R\gamma(\gamma-1)^{-1}$ is the specific heat 
+where $\Delta S_0 = \epsilon\ln (1 + L_z)$ is the initial entropy difference 
+between the top and bottom of the atmosphere and
+$c_P = \gamma(\gamma-1)^{-1}$ is the specific heat 
 at constant pressure. The profiles of $\nu$ and $\chi$ are constant with
@@
 the thermal conductivity, $\kappa = \rho\chi$, and
-the dynamic viscosity, $\mu = \rho\chi$, free to evolve
-as the density profile changes.  Throughout this letter,
-we will use Ra and Ra$_{\text{top}}$ interchangeably.
+the dynamic viscosity, $\mu = \rho\nu$, free to evolve
+as the density profile changes.  Henceforth,
+when we use Ra, we are referring to Ra$_{\text{top}}$.
 
-We decompose our thermodynamic variables such that $T = T_0 + T_1$ and
-$\ln\rho = (\ln\rho)_0 + (\ln\rho)_1$, 
-and the velocity $\bm{u} = u\hat{x} + v\hat{y} +  w\hat{z}$ 
-has no background component.  In our 2D runs, $v = 0$.
 We evolve the Fully Compressible Navier-Stokes equations,
@@
 Taking an inner product of
-(\ref{eqn:momentum_eqn}) with $\bm{u}$ and adding it to 
-(\ref{eqn:energy_eqn}) reveals the full energy equation,
+(\ref{eqn:momentum_eqn}) with $\rho\bm{u}$ and adding it to 
+$\rho c_V\times$(\ref{eqn:energy_eqn}) reveals the full energy equation,
 \begin{equation}
@@
 and the viscous flux, 
-$\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$, and each 
-must be considered. 
-Understanding how these fluxes interact  
+$\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$.
+Understanding how each of these fluxes interact  
 is crucial in characterizing convective heat transport.
@@
 Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
+We decompose our thermodynamic variables such that $T = T_0 + T_1$ and
+$\ln\rho = (\ln\rho)_0 + (\ln\rho)_1$, 
+and the velocity $\bm{u} = u\hat{x} + v\hat{y} +  w\hat{z}$.
+In our 2D runs, $v = 0$.
+Subscript 0 variables, set by (\ref{eqn:polytrope}), 
+have no time derivative and vary only in $z$.
 Variables are time-evolved on a dealiased Chebyshev (vertical)
@@
 physical grid dimensions are 3/2 the size of the coefficient grid.  
-Grid sizes range from
-64x256 coefficient points at the lowest values of 
-Ra to 1024x4096 coefficient points at Ra $> 10^{7}$ in 2D,
+Domain sizes range from
+64x256 coefficients at the lowest values of 
+Ra to 1024x4096 coefficients at Ra $> 10^{7}$ in 2D,
 and from 64x128$^2$ to  256x512$^2$ in 3D. 
@@
 stiff linear acoustic wave contribution and are able to
-efficiently study flows at moderate ($\approx 1$) 
-and very low ($\approx 10^{-4}$) Ma.  Our equations take the form
+efficiently study flows at high ($\sim 1$) 
+and low ($\sim 10^{-4}$) Ma.  Our equations take the form
 of the FC equations in \cite{lecoanet&all2014}, extended to include
@@
 We filter this noise spectrum in coefficient space, 
-such that 25\% of the coefficients
+such that only the lower 25\% of the coefficients
 have power. We non-dimensionalize our computational domains by setting
-all thermodynamic variables to unity at $z = L_z$ by choosing
+all thermodynamic variables to unity at $z = L_z$ choosing
 $R = T_t = \rho_t = 1$.  By this choice, the non-dimensional
-grid length scale is the inverse temperature gradient scale and the 
-simulation timescale is the isothermal sound crossing time, 
+length scale is the inverse temperature gradient scale and the 
+timescale is the isothermal sound crossing time, 
 $\tau_I$, of this unit length.
@@
 All reported results are taken from time averages
-over many buoyancy times beginning 100$t_b$ 
-after the start of our simulations in order to
+over many $t_b$ beginning \{100, 40\}$t_b$
+after the start of our \{2D, 3D\} simulations in order to
 assure our results are not biased by the convective transient.
@@
 atmosphere.
-(a) Ma is plotted as a function of $\epsilon$, the superadiabatic excess,
-at various values of Ra.
-(b) Ma is plotted as a function of Ra at various values of $\epsilon$.
+(a) Ma, at various values of Ra, 
+is plotted as a function of $\epsilon$.
+(b) Ma, at various values of $\epsilon$, 
+is plotted as a function of Ra/Ra$_{\text{crit}}$.
 Larger symbols with white dots designate 3D runs.
@@
 variance with depth. By performing a linear stability analysis, 
-we determined that the onset of convection in 2D
+we determined that the onset of convection
 occurs at $\text{Ra}_{\text{crit}} = \{11.15, 10.06, 10.97, 10.97\}$ 
-for $\epsilon = \{1.0, 0.5, 10^{-4}, 10^{-7}\}$, respectively.  These
-onset values hold in 3D.
-We studied Rayleigh
-numbers $\lesssim \left\{10^7, 10^5, 10^4, 10^3\right\}$Ra$_{\text{crit}}$ 
-for $\epsilon = \{0.5, 10^{-4}, 1.0, 10^{-7}\}$, respectively.
+for $\epsilon = \{1.0, 0.5, 10^{-4}, 10^{-7}\}$, respectively.
 
-We find that the Mach number is a strong function of 
+We measure the adiabatic Mach number (Ma = $|\bm{u}|/\sqrt{\gamma T}$).
+We find that Ma is a strong function of 
 $\epsilon$ and a weak function of Ra.  
 In our 2D runs, when Ma $< 1$ we observe a scaling law of
-Ma(Ra$, \epsilon) \propto \epsilon^{1/2}$Ra$^{1/4}$, 
-but this relation breaks down as the mean
-Ma approaches 1 and the flows become supersonic (see Fig. \ref{fig:ma_v_eps}).  
-In 3D, Ma appears to be a function of $\epsilon$ alone, with
-Ma $\propto \epsilon^{1/2}$.
-Furthermore, the value of $\epsilon$ sets the size of the
-evolved thermodynamic variables, such that
+Ma(Ra$, \epsilon) \propto \epsilon^{1/2}$Ra$^{1/4}$.
+this relation breaks down as the mean
+Ma approaches 1 (see Fig. \ref{fig:ma_v_eps}).  This transition
+occurs near Ra/Ra$_\text{crit} \approx \{10^{2}, 10^{3}\}$ for $\epsilon = \{1, 0.5\}$.
+In our limited 3D runs, Ma appears to be a function of $\epsilon$ alone, with
+Ma $\propto \epsilon^{1/2}$, so at high Ra, Ma$_{\text{3D}} < \text{Ma}_{\text{2D}}$.
+The value of $\epsilon$ also sets the size of the
+evolved thermodynamic fluctuations, such that
 $T_1/T_0 \propto \epsilon$ and $\rho_1/\rho_0 \propto \epsilon$.  
 These fluctuations are very small when $\epsilon$ and Ma are small,
-but can be O(1) for values of $\epsilon$ near $m_{\text{ad}}$.
+but can be O(1) for values of $\epsilon$ near 1.
 
@@
 The time- and horizontally-averaged profile is removed in all cases.  
-(a) An $\epsilon = 10^{-4}$, low Ma flow. (b) An $\epsilon = 0.5$, flow,
-in which shock systems can be seen in the upper atmosphere (e.g.
-$(x, z) \approx (30, 18-19), (70, 15-19))$.
-(c) A high Ra, $\epsilon = 0.5$ case.  Convective structures become
-much smaller scale, and shock systems can be see near $(x, z) \approx (30, 16-19),
-(65, 17-19)$.
+(a) A low Ma flow at moderate Ra. (b) A high Ma flow at the same Ra as in (a).
+(c) a high Ma flow at high Ra.
+Shock systems can be seen in the upper atmosphere of the high Ma flows,
+for example at $(x, z) \approx (70, 15-19)$ in (b) and $(x, z) \approx 
+(65, 17-19)$ in (c).
 \label{fig:entropy_snapshots} }
@@
 
-Low Ma flows (e.g. $\epsilon = 10^{-4}$)
+Low Ma flows (e.g., $\epsilon = 10^{-4}$)
 display the classic narrow downflow and broad upflow lanes of stratified
 convection (Fig. \ref{fig:entropy_snapshots}a).
-While it has been suggested that buoyancy breaking as 
-a result of pressure forces leads to
-the asymmetric nature of up- and downflows
-\cite{hurlburt&all1984}, at low $\epsilon$ this 
-effect seems to be unimportant, and the convective structures form
-as a result of flows obeying mass conservation while traversing
-the stratified medium.  
-Our choice of fixed-temperature, stress free boundary conditions 
-allows the flux at the boundaries to vary, while also allowing
-for domain-wide horizontal velocity profiles along the boundaries.
-2D runs at $\text{Ra }> 10^3$Ra$_{\text{crit}}$
-and $\epsilon = 10^{-4}$ exhibit long-term states of
-flux disequilibrium, in which roll solutions such as those pictured in 
-Fig. \ref{fig:entropy_snapshots}a
-are punctuated by shearing states similar to those previously
-reported in two-dimensional RB convection \cite{goluskin&all2014}.  
-During both of these states, the system is in flux disequilibrium.
-A long time average
-over both of these states produces a flat flux profile which
-can be sensibly analyzed, but the presence of these time-dependent states
-makes it difficult to measure fluid quantities in these higher-Ra
-cases at low $\epsilon$.
-
-At high Ma (e.g. $\epsilon = 0.5$), bulk thermodynamic structures are similar but
+At high Ma (e.g., $\epsilon = 0.5$), bulk thermodynamic structures are similar but
 shock systems form in the upper atmosphere near downflow lanes 
@@
 small eddies which traverse the domain multiple
-times before diffusing.
+times before diffusing.  Our choice of fixed-temperature, stress free boundary conditions 
+allows the flux at the boundaries to vary, while also allowing
+for mean horizontal velocity profiles along the boundaries (winds).
+We find these windy convective states, reminiscent of similar states
+in RB convection \cite{goluskin&all2014}, at $\epsilon = 10^{-4}$ for high
+values of Ra. Roll states (Fig. \ref{fig:entropy_snapshots}a) with high convective
+transport alternate with windy states of lower transport.
 
@@
 \caption{
-(a) Variation of Nu as Ra increases at high and low $\epsilon$. 
-Errors bars indicate the properly normalized range of the
-value of Nu as a function of depth and
+Flow properties at high and low $\epsilon$. 
+(a) Nu vs. Ra/Ra$_{\text{crit}}$.
+Errors bars indicate the variance of Nu with depth;
 large error bars indicate a poorly converged solution.
-(b) Variation of Re as Ra increases at high and low $\epsilon$.
+(b) Re vs. Ra/Ra$_{\text{crit}}$.
 Re is measured at the midplane of the atmosphere.
 Larger symbols with white dots designate 3D runs.
- \label{fig:re_and_nu_v_ra}.
+ \label{fig:re_and_nu_v_ra}
 }
@@
 $F_{\text{A}} \equiv -\langle\kappa\rangle \partial_z T_{\text{ad}}$ 
-is the conductive flux of the proper corresponding adiabatic atmosphere in
-in thermal equilibrium.
+is the conductive flux of the proper corresponding adiabatic atmosphere
 For a compressible ideal gas in hydrostatic equilibrium,
@@
 The variation of Nu with Ra is shown in 
-Fig. \ref{fig:re_and_nu_v_ra}a.
+Fig. \ref{fig:re_and_nu_v_ra}a.  We find that the Nu depends primarily
+on Ra, not on $\epsilon$, except where dynamical regimes change.
 In 2D and at low to moderate Ra, 
@@
 reminiscent of scaling laws in classical \RB theory \cite{king&all2012}.
-At large Ra, Nu $\propto$ Ra$^{1/5}$ 
-at $\epsilon = 0.5$.
-The scaling of Nu with Ra 
-is unclear at low $\epsilon$ once Ra is sufficiently large
-for shearing states to occur.  It is also important to note that
+As the flow becomes supersonic,  Nu $\propto$ Ra$^{1/5}$.
+2D runs at $\text{Ra }> 10^3$Ra$_{\text{crit}}$
+and $\epsilon = 10^{-4}$ exhibit windy convective states.
+In these runs, the system is in flux equilibrium only when
+time averaged over roll states and windy states.
+A long time average
+over both of these states produces a flat flux profile which
+can be sensibly analyzed, but the presence of these time-dependent states
+makes it difficult to equilibrate these higher Ra cases.
+It is also important to note that
 the value of Nu is heavily dependent upon the specific thermodynamic
@@
 heat more efficiently than single roll states, and slight changes in
-Ra can result in a solution latching on to one solution or the other.
-In 3D, it appears that Nu $\propto$ Ra$^{2/7}$, a classic scaling law
+Ra can result in a simulation latching on to one solution or the other.
+In our limited 3D runs, it appears that Nu $\propto$ Ra$^{2/7}$, a classic scaling law
 seen in RB studies \cite{johnston&doering2009}.
 
-The Reynolds number (Re = $|\bm{u}|L_z/\nu$) and Peclet number
+The rms Reynolds number (Re = $|\bm{u}|L_z/\nu$) and Peclet number
 (Pe = Pr Re)
@@
 Re at the midplane ($z=L_z/2$) of the atmosphere in
-Fig. \ref{fig:re_and_nu_v_ra}b.
-In 2D and at low Ra, Re $\propto$ Ra$^{3/4}$.  At high Ra and $\epsilon$, 
-where the average Ma $\approx 1$, 
-this scaling gives way to a Re $\propto$ Ra$^{1/2}$,
-where all changes in Re are due to the lowering of the diffusivity
-through raising Ra.
-For large values of Ra but at low $\epsilon$, there appears to be a scaling
-of Re $\propto$ Ra$^{2/3}$, but once again the shearing states have made
-these points difficult to measure.  In 3D, the scaling of Re appears to
-consistently be Re $\propto$ Ra$^{1/2}$, consistent with the high-$\epsilon$,
-high Ra results seen in 2D and the lack of scaling of Ma with Ra in Fig. 
-\ref{fig:ma_v_eps}b.
+Fig. \ref{fig:re_and_nu_v_ra}b.  Largely we find that Ra and
+Pe depend on Ra, but not $\epsilon$, except when the flow states
+change.
+In 2D and at low Ra, Re $\propto$ Ra$^{3/4}$.  When the flows
+become supersonic, 
+this scaling gives way to Re $\propto$ Ra$^{1/2}$.
+In our limited 3D runs, the scaling of Re is
+Re $\propto$ Ra$^{1/2}$, consistent with the supersonic results.
 
@@
 \includegraphics[width=3.4375in]{./figs/density_v_ra.png}
-\caption{\label{fig:nrho_v_ra} The stratification of 
-evolved solutions is measured
-in two ways.  Solid symbols show $\ln(\rho(z=0)/\rho(z=L_z))$, 
-the density contrast
-as measured at the upper and lower boundary.  The empty symbols show 
-$\ln(\text{max}(\rho)/\text{min}(\rho))$. 
-Unsurprisingly, at low $\epsilon$ the evolved
-$n_{\rho}$ is not different from the initial conditions to first order.  
+\caption{\label{fig:nrho_v_ra} 
+Solid symbols show the density contrast measured
+in density scale heights between the upper and lower boundary, 
+$n_\rho = \ln[\rho(z=0)/\rho(z=L_z)]$.
+Empty symbols show 
+$n_\rho = \ln[\text{max}(\rho)/\text{min}(\rho)]$. 
+At low $\epsilon$ the evolved
+$n_{\rho}$ is close to the initial conditions of $n_\rho = 3$.  
 At high $\epsilon$,
-the density contrast shrinks, and once the mean 
-Ma approaches 1 (as in Fig. \ref{fig:ma_v_eps}b), the two methods of
-measuring the density stratification bifurcate as density 
-inversions form within the thermal
-boundary layers. Larger symbols with white dots represent 3D runs.}
+the density stratification decreases.  Once the mean 
+Ma approaches 1 (at Ra/Ra$_{\text{crit}} \approx \{10^2, 10^3\}$ for $\epsilon = \{1, 0.5\}$
+as in Fig. \ref{fig:ma_v_eps}b), density inversions form within the thermal
+boundary layers. Larger symbols represent 3D runs.}
 \end{figure}
 
-As the thermodynamic variables converge to their steady state values, 
-the density profile evolves while remaining in hydrostatic equilibrium 
-to zeroth order.  In Fig. \ref{fig:nrho_v_ra} we show the number of density 
-scale heights present in the evolved solution using two measures.  
-We find that in 2D, once the average Ma of the domain
-becomes approximately one, large density inversions begin to 
-form in the boundary layers, as was reported by \cite{brandenburg&all2005}.  
-The agreement of Nu across $\epsilon$ (Fig. \ref{fig:re_and_nu_v_ra}a), 
+In the evolved state, the flows change the density stratification,
+as shown in Fig. \ref{fig:nrho_v_ra}.
+We find that supersonic flows support persistent density inversions (empty symbols)
+in the boundary layers, as
+was reported by \cite{brandenburg&all2005}.  We find this in 2D and 3D.
+Surprisingly, the evolved $n_\rho$ is always less than the initial $n_\rho = 3$,
+and turbulent pressure support plays a larger role than atmospheric slumping.
+The agreement of Nu, Re across $\epsilon$ (Fig. \ref{fig:re_and_nu_v_ra}), 
 particularly at low Ra in which all four of our cases collapse onto a single
 power law, is striking in light of the vastly different evolved stratifications
-felt by the flows.  In 3D, despite the Ma not scaling with Ra, we see similar density
-inversions at high $\epsilon$ once Ra is sufficiently large.
+felt by the flows.
 

### 2017-03-22 referee_process/first_submission/referee_response.tex
finishes off pre-PDP paper stuff
gets in fixes from Ben & I today

@@
 \begin{singlespace}
-We have returned the revised version of our paper, 
-``Convective heat transport in stratified atmospheres at low and high
-Mach number,'' in which we have addressed the concerns of the referees.
-We hope this version of the document is acceptable for publication.  The text 
-has been adjusted to address the criticism of the referee reports,
-with a detailed description of our changes below.
-
-We are grateful for the careful reading and responses of the referees.  
-We thank referee A, whose
-comments pushed us to undertake our first 3D runs in which we found the
-transport results were nearly identical to our 2D results.
-Upon reflecting on the
-comments of referee B, we realized that the old definition of the
-Nusselt number (Nu) that we were using was flawed, and have since defined
+We thank the two referees for their careful read and detailed and constructive
+critique of our letter.  In responding to these two reports, the science within
+our paper has been significantly strengthened.
+In addressing the questions raised by report A, we have
+undertaken our first 3D runs and we report on the results of these in the
+revised draft.  In responding to report B,
+we realized that our previous definition of the
+Nusselt number (Nu) was flawed, and have since defined
 a slightly modified, more appropriate Nu.  This new definition better unifies
 the results at low and high Mach number (Ma) and makes it easier to understand
-the changes between the low and high Ma regimes.  Furthermore, 
-the comments of referee B drove us to better analyze all properties of our evolved
-atmospheres, and we have come to better understand how the Reynolds number scales with
-the Rayleigh number, and also how the structure of the evolved atmospheric density
-compares to the initial atmosphere.
+the changes between the low and high Ma regimes. We have streamlined our discussion
+of the control parameters and have shown how evolved properties (e.g, Ma) depend
+on the control parameters of our experiment.  Our previous presentation of the
+experiment was confusing, and following the report's comments we feel that we
+have improved the presentation.
 
@@
 process we have gained a greater understanding of the fundamental
-fluid properties in our simulations and how they change coherently
-across parameter space.  We have removed the previous figure 3 from our
-draft, as we feel it did not share any important information (the sum of
-the fluxes adds up to a flat line in an equilibrated solution, and this
-is well known).  The previous figure 4 has now become figure 3, and in addition
-to showing the scaling of Nu with Ra, we now also show the scaling of the
-Reynolds number, Re, with Ra.  We have added a new figure 4, in which we
-find that the density contrast across the domain at high $\epsilon$ appreciably
-shrinks in the evolved state compared to the initial state.  Furthermore, we
-find that density inversions form near the boundary layers of these atmospheres
-once the mean atmospheric Mach number approaches one, and show that this density
-inversion becomes significant at high Ra and high $\epsilon$.
+fluid properties in our simulations.
+
+We include the revised version of our paper, ``Convective heat transport in stratified
+atmospheress at low and high Mach number,'' in which we have addressed the critique contained
+in both reports.  We think the science has been substatially improved by the critque, as has
+the presentation of the experiment and the results.  The text and figures have been substantially
+revised in addressing the critique.  
+Below we include a detailed response to the reports; we include the text of
+the reports inline in their entirety along with our responses.  We address major
+points of the critiques first and then address minor points.
+
+$\,$\newline
+\noindent
+Sincerely,
+
+Evan H. Anders \& Benjamin P. Brown
+
 %\end{singlespace}
@@
 
-\textbf{Detailed response to referee report A:}
+\section{Response to report A:}
+\subsection{Major Points}
 
@@
 
-We have run and analyzed select 3D cases at both low and high $\epsilon$
+We now have run and analyzed select 3D cases at both low and high $\epsilon$
 at select values of the Rayleigh number.  These simulations have shown
-us that the density profile, Mach number, and Reynolds number of the
-evolved 3D state are nearly identical to the 2D simulations.  The Nusselt
-number appears to change slightly between the 2D and 3D cases at low $\epsilon$, 
-but the high $\epsilon$ results agree almost perfectly.  These results are shown
-in Figs. 1, 3, and 4, and the agreement suggests that 2D cases
-represent the bulk properties of the 3D dynamics well.
+us that many fluid properties (e.g., the density profile, Mach number, and Reynolds number)
+of the evolved 3D state are similar to the 2D simulations.  We now report on these
+limited 3D results as well as our more extensive 2D results. These results are shown
+in Figs. 1, 3, and 4, with large symbols, and are discussed in the text.
+Broadly, there seems to be some agreement between the 2D and 3D dynamics.
 
@@
 
-Boussinesq theory and DNS results have shown that the scaling of Nu with Ra
-is nearly the same in 2D and 3D for fluids with Pr $\geq$ 1 \cite{ahlers&all2009}.
-We have shown that this is true in our results, and have mentioned this connection
-to Boussinesq convection in the first paragraph of our discussion section.
+This concludes our response to report A.  We thank referee A for this report.
 
@@
 
-\textbf{Detailed response to referee report A:}
+\section{Response to report B:}
+
+\subsection{Major Points}
 
@@
 \end{myquotation}
-We thank referee B for their honesty regarding the confusing
-structure of the paper.  We have tried to restructure the text in
-a more sequential and thoughtful manner.
+We appreciate the honesty in report B, and we have come to agree that the
+structure of our previous draft was confusing.  We have restructured the text
+to clarify the presentation of both the experiment and the results. 
+We have highlighted the major results of flow properties and how those
+scale in low- and high- Mach number convection.  As can be seen in
+the rest of our response and the revised letter, under our new analysis
+supersonic flows behave substantially similarly to other flows.  Surprisingly,
+compressible convection at high and low superadiabaticity is more similar
+than different, in contrast to our initial analysis.
 
@@
 \end{myquotation}
-It is true that $\epsilon$ is the primary control parameter we are
-referring to when we mentioned ``high'' or ``low'' Mach number. This
-is because Ma is a very strong function of $\epsilon$, and a weaker
-function of Ra, as shown in Fig. 1.  At the ranges of Ra which we are
-reasonable to examine via DNS (up to nearly $10^7$Ra$_{\text{crit}}$),
-the Ma increases by less than a factor of 100 from simulations at
-onset to simulations near the state-of-the-art.  Thus, the choice of
-very low $\epsilon$ ($10^{-4}$, $10^{-7}$) forces all simulations at
-that parameter into the Ma $\ll 1$ regime, regardless of Ra.  Whereas the
-choice of $\epsilon \approx 1$ forces all simulations into the Ma $\approx 1$
-regime.
-
-This being said, it is understandable that the manner in which we presented
-Ma and $\epsilon$ was somewhat confusing.  We have changed the text to try
-to more explicitly state that $\epsilon$ is the control parameter, and that
-setting $\epsilon$ to be very small allows us to study low Ma convection,
-whereas setting $\epsilon$ near 1 allows us to study high Ma convection.  We
-have chosen to retain the title of the letter while adding clarification to
-the text.
+We agree with the report. We now present the experiment with $\epsilon$
+as the control parameter, and we show that Ma is a strong function of
+$\epsilon$ and a weaker function of Ra (Fig. 1).  In our studies, we
+find and show that $\epsilon$ and Ra largely determine Ma and Re in the
+evolved state, respectively (Fig. 1 \& 3).
 
@@
 \end{myquotation}
-It appears that the ``spinners'' are not the primary cause of the change
-of the Nu scaling at about Ma = 1.  We see a similar change in the scaling
-of the Reynolds number, and this suggests that a large fraction of the
-increase in energy transport with Ra is caused by increasing velocities.
-Once the mean flow speed is at Ma = 1, the convective transport
-can no longer benefit from increases in velocities, and only changes in
-the size of thermodynamic variables or changes in the strength of the
-diffusivity are left to increase the Nusselt Number.  This is
-mentioned in the second paragraph of the Discussion section.
+In revisiting our results, we found that the substantial differences between
+low and high $\epsilon$ in heat transport arose from a poor definition of
+Nu and from changes to the overall stratification.  We have determined a
+more consistent version of Nu (based on current properties rather than initial
+properties).  Now, high and low $\epsilon$ transport is substantially similar.
+We do see a small change in transport when 2D simulations achieve a mean
+Ma of O(1), and to test this we have conducted an aditional suite of
+experiments at higher $\epsilon = 1$.  In these solutions, all of the flow
+properties show a change of behavior at the point at which the flows enter the
+sonic regime.  This is shown in Figs. 1, 3, and 4 and discussed in the text.
 
+Figure 4 shows a surprising result.  We have removed the former Fig. 3 (fluxes
+as a function of height) so that we can discuss the result in our ccurrent
+Fig. 4 fully.  We find that the density contrast across the domain at high $\epsilion$
+appreciably shrinks in the evolved state compared to the initial state.  Furthermore, we find
+that density inversions form near the boundaroy layers of these atmospheres once the mean atmospheric Mach number approaches
+one, and show that this density inversion becomes significant at high Ra and high $\epsilon$,
+and persists in 3D.  This is discussed fully in the Results \& Discussion section.
+
+We have addressed the major points in the critique; we now continue with the
+minor points and clarifications.
+
+\subsection{Minor Points}
 \begin{myquotation}
@@
 understand, which I will try and list here, in chronological order.
-
-Introduction
 
@@
 When the convection is low Ma, the convective dynamics are much slower
-than the linear acoustic waves.  By stepping this linear component
-implicitly, we bypass the high Ma component of these waves and timestep
-on the order of the convective dynamics.  This is noted in the second to
+than the linear acoustic waves.  In explicit timestepping schemes, these
+fast acoustic waves set the Courant Friedrich Lewy (CFL) limit.
+By employing modern IMEX schemes, we are able to implicitly involve these
+fast linear waves and timestep on the timescale of the slow convective
+dynamics.    This is detailed in the second to
 last paragraph of the Experiment section.
@@
 \end{myquotation}
-We have reworded this sentence at the beginning of the second paragraph of the
-Introduction to clarify that we are referring to Boussinesq convection.
+We have clarified that we are referring to incompressible Boussinesq convection
+in the Introduction.
 
@@
 \end{myquotation}
-The third paragraph of the introduction has been restructured.  We note
-that $\epsilon$ is a control parameter whose primary job is to modify
-the Ma of the resulting solution.
+We have clarified the discussion of how Ma scales with $\epsilon$ and
+Ra throughout the text.
 
@@
 \end{myquotation}
-$z_0 = L_z + 1$ was confusing notation and has been removed.  
+We agree that $z_0$ was confusing notation and this has been removed.  
 We define $z$ shortly below Eqn (1).
@@
 \end{myquotation}
-Ben, what is he asking us to write out?
-In our numerical simulations, one time unit is the isothermal sound
-crossing time at the top of the layer.  However, convective dynamics
-have a typical overturn time which can be a few simulation time units
-(at high $\epsilon$) or it can have an overturn time of many simulation
-time units (at low $\epsilon$).  The buoyancy time allows us to estimate this.
+We have clarified that the equations are non-dimensionalized on
+the isothermal sound crossing timescale.  We have also clarified
+how the evolution time of the flow is linked to the buoyancy time.
+This appears in the final paragraph of the experiment section.
 
@@
 \end{myquotation}
-The initial entropy gradient of the polytrope is $\nabla S \propto -\epsilon$,
-and as a result evolved variables are $O(\epsilon)$.  We have removed this
-sentence, as it is confusing, and mentioned the scaling of thermodynamic variables
-with $\epsilon$ in the second paragraph of the Results section, where we now describe
-Fig. 1.
+We agree that this sentence was confusing and have moved the
+discussion of the magnitude of evolved fluctations to the
+discussion of Fig. 1.
 
@@
 \end{myquotation}
-$\mu$ is initially constant, which means that $\mu = \nu\rho_0$
-must be constant.  Since we are in a stratified atmosphere, this
-means that $\nu \propto 1/\rho_0$.  A similar relation between
-$\kappa$ and $\chi$ exists.  Thus, while $\nu$ and $\chi$ are constant
-in time, they are \emph{not} constant with height, and their
-gradients must be included in the equation set.
-$\mu$ and $\kappa$ are allowed to evolve with the
-density profile, and we have discussed this more clearly in the
-second paragraph of the Experiment section.
+Our equations are formulated as the evolution of velocities rather
+than momentum, and in this formulation $\nu$ and $\chi$ are the
+natural variables.  If $\nu$ and $\chi$ are constant in space,
+the problem becomes a constant coefficient problem and is numerically
+simple.  However, a spacially constant $\nu$ and $\chi$ does not satisfy
+thermal equilibrium within the initial polytrope, which is only satisfied when
+$\kappa = \rho\chi$ is constant.  To satisfy thermal equilibrium required
+a gradient in $\chi$, and to satisfy a constant Pr through the domain we
+must also have a gradient in $\nu$.  $\nu$ and $\chi$ are now nonconstant
+coefficients, and this approach, as we take here, is much more challenging numerically. 
+ We have
+clarified and detailed the profiles of $\nu, \chi, \mu, \text{and} \kappa$
+in the second paragraph of the experiment section.
 
@@
 \end{myquotation}
-In our low Ma simulations, pressure fluctuations are small and
-tend to not be positive in the upper atmosphere and negative in the lower atmosphere
-regardless of whether we are observing an upflow or a downflow.  The classical argument
-\cite{hurlburt&all1984} of ``buoyancy breaking accelerates downflows and deccelerates
-upflows'' appears to break down at low Ma.
+Being unable to determine how $\epsilon$ affects symmetries in the
+flow, we have removed this discussion.
 
 \begin{myquotation}
-'exhibit states in which the flux entering...': Surely in a
+`exhibit states in which the flux entering...': Surely in a
 stationary state the flux in has to equal the flux out. Are the
@@
 \end{myquotation}
-We are saying this is a non-stationary state.  The combination of fixed-temperature
-boundary conditions and no-slip boundary conditions allows the system to fluctuate between
+As detailed in the revised text, the combination of fixed-temperature
+boundary conditions and no-slip boundary conditions allows the system to alternate between
 roll states of convection and shear states of convection.  These states persist over long
 time scales (hundreds of buoyancy times) and the atmosphere is in flux disequilibrium in both states.
-We have updated the text in the third paragraph of the Results section to make this clearer.
+A sensible equilibrium and average emerges over long times.  This discussion appears with
+the discussion of Fig. 3a.
 
@@
 kinetic and potential energies, could be extended to stratified, compresible flows which also
-have potential energy.  At low $\epsilon$, where the density profile is simple and very similar
-to the initial polytrope in the evolved state, it seems that this extension would be easier to
-develop.  However, we are inexperienced in applying boundary layer theory and 
-will need to educate ourselves
-further on the development of the Grossman-Lohse theory before we can say
-with certainty that an expansion of this theory to stratified convection is tractable. 
-We have removed this suggestion from
-the Discussion section and made suggestions towards further experiments which we are certain our
-work can inform.
+have potential energy.  At low $\epsilon$, it seems the extension would be easier to
+develop. However, we are inexperienced in boundary layer theory and presently 
+cannot say with certainty that an expansion of this theory to stratified convection is tractable. 
+We have removed this suggestion from letter.  We have also combined the Results \& Discussion
+sections.
 
 \begin{myquotation}
-'under solar conditions ... we expect that epsilon  $\approx 10^{-20}$
-...': Is this small epsilon a reflection of efficient mixing of
+`under solar conditions ... we expect that epsilon  $\approx 10^{-20}$
+...`: Is this small epsilon a reflection of efficient mixing of
 convection in the ultimate nonlinear state or of the initial linear
@@
 \end{myquotation}
-These approximations in the initial letter were a representation of the choices of
-parameters necessary to achieve the desired Mach number and Rayleigh number of convective
-motions in the deep solar interior.  There, Ma $\approx 10^{-4}$ and Ra $\approx 10^{20}$.
-We made an estimate of what $\epsilon$ would be necessary to achieve low Ma at such large
-values of Ra based on the observed scaling of Mach number with $\epsilon$ and Ra
-in Fig. 1.
+This is a good question which we do not know the answer to.  As a result, we have
+removed this large extrapolation of our results from Fig. 1 from the discussion
+entirely.
+
+This concludes our response to report B.  We thank referee B for this report.
 
@@
 \noindent
-\textbf{Closing}
-\newline
-$\,$\newline
-We hope that these modifications to the text have sufficiently clarified our work for experts
-in the field while also keeping it broad enough to remain interesting for non-experts.
-Thank you for considering our newly revised manuscript for publication.
 
@@
 
-\noindent
-Sincerely,
-
-Evan H. Anders \& Benjamin P. Brown
-
 \bibliography{../../biblio.bib}

### 2017-03-22 tex/nusselt_paper.tex
gets in fixes from Ben & I today

@@
 
-\section{Results}
+\section{Results \& Discussion}
 \refstepcounter{section}
@@
 
-\section{Discussion}
-\refstepcounter{section}
-\label{sec:discussion}
-In this letter we have studied fundamental heat transport by 
-stratified convection in simplified 2D and 3D polytropic atmospheres.
-We argue that these atmospheres are the natural extension
-of the RB problem to stratified systems, 
-and are an ideal laboratory for understanding the basic 
-properties of stratified convection. 
-The primary difference we see between our 2D and 3D results is that the Ma
-is not a function of Ra in 3D, and this has far-reaching consequences.  Otherwise,
-we see only slightly different scaling in Nu(Ra) in 2D and 3D, 
-which aligns with expectations
-of Boussinesq theory and numerical simulation results at 
-values of Pr $\geq$ 1 \cite{ahlers&all2009}.
+%Discussion
 
-At low Ra and Ma, the scaling of Nu with Ra is reminiscent of RB convection.  
-However, at high Ra and Ma, the scaling of Nu becomes weaker, changing
-from a 1/3 to a 1/5 power law, a decrease by nearly a factor of 1/3.
-Similarly, the Reynolds number switches from a 3/4 power law to
-a 1/2 scaling in this regime shift, a similar decrease.
-This seems to suggest that a large portion of the scaling of the Nusselt number
-and Reynolds number in the low-Ma regime
-comes from increases in velocity.  Once the velocity reaches
-its natural maximum, heat transport can no longer benefit from increased velocities.
-The same is true of the Reynolds number, which scales directly with system diffusivities
-once the Mach number reaches its maximum value.
+In summary, we have found that the evolved flow properties of stratified,
+compressible convection scale in a manner reminiscent of RB convection.
+We argue that polytropically stratified atmospheres are the natural
+extension of the RB problem with an additional control parameter, $\epsilon$,
+whose primary role is to set the Ma of the flows.  We show that other properties
+of the evolved solutions (Nu, Re) are nearly identical at vastly different values
+of $\epsilon$, except for where there is a transition between the subsonic
+and supersonic regimes.  We also see that Nu scales similarly in 3D and 2D,
+and that Ma in 3D solutions seems to be a function of $\epsilon$ alone,
+allowing for simple specification of the evolved Ma using input parameters.
 
-Time-dependent oscillating shear states have developed spontaneously
-at values of $\epsilon=10^{-4}$ and Ra $\gtrsim 10^3$Ra$_{\text{crit}}$ in our 2D simulations.  
-Similar states have been observed in 2D RB convection \cite{goluskin&all2014}, and these should
-be studied in more detail.  These states are fundamentally in flux disequilibrium
-and last for large time scales (O(100$t_b$)),
-making it very difficult to choose a proper time window over which to calculate a 
-meaningful Nusselt number.  It would
-be beneficial for future studies to examine atmosperes with fixed flux or no slip
-boundary conditions to better converge and study cases at low $\epsilon$ and high
-Ra.
-
-Finally, we have found that the stratification of 
-these atmospheres evolves in a complex
+We have observed interesting phenomena, such as time-dependent oscillating shearing ``windy''
+states in our 2D simulations.  Unlike in RB \cite{goluskin&all2014}, our solutions with
+windy states have transport which scales in line with our non-windy solutions.
+Furthermore, the stratification of 
+these polytropic atmospheres evolves in a complex
 manner.  Future work should aim to 
 understand the importance of stratification on
-convective heat transport, and the manner in which
-boundary layer density inversions interact with
-the formation and transport properties of thermal plumes.
+convective heat transport and other flow properties.
 
@@
 for many useful discussions. We also thank the two anonymous referees whose
-critical comments greatly improved the quality of this letter.
+careful comments greatly improved the quality of this letter.
 

### 2017-03-23 tex/nusselt_paper.tex
first cut at the new abstract

@@
 plane-parallel, polytropically stratified atmospheres. 
-We hold the density stratification ($n_{\rho}$), aspect
-ratio, and Prandtl 
-number (Pr) constant while varying the superadiabaticity
-and Ra.  We find that Ma is a strong function of the superadiabaticity
+We perform a suite of 2D and 3D simulations in which we vary the initial
+superadiabaticity ($\epsilon$) and Ra at a set
+initial density stratification ($n_{\rho}$), aspect
+ratio, and Prandtl number (Pr).
+We find that Ma is a strong function of $\epsilon$
 in both 2D and 3D simulations, and that it is a 
 weak function of Ra in 2D.
-In 2D simulations, the scaling of the Nusselt Number (Nu) and the Reynolds number (Re)
-with Ra weaken
-once the mean Ma of the solution is unity, but in 3D
-Re and Nu seem to have consistent scaling across Ra.
-We further find that when the superadiabaticity and Ma are large,
-density inversions form in the thermal boundary layers.
-%As Ra increases and $\text{Ma} \rightarrow 1$, a scaling 
-%of Nu $\propto$ Ra$^{0.45}$ is observed.  
-%As Ra increases to a regime where Ma $\geq 1$,
-%this scaling gives way to a weaker Nu $\propto$ Ra$^{0.19}$. 
-%In the regime of Ma $\ll 1$, a consistent
-%Nu $\propto$ Ra$^{0.31}$ is retrieved,  reminiscent of the 
-%Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
+The scaling of evolved fluid properties (Nusselt number, Reynolds number,
+stratification) differs in the subsonic and supersonic regimes; however,
+aside from the sonic transition, the evolved flow properties
+of low and high Ma flows are nearly identical.  Our limited 3D runs suggest that
+evolved fluid properties behave similarly in 2D and 3D, but with modified
+scaling laws.
 \end{abstract}
@@
 In the widely-studied \RB (RB) problem of incompressible Boussinesq convection, 
-a negative temperature gradient leads to convective instability.
+a negative temperature gradient causes convective instability.
 In the evolved solution, upflows and downflows are symmetrical, the
-temperature in the interior becomes isothermal and
+temperature in the interior becomes isothermal, and
 the conductive flux ($\propto \grad T$) approaches 
@@
 For compressible convection in a stratified atmosphere, a
-negative entropy gradient leads to convective instability.
+negative entropy gradient causes convective instability.
 Early numerical experiments of moderate-to-high Ma compressible convection
@@
 \cite{cattaneo&all1991, brummell&all1996} dimensions
-revealed that the evolved state differs from the RB case.
+revealed a different evolved state from the RB case.
 Downflow lanes
 become fast and narrow, and upflow lanes turn into broad, slow upwellings.
-Furthermore, the \emph{entropy} gradient is negated by convection in the interior, and
-a significant temperature gradient and conductive flux persist in the presence of
+Furthermore, the \emph{entropy} gradient is negated by convection in the interior, so
+a significant temperature gradient and conductive flux persist despite
 efficient convection.
@@
 showed little
-variance with depth. By performing a linear stability analysis, 
-we determined that the onset of convection
+variance with depth. A linear stability analysis determined
+that convective onset
 occurs at $\text{Ra}_{\text{crit}} = \{11.15, 10.06, 10.97, 10.97\}$ 
@@
 $\langle \kappa \rangle = \langle \rho\chi \rangle$, which is nearly
-$\kappa_0$ when $\epsilon$ is small but can change appreciably for large
+$\kappa_0$ for small $\epsilon$ but changes appreciably for large
 values of $\epsilon$.
 In incompressible Boussinesq convection, where $\grad S = 0$ only when 
-$\grad T = 0$, this definition reduces to the traditional definition
-of the Nusselt number \cite{otero&all2002, johnston&doering2009}.
+$\grad T = 0$, this definition reduces to the traditionally defined
+Nusselt number \cite{otero&all2002, johnston&doering2009}.
 
@@
 
-We have observed interesting phenomena, such as time-dependent oscillating shearing ``windy''
+We have observed interesting phenomena, such as time-dependent oscillating shearing windy
 states in our 2D simulations.  Unlike in RB \cite{goluskin&all2014}, our solutions with

### 2017-03-23 referee_process/first_submission/referee_response.tex
near-final versions uploaded

@@
 \begin{singlespace}
-We thank the two referees for their careful read and detailed and constructive
-critique of our letter.  In responding to these two reports, the science within
+We thank the two referees for their careful reading of our letter
+and their detailed and constructive critique.
+In responding to these two reports, the science within
 our paper has been significantly strengthened.
-In addressing the questions raised by report A, we have
-undertaken our first 3D runs and we report on the results of these in the
+Addressing the questions raised by report A has led us to undertake
+our first 3D runs, and we report on the results of these in the
 revised draft.  In responding to report B,
@@
 We include the revised version of our paper, ``Convective heat transport in stratified
-atmospheress at low and high Mach number,'' in which we have addressed the critique contained
-in both reports.  We think the science has been substatially improved by the critque, as has
-the presentation of the experiment and the results.  The text and figures have been substantially
+atmospheres at low and high Mach number,'' in which we have addressed the critique contained
+in both reports.  We think the science has been substantially improved by the critique, as has
+the presentation of the experiment and the results.  The text and figures have been significantly
 revised in addressing the critique.  
 Below we include a detailed response to the reports; we include the text of
-the reports inline in their entirety along with our responses.  We address major
+the reports in their entirety along with our responses inline.  We address major
 points of the critiques first and then address minor points.
@@
 \newline
-
-\section{Response to report A:}
-\subsection{Major Points}
+\noindent
+\Large{\textbf{Response to report A:}}\newline$\,$\newline\indent
+\large{\textbf{Major Points}}
 
@@
 \newline
-
-\section{Response to report B:}
-
-\subsection{Major Points}
+\noindent
+\Large{\textbf{Response to report B:}}\newline$\,$\newline\indent
+\large{\textbf{Major Points}}
 
@@
 We do see a small change in transport when 2D simulations achieve a mean
-Ma of O(1), and to test this we have conducted an aditional suite of
+Ma of O(1), and to test this we have conducted an additional suite of
 experiments at higher $\epsilon = 1$.  In these solutions, all of the flow
@@
 Figure 4 shows a surprising result.  We have removed the former Fig. 3 (fluxes
-as a function of height) so that we can discuss the result in our ccurrent
-Fig. 4 fully.  We find that the density contrast across the domain at high $\epsilion$
+as a function of height) so that we can discuss the result in our current
+Fig. 4 fully.  We find that the density contrast across the domain at high $\epsilon$
 appreciably shrinks in the evolved state compared to the initial state.  Furthermore, we find
-that density inversions form near the boundaroy layers of these atmospheres once the mean atmospheric Mach number approaches
+that density inversions form near the boundary layers of these atmospheres once the mean atmospheric Mach number approaches
 one, and show that this density inversion becomes significant at high Ra and high $\epsilon$,
@@
 
-\subsection{Minor Points}
+$\,$
+\newline
+$\,$
+\newline
+\indent
+\large{\textbf{Minor Points}}\newline
 \begin{myquotation}
@@
 
-'Numerical constraints ... to moderately high Ma': What is the
+`Numerical constraints ... to moderately high Ma': What is the
 numerical constraint of low Ma flow?
@@
 \begin{myquotation}
-'RB' By `Rayleigh-Benard problem' here I assume that the
+`RB' By `Rayleigh-Benard problem' here I assume that the
 authors are referring to Boussinesq dynamics? It might be a good idea
@@
 \begin{myquotation}
-'the Ma is controlled by the superadiabatic excess': It is clear
+`the Ma is controlled by the superadiabatic excess': It is clear
 from Fig 1 that this is not a complete statement.
@@
 \begin{myquotation}
-'The scaling of the entropy gradient with epsilon ... evolved
+`The scaling of the entropy gradient with epsilon ... evolved
 values ': I really have no idea what these two sentences mean,
@@
 We agree that this sentence was confusing and have moved the
-discussion of the magnitude of evolved fluctations to the
+discussion of the magnitude of evolved fluctuations to the
 discussion of Fig. 1.
@@
 the problem becomes a constant coefficient problem and is numerically
-simple.  However, a spacially constant $\nu$ and $\chi$ does not satisfy
+simple.  However, a spatially constant $\nu$ and $\chi$ does not satisfy
 thermal equilibrium within the initial polytrope, which is only satisfied when
@@
 \begin{myquotation}
-'IMEX': I am assuming this acronym stands for implicit-explicit?
+`IMEX': I am assuming this acronym stands for implicit-explicit?
 Maybe write out?
@@
 \begin{myquotation}
-'extended to include variable nu and chi' : see above. This seems
+`extended to include variable nu and chi' : see above. This seems
 very unnecessary!
@@
 \begin{myquotation}
-'While it has been suggested that pressure forces...': I do not
+`While it has been suggested that pressure forces...': I do not
 understand the discussion here. Do the authors regard the breakup of
@@
 We believe that the Grossman-Lohse theory, which models the energy dissipation rate of both
-kinetic and potential energies, could be extended to stratified, compresible flows which also
+kinetic and potential energies, could be extended to stratified, compressible flows which also
 have potential energy.  At low $\epsilon$, it seems the extension would be easier to

### 2017-03-23 tex/nusselt_paper.tex
near-final versions uploaded

@@
 \begin{abstract}
-Convection in astrophysical systems is stratified and
-often occurs at high Rayleigh number (Ra) and low
-Mach number (Ma).
-Here we study stratified convection in the context of 
+%Convection in astrophysical systems is stratified and
+%often occurs at high Rayleigh number (Ra) and low
+%Mach number (Ma).
+We study stratified convection in the context of 
 plane-parallel, polytropically stratified atmospheres. 
 We perform a suite of 2D and 3D simulations in which we vary the initial
-superadiabaticity ($\epsilon$) and Ra at a set
-initial density stratification ($n_{\rho}$), aspect
-ratio, and Prandtl number (Pr).
-We find that Ma is a strong function of $\epsilon$
+superadiabaticity ($\epsilon$) and the Rayleigh number (Ra) at a set
+initial density stratification, aspect
+ratio, and Prandtl number.
+We find that the Mach number (Ma) is a strong function of $\epsilon$
 in both 2D and 3D simulations, and that it is a 
 weak function of Ra in 2D.
-The scaling of evolved fluid properties (Nusselt number, Reynolds number,
-stratification) differs in the subsonic and supersonic regimes; however,
+Surprisingly, we find that the evolved heat transport, 
+quantified by the Nusselt number (Nu),
+follows scaling relationships similar to those found in the well-studied, 
+incompressble Rayleigh-B\'{e}nard problem.
+The scaling of evolved fluid properties (Nu, Reynolds number,
+stratification) differs in the subsonic and supersonic regimes; 
 aside from the sonic transition, the evolved flow properties
-of low and high Ma flows are nearly identical.  Our limited 3D runs suggest that
-evolved fluid properties behave similarly in 2D and 3D, but with modified
-scaling laws.
+of low and high Ma flows are nearly identical.  
+Our limited 3D runs suggest that
+evolved fluid properties behave similarly in 2D and 3D.
 \end{abstract}
@@
 and initial atmospheric stratification
-constant.  We also examine the behavior of flow properties, as quantifed by Ma and Re.
+constant.  We also examine the behavior of flow properties, as quantified by Ma and Re.
 
@@
 In our 2D cases, we only consider $x$ and $z$.
-
-%
-%We examine the simplest stratified extension of RB by studying a
-%fluid composed of monatomic ideal gas particles with an adiabatic 
-%index of $\gamma = 5/3$ and whose equation of state is $P = R\rho T$. 
-%This is consistent with the approach used in earlier work.
-%The initial atmosphere is a plane-parallel polytrope in which 
-%the gravitational acceleration and conductive flux, 
-%$\bm{F}_{\text{cond,0}} = -\kappa \partial_z T_0$, do not vary with depth. To
-%achieve the latter condition, both $\kappa$ and $\partial_z T_0$ are constant.
-%Under these assumptions, satisfying hydrostatic 
-%equilibrium produces a stratification of
-%\begin{equation}
-%\begin{split}
-%\rho_0(z) &= \rho_{t}(z_0 - z)^m, \\
-%T_0(z)    &= T_{t}(z_0 - z),
-%\label{eqn:polytrope}
-%\end{split}
-%\end{equation}
-%where $m = m_{\text{ad}} - \epsilon$ is the polytropic index.
-%The adiabatic polytropic index is $m_{\text{ad}} \equiv (\gamma-1)^{-1}$, and
-%the superadiabatic excess is $\epsilon$ which sets the scale 
-%of the entropy gradient ($\partial_z S_0 \propto -\epsilon$).
-%A significant advance of this work is the ability to study large 
-%and small values of $\epsilon$, as will be discussed.
-%Thermodynamic variables are nondimensionalized at the 
-%top of the atmosphere as  $P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, 
-%requiring $z_0 \equiv L_z + 1$ and $R = T_{t} = \rho_{t} = 1$.
-%By this choice, the non-dimensional length scale is the inverse 
-%temperature gradient scale and the timescale is the isothermal 
-%sound crossing time of this unit length.
-%The height $z$ increases upwards within $[0, L_{z}]$, 
-%where $L_{z} = e^{n_{\rho}/m} - 1$ is
-%determined by $n_\rho$ and $\epsilon$.
-%The characteristic timescale of convective dynamics
-%is related to the atmospheric buoyancy time, 
-%$t_{\text{b}} = \sqrt{L_z/g\epsilon}$, with $g = (m+1)$.
-%Throughout this letter, we use buoyancy time units and 
-%choose $n_{\rho} = 3$ such that the 
-%initial density varies by a factor of 20.
-%All atmospheres studied here have an aspect ratio of 4, 
-%such that $L_x = 4L_z$.
-%
 
@@
 such that only the lower 25\% of the coefficients
-have power. We non-dimensionalize our computational domains by setting
+have power. We nondimensionalize our computational domains by setting
 all thermodynamic variables to unity at $z = L_z$ choosing
@@
 Ma(Ra$, \epsilon) \propto \epsilon^{1/2}$Ra$^{1/4}$.
-this relation breaks down as the mean
+This relation breaks down as the mean
 Ma approaches 1 (see Fig. \ref{fig:ma_v_eps}).  This transition
@@
 convection (Fig. \ref{fig:entropy_snapshots}a).
-At high Ma (e.g., $\epsilon = 0.5$), bulk thermodynamic structures are similar but
+At high Ma (e.g., $\epsilon = 0.5$, Ra/Ra$_{\text{crit}} \gtrsim 10^3$), 
+bulk thermodynamic structures are similar but
 shock systems form in the upper atmosphere near downflow lanes 
-for sufficiently large values of $\epsilon$ and Ra (Fig. \ref{fig:entropy_snapshots}b,c).
-Similar shock phenomena were reported in
-both two \cite{cattaneo&all1990} and 
+(Fig. \ref{fig:entropy_snapshots}b\&c).
+These shock phenomena were reported in
+two \cite{cattaneo&all1990} and 
 three \cite{malagoli&all1990} dimensional polytropic simulations previously.
@@
 (Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
-no longer span the whole domain but rather break up into 
+no longer span the domain depth; rather, they break up into 
 small eddies which traverse the domain multiple
@@
 We find these windy convective states, reminiscent of similar states
-in RB convection \cite{goluskin&all2014}, at $\epsilon = 10^{-4}$ for high
-values of Ra. Roll states (Fig. \ref{fig:entropy_snapshots}a) with high convective
+in RB convection \cite{goluskin&all2014}, at $\epsilon = 10^{-4}$ and
+Ra/Ra$_{\text{crit}} \gtrsim 10^{3}$. Roll states (Fig. \ref{fig:entropy_snapshots}a) with high convective
 transport alternate with windy states of lower transport.
@@
 
-We have observed interesting phenomena, such as time-dependent oscillating shearing windy
-states in our 2D simulations.  Unlike in RB \cite{goluskin&all2014}, our solutions with
+We observe interesting phenomena, such as time-dependent, windy
+states of shear in our 2D simulations.  
+Unlike in RB \cite{goluskin&all2014}, our solutions with
 windy states have transport which scales in line with our non-windy solutions.
@@
 
-Our studies
-here will serve as a foundation both for understanding and 
+Our studies here will serve as a foundation for 
 comparing heat transport in stratified convection
-to that in RB convection \cite{johnston&doering2009}, 
-and for future studies of transport in stratified convection.  
-These results can be used to determine if simplified equation sets, 
-such as the anelastic equations, carry heat in the same manner as the 
-FC equations.
+to that in RB convection \cite{johnston&doering2009}
+and for better quantifying transport in stratified convection.  
+These results can be used to determine if fluid properties
+scale appropriately in simplified equation sets, 
+such as the anelastic equations.
 This work will also be useful in coming to understand more realistic systems, 
@@
 atmospheres bounded by stable regions \cite{hurlburt&all1986}, 
-or regions with realistic profiles of $\kappa$.
+and regions with realistic profiles of $\kappa$.
 

### 2017-03-23 referee_process/first_submission/referee_response.tex
updates referee response letter with final read from Evan

@@
 our paper has been significantly strengthened.
-Addressing the questions raised by report A has led us to undertake
+Addressing the questions raised by report A led us to undertake
 our first 3D runs, and we report on the results of these in the
@@
 atmospheres at low and high Mach number,'' in which we have addressed the critique contained
-in both reports.  We think the science has been substantially improved by the critique, as has
+in both reports.  We think the science has been substantially improved, as has
 the presentation of the experiment and the results.  The text and figures have been significantly
-revised in addressing the critique.  
+revised.  
 Below we include a detailed response to the reports; we include the text of
@@
 \end{myquotation}
-
+\noindent
 This concludes our response to report A.  We thank referee A for this report.
@@
 This paper essentially examines the heat transport in compressible
-convection as as function of Rayleigh number and Mach number for fixed
-density stratification and Prandtl number via 2D simulations The major
+convection as a function of Rayleigh number and Mach number for fixed
+density stratification and Prandtl number via 2D simulations. The major
 results cited are the scalings of the heat transport (measured by a
@@
 scale in low- and high- Mach number convection.  As can be seen in
-the rest of our response and the revised letter, under our new analysis
-supersonic flows behave substantially similarly to other flows.  Surprisingly,
+the rest of our response and the revised letter, 
+supersonic flows behave substantially similarly to other flows
+under our new analysis.  Surprisingly,
 compressible convection at high and low superadiabaticity is more similar
@@
 Nu and from changes to the overall stratification.  We have determined a
-more consistent version of Nu (based on current properties rather than initial
+more consistent version of Nu (based on evolved properties rather than initial
 properties).  Now, high and low $\epsilon$ transport is substantially similar.
@@
 
+$\,$\newline\noindent
 We have addressed the major points in the critique; we now continue with the
@@
 than the linear acoustic waves.  In explicit timestepping schemes, these
-fast acoustic waves set the Courant Friedrich Lewy (CFL) limit.
-By employing modern IMEX schemes, we are able to implicitly involve these
+fast acoustic waves set the Courant–Friedrichs–Lewy (CFL) limit.
+By employing modern IMEX schemes, we are able to implicitly evolve these
 fast linear waves and timestep on the timescale of the slow convective
@@
 how the evolution time of the flow is linked to the buoyancy time.
-This appears in the final paragraph of the experiment section.
+This appears in the final paragraph of the Experiment section.
 
@@
 thermal equilibrium within the initial polytrope, which is only satisfied when
-$\kappa = \rho\chi$ is constant.  To satisfy thermal equilibrium required
+$\kappa = \rho\chi$ is constant.  To satisfy thermal equilibrium requires
 a gradient in $\chi$, and to satisfy a constant Pr through the domain we
@@
  We have
-clarified and detailed the profiles of $\nu, \chi, \mu, \text{and} \kappa$
-in the second paragraph of the experiment section.
+clarified and detailed the profiles of $\nu, \,\chi, \,\mu,\text{ and }\kappa$
+in the second paragraph of the Experiment section.
 
@@
 adiabatic temperature gradient is what we found and what is reported by
-Spiegel and Veronis, $\partial_z T_{ad} = -g/c_P$, \cite{spiegel&veronis1960}.
+Spiegel and Veronis, $\partial_z T_{ad} = -g/c_P$ \cite{spiegel&veronis1960}.
 We have updated the text following Eqn 8 to reflect this.
@@
 \end{myquotation}
+We have combined the Results \& Discussion sections in the revised draft.
+
 We believe that the Grossman-Lohse theory, which models the energy dissipation rate of both
@@
 cannot say with certainty that an expansion of this theory to stratified convection is tractable. 
-We have removed this suggestion from letter.  We have also combined the Results \& Discussion
-sections.
+We have removed this suggestion from letter.
 
@@
 This is a good question which we do not know the answer to.  As a result, we have
-removed this large extrapolation of our results from Fig. 1 from the discussion
+removed this large extrapolation of our results in Fig. 1 from the discussion
 entirely.
 
+$\,$\newline\noindent
 This concludes our response to report B.  We thank referee B for this report.

### 2017-03-23 tex/nusselt_paper.tex
Puts final read through of paper from Evan into repo

@@
 stratification) differs in the subsonic and supersonic regimes; 
-aside from the sonic transition, the evolved flow properties
+aside from the sonic transition, the evolved fluid properties
 of low and high Ma flows are nearly identical.  
@@
 Furthermore, the \emph{entropy} gradient is negated by convection in the interior, so
-a significant temperature gradient and conductive flux persist despite
+a significant temperature gradient and conductive flux can persist despite
 efficient convection.
@@
 and the Peclet number (Pe, advection vs. thermal diffusion).  
-In stratified atmospheres, the magnitude of the unstable entropy gradient, 
+In stratified atmospheres, the magnitude of the unstable entropy gradient
 joins Ra and Pr as an important control parameter.  This 
@@
 We examine a monatomic ideal gas with an adiabatic index of
-$\gamma = 5/3$ whose equation of state is $P = R\rho T$. In this
-work we take $R = 1$.
-This is consistent with the approach used in earlier work \cite{graham1975, chan&all1982,
+$\gamma = 5/3$ whose equation of state is $P = R\rho T$. This is consistent with the approach used in earlier work \cite{graham1975, chan&all1982,
 hurlburt&all1984, cattaneo&all1990, cattaneo&all1991, brummell&all1996} 
 and is the simplest stratified extension of RB.
+In this work we take $R = 1$.
 We study atmospheres which are initially polytropically stratified,
@@
 where $m$ is the polytropic index and $L_z$ is the depth of the atmosphere.
+The height coordinate, $z$, increases upwards in the range $[0, L_z]$.
 Subscript 0 indicates initial conditions and subscript $t$ indicates values
-at $z = L_z$.
-The height coordinate, $z$, increases upwards in the range $[0, L_z]$.  We
+at $z = L_z$.   We
 specify the depth of the atmosphere, $L_z = e^{n_{\rho}/m} - 1$, by choosing
@@
 $\ln\rho = (\ln\rho)_0 + (\ln\rho)_1$, 
-and the velocity $\bm{u} = u\hat{x} + v\hat{y} +  w\hat{z}$.
+and the velocity is $\bm{u} = u\hat{x} + v\hat{y} +  w\hat{z}$.
 In our 2D runs, $v = 0$.
@@
 have power. We nondimensionalize our computational domains by setting
-all thermodynamic variables to unity at $z = L_z$ choosing
+all thermodynamic variables to unity at $z = L_z$, choosing
 $R = T_t = \rho_t = 1$.  By this choice, the non-dimensional
@@
 $\epsilon$ and a weak function of Ra.  
-In our 2D runs, when Ma $< 1$ we observe a scaling law of
-Ma(Ra$, \epsilon) \propto \epsilon^{1/2}$Ra$^{1/4}$.
+In our 2D runs, when Ma $< 1$, we observe a scaling law of
+Ma(Ra$, \epsilon) \appropto \epsilon^{1/2}$Ra$^{1/4}$.
 This relation breaks down as the mean
@@
 In our limited 3D runs, Ma appears to be a function of $\epsilon$ alone, with
-Ma $\propto \epsilon^{1/2}$, so at high Ra, Ma$_{\text{3D}} < \text{Ma}_{\text{2D}}$.
+Ma $\appropto \epsilon^{1/2}$, so at high Ra, Ma$_{\text{3D}} < \text{Ma}_{\text{2D}}$.
 The value of $\epsilon$ also sets the size of the
 evolved thermodynamic fluctuations, such that
-$T_1/T_0 \propto \epsilon$ and $\rho_1/\rho_0 \propto \epsilon$.  
+$T_1/T_0 \appropto \epsilon$ and $\rho_1/\rho_0 \appropto \epsilon$.  
 These fluctuations are very small when $\epsilon$ and Ma are small,
@@
 (a) A low Ma flow at moderate Ra. (b) A high Ma flow at the same Ra as in (a).
-(c) a high Ma flow at high Ra.
+(c) A high Ma flow at high Ra.
 Shock systems can be seen in the upper atmosphere of the high Ma flows,
-for example at $(x, z) \approx (70, 15-19)$ in (b) and $(x, z) \approx 
+for example at $(x, z) \sim (70, 15-19)$ in (b) and $(x, z) \sim 
 (65, 17-19)$ in (c).
@@
 small eddies which traverse the domain multiple
-times before diffusing.  Our choice of fixed-temperature, stress free boundary conditions 
+times before diffusing.  Our choice of fixed temperature, stress free boundary conditions 
 allows the flux at the boundaries to vary, while also allowing
@@
 $F_{\text{A}} \equiv -\langle\kappa\rangle \partial_z T_{\text{ad}}$ 
-is the conductive flux of the proper corresponding adiabatic atmosphere
-For a compressible ideal gas in hydrostatic equilibrium,
+is the conductive flux of the proper corresponding adiabatic atmosphere.
+For a compressible, ideal gas in hydrostatic equilibrium,
 $\partial_z T_{\text{ad}} \equiv - g / c_{P}$ \cite{spiegel&veronis1960}.  
@@
 In 2D and at low to moderate Ra, 
-Nu $\propto$ Ra$^{1/3}$ regardless of $\epsilon$,
+Nu $\appropto$ Ra$^{1/3}$ regardless of $\epsilon$,
 reminiscent of scaling laws in classical \RB theory \cite{king&all2012}.
-As the flow becomes supersonic,  Nu $\propto$ Ra$^{1/5}$.
-2D runs at $\text{Ra }> 10^3$Ra$_{\text{crit}}$
+As the flow becomes supersonic,  Nu $\appropto$ Ra$^{1/5}$.
+2D runs at $\text{Ra }\gtrsim 10^3$Ra$_{\text{crit}}$
 and $\epsilon = 10^{-4}$ exhibit windy convective states.
@@
 Ra can result in a simulation latching on to one solution or the other.
-In our limited 3D runs, it appears that Nu $\propto$ Ra$^{2/7}$, a classic scaling law
+In our limited 3D runs, it appears that Nu $\appropto$ Ra$^{2/7}$, a classic scaling law
 seen in RB studies \cite{johnston&doering2009}.
@@
 Re at the midplane ($z=L_z/2$) of the atmosphere in
-Fig. \ref{fig:re_and_nu_v_ra}b.  Largely we find that Ra and
-Pe depend on Ra, but not $\epsilon$, except when the flow states
+Fig. \ref{fig:re_and_nu_v_ra}b.  Largely we find that Re
+depends on Ra, but not $\epsilon$, except when the flow states
 change.
-In 2D and at low Ra, Re $\propto$ Ra$^{3/4}$.  When the flows
+In 2D and at low Ra, Re $\appropto$ Ra$^{3/4}$.  When the flows
 become supersonic, 
-this scaling gives way to Re $\propto$ Ra$^{1/2}$.
+this scaling gives way to Re $\appropto$ Ra$^{1/2}$.
 In our limited 3D runs, the scaling of Re is
-Re $\propto$ Ra$^{1/2}$, consistent with the supersonic results.
+Re $\appropto$ Ra$^{1/2}$, consistent with the supersonic results.
 
@@
 and turbulent pressure support plays a larger role than atmospheric slumping.
-The agreement of Nu, Re across $\epsilon$ (Fig. \ref{fig:re_and_nu_v_ra}), 
+The agreement of Nu \& Re across $\epsilon$ (Fig. \ref{fig:re_and_nu_v_ra}), 
 particularly at low Ra in which all four of our cases collapse onto a single

### 2017-03-23 referee_process/first_submission/referee_response.tex
Final edits to referee letter.

@@
 the changes between the low and high Ma regimes. We have streamlined our discussion
-of the control parameters and have shown how evolved properties (e.g, Ma) depend
+of the control parameters and have shown how evolved properties (e.g., Ma) depend
 on the control parameters of our experiment.  Our previous presentation of the
@@
 one, and show that this density inversion becomes significant at high Ra and high $\epsilon$,
-and persists in 3D.  This is discussed fully in the Results \& Discussion section.
+and persists in 3D.  This is discussed fully in the Results \&
+Discussion section.  We have combined the Results \& Discussion sections in the revised draft.
 
@@
 Our equations are formulated as the evolution of velocities rather
-than momentum, and in this formulation $\nu$ and $\chi$ are the
+than momentum; this formluation is crucial to our current IMEX
+timestepping of acoustic waves at low Mach numbers.  
+In this velocity-based formulation, $\nu$ and $\chi$ are the
 natural variables.  If $\nu$ and $\chi$ are constant in space,
@@
 thermal equilibrium within the initial polytrope, which is only satisfied when
-$\kappa = \rho\chi$ is constant.  To satisfy thermal equilibrium requires
+$\kappa_0 = \rho_0\chi$ is constant (where as in the letter, subscript 0
+denotes initial values).  To satisfy thermal equilibrium requires
 a gradient in $\chi$, and to satisfy a constant Pr through the domain we
@@
 very unnecessary!
+\end{myquotation}
+See above description of $\nu$ and $\chi$ in our equations.
 
+\begin{myquotation}
 Results
@@
 \end{myquotation}
+On further reflection, we realized that we are uncertain about how to
+quantify asymmetries as the flows break up.  
 Being unable to determine how $\epsilon$ affects symmetries in the
@@
 \end{myquotation}
-We have combined the Results \& Discussion sections in the revised draft.
-
 We believe that the Grossman-Lohse theory, which models the energy dissipation rate of both

### 2017-06-09 code/plotting/base/parameter_space_buddy.py
some plot tweaking

@@ -98,8 +98,8 @@ class ParameterSpaceBuddy():
         for i, dir in enumerate(important_dirs):
             if np.mod(i, comm_world.size) != comm_world.rank:
                 continue
-            try:
-#            if True:
+#            try:
+            if True:
                 comm_new = comm_world.Create(comm_world.Get_group().Incl(np.ones(1)*comm_world.rank))
 
                 #This exception exists because my old data is crappy -- consider removing this point.
@@ -117,16 +117,16 @@ class ParameterSpaceBuddy():
                 plotter.communicate_profiles()
                 plotter.save_profiles(filename=self.out_file_name.split('.h5')[0])
                 plotter.make_plots(figsize=(3*len(keys), 8))
-            except:
-                print('AN ERROR HAS OCCURED IN {:s}'.format(dir[0]))
-                import sys
-                sys.stdout.flush()
+#            except:
+#                print('AN ERROR HAS OCCURED IN {:s}'.format(dir[0]))
+#                import sys
+#                sys.stdout.flush()
 
     def read_files(self, keys):
         import h5py
         for i, dir in enumerate(self.dir_info):
-            try:
-#            if True:
+#            try:
+            if True:
                 f = h5py.File(dir[0]+self.out_dir_name+self.out_file_name, 'r')
 
                 Lz = np.exp(dir[self.parameters.index('nrhocz')+1]/(1.5-dir[self.parameters.index('eps')+1]))-1
@@ -154,10 +154,10 @@ class ParameterSpaceBuddy():
                     if np.isnan(storage[key][0]):
                         raise
                 dir[-1] = storage
-            except:
-                print("PROBLEMS READING OUTPUT FILE IN {:s}".format(dir[0]))
-                import sys
-                sys.stdout.flush()
+#            except:
+#                print("PROBLEMS READING OUTPUT FILE IN {:s}".format(dir[0]))
+#                import sys
+#                sys.stdout.flush()
         return self.dir_info
 
 

### 2017-06-09 code/plotting/base/plot_buddy_base.py

@@ -153,16 +153,18 @@ class PlotBuddy:
         '''
         file_name = self.root_dir + '/atmosphere/atmosphere.h5'
         f = h5py.File('{:s}'.format(file_name))
+        print(file_name)
         self.atmosphere = dict()
         for key in f.keys():
             if f[key].shape == ():
                 self.atmosphere[key] = f[key].value
             else:
                 self.atmosphere[key] = f[key][:]
-        nu_top = np.sqrt(self.atmosphere['prandtl']*(self.atmosphere['Lz']**3 * \
+        nu_top = np.sqrt(self.atmosphere['prandtl']
+                        *(self.atmosphere['Lz']**3 * \
                         np.abs(self.atmosphere['delta_s_atm']/self.atmosphere['Cp'])*\
                             self.atmosphere['g'])/self.atmosphere['rayleigh'])
-        chi_top = nu_top/self.atmosphere['prandtl']
+        chi_top = nu_top/1#self.atmosphere['prandtl']
         self.atmosphere['chi'] = chi_top/self.atmosphere['rho0']
         self.atmosphere['nu'] = nu_top/self.atmosphere['rho0']
 
@@ -228,7 +230,7 @@ class PlotBuddy:
         my_weirds = 0
         my_weird_indices = []
         for i, item in enumerate(self.local_files[self.file_dirs[0]]):
-            f = h5py.File("{:s}".format(item[0]), flag='r')
+            f = h5py.File("{:s}".format(item[0]), 'r')
             t = np.array(f['scales']['sim_time'][:], dtype=np.float32)
             f.close()
             if '_s1.h5' in item[0] and t[0] == 0:
@@ -343,7 +345,7 @@ class PlotBuddy:
         count = 0
         for i, file in enumerate(file_list):
             logger.info('opening file {}'.format(file[0]))
-            f = h5py.File("{:s}".format(file[0]), flag='r')
+            f = h5py.File("{:s}".format(file[0]), 'r')
             for j in range(len(profile_name)):
                 field = np.array(f[str(subkey[j])][str(profile_name[j])], dtype=np.float32)
                 if i == 0:

### 2017-06-09 code/plotting/parameter_space_plots.py

@@ -14,6 +14,7 @@ import matplotlib
 matplotlib.use('Agg')
 matplotlib.rcParams.update({'font.size': 11})
 import matplotlib.pyplot as plt
+plt.style.use('classic')
 from base.plot_buddy import ParameterSpaceBuddy, ProfileBuddy, COLORS
 import os
 import numpy as np
@@ -53,7 +54,7 @@ def line_leastsq(x, y, y_uncert):
     p = np.array((slope, intercept))
     covar = np.array(((s, -sx),(-sx, sx2)))/Delta
     return p, covar
-START_FILE=50
+START_FILE=20
 N_FILES=1000
 golden_ratio=1.618
 FIGWIDTH=3+7.0/16
@@ -69,16 +70,18 @@ comm = MPI.COMM_WORLD
 #root_dir='/nobackup/eanders/sp2017/comps_data/'
 root_dir='/nobackup/eanders/sp2017/fc_poly_hydro/'
 mach_dir='/nobackup/eanders/sp2017/mach_eps/'
-threeD_dir = '/nobackup/bpbrown/polytrope-evan/'
+threeD_dir = '/nobackup/bpbrown/polytrope-evan-3D/'
+threeD_out_dir='/parameter_calcs/'
 param_keys = ['Ra', 'eps', 'nrhocz', 'Pr']
 
-keys = ['Nusselt', 'Nusselt_5', 'Nusselt_6', 'norm_5_kappa_flux_z',  'Re_rms', 'Ma_ad', 'Ma_iso', 'ln_rho1', 'T1', 'vel_rms',\
-    'rho_full', 'T_full', 'kappa_flux_z', 'enthalpy_flux_z', 'PE_flux_z', 'KE_flux_z', 'viscous_flux_z', 'kappa_flux_fluc_z']
+keys = ['Nusselt_AB17', #'Nusselt', 'Nusselt_5', 'Nusselt_6', 'norm_5_kappa_flux_z',  
+    'Re_rms', 'Ma_ad', 'Ma_iso', 'ln_rho1', 'T1', 'vel_rms',\
+    'rho_full', 'T_full', 'kappa_flux_z', 'enthalpy_flux_z', 'PE_flux_z', 'KE_flux_z', 'viscous_flux_z', 'kappa_flux_z']# 'kappa_flux_fluc_z']
[…]

### 2017-06-09 code/stratified_dynamics/polytropes.py

@@ -175,10 +175,3 @@ class FC_polytrope_3d(FC_equations_3d, Polytrope):
         super(FC_polytrope_3d, self).set_equations(*args, **kwargs)
         self.test_hydrostatic_balance(T=self.T0, rho=self.rho0)
 
-class AN_polytrope(AN_equations, Polytrope):
-    def __init__(self, *args, **kwargs):
-        super(AN_polytrope, self).__init__() 
-        Polytrope.__init__(self, *args, **kwargs)
-        logger.info("solving {} in a {} atmosphere".format(self.equation_set, self.atmosphere_name))
-        
-       

### 2017-06-12 referee_process/second_submission/referee_response.tex
adds template for referee response 2

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[aps, 11pt, singlecolumn]{revtex4-1} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\usepackage{natbib}
\bibliographystyle{apsrev}
\usepackage{setspace}

\begin{document}
%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\noindent
Dear Editor,
$\,$\newline

\newenvironment{myquotation}{
\begin{quotation}
\itshape
}{ 
\end{quotation}
}

\begin{singlespace}
Editor letter goes here

$\,$\newline
\noindent
Sincerely,

Evan H. Anders \& Benjamin P. Brown

%\end{singlespace}

$\,$
\newline
$\,$
\newline
\noindent
\Large{\textbf{Response to report B:}}\newline$\,$\newline\indent

\begin{myquotation}

The second submission of this paper, after the first round of review,
is SUBSTANTIALLY different from the first time around, and essentially
needs refereeing from scratch as a new paper. The paper does still
essentially examine the heat transport in compressible convection as
as function of superadiabaticity and Rayleigh number (and therefore
varying thermal diffusivity) for fixed density stratification and
Prandtl number via 2D simulations The new paper adjusted the
formulation of the Nusselt number, changing the results substantially,
and added some 3D simulations to the previously all-2D simulations.
The major result is the scalings of the heat transport (measured by
their Nusselt number) with the Rayleigh number bears a remarkable
similarity to standard Boussinesq Rayleigh-Benard convection, at all
the wide range of superadiabaticities simulated. This in itself is an
interesting result, as it somewhat surprising considering that their
fixed background stratification has quite a strong density contrast
($\sim$20) and some of their departures from adiabaticity are large
($\epsilon \sim$ 1 $\rightarrow$ adiabatic index m=0.5).

I think this paper is getting closer to publishable, although I still
find the explanation of the setup of the model in particular somewhat
opaque though, and the interesting results not really addressed in any
detail, as I'll explain below.

I am glad that the authors took my comments on the setup from before
at least partially to heart! I still think things could be clearer.
Most specifically again, is the question of what are the salient
parameters of compressible convection. There are 4, as mentioned
previously, and the authors here have chosen to keep one fixed -- a
measure of the stratification, for which they use $n_\rho$. For the
others, it is nice to cast things in terms of a Rayleigh number and a
Prandtl number since this gels nicely with standard Boussinesq
Rayleigh-Benard convection (RBC). However, then the third parameter,
the superadiabaticity, which the authors call $\epsilon$, is also part of
the definition of the Rayleigh number, and therefore, as it should be,
the Rayleigh parameter is really a definition of the thermal
diffusivity. To the unaware reader more familiar with RBC, this can be
a bit confusing, since there are no independent measures of the
driving (superadiabaticity) and the thermal diffusivity there. It
would really help the reader here to point out the following in
relation to the simulation sets that are performed:

\begin{itemize}
\item At fixed $\epsilon$, varying Ra means that the thermal diffusivity $\chi_t$
scales like 1/$\sqrt{\text{Ra}}$.
\item At fixed Ra, varying $\epsilon$ means that the thermal diffusivity $\chi_t$
scales like $\epsilon$.
\item Since Pr=fixed, viscous diffusivity scales like thermal diffusivity.
\item (and of course, all vary with depth individually)
\end{itemize}
\end{myquotation}
I need to add this to the experiment section.

\begin{myquotation}
Beyond that, I think everything is right. The expression for the
polytopes in terms of the number of density scale heights makes the
notation a little over-complex. There are some disconnects in where
the non-dimensionalisation is performed (they say that ``take R=1'' at
one point and then non-dimensionalise R out again later, for example).
The description of which of the diffusivities or the
conductivity/dynamic viscosity are constant could certainly be
tightened up.
\end{myquotation}
I need to tighten up the description of polytropes, and only talk about
non-dimensionalizing R once.

\begin{myquotation}
With regard to the results:

In light of what I said above, the results in Fig 2. are not
surprising. Higher Ra here at fixed epsilon means lower thermal
diffusivity, and therefore eddies might be expected to retain their
identity longer. The above explanation would help.
\end{myquotation}
Agreed, we hope that the added explanation makes this clearer to the
reader.

\begin{myquotation}
There is quite a bit of mention of “windy” states without any real
technical description of what they are. Please either give more
information (at least something visual to distinguish from non-windy
states) or remove the distraction.
\end{myquotation}
I think it might be a good idea to remove them in order to keep it 
letter-length, but I'll see if I can keep it short \& explain 
relevant pieces.

\begin{myquotation}
Nusselt number: Usually this is a ratio of heat transport in the
turbulent state to that in the conduction state. So therefore, aren’t
the two $F_A$’s different on the top and the bottom? The top has a
modified kappa but the bottom has the original kappa profile?
\end{myquotation}
Nope!  That's our new change.  Maybe make this clearer.

\begin{myquotation}
I think the paragraphs on the Nu vs Ra and the Re/Pe vs Ra are the
meat of the paper! It would really be nice here to know what causes
the difference between 2D and 3D in the Nu plots. The 2/7 law is often
associated with more “windy” states. That seems LESS likely in 3D, so
what is going on? Note also that the sensitive dependence on the exact
roll or other structure seems to imply that the simulation box is too
small. This dependence should not be the case.
\end{myquotation}
Yeah, AR=4, 8, and 16 all return the windy states, so there's some strange
physics here.  I'll try to explain the discrepancy between 2D and 3D, though.

\begin{myquotation}
The Re vs Ra are a bit mysterious at low Ra. I would expect the Re ~
RA$^{1/2}$. Can you explain these alternative scalings or at least why the
expected scaling emerges at large Ra? Are the 2D ones just
over-constrained?
\end{myquotation}
Yes, can explain: we're combining the 1/2 scaling law that we expect from
the Ra changing diffusivity with the 1/4 scaling law of rising Ma in 2D,
which produces the 3/4 law.

\begin{myquotation}
Regarding Fig 4 — are the authors calculating the integrated evolved
density profile to get this number? If the effect is only in the
boundary layer as they mention, I am surprised that the deviation is
so large. This figure needs much more explanation!
\end{myquotation}
We're calculating the horizontally averaged, time-integrated, evolved density
profile and then taking two measures of it.  One is max/min, one is top of domain
/ bottom of domain.  We should probably explain this more and mention that it persists
even at high $\epsilon$ in 3D.

\noindent
This concludes our response to report B.  We thank referee B for this second report.

$\,$
\newline
$\,$
\newline
\noindent
\Large{\textbf{Response to report C:}}\newline$\,$\newline\indent

\begin{myquotation}
This Letter reports results from a numerical study of thermal
convection in a compressible fluid at unity Prandtl number and a range
of initial stratification. The main result is the scaling of the
Nusselt number with the Rayleigh number, supplemented by some
observations such as characteristic changes in the transition between
subsonic and supersonic regimes.

This problem is highly challenging. Ideally, a numerical exploration
should be guided by some theoretical insights or practical
observations. The present paper appears to be ``purely'' numerical
without such guidance, albeit some comparison with the well-known
problem of incompressible Rayleigh--Bernard convection. Nevertheless,
the results are significant and should be published. While I do not
wholeheartedly recommend this paper to PRL, I would not object to its
acceptance.
\end{myquotation}
Is there any way we can bring in some more ``we're guided by X and thus
we expected to get our results''?

\begin{myquotation}
Below is a minor comment that the authors may find useful.

Most parts of the paper is relatively well written, except in the
introduction. Here, there is room for improvement. The introductory
paragraph is virtually empty. I would cite a couple of papers for
"These prior studies" and be specific about both "important insight"
and known "fundamental properties". The final paragraph of the
introduction has failed to fulfill its mission. I would explicitly
state (at least) the most significant result of the paper in this
paragraph.
\end{myquotation}
We need to beef up the intro, as specified here.

$\,$\newline\noindent
This concludes our response to report C.  We thank referee C for this report.

$\,$
\newline
\noindent

\end{singlespace}

\bibliography{../../biblio.bib}
\end{document}

### 2017-06-12 tex/nusselt_paper.tex
reworks the Ra/Pr discussion

@@
 the superadiabatic excess, $\epsilon = m_{ad} - m$, where 
-$m_{ad} = (\gamma - 1)^{-1}$.
+$m_{ad} = (\gamma - 1)^{-1}$ and the initial entropy
+difference between the top and bottom boundaries is
+$\Delta S_0 = \epsilon\ln (1 + L_z)$.  At a fixed value of
+$\epsilon$, the diffusivities are set by the
+Rayleigh number (Ra) and the Prandtl number (Pr),
+\begin{equation}
+\text{Ra}_{t} = \frac{g L_z^3 (\Delta S_0 / c_P)}{\nu_t\chi_t},
+\qquad
+\text{Pr} = \frac{\nu}{\chi},
+\end{equation}
+where $c_P = \gamma/(\gamma-1)$ is the specific heat at
+constant pressure, and $\nu$ and $\chi$ are the thermal diffusivity and
+kinematic viscosity, respectively.
 The atmospheric thermal diffusivity, $\chi$,
@@
 are determined by the Rayleigh number (Ra) and the Prandtl
-number (Pr).  We set $\text{Pr } = \nu/\chi = 1$ throughout
-this work. The polytropic initial conditions are in
-thermal equilibrium, $\kappa_0 \partial_z T_0 =$ const,
-so $\kappa_0 = \chi \rho_0$ must be constant. To keep
-Pr constant with height, we set $\chi = \chi_t/\rho_0$
-and $\nu = \nu_t/\rho_0$.  Under these constraints, the
-diffusivity profiles are specified by choosing Ra
-at the top of the domain,
+number (Pr).  These polytropes are initially in
+thermal equilibrium, so the initial thermal
+conductivity, $\kappa_0 = \chi \rho_0$ must be
+constant.  Throughout this work we specify
+that Pr $= 1$ and is constant with depth.  By this
+choice, $\chi = \chi_t / \rho_0$ and $\nu = \nu_t / \rho_0$.
+We leave $\kappa = \rho\chi$ and the dynamic viscosity,
+$\mu = \rho\nu$, free to evolve as the density 
+profile evolves.  This formulation 
+means Ra at the bottom of the domain is greater than
+Ra$_t$ by a factor of $e^{2n_\rho}$, and henceforth
+when we specify Ra we are referring to Ra$_t$.
+
+Our diffusivities thus scale as
 \begin{equation}
-\text{Ra}_{\text{top}} = \frac{g L_z^3 (\Delta S_0 / c_P)}{\nu_t\chi_t},
+\chi_t \propto \sqrt{\frac{\epsilon}{\text{Pr}\cdot\text{Ra}_t}}, \qquad
+\nu_t \propto \sqrt{\frac{\epsilon\cdot\text{Pr}}{\text{Ra}_t}},
 \end{equation}
-where $\Delta S_0 = \epsilon\ln (1 + L_z)$ is the initial entropy difference 
-between the top and bottom of the atmosphere and
-$c_P = \gamma(\gamma-1)^{-1}$ is the specific heat 
-at constant pressure. The profiles of $\nu$ and $\chi$ are constant with
-time, and Ra at the bottom of the atmosphere is greater than Ra$_{\text{top}}$
-by a factor of $e^{2n_{\rho}}$.  This formulation leaves
-the thermal conductivity, $\kappa = \rho\chi$, and
-the dynamic viscosity, $\mu = \rho\nu$, free to evolve
-as the density profile changes.  Henceforth,
-when we use Ra, we are referring to Ra$_{\text{top}}$.
+and for constant Pr = 1, as in this work, $\chi_t = \nu_t$.
 
@@
 all thermodynamic variables to unity at $z = L_z$, choosing
-$R = T_t = \rho_t = 1$.  By this choice, the non-dimensional
+$T_t = \rho_t = 1$.  By this choice, the non-dimensional
 length scale is the inverse temperature gradient scale and the 

### 2017-06-12 code/plotting/parameter_space_plots.py
updates plot scripts

@@ -54,7 +54,7 @@ def line_leastsq(x, y, y_uncert):
     p = np.array((slope, intercept))
     covar = np.array(((s, -sx),(-sx, sx2)))/Delta
     return p, covar
-START_FILE=20
+START_FILE=100
 N_FILES=1000
 golden_ratio=1.618
 FIGWIDTH=3+7.0/16
@@ -71,21 +71,24 @@ comm = MPI.COMM_WORLD
 root_dir='/nobackup/eanders/sp2017/fc_poly_hydro/'
 mach_dir='/nobackup/eanders/sp2017/mach_eps/'
 threeD_dir = '/nobackup/bpbrown/polytrope-evan-3D/'
+mach_threeD_dir = '/nobackup/eanders/sp2017/mach_eps_3D/'
 threeD_out_dir='/parameter_calcs/'
 param_keys = ['Ra', 'eps', 'nrhocz', 'Pr']
 
-keys = ['Nusselt_AB17', #'Nusselt', 'Nusselt_5', 'Nusselt_6', 'norm_5_kappa_flux_z',  
+keys = ['Nusselt', 'Nusselt_5', 'Nusselt_6', 'norm_5_kappa_flux_z',  
     'Re_rms', 'Ma_ad', 'Ma_iso', 'ln_rho1', 'T1', 'vel_rms',\
-    'rho_full', 'T_full', 'kappa_flux_z', 'enthalpy_flux_z', 'PE_flux_z', 'KE_flux_z', 'viscous_flux_z', 'kappa_flux_z']# 'kappa_flux_fluc_z']
+    'rho_full', 'T_full', 'kappa_flux_z', 'enthalpy_flux_z', 'PE_flux_z', 'KE_flux_z', 'viscous_flux_z', 'kappa_flux_z', 'kappa_flux_fluc_z']
 plot_keys = [('Nusselt_6', 'minmax'), ('Re_rms', 'midplane'), ('Ma_ad_post', 'minmax'), ('density_contrasts', 'val'), ('rho_full', 'logmaxovermin')]
 
 root_buddy = ParameterSpaceBuddy(root_dir, parameters=param_keys)
 mach_buddy = ParameterSpaceBuddy(mach_dir, parameters=param_keys)
 threeD_buddy = ParameterSpaceBuddy(threeD_dir, parameters=param_keys, out_dir_name=threeD_out_dir)
[…]

### 2017-06-13 tex/nusselt_paper.tex
fixes a type in abstract

@@
 follows scaling relationships similar to those found in the well-studied, 
-incompressble Rayleigh-B\'{e}nard problem.
+incompressible Rayleigh-B\'{e}nard problem.
 The scaling of evolved fluid properties (Nu, Reynolds number,
@@
 and for constant Pr = 1, as in this work, $\chi_t = \nu_t$.
+We carry out two experiments in this letter: one in which
+we fix $\epsilon$ and vary Ra, thus increasing the diffusive
+timescales, and a second in which we fix Ra and vary $\epsilon$,
+thus...
 
@@
 Nu $\appropto$ Ra$^{1/3}$ regardless of $\epsilon$,
-reminiscent of scaling laws in classical \RB theory \cite{king&all2012}.
+reminiscent of scaling laws in \RB boundary layer theory 
+\cite{grossman&lohse2000, ahlers&all2009}.
 As the flow becomes supersonic,  Nu $\appropto$ Ra$^{1/5}$.

### 2017-06-13 tex/nusselt_paper.tex
lots of small tweaks

@@
 We perform a suite of 2D and 3D simulations in which we vary the initial
-superadiabaticity ($\epsilon$) and the Rayleigh number (Ra) at a set
+superadiabaticity ($\epsilon$) and the Rayleigh number (Ra) while fixing the
 initial density stratification, aspect
 ratio, and Prandtl number.
-We find that the Mach number (Ma) is a strong function of $\epsilon$
-in both 2D and 3D simulations, and that it is a 
-weak function of Ra in 2D.
-Surprisingly, we find that the evolved heat transport, 
+The evolved Mach number (Ma) scales according to
+$\text{Ma} \propto \epsilon^{1/2}\text{Ra}^{\alpha}$, where
+$\alpha = 0$ in 3D and $\alpha \approx 1/4$ in 2D.
+The evolved heat transport, 
 quantified by the Nusselt number (Nu),
 follows scaling relationships similar to those found in the well-studied, 
-incompressible Rayleigh-B\'{e}nard problem.
-The scaling of evolved fluid properties (Nu, Reynolds number,
-stratification) differs in the subsonic and supersonic regimes; 
-aside from the sonic transition, the evolved fluid properties
-of low and high Ma flows are nearly identical.  
-Our limited 3D runs suggest that
-evolved fluid properties behave similarly in 2D and 3D.
+incompressible Rayleigh-B\'{e}nard problem in both 2D and 3D.
+At large values of $\epsilon$, significant density inversions appear in the
+evolved atmospheres and seem to persist in both 2D and 3D.
 \end{abstract}
@@
 and is the simplest stratified extension of RB.
-In this work we take $R = 1$.
 We study atmospheres which are initially polytropically stratified,
@@
 
-Convective dynamics are controlled by the superadiabaticity
+We nondimensionalize our domains by setting
+all thermodynamic variables to unity at $z = L_z$, choosing
+$R = T_t = \rho_t = 1$.  By this choice, the non-dimensional
+length scale is the inverse temperature gradient scale and the 
+timescale is the isothermal sound crossing time, 
+$\tau_I$, of this unit length.
+Meaningful convective dynamics occur on 
+timescales of the atmospheric buoyancy time,
+$t_b = \tau_I \sqrt{L_z/g\epsilon}$.
+
+At fixed $n_\rho$, convective dynamics are 
+controlled by the superadiabaticity
 of the atmospheres as well as the atmospheric diffusivities.
@@
 kinematic viscosity, respectively.
-The atmospheric thermal diffusivity, $\chi$,
-and kinematic viscosity (viscous diffusivity), $\nu$,
-are determined by the Rayleigh number (Ra) and the Prandtl
-number (Pr).  These polytropes are initially in
+These polytropes are initially in
 thermal equilibrium, so the initial thermal
-conductivity, $\kappa_0 = \chi \rho_0$ must be
+conductivity, $\kappa_0 = \chi \rho_0$, must be
 constant.  Throughout this work we specify
-that Pr $= 1$ and is constant with depth.  By this
-choice, $\chi = \chi_t / \rho_0$ and $\nu = \nu_t / \rho_0$.
-We leave $\kappa = \rho\chi$ and the dynamic viscosity,
-$\mu = \rho\nu$, free to evolve as the density 
-profile evolves.  This formulation 
+that Pr $= 1$ and is constant with depth.  By these
+choices, $\chi = \chi_t / \rho_0$ and $\nu = \nu_t / \rho_0$.
+This formulation 
 means Ra at the bottom of the domain is greater than
@@
 when we specify Ra we are referring to Ra$_t$.  
+We leave $\kappa = \rho\chi$ and 
+$\mu = \rho\nu$ (the dynamic viscosity) free to evolve as the density 
+profile evolves.
 
-Our diffusivities thus scale as
+Atmospheric diffusivities thus scale as
 \begin{equation}
@@
 \nu_t \propto \sqrt{\frac{\epsilon\cdot\text{Pr}}{\text{Ra}_t}},
+\label{eqn:diffusivities}
 \end{equation}
@@
 We carry out two experiments in this letter: one in which
-we fix $\epsilon$ and vary Ra, thus increasing the diffusive
-timescales, and a second in which we fix Ra and vary $\epsilon$,
-thus...
+we fix $\epsilon$ and increase Ra, thus increasing the diffusive
+timescales, and a second in which we fix Ra and raise $\epsilon$,
+thus decreasing the ratio of the buoyant timescale to the 
+diffusive timescales.
 
@@
 such that only the lower 25\% of the coefficients
-have power. We nondimensionalize our computational domains by setting
-all thermodynamic variables to unity at $z = L_z$, choosing
-$T_t = \rho_t = 1$.  By this choice, the non-dimensional
-length scale is the inverse temperature gradient scale and the 
-timescale is the isothermal sound crossing time, 
-$\tau_I$, of this unit length.
-Meaningful convective dynamics occur on 
-timescales of the atmospheric buoyancy time,
-$t_b = \tau_I \sqrt{L_z/g\epsilon}$. 
-All reported results are taken from time averages
+have power. All reported results are taken from time averages
 over many $t_b$ beginning \{100, 40\}$t_b$
@@
 Ma $\appropto \epsilon^{1/2}$, so at high Ra, Ma$_{\text{3D}} < \text{Ma}_{\text{2D}}$.
-The value of $\epsilon$ also sets the size of the
-evolved thermodynamic fluctuations, such that
-$T_1/T_0 \appropto \epsilon$ and $\rho_1/\rho_0 \appropto \epsilon$.  
-These fluctuations are very small when $\epsilon$ and Ma are small,
-but can be O(1) for values of $\epsilon$ near 1.
 
@@
 three \cite{malagoli&all1990} dimensional polytropic simulations previously.
-As Ra is increased to large values 
-(Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures 
-no longer span the domain depth; rather, they break up into 
-small eddies which traverse the domain multiple
-times before diffusing.  Our choice of fixed temperature, stress free boundary conditions 
-allows the flux at the boundaries to vary, while also allowing
-for mean horizontal velocity profiles along the boundaries (winds).
-We find these windy convective states, reminiscent of similar states
-in RB convection \cite{goluskin&all2014}, at $\epsilon = 10^{-4}$ and
-Ra/Ra$_{\text{crit}} \gtrsim 10^{3}$. Roll states (Fig. \ref{fig:entropy_snapshots}a) with high convective
-transport alternate with windy states of lower transport.
+As Ra is increased to large values (Fig. \ref{fig:entropy_snapshots}c) 
+and diffusivities become small according to (\ref{eqn:diffusivities}),
+thermodynamic structures break up into small eddies which traverse the
+domain repeatedly before diffusing.
+Furthermore, the value of $\epsilon$ sets the size of the
+evolved thermodynamic fluctuations from their adiabatic values,
+as evidenced by the scalings of the colorbars.
+%These fluctuations are very small when $\epsilon$ and Ma are small,
+%but can be O(1) for values of $\epsilon$ near 1.
+
+%Our choice of fixed temperature, stress free boundary conditions 
+%allows the flux at the boundaries to vary, while also allowing
+%for mean horizontal velocity profiles along the boundaries (winds).
+%We find these windy convective states, reminiscent of similar states
+%in RB convection \cite{goluskin&all2014}, at $\epsilon = 10^{-4}$ and
+%Ra/Ra$_{\text{crit}} \gtrsim 10^{3}$. Roll states (Fig. \ref{fig:entropy_snapshots}a) with high convective
+%transport alternate with windy states of lower transport.
 
@@
 As the flow becomes supersonic,  Nu $\appropto$ Ra$^{1/5}$.
-2D runs at $\text{Ra }\gtrsim 10^3$Ra$_{\text{crit}}$
-and $\epsilon = 10^{-4}$ exhibit windy convective states.
-In these runs, the system is in flux equilibrium only when
-time averaged over roll states and windy states.
-A long time average
-over both of these states produces a flat flux profile which
-can be sensibly analyzed, but the presence of these time-dependent states
-makes it difficult to equilibrate these higher Ra cases.
+%2D runs at $\text{Ra }\gtrsim 10^3$Ra$_{\text{crit}}$
+%and $\epsilon = 10^{-4}$ exhibit windy convective states.
+%In these runs, the system is in flux equilibrium only when
+%time averaged over roll states and windy states.
+%A long time average
+%over both of these states produces a flat flux profile which
+%can be sensibly analyzed, but the presence of these time-dependent states
+%makes it difficult to equilibrate these higher Ra cases.
 It is also important to note that
@@
 Ra can result in a simulation latching on to one solution or the other. 
+(ADD SOMETHING ABOUT THIS BEING ASPECT RATIO INDEPENDENT AND MAYBE BRIEFLY
+MENTION WINDY STATES HERE?)
 In our limited 3D runs, it appears that Nu $\appropto$ Ra$^{2/7}$, a classic scaling law
@@
 
-We observe interesting phenomena, such as time-dependent, windy
-states of shear in our 2D simulations.  
-Unlike in RB \cite{goluskin&all2014}, our solutions with
-windy states have transport which scales in line with our non-windy solutions.
-Furthermore, the stratification of 
+%We observe interesting phenomena, such as time-dependent, windy
+%states of shear in our 2D simulations.  
+%Unlike in RB \cite{goluskin&all2014}, our solutions with
+%windy states have transport which scales in line with our non-windy solutions.
+The stratification of 
 these polytropic atmospheres evolves in a complex

### 2017-06-14 referee_process/second_submission/referee_response.tex
lots of small tweaks
lots of work on referee stuff.

@@
 \begin{singlespace}
-Editor letter goes here
+We thank the two referees for their detailed and constructive critique.
+The science in our paper has not greatly changed since the last iteration.
+We have completed a select few 3D runs which do not change our results,
+but which make the scaling of parameters at 3D more clear to the reader.
+We have modified the text of the paper to address the critiques of
+both reports, and have adjusted the styles of select figures in order to
+more efficiently call out interesting results.
+
+We include the revised version of our paper.  Below, we include a
+detailed response to the reports; we include the text of the reports
+in their entirety along with our responses inline.
 
@@
 \end{myquotation}
-I need to add this to the experiment section.
+We have reworked the discussion of defining Ra and Pr, and have added
+a new Eqn (3) which demonstrates explicitly states how our diffusivities
+scale with input parameters.  We have also explicitly stated the two types
+of experiments we perform (varying $\epsilon$ while holding Ra constant,
+and vice versa), and what these experiments do to the timescales of
+our problem.
 
@@
 \end{myquotation}
-I need to tighten up the description of polytropes, and only talk about
-non-dimensionalizing R once.
+We have moved the discussion of non-dimensionalization between the
+definition of the polytrope and the discussion of diffusivities in
+order to make the discussion flow more logically.
 
@@
 \end{myquotation}
-Agreed, we hope that the added explanation makes this clearer to the
-reader.
+We have adjusted our mention of Fig. 2c such that it calls out that
+the long-lasting eddies are what we expect.
 
@@
 \end{myquotation}
-I think it might be a good idea to remove them in order to keep it 
-letter-length, but I'll see if I can keep it short \& explain 
-relevant pieces.
+We have removed the three scattered discussions of ``windy'' states,
+and replaced them with a short mention in the paragraph describing
+Fig. 1.  Figs. 1, 2, and 3 have been updated to make it clear which
+runs exhibited ``windy'' states.
 
@@
 \end{myquotation}
-Nope!  That's our new change.  Maybe make this clearer.
+The change in $\kappa$ as $\rho$ evolves means that the evolved
+atmosphere can have a very different conductive state than the
+initial atmosphere, particularly at large values of $\epsilon$.
+Thus, both the top and bottom of Nu use the evolved state's
+value of $F_A$.  In the previous iteration of the letter, 
+$F_A$ was entirely defined by the initial atmosphere, and
+the $F_{\text{cond}}$ used in the denominator of Nu was
+based on the initial atmosphere, as well.  This led to the
+large deviation in Nu scaling at high and low $\epsilon$,
+as a result of the large shifts in the density profile,
+but as Fig. 4 shows, this shift was merely a result of the
+density profile changing rather than a difference in the
+amount of flux being carried.
 
@@
 \end{myquotation}
-Yeah, AR=4, 8, and 16 all return the windy states, so there's some strange
-physics here.  I'll try to explain the discrepancy between 2D and 3D, though.
+I really have no idea what the 2/7 law means.
+We have added a note that mentions that higher aspect ratios do \emph{not}
+seem to change the solution outcome.
 
 \begin{myquotation}
-The Re vs Ra are a bit mysterious at low Ra. I would expect the Re ~
-RA$^{1/2}$. Can you explain these alternative scalings or at least why the
+The Re vs Ra are a bit mysterious at low Ra. I would expect the Re $\sim$
+Ra$^{1/2}$. Can you explain these alternative scalings or at least why the
 expected scaling emerges at large Ra? Are the 2D ones just
@@
 \end{myquotation}
-Yes, can explain: we're combining the 1/2 scaling law that we expect from
-the Ra changing diffusivity with the 1/4 scaling law of rising Ma in 2D,
-which produces the 3/4 law.
+The increased scaling of Re with Ra is now explained in the text.
 
 \begin{myquotation}
-Regarding Fig 4 — are the authors calculating the integrated evolved
+Regarding Fig 4 -- are the authors calculating the integrated evolved
 density profile to get this number? If the effect is only in the
@@
 We're calculating the horizontally averaged, time-integrated, evolved density
-profile and then taking two measures of it.  One is max/min, one is top of domain
-/ bottom of domain.  We should probably explain this more and mention that it persists
-even at high $\epsilon$ in 3D.
+profile and then taking two measures of it, as we now call out more clearly in the text.  
+One measure is the density max/min, and the other is the density at top/bottom.
+If density were monotonic, these measurements would be equivalent, but since density
+inversions form within the boundary layers, the max/min are found away from the boundaries
+before the density profile turns around.  We have observed boundary layers at the top of
+the domain which span more than one density scale height at $\epsilon = 1$.
 
@@
 acceptance.
-\end{myquotation}
-Is there any way we can bring in some more ``we're guided by X and thus
-we expected to get our results''?
 
-\begin{myquotation}
 Below is a minor comment that the authors may find useful.
@@
 \end{myquotation}
-We need to beef up the intro, as specified here.
+We have made the introduction more specific, as recommended in the above paragraph.
 

### 2017-06-14 tex/nusselt_paper.tex
lots of work on referee stuff.

@@
 ratio, and Prandtl number.
-The evolved Mach number (Ma) scales according to
-$\text{Ma} \propto \epsilon^{1/2}\text{Ra}^{\alpha}$, where
-$\alpha = 0$ in 3D and $\alpha \approx 1/4$ in 2D.
 The evolved heat transport, 
@@
 incompressible Rayleigh-B\'{e}nard problem in both 2D and 3D.
+The evolved Mach number (Ma) scales according to
+$\text{Ma} \propto \epsilon^{1/2}\text{Ra}^{\alpha}$, where
+$\alpha = 0$ in 3D and $\alpha \approx 1/4$ in 2D.
 At large values of $\epsilon$, significant density inversions appear in the
@@
 the convective envelope of the Sun, which spans 14 density scale heights.
-In the bulk of these systems, flows are at very low Mach number (Ma), 
-but numerical constraints have restricted most studies of 
+In the bulk of these systems, especially in the deep interior far below the surface,
+flows are at very low Mach number (Ma).  Unfortunately,
+numerical constraints have restricted most studies of 
 compressible convection to high Ma.
-These prior studies have provided important insight into the low temperature, 
+These prior studies \cite{hurlburt&all1984, cattaneo&all1990, brummell&all1996,
+brandenburg&all2005} have provided insight into the nature of
+convection in the low temperature,
 high Ma region near the Sun's surface. Few fundamental
-properties of low Ma convection, which characterizes deeper motions,
-are known.
+properties of low Ma compressible convection, such as the nature of
+convective heat transport, are known.
 
@@
 constant.  We also examine the behavior of flow properties, as quantified by Ma and Re.
+We find that the scaling of Nu is similar to the scaling of Nu in \RB convection,
+and that this scaling is not appreciably changed by the magnitude of the superadiabaticity.
 
@@
 occurs near Ra/Ra$_\text{crit} \approx \{10^{2}, 10^{3}\}$ for $\epsilon = \{1, 0.5\}$.
+We conjecture that the scaling of Ma with Ra is due to high-velocity ``spinners'' which
+form between upflow and downflow lanes in 2D, and which are constantly fed by 
+the relatively stationary upflows and downflows (BEN NEED CITES).
 In our limited 3D runs, Ma appears to be a function of $\epsilon$ alone, with
 Ma $\appropto \epsilon^{1/2}$, so at high Ra, Ma$_{\text{3D}} < \text{Ma}_{\text{2D}}$.
+Simulations in the range of Ra/Ra$_{\text{crit}} > 10^3$ at $\epsilon = 10^{-4}$
+exhibited ``windy'' states of convection, in which a large-scale horizontal
+shearing flow replaced the more standard upflow/downflow morphology of
+convection.  These states are represented in Figs. 
+\ref{fig:ma_v_eps}, \ref{fig:re_and_nu_v_ra}, \& \ref{fig:nrho_v_ra}
+as hatched points, and while they do not appear to greatly modify the
+scalings of fluid properties measured in this work, these states warrant
+further investigation, and similar states have been seen in
+RB convection \cite{goluskin&all2014}.
 
@@
 reminiscent of scaling laws in \RB boundary layer theory 
-\cite{grossman&lohse2000, ahlers&all2009}.
+\cite{grossman&lohse2000, ahlers&all2009, king&all2012}.
 As the flow becomes supersonic,  Nu $\appropto$ Ra$^{1/5}$.
@@
 Ra can result in a simulation latching on to one solution or the other. 
-(ADD SOMETHING ABOUT THIS BEING ASPECT RATIO INDEPENDENT AND MAYBE BRIEFLY
-MENTION WINDY STATES HERE?)
+Select simulations were run at aspect ratios of 8 and 16, and identical flow
+morphologies were obtained, which suggests that these states are sensitive to
+parameters other than the width of the domain.
 In our limited 3D runs, it appears that Nu $\appropto$ Ra$^{2/7}$, a classic scaling law
@@
 change.
-In 2D and at low Ra, Re $\appropto$ Ra$^{3/4}$.  When the flows
+In 2D and at low Ra, Re $\appropto$ Ra$^{3/4}$.  The heightened scaling
+of Re in 2D is due to the scaling of velocity (Ma) with Ra, as is
+seen in Fig. \ref{ma_v_ra}.  When the flows
 become supersonic, 
@@
 as shown in Fig. \ref{fig:nrho_v_ra}.
+Here we take two different measurements of the stratification present in the
+time-averaged, horizontally-averaged density profile: the density difference
+between the max and min value of the density profile (empty symbols) and the
+density difference between the top and bottom of the atmosphere (solid symbols).
 We find that supersonic flows support persistent density inversions (empty symbols)
 in the boundary layers, as
-was reported by \cite{brandenburg&all2005}.  We find this in 2D and 3D.
+was reported by \cite{brandenburg&all2005}.  We find this in 2D and 3D, even
+at very large $\epsilon$.
 Surprisingly, the evolved $n_\rho$ is always less than the initial $n_\rho = 3$,

### 2017-06-16 tex/nusselt_paper.tex
puts in this afternoon edits

@@
 follows scaling relationships similar to those found in the well-studied, 
-incompressible Rayleigh-B\'{e}nard problem in both 2D and 3D.
+incompressible Rayleigh-B\'{e}nard problem in both 2D and 3D and is not
+appreciably affected by the magnitude of $\epsilon$.
 The evolved Mach number (Ma) scales according to
@@
 compressible convection to high Ma.
-These prior studies \cite{hurlburt&all1984, cattaneo&all1990, brummell&all1996,
+These prior studies \cite{graham1975, chan&all1982,
+hurlburt&all1984, cattaneo&all1990, brummell&all1996,
 brandenburg&all2005} have provided insight into the nature of
@@
 high Ma region near the Sun's surface. Few fundamental
-properties of low Ma compressible convection, such as the nature of
+properties of low Ma compressible convection, such as the scaling of
 convective heat transport, are known.
@@
 hurlburt&all1984, cattaneo&all1990} and three 
-\cite{cattaneo&all1991, brummell&all1996} dimensions
+\cite{cattaneo&all1991, brandenburg&all2005, brummell&all1996} dimensions
 revealed a different evolved state from the RB case.
@@
 constant.  We also examine the behavior of flow properties, as quantified by Ma and Re.
-We find that the scaling of Nu is similar to the scaling of Nu in \RB convection,
+We find here that the scaling of Nu in stratified, compressible convection 
+is similar to that in \RB convection,
 and that this scaling is not appreciably changed by the magnitude of the superadiabaticity.
@@
 We examine a monatomic ideal gas with an adiabatic index of
-$\gamma = 5/3$ whose equation of state is $P = R\rho T$. This is consistent with the approach used in earlier work \cite{graham1975, chan&all1982,
+$\gamma = 5/3$ whose equation of state is $P = R\rho T$. This is consistent with the approach used in earlier work 
+\cite{graham1975, chan&all1982, brandenburg&all2005,
 hurlburt&all1984, cattaneo&all1990, cattaneo&all1991, brummell&all1996} 
@@
 the number of density scale heights, $n_{\rho}$, it spans initially.
-Throughout this letter we set $n_{\rho} = 3$.  Satisfying hydrostatic
-equilibrium sets the value of gravity, $g = T_t (m + 1)$, which is
+Throughout this letter we set $n_{\rho} = 3$.  The polytropic
+index is $m = m_{ad} - \epsilon$, where $m_{ad} = (\gamma - 1)^{-1}$
+and $\epsilon$ is the superadiabatic excess.  Satisfying hydrostatic
+equilibrium sets the value of gravity, $g = RT_t (m + 1)$, which is
 constant with depth.  We study atmospheres with aspect
@@
 
-We nondimensionalize our domains by setting
+These domains are nondimensionalized by setting
 all thermodynamic variables to unity at $z = L_z$, choosing
@@
 of the atmospheres as well as the atmospheric diffusivities.
-The superadiabaticity, or the magnitude of the (negative) 
-entropy gradient, is set by 
-the superadiabatic excess, $\epsilon = m_{ad} - m$, where 
-$m_{ad} = (\gamma - 1)^{-1}$ and the initial entropy
+The superadiabaticity is set by $\epsilon$ and 
+the initial entropy
 difference between the top and bottom boundaries is
@@
 conductivity, $\kappa_0 = \chi \rho_0$, must be
-constant.  Throughout this work we specify
-that Pr $= 1$ and is constant with depth.  By these
-choices, $\chi = \chi_t / \rho_0$ and $\nu = \nu_t / \rho_0$.
+constant with depth.  Throughout this work we specify
+that Pr $= 1$ and is depth invariant.  By these
+choices, $\chi(z) = \chi_t / \rho_0$ and $\nu(z) = \nu_t / \rho_0$.
 This formulation 
-means Ra at the bottom of the domain is greater than
-Ra$_t$ by a factor of $e^{2n_\rho}$, and henceforth
+sets Ra at the bottom of the domain greater than
+Ra$_t$ by a factor of $e^{2n_\rho}$. Henceforth
 when we specify Ra we are referring to Ra$_t$.  
@@
 
-Atmospheric diffusivities thus scale as
+Under this formulation, diffusivities scale as
 \begin{equation}
@@
 timescales, and a second in which we fix Ra and raise $\epsilon$,
-thus decreasing the ratio of the buoyant timescale to the 
-diffusive timescales.
+thus increasing the ratio of the diffusive timescales to the
+buoyant timescale.
 
@@
 
-We measure the adiabatic Mach number (Ma = $|\bm{u}|/\sqrt{\gamma T}$).
-We find that Ma is a strong function of 
+We measure the adiabatic Mach number (Ma = $|\bm{u}|/\sqrt{\gamma T}$),
+and find that it is a strong function of 
 $\epsilon$ and a weak function of Ra.  
@@
 shearing flow replaced the more standard upflow/downflow morphology of
-convection.  These states are represented in Figs. 
+convection, similar to analogous states which have been studied in
+RB convection \cite{goluskin&all2014}.  These states are represented in Figs. 
 \ref{fig:ma_v_eps}, \ref{fig:re_and_nu_v_ra}, \& \ref{fig:nrho_v_ra}
-as hatched points, and while they do not appear to greatly modify the
-scalings of fluid properties measured in this work, these states warrant
-further investigation, and similar states have been seen in
-RB convection \cite{goluskin&all2014}.
+as hatched points, and while this phenomeonon does not appear to greatly modify the
+scaling of fluid properties measured in this work, these states warrant
+further investigation.
 
@@
 three \cite{malagoli&all1990} dimensional polytropic simulations previously.
-As Ra is increased to large values (Fig. \ref{fig:entropy_snapshots}c) 
-and diffusivities become small according to (\ref{eqn:diffusivities}),
+As in (\ref{eqn:diffusivities}), diffusivities become small as Ra 
+is increased to large values (Fig. \ref{fig:entropy_snapshots}c) and
 thermodynamic structures break up into small eddies which traverse the
@@
 of Re in 2D is due to the scaling of velocity (Ma) with Ra, as is
-seen in Fig. \ref{ma_v_ra}.  When the flows
+seen in Fig. \ref{fig:ma_v_eps}.  When the flows
 become supersonic, 
-this scaling gives way to Re $\appropto$ Ra$^{1/2}$.
+this scaling gives way to Re $\appropto$ Ra$^{1/2}$, as expected
+by the scaling of diffusivities in (\ref{eqn:diffusivities}).
 In our limited 3D runs, the scaling of Re is

### 2017-06-16 code/plotting/base/parameter_space_buddy.py
updates plot scripts

@@ -125,8 +125,8 @@ class ParameterSpaceBuddy():
     def read_files(self, keys):
         import h5py
         for i, dir in enumerate(self.dir_info):
-#            try:
-            if True:
+            try:
+#            if True:
                 f = h5py.File(dir[0]+self.out_dir_name+self.out_file_name, 'r')
 
                 Lz = np.exp(dir[self.parameters.index('nrhocz')+1]/(1.5-dir[self.parameters.index('eps')+1]))-1
@@ -154,10 +154,10 @@ class ParameterSpaceBuddy():
                     if np.isnan(storage[key][0]):
                         raise
                 dir[-1] = storage
-#            except:
-#                print("PROBLEMS READING OUTPUT FILE IN {:s}".format(dir[0]))
-#                import sys
-#                sys.stdout.flush()
+            except:
+                print("PROBLEMS READING OUTPUT FILE IN {:s}".format(dir[0]))
+                import sys
+                sys.stdout.flush()
         return self.dir_info
 
 
@@ -283,7 +283,21 @@ class ParameterSpaceBuddy():
                     kwargs['markeredgewidth'] = 1
             if label:
                 kwargs['label'] = label
-            ax.errorbar(x_vals, y_vals, xerr=x_err, yerr=y_err, color=color, marker=markers[i], ms=markersize[i], ls='None', capsize=0, **kwargs)
+
+            if grouping == 'eps' and group == 1e-4 and annotate == '':
+                
+                ax.errorbar(x_vals, y_vals, xerr=x_err, yerr=y_err, color=color, marker=markers[i], ms=markersize[i], ls='None', capsize=0,
+                        zorder=1, **kwargs)
+                x_vals = np.array(x_vals)
+                y_vals = np.array(y_vals)
+                y_vals2 = y_vals[x_vals >= 1e3]
+                x_vals2 = x_vals[x_vals >= 1e3]
+                print(x_vals2, y_vals2)
+                ax.scatter(x_vals2, y_vals2, marker=markers[i], c=color, s=35, hatch=10*'\\', edgecolor='black', lw=0.5, zorder=2) 
+                                            #hatch='/', edgecolor='white')
+            else:
+                ax.errorbar(x_vals, y_vals, xerr=x_err, yerr=y_err, color=color, marker=markers[i], ms=markersize[i], ls='None', capsize=0,
+                        zorder=5, **kwargs)
             if annotate != '':
                 for x, y in zip(x_vals, y_vals):
                     if empty_markers:
[…]

### 2017-06-16 code/plotting/parameter_space_plots.py

@@ -219,6 +219,7 @@ ax2.plot(x_3ds/11, y_3ds, dashes=(5,1,2,1,2,1), color='dimgrey')
 ax2.annotate(r'$\mathrm{2D}$', xy=(5e2, 1500), va='center', ha='center', fontsize=10)
 ax2.annotate(r'$\mathrm{3D}$', xy=(3e3, 60), va='center', ha='center', fontsize=10, color='dimgrey')
 ax2.set_ylim(1, 5e4)
+ax2.set_xlim(1e0, 1e7)
 ax2.set_xlabel(r'$\mathrm{Ra}/\mathrm{Ra}_{\mathrm{crit}}$')
 ax2.set_ylabel(r'$\mathrm{Re}$')
 ax2.set_xscale('log')
@@ -312,6 +313,7 @@ ax1.set_xlabel(r'$\mathrm{Ra}/\mathrm{Ra}_{\mathrm{crit}}$')
 ax1.set_ylabel(r'$\mathrm{Ma}$')
 ax1.set_xscale('log')
 ax1.set_yscale('log')
+ax1.set_xlim(1e0, 1e7)
 handles, labels = ax1.get_legend_handles_labels()
 legend1 = ax1.legend(handles[:1], labels[:1], loc='center right', fontsize=legend_fontsize, numpoints=1, 
                                               borderpad=0.3, labelspacing=0.3, handletextpad=0.3, borderaxespad=0.3, fancybox=True)
@@ -348,7 +350,7 @@ ax2, data, groups = mach_buddy.plot_parameter_space_comparison(ax2, 'eps', 'Ma_a
 #    print(key, p)
 x1s = np.logspace(-7, 1, 100)
 y1s = (0.5)*x1s**(1/2)
-ax2.plot(x1s, y1s, dashes=(5,1.5), color='black', label=r'$\mathrm{Ra}^{1/2}$')
+ax2.plot(x1s, y1s, dashes=(5,1.5), color='black', label=r'$\epsilon^{1/2}$')
 
 handles, labels = ax2.get_legend_handles_labels()
 legend1 = ax2.legend(handles[:1], labels[:1], loc='upper left', fontsize=legend_fontsize, numpoints=1, 
@@ -409,6 +411,7 @@ ax1, data, groups = root_buddy.plot_parameter_space_comparison(ax1, 'Ra', 'densi
[…]

### 2017-06-16 tex/nusselt_paper.tex
ready for ben to take a look at

@@
 where $m$ is the polytropic index and $L_z$ is the depth of the atmosphere.
+The polytropic
+index is set by the superadiabatic excess, $\epsilon = m_{ad} - m$, where
+$m_{ad} = (\gamma - 1)^{-1}$ is the adiabatic value of $m$.
 The height coordinate, $z$, increases upwards in the range $[0, L_z]$.
@@
 the number of density scale heights, $n_{\rho}$, it spans initially.
-Throughout this letter we set $n_{\rho} = 3$.  The polytropic
-index is $m = m_{ad} - \epsilon$, where $m_{ad} = (\gamma - 1)^{-1}$
-and $\epsilon$ is the superadiabatic excess.  Satisfying hydrostatic
+Throughout this letter we set $n_{\rho} = 3$.    Satisfying hydrostatic
 equilibrium sets the value of gravity, $g = RT_t (m + 1)$, which is
@@
 At fixed $n_\rho$, convective dynamics are 
-controlled by the superadiabaticity
-of the atmospheres as well as the atmospheric diffusivities.
-The superadiabaticity is set by $\epsilon$ and 
-the initial entropy
-difference between the top and bottom boundaries is
-$\Delta S_0 = \epsilon\ln (1 + L_z)$.  At a fixed value of
+controlled by $\epsilon$ as well as the atmospheric diffusivities.
+At a fixed value of
 $\epsilon$, the diffusivities are set by the
@@
 \end{equation}
-where $c_P = \gamma/(\gamma-1)$ is the specific heat at
+where $\Delta S_0 = \epsilon\ln (1 + L_z)$ is the initial entropy
+difference between the top and bottom boundaries,
+$c_P = \gamma/(\gamma-1)$ is the specific heat a
 constant pressure, and $\nu$ and $\chi$ are the thermal diffusivity and
 kinematic viscosity, respectively.
-These polytropes are initially in
-thermal equilibrium, so the initial thermal
-conductivity, $\kappa_0 = \chi \rho_0$, must be
-constant with depth.  Throughout this work we specify
-that Pr $= 1$ and is depth invariant.  By these
-choices, $\chi(z) = \chi_t / \rho_0$ and $\nu(z) = \nu_t / \rho_0$.
+Throughout this work we specify
+that Pr $= 1$ and is depth invariant.
+Polytropes, as specified in (\ref{eqn:polytrope}),
+are in thermal equilibrium. Thus, the initial thermal
+conductivity, $\kappa_0 = \chi \rho_0$, is
+constant with depth. 
+By these
+choices, $\nu(z) \equiv \chi(z) \equiv \chi_t / \rho_0$.
 This formulation 
@@
 when we specify Ra we are referring to Ra$_t$.  
-We leave $\kappa = \rho\chi$ and 
-$\mu = \rho\nu$ (the dynamic viscosity) free to evolve as the density 
+The full values of $\kappa = \rho\chi$ and 
+$\mu = \rho\nu$ (the dynamic viscosity) are free to evolve as the density 
 profile evolves.
@@
 \begin{equation}
-\chi_t \propto \sqrt{\frac{\epsilon}{\text{Pr}\cdot\text{Ra}_t}}, \qquad
-\nu_t \propto \sqrt{\frac{\epsilon\cdot\text{Pr}}{\text{Ra}_t}},
+\chi_t = \nu_t \propto \sqrt{\frac{\epsilon}{\text{Ra}_t}}
 \label{eqn:diffusivities}
 \end{equation}
-and for constant Pr = 1, as in this work, $\chi_t = \nu_t$.
+for constant Pr = 1, as in this work.
 We carry out two experiments in this letter: one in which
@@
 timescales, and a second in which we fix Ra and raise $\epsilon$,
-thus increasing the ratio of the diffusive timescales to the
+thus modifying the ratio of the diffusive timescales to the
 buoyant timescale.

### 2017-06-19 referee_process/second_submission/referee_response.tex
work with Ben

@@
 \end{myquotation}
-We have made the introduction more specific, as recommended in the above paragraph.
+We have clarified the structure of the introduction paragraph, have included
+citations to prior work at high Ma, and have set the context for the study
+of fundamental heat transport conducted here at low as well as high Ma.
 

### 2017-06-19 tex/nusselt_paper.tex
work with Ben

@@
 follows scaling relationships similar to those found in the well-studied, 
-incompressible Rayleigh-B\'{e}nard problem in both 2D and 3D and is not
-appreciably affected by the magnitude of $\epsilon$.
-The evolved Mach number (Ma) scales according to
-$\text{Ma} \propto \epsilon^{1/2}\text{Ra}^{\alpha}$, where
-$\alpha = 0$ in 3D and $\alpha \approx 1/4$ in 2D.
-At large values of $\epsilon$, significant density inversions appear in the
-evolved atmospheres and seem to persist in both 2D and 3D.
+incompressible Rayleigh-B\'{e}nard problem.  This scaling holds up in both 2D and 3D and is not
+appreciably affected by the magnitude of $\epsilon$. %think about last sentence.
 \end{abstract}
@@
 In stratified atmospheres, the magnitude of the unstable entropy gradient
-joins Ra and Pr as an important control parameter.  This 
+joins Ra and Pr as a third important and independent control parameter.  This 
 \emph{superadiabatic excess} \cite{graham1975}, $\epsilon$,
@@
 Subscript 0 indicates initial conditions and subscript $t$ indicates values
-at $z = L_z$.   We
+at $z = L_z$.   Stratified atmospheres have a fourth non-dimensional parameter,
+the number of density scale heights, $n_{\rho} = \ln\left[\rho_0(z=0)/\rho_t\right]$.  We
 specify the depth of the atmosphere, $L_z = e^{n_{\rho}/m} - 1$, by choosing
-the number of density scale heights, $n_{\rho}$, it spans initially.
+the initial value of $n_{\rho}$.
 Throughout this letter we set $n_{\rho} = 3$.    Satisfying hydrostatic
@@
 profile evolves.  
-
 Under this formulation, diffusivities scale as
+$\chi_t, \nu_t \propto \sqrt{g L_z^3 \epsilon / \text{Ra}_t}$.
+The thermal diffusion timescale is $t_\chi \equiv L_z^2 / \chi$. The
+ratio of the diffusion time to the buoyancy time is
 \begin{equation}
-\chi_t = \nu_t \propto \sqrt{\frac{\epsilon}{\text{Ra}_t}}
-\label{eqn:diffusivities}
+\frac{t_\chi}{t_b} = \left(\frac{c_P}{n_\rho}\right)^{1/2}\text{Ra}_t^{1/2}
+\left(m_{ad} - \epsilon\right)^{1/2}.
+\label{eqn:timescales}
 \end{equation}
-for constant Pr = 1, as in this work.
 We carry out two experiments in this letter: one in which
-we fix $\epsilon$ and increase Ra, thus increasing the diffusive
-timescales, and a second in which we fix Ra and raise $\epsilon$,
-thus modifying the ratio of the diffusive timescales to the
-buoyant timescale.
+we fix $\epsilon$ and increase Ra, thus increasing the ratio in
+(\ref{eqn:timescales}), and a second in which we fix Ra and change $\epsilon$.
+In this second experiment, the buoyancy time $t_b$ scales as $\epsilon^{-1/2}$
+relative to the speed of sound, and we see this reflected in the Mach
+number scaling. The ratio in (\ref{eqn:timescales}) is
+independent of $\epsilon$ when $\epsilon \ll m_{ad}$.
 
@@
 three \cite{malagoli&all1990} dimensional polytropic simulations previously.
-As in (\ref{eqn:diffusivities}), diffusivities become small as Ra 
+As in (\ref{eqn:timescales}), diffusivities become small as Ra 
 is increased to large values (Fig. \ref{fig:entropy_snapshots}c) and
@@
 this scaling gives way to Re $\appropto$ Ra$^{1/2}$, as expected
-by the scaling of diffusivities in (\ref{eqn:diffusivities}).
+by the scaling of diffusivities in (\ref{eqn:timescales}).
 In our limited 3D runs, the scaling of Re is

### 2017-06-20 tex/nusselt_paper.tex
fixes up experiment

@@
 joins Ra and Pr as a third important and independent control parameter.  This 
-\emph{superadiabatic excess} \cite{graham1975}, $\epsilon$,
-sets the scale of the atmospheric entropy gradient.
+\emph{superadiabatic excess}, $\epsilon$,
+sets the scale of the atmospheric entropy gradient \cite{graham1975}.
 We find here that $\epsilon$ primarily controls the Ma of the evolved solution.
@@
 and is the simplest stratified extension of RB.
-We study atmospheres which are initially polytropically stratified,
+The atmospheres studied are initially polytropically stratified,
 \begin{equation}
@@
 These domains are nondimensionalized by setting
-all thermodynamic variables to unity at $z = L_z$, choosing
-$R = T_t = \rho_t = 1$.  By this choice, the non-dimensional
+$R = T_t = \rho_t = 1$ at $z = L_z$.
+By this choice, the non-dimensional
 length scale is the inverse temperature gradient scale and the 
@@
 \end{equation}
-where $\Delta S_0 = \epsilon\ln (1 + L_z)$ is the initial entropy
+where $\Delta S_0 = \epsilon\ln (1 + L_z) = \epsilon n_\rho / m$ 
+is the initial entropy
 difference between the top and bottom boundaries,
-$c_P = \gamma/(\gamma-1)$ is the specific heat a
+$c_P = \gamma/(\gamma-1)$ is the specific heat at
 constant pressure, and $\nu$ and $\chi$ are the thermal diffusivity and
@@
 that Pr $= 1$ and is depth invariant.
-Polytropes, as specified in (\ref{eqn:polytrope}),
-are in thermal equilibrium. Thus, the initial thermal
+The initial thermal conductivity,
+Polytropes, as specified in ,
+are in thermal equilibrium. The initial thermal
 conductivity, $\kappa_0 = \chi \rho_0$, is
-constant with depth. 
+constant with depth, such that (\ref{eqn:polytrope}) is in
+thermal equilibrium. 
 By these
@@
 The full values of $\kappa = \rho\chi$ and 
-$\mu = \rho\nu$ (the dynamic viscosity) are free to evolve as the density 
+$\mu = \rho\nu$ (the dynamic viscosity) change as the density 
 profile evolves.  
-Under this formulation, diffusivities scale as
+The diffusivities scale as
 $\chi_t, \nu_t \propto \sqrt{g L_z^3 \epsilon / \text{Ra}_t}$.
-The thermal diffusion timescale is $t_\chi \equiv L_z^2 / \chi$. The
-ratio of the diffusion time to the buoyancy time is
+Defining the thermal diffusion timescale as $t_\chi \equiv L_z^2 / \chi$, the
+ratio of $t_\chi$ to the buoyancy time is
 \begin{equation}
@@
 \end{equation}
-We carry out two experiments in this letter: one in which
+We carry out two experiments in this letter. In the first,
 we fix $\epsilon$ and increase Ra, thus increasing the ratio in
-(\ref{eqn:timescales}), and a second in which we fix Ra and change $\epsilon$.
-In this second experiment, the buoyancy time $t_b$ scales as $\epsilon^{-1/2}$
-relative to the speed of sound, and we see this reflected in the Mach
-number scaling. The ratio in (\ref{eqn:timescales}) is
+(\ref{eqn:timescales}). In the second, we fix Ra and vary $\epsilon$,
+scaling the buoyancy time $t_b$ as $\epsilon^{-1/2}$
+relative to the speed of sound; we see this reflected in the evolved Mach
+number scaling (e.g., Fig. \ref{fig:ma_v_eps}). The ratio in (\ref{eqn:timescales}) is
 independent of $\epsilon$ when $\epsilon \ll m_{ad}$.
 
-We evolve the Fully Compressible Navier-Stokes equations,
+The Fully Compressible Navier-Stokes equations,
 \begin{align}
@@
 \end{align}
-with the viscous stress tensor given by
+are evolved with the viscous stress tensor given by
 \begin{equation}
@@
 Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
-We decompose our thermodynamic variables such that $T = T_0 + T_1$ and
+Thermodynamic variables are decomposed such that $T = T_0 + T_1$ and
 $\ln\rho = (\ln\rho)_0 + (\ln\rho)_1$, 
-and the velocity is $\bm{u} = u\hat{x} + v\hat{y} +  w\hat{z}$.
+and the velocity is $\bm{u} = w\bm{\hat{z}} + u\bm{\hat{x}} + v\bm{\hat{y}}$.
 In our 2D runs, $v = 0$.
@@
 We impose impenetrable, stress free, fixed temperature boundary conditions at
-the top and bottom of the domain such that 
+the top and bottom of the domain, with 
 $w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. 
@@
 random white noise whose magnitude is infinitesimal
-compared to $T_0$ and $\epsilon$.
+compared to $\epsilon T_0$.
 We filter this noise spectrum in coefficient space, 
@@
 over many $t_b$ beginning \{100, 40\}$t_b$
-after the start of our \{2D, 3D\} simulations in order to
-assure our results are not biased by the convective transient.
+after the start of our \{2D, 3D\} simulations to
+ensure our results are not biased by the convective transient.
 

### 2017-06-20 tex/nusselt_paper.tex
fixes flywheel discussion

@@
 This relation breaks down as the mean
-Ma approaches 1 (see Fig. \ref{fig:ma_v_eps}).  This transition
+Ma approaches 1 (Fig. \ref{fig:ma_v_eps}).  This transition
 occurs near Ra/Ra$_\text{crit} \approx \{10^{2}, 10^{3}\}$ for $\epsilon = \{1, 0.5\}$.
-We conjecture that the scaling of Ma with Ra is due to high-velocity ``spinners'' which
-form between upflow and downflow lanes in 2D, and which are constantly fed by 
-the relatively stationary upflows and downflows (BEN NEED CITES).
 In our limited 3D runs, Ma appears to be a function of $\epsilon$ alone, with
 Ma $\appropto \epsilon^{1/2}$, so at high Ra, Ma$_{\text{3D}} < \text{Ma}_{\text{2D}}$.
+We conjecture that the scaling of Ma with Ra in the 2D runs 
+is due to the formation of coherent high-velocity ``spinners,'' which form
+between upflow and downflow lanes in 2D.  These structures, which are reminiscent of flywheel
+modes in RB convection, do not appear in our 3D runs these parameters
+\cite{jones&all1976, brummell&all2002}.
 Simulations in the range of Ra/Ra$_{\text{crit}} > 10^3$ at $\epsilon = 10^{-4}$

### 2017-06-20 tex/nusselt_paper.tex
changes to letter with Ben

@@
 shearing flow replaced the more standard upflow/downflow morphology of
-convection, similar to analogous states which have been studied in
-RB convection \cite{goluskin&all2014}.  These states are represented in Figs. 
+convection.  Similar states have been studied in
+RB convection \cite{goluskin&all2014}.  These runs are represented in Figs. 
 \ref{fig:ma_v_eps}, \ref{fig:re_and_nu_v_ra}, \& \ref{fig:nrho_v_ra}
-as hatched points, and while this phenomeonon does not appear to greatly modify the
+as hatched points, and while this phenomenon does not appear to greatly modify the
 scaling of fluid properties measured in this work, these states warrant
@@
 shock systems form in the upper atmosphere near downflow lanes 
-(Fig. \ref{fig:entropy_snapshots}b\&c).
-These shock phenomena were reported in
-two \cite{cattaneo&all1990} and 
-three \cite{malagoli&all1990} dimensional polytropic simulations previously.
-As in (\ref{eqn:timescales}), diffusivities become small as Ra 
-is increased to large values (Fig. \ref{fig:entropy_snapshots}c) and
-thermodynamic structures break up into small eddies which traverse the
-domain repeatedly before diffusing.
-Furthermore, the value of $\epsilon$ sets the size of the
-evolved thermodynamic fluctuations from their adiabatic values,
-as evidenced by the scalings of the colorbars.
-%These fluctuations are very small when $\epsilon$ and Ma are small,
-%but can be O(1) for values of $\epsilon$ near 1.
-
-%Our choice of fixed temperature, stress free boundary conditions 
-%allows the flux at the boundaries to vary, while also allowing
-%for mean horizontal velocity profiles along the boundaries (winds).
-%We find these windy convective states, reminiscent of similar states
-%in RB convection \cite{goluskin&all2014}, at $\epsilon = 10^{-4}$ and
-%Ra/Ra$_{\text{crit}} \gtrsim 10^{3}$. Roll states (Fig. \ref{fig:entropy_snapshots}a) with high convective
-%transport alternate with windy states of lower transport.
+(Fig. \ref{fig:entropy_snapshots}b\&c), as reported previously
+\cite{cattaneo&all1990, malagoli&all1990}.
+At large Ra, the diffusion timescale becomes long (\ref{eqn:timescales}), 
+and
+thermodynamic structures form small eddies which traverse the
+domain repeatedly before diffusing (Fig. \ref{fig:entropy_snapshots}c).
+As evidenced by the colorbar scalings, the
+amplitudes of thermodynamic fluctuations scale with $\epsilon$.
 
@@
 %makes it difficult to equilibrate these higher Ra cases.
-It is also important to note that
+It is also important to note that, in 2D,
 the value of Nu is heavily dependent upon the specific thermodynamic
-structures of the solution, as double roll states will transport
-heat more efficiently than single roll states, and slight changes in
-Ra can result in a simulation latching on to one solution or the other. 
-Select simulations were run at aspect ratios of 8 and 16, and identical flow
-morphologies were obtained, which suggests that these states are sensitive to
-parameters other than the width of the domain.
+structures of the solution, and slight changes in
+Ra can result in a simulation converging to one solution or another. 
+Select simulations were run at higher aspect ratios (8 and 16), and similar flow
+morphologies were obtained, suggesting that these states not highly
+sensitive to aspect ratio.
 In our limited 3D runs, it appears that Nu $\appropto$ Ra$^{2/7}$, a classic scaling law
@@
 compare the importance of advection to diffusion in the evolved
-convective state.  For Pr = 1, such as in this work, Pe = Re.  
+convective state.  For Pr = 1, Pe = Re.  
 Our choice of $\{\nu,\chi\}\propto \rho_0^{-1}$ drastically changes
@@
 Re at the midplane ($z=L_z/2$) of the atmosphere in
-Fig. \ref{fig:re_and_nu_v_ra}b.  Largely we find that Re
-depends on Ra, but not $\epsilon$, except when the flow states
-change.
-In 2D and at low Ra, Re $\appropto$ Ra$^{3/4}$.  The heightened scaling
-of Re in 2D is due to the scaling of velocity (Ma) with Ra, as is
-seen in Fig. \ref{fig:ma_v_eps}.  When the flows
+Fig. \ref{fig:re_and_nu_v_ra}b.  We find that Re
+depends on largely Ra, but not $\epsilon$, except when the flow regime
+changes.
+In 2D Re $\appropto$ Ra$^{3/4}$ at low Ra.    When the 2D flows
 become supersonic, 
-this scaling gives way to Re $\appropto$ Ra$^{1/2}$, as expected
-by the scaling of diffusivities in (\ref{eqn:timescales}).
-In our limited 3D runs, the scaling of Re is
+Re $\appropto$ Ra$^{1/2}$, as expected
+from (\ref{eqn:timescales}).
+In our limited 3D runs,
 Re $\appropto$ Ra$^{1/2}$, consistent with the supersonic results.
+The heightened scaling
+of Re in 2D follows the scaling of velocity (Ma) with Ra, as
+seen in Fig. \ref{fig:ma_v_eps}, and reflects the presence of coherent
+spinners, which do not exist in 3D.
 
@@
 
-In the evolved state, the flows change the density stratification,
+In the evolved state, the flows can change the density stratification,
 as shown in Fig. \ref{fig:nrho_v_ra}.
-Here we take two different measurements of the stratification present in the
-time-averaged, horizontally-averaged density profile: the density difference
-between the max and min value of the density profile (empty symbols) and the
-density difference between the top and bottom of the atmosphere (solid symbols).
-We find that supersonic flows support persistent density inversions (empty symbols)
+We measure the 
+time- and horizontally-averaged density profile in two ways. Empty symbols
+show the density difference
+between the max and min value of the profile, while solid symbols
+show the difference between the top and bottom of the atmosphere. 
+We find that supersonic flows support persistent density inversions 
 in the boundary layers, as
-was reported by \cite{brandenburg&all2005}.  We find this in 2D and 3D, even
+was reported by \cite{brandenburg&all2005}.  This is visible when
+solid symbols lie below empty symbols.  We find this in 2D and 3D, even
 at very large $\epsilon$.
@@
 and turbulent pressure support plays a larger role than atmospheric slumping.
+The appears to arise as a result of the convection making the interior isentropic,
+tied with our fixed-temperature boundary conditions; 
+we expect the behavior of the stratification to be dependent on the choice of
+thermal boundary conditions.
 The agreement of Nu \& Re across $\epsilon$ (Fig. \ref{fig:re_and_nu_v_ra}), 
@@
 of $\epsilon$, except for where there is a transition between the subsonic
-and supersonic regimes.  We also see that Nu scales similarly in 3D and 2D,
-and that Ma in 3D solutions seems to be a function of $\epsilon$ alone,
+and supersonic regimes.  We also see that Nu scales similarly in 2D and 3D,
+and that Ma in 3D solutions appears to be a function of $\epsilon$ alone,
 allowing for simple specification of the evolved Ma using input parameters.
-
-%We observe interesting phenomena, such as time-dependent, windy
-%states of shear in our 2D simulations.  
-%Unlike in RB \cite{goluskin&all2014}, our solutions with
-%windy states have transport which scales in line with our non-windy solutions.
 The stratification of 
@@
 We thank Jon Aurnou, Axel Brandenburg, Keith Julien, Mark Rast, and Jeff Oishi 
-for many useful discussions. We also thank the two anonymous referees whose
+for many useful discussions. We also thank the three anonymous referees whose
 careful comments greatly improved the quality of this letter.

### 2017-06-20 referee_process/second_submission/referee_response.tex
updates to editor response letter

@@
 We thank the two referees for their detailed and constructive critique.
-The science in our paper has not greatly changed since the last iteration.
-We have completed a select few 3D runs which do not change our results,
-but which make the scaling of parameters at 3D more clear to the reader.
+We have completed further 3D runs which make the scaling of parameters at 3D 
+more clear to the reader.
 We have modified the text of the paper to address the critiques of
@@
 We have reworked the discussion of defining Ra and Pr, and have added
-a new Eqn (3) which demonstrates explicitly states how our diffusivities
-scale with input parameters.  We have also explicitly stated the two types
+a new Eqn (3) and related discussion which demonstrates explicitly 
+how our timescales vary with input parameters.  
+We have also explicitly stated the two types
 of experiments we perform (varying $\epsilon$ while holding Ra constant,
@@
 \end{myquotation}
-We have moved the discussion of non-dimensionalization between the
-definition of the polytrope and the discussion of diffusivities in
-order to make the discussion flow more logically.
+We agree. We have moved the discussion of non-dimensionalization after the
+definition of the polytrope and before the discussion of diffusivities.
 
@@
 \end{myquotation}
-We have adjusted our mention of Fig. 2c such that it calls out that
-the long-lasting eddies are what we expect.
+We agree and Eqn. 3 shows now shows this clearly.
+We have revised our discussion of Fig. 2c such that it 
+explicitly states that long-lasting eddies are what we expect based on 
+input parameters.
 
@@
 We have removed the three scattered discussions of ``windy'' states,
-and replaced them with a short mention in the paragraph describing
+and consolidated them to a short discussion in the paragraph describing
 Fig. 1.  Figs. 1, 2, and 3 have been updated to make it clear which
-runs exhibited ``windy'' states.
+runs exhibited ``windy'' states, and we think including them in the
+discussion at this level may be useful to the field when comparing to
+the work of Goluskin or others.
 
@@
 \end{myquotation}
-The change in $\kappa$ as $\rho$ evolves means that the evolved
-atmosphere can have a very different conductive state than the
-initial atmosphere, particularly at large values of $\epsilon$.
-Thus, both the top and bottom of Nu use the evolved state's
-value of $F_A$.  In the previous iteration of the letter, 
-$F_A$ was entirely defined by the initial atmosphere, and
-the $F_{\text{cond}}$ used in the denominator of Nu was
-based on the initial atmosphere, as well.  This led to the
+The evolution of $\kappa$ with $\rho$ (see discussion between
+Eqns 2 \& 3) means that the evolved atmosphere has a different
+conductive state than the initial atmosphere.  $\rho$ evolves
+the most at large $\epsilon$ (Fig. 4).
+Thus, both the numerator and denominator of Eqn. (9) 
+use the same evolved state and
+value of $F_A$.  In the first version of the letter, 
+$F_A$ was instead defined by the initial atmosphere, and
+the $F_{\text{cond}}$ used in the denominator of Eqn. (9) was
+based on the initial atmosphere as well, as traditionally
+in Rayleigh-Benard.  This led to the
 large deviation in Nu scaling at high and low $\epsilon$,
-as a result of the large shifts in the density profile,
-but as Fig. 4 shows, this shift was merely a result of the
+as a result of the large shifts in the density profile.
+However, as Fig. 4 shows, this shift was merely a result of the
 density profile changing rather than a difference in the
@@
 \end{myquotation}
-I really have no idea what the 2/7 law means.
-We have added a note that mentions that higher aspect ratios do \emph{not}
-seem to change the solution outcome.
+We also are unsure of what the 2/7 scaling relationship means for these
+fully compressible states.  We are interested in exploring this and potential
+boundary layer theories in future work, but a full examination of this
+is beyond the scope of this letter.
+We have conducted a very small number of high aspect ratio solutions which
+do not appear to converge to vastly different flow morphology.  We mention this
+in the discussion of Fig. 3a.
 
@@
 \end{myquotation}
-The increased scaling of Re with Ra is now explained in the text.
+The increased scaling of Re with Ra is now explained in the text at the end
+of the discussion of Fig 3b.  2D solutions build over-constrained spinners
+like flywheeling convection in Rayleigh-Benard, which don't seem to appear
+in our 3D solutions at these parameters.
 
@@
 \end{myquotation}
-We're calculating the horizontally averaged, time-integrated, evolved density
-profile and then taking two measures of it, as we now call out more clearly in the text.  
-One measure is the density max/min, and the other is the density at top/bottom.
-If density were monotonic, these measurements would be equivalent, but since density
-inversions form within the boundary layers, the max/min are found away from the boundaries
-before the density profile turns around.  We have observed boundary layers at the top of
+We have expanded our discussion of these two measurements when we discuss Fig. 4 in the text.
+If density were monotonic, these measurements would be equivalent, but density
+inversions form within the boundary layers and the max/min are found away from the boundaries.
+We have observed inverted boundary layers at the top of
 the domain which span more than one density scale height at $\epsilon = 1$.
+These are interesting and it's surprising that they persist in 3D.
+
+~\newline
 

### 2017-06-29 tex/nusselt_paper.tex
submission 3 version upload

@@
 \label{sec:intro}
-Convection transports energy in stellar and planetary atmospheres.
-In these objects, flows are compressible and
-feel the atmospheric stratification.  While in some systems this stratification 
-is negligible, it is significant in regions such as
+Convection transports energy in stellar and planetary atmospheres
+where flows are compressible and
+feel the atmospheric stratification.  This stratification 
+is significant in regions such as
 the convective envelope of the Sun, which spans 14 density scale heights.
-In the bulk of these systems, especially in the deep interior far below the surface,
+In the bulk of these systems, particularly in the deep interior,
 flows are at very low Mach number (Ma).  Unfortunately,
@@
 
-In the widely-studied \RB (RB) problem of incompressible Boussinesq convection, 
+In the widely-studied \RB problem of incompressible Boussinesq convection (RBC), 
 a negative temperature gradient causes convective instability.
@@
 \cite{cattaneo&all1991, brandenburg&all2005, brummell&all1996} dimensions
-revealed a different evolved state from the RB case.
+revealed a different evolved state from RBC.
 Downflow lanes
@@
 
-In RB convection, there exist two primary dynamical control parameters: 
+In RBC, there exist two primary dynamical control parameters: 
 the Rayleigh number (Ra, the ratio of
@@
 hurlburt&all1984, cattaneo&all1990, cattaneo&all1991, brummell&all1996} 
-and is the simplest stratified extension of RB.
+and is the simplest stratified extension of RBC.
 The atmospheres studied are initially polytropically stratified,
@@
 where $\Delta S_0 = \epsilon\ln (1 + L_z) = \epsilon n_\rho / m$ 
-is the initial entropy
-difference between the top and bottom boundaries,
+is the initial entropy difference across the domain,
 $c_P = \gamma/(\gamma-1)$ is the specific heat at
-constant pressure, and $\nu$ and $\chi$ are the thermal diffusivity and
-kinematic viscosity, respectively.
+constant pressure, $\nu$ is the thermal diffusivity, 
+and $\chi$ is the kinematic viscosity.
 Throughout this work we specify
 that Pr $= 1$ and is depth invariant.
-The initial thermal conductivity,
-Polytropes, as specified in ,
-are in thermal equilibrium. The initial thermal
+The initial thermal
 conductivity, $\kappa_0 = \chi \rho_0$, is
 constant with depth, such that (\ref{eqn:polytrope}) is in
-thermal equilibrium. 
+thermal equilibrium ($\grad\cdot[\kappa_0\grad T_0] = 0$).
 By these
@@
 relative to the speed of sound; we see this reflected in the evolved Mach
-number scaling (e.g., Fig. \ref{fig:ma_v_eps}). The ratio in (\ref{eqn:timescales}) is
+number scaling (Fig. \ref{fig:ma_v_eps}). The ratio in (\ref{eqn:timescales}) is
 independent of $\epsilon$ when $\epsilon \ll m_{ad}$.
@@
 We utilize the 
-Dedalus\footnote{http://dedalus-project.org/} \cite{burns&all2016} 
-pseudospectral framework to time-evolve  
+Dedalus\footnote{http://dedalus-project.org/} 
+pseudospectral framework \cite{burns&all2016} to time-evolve  
 (\ref{eqn:continuity_eqn})-(\ref{eqn:energy_eqn}) 
@@
 between upflow and downflow lanes in 2D.  These structures, which are reminiscent of flywheel
-modes in RB convection, do not appear in our 3D runs these parameters
+modes in RBC, do not appear in our 3D runs at these parameters
 \cite{jones&all1976, brummell&all2002}.
@@
 convection.  Similar states have been studied in
-RB convection \cite{goluskin&all2014}.  These runs are represented in Figs. 
+RBC \cite{goluskin&all2014}.  These runs are represented in Figs. 
 \ref{fig:ma_v_eps}, \ref{fig:re_and_nu_v_ra}, \& \ref{fig:nrho_v_ra}
@@
 The efficiency of convection is quantified by the Nusselt number (Nu).  
-Nu is well-defined in RB convection
+Nu is well-defined in RBC
 as the total flux normalized by the steady-state conductive flux 
@@
 Select simulations were run at higher aspect ratios (8 and 16), and similar flow
-morphologies were obtained, suggesting that these states not highly
+morphologies were obtained, suggesting that these states are not highly
 sensitive to aspect ratio.
 In our limited 3D runs, it appears that Nu $\appropto$ Ra$^{2/7}$, a classic scaling law
-seen in RB studies \cite{johnston&doering2009}.
+seen in RBC \cite{johnston&doering2009}.
 
@@
 and turbulent pressure support plays a larger role than atmospheric slumping.
-The appears to arise as a result of the convection making the interior isentropic,
+This appears to arise as a result of the convection making the interior isentropic,
 tied with our fixed-temperature boundary conditions; 
@@
 In summary, we have found that the evolved flow properties of stratified,
-compressible convection scale in a manner reminiscent of RB convection.
+compressible convection scale in a manner reminiscent of RBC.
 We argue that polytropically stratified atmospheres are the natural
-extension of the RB problem with an additional control parameter, $\epsilon$,
+extension of the RBC problem with an additional control parameter, $\epsilon$,
 whose primary role is to set the Ma of the flows.  We show that other properties
@@
 comparing heat transport in stratified convection
-to that in RB convection \cite{johnston&doering2009}
+to that in RBC \cite{johnston&doering2009}
 and for better quantifying transport in stratified convection.  
@@
 
-\subsection{acknowledgements}
+\begin{acknowledgments}
 EHA acknowledges the support of the University of Colorado's George 
@@
 careful comments greatly improved the quality of this letter.
+\end{acknowledgments}
 

### 2017-07-26 tex/nusselt_paper.tex
rough broad changes to PRFluid format

@@
 %\documentclass[iop]{emulateapj}
-\documentclass[aps, prl, twocolumn, nofootinbib, groupedaddress, amsfonts, amssymb, amsmath]{revtex4-1}
+\documentclass[aps, prfluids, onecolumn, notitlepage, nofootinbib, groupedaddress, amsfonts, amssymb, amsmath]{revtex4-1}
 \usepackage{graphicx}
@@
 \section{Introduction}
-\refstepcounter{section}
 \label{sec:intro}
@@
 
-In this letter we study the behavior of convective heat transport, 
+Here we study the behavior of convective heat transport, 
 quantified by the Nusselt number (Nu), in plane-parallel, 
@@
 \section{Experiment} 
-\refstepcounter{section}
 \label{sec:experiment}
@@
 the initial value of $n_{\rho}$.
-Throughout this letter we set $n_{\rho} = 3$.    Satisfying hydrostatic
+Throughout this work we set $n_{\rho} = 3$.    Satisfying hydrostatic
 equilibrium sets the value of gravity, $g = RT_t (m + 1)$, which is
@@
 timescales of the atmospheric buoyancy time,
-$t_b = \tau_I \sqrt{L_z/g\epsilon}$.
+$t_b = \tau_I \sqrt{L_z m c_P/g\epsilon n_\rho}$.
 
@@
 \end{equation}
-We carry out two experiments in this letter. In the first,
+We carry out two experiments in this study. In the first,
 we fix $\epsilon$ and increase Ra, thus increasing the ratio in
@@
 \frac{\partial\bm{u}}{\partial t} + \grad T - 
-&\nu\grad\cdot\lilstressT - \lilstressT\cdot\grad\nu = \\
-&-\bm{u}\cdot\grad\bm{u} - T\grad\ln\rho + \bm{g} + 
+&\nu\grad\cdot\lilstressT - \lilstressT\cdot\grad\nu =
+-\bm{u}\cdot\grad\bm{u} - T\grad\ln\rho + \bm{g} + 
 \nu\lilstressT\cdot\grad\ln\rho,
@@
 \frac{\partial T}{\partial t} -\frac{1}{c_V}\left(\right.\chi&\left.
-    \grad^2 T + \grad T\cdot\grad\chi\right) = \\
-	&-\bm{u}\cdot\grad T - (\gamma-1)T\grad\cdot{\bm{u}} \\
-	&+ \frac{1}{c_V}\left(\chi\grad T \cdot\grad\ln\rho +
+    \grad^2 T + \grad T\cdot\grad\chi\right) =
+	-\bm{u}\cdot\grad T - (\gamma-1)T\grad\cdot{\bm{u}}
+	+ \frac{1}{c_V}\left(\chi\grad T \cdot\grad\ln\rho +
 	\nu\left[\lilstressT\cdot\nabla\right]\cdot\bm{u}\right), 
@@
 \section{Results \& Discussion}
-\refstepcounter{section}
 \label{sec:results}
@@
 \begin{figure}[t]
-\includegraphics[width=3.4375in]{./figs/ma_v_Ra.png}
+\includegraphics[width=\textwidth]{./figs/ma_v_Ra.png}
 \caption{The mean adiabatic Mach number of long-time-averaged profiles
@@
 for $\epsilon = \{1.0, 0.5, 10^{-4}, 10^{-7}\}$, respectively.
+
+\subsection{Fluid Numbers \& Flows}
 
@@
 
-\begin{figure}[t]
-\includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
+\begin{figure}[t!]
+\includegraphics[width=\textwidth]{./figs/snapshots_fig.png}
 \caption{Characteristic entropy fluctuations in evolved 2D flows roughly
@@
 (a) A low Ma flow at moderate Ra. (b) A high Ma flow at the same Ra as in (a).
-(c) A high Ma flow at high Ra.
+(c) A high Ma flow at high Ra.  In all cases, the broad upflow and narrow downflows
+traditionally seen in stratified convection are apparent.
 Shock systems can be seen in the upper atmosphere of the high Ma flows,
@@
 \begin{figure}[t]
-\includegraphics[width=3.4375in]{./figs/re_and_nu_v_Ra.png}
+\includegraphics[width=\textwidth]{./figs/re_and_nu_v_Ra.png}
 \caption{
@@
 As the flow becomes supersonic,  Nu $\appropto$ Ra$^{1/5}$.
-%2D runs at $\text{Ra }\gtrsim 10^3$Ra$_{\text{crit}}$
-%and $\epsilon = 10^{-4}$ exhibit windy convective states.
-%In these runs, the system is in flux equilibrium only when
-%time averaged over roll states and windy states.
-%A long time average
-%over both of these states produces a flat flux profile which
-%can be sensibly analyzed, but the presence of these time-dependent states
-%makes it difficult to equilibrate these higher Ra cases.
 It is also important to note that, in 2D,
@@
 
+\subsection{Change of Stratification}
+
 \begin{figure}[t]
-\includegraphics[width=3.4375in]{./figs/density_v_ra.png}
+\includegraphics[width=0.5\textwidth]{./figs/density_v_ra.png}
 \caption{\label{fig:nrho_v_ra} 
@@
 
-%Discussion
-
+\section{Discussion \& Future Work}
 In summary, we have found that the evolved flow properties of stratified,
@@
 for many useful discussions. We also thank the three anonymous referees whose
-careful comments greatly improved the quality of this letter.
+careful comments greatly improved the quality of this paper.
 \end{acknowledgments}

### 2017-07-27 tex/nusselt_paper.tex
overhaul of snapshot figure

@@
 In the widely-studied \RB problem of incompressible Boussinesq convection (RBC), 
-a negative temperature gradient causes convective instability.
+a sufficiently negative temperature gradient causes convective instability.
 In the evolved solution, upflows and downflows are symmetrical, the
@@
 timescales of the atmospheric buoyancy time,
-$t_b = \tau_I \sqrt{L_z m c_P/g\epsilon n_\rho}$.
+$t_b = \tau_I \sqrt{L_z\,m\,c_P/g\,\epsilon\,n_\rho}$.
 
@@
 \begin{equation}
-\frac{t_\chi}{t_b} = \left(\frac{c_P}{n_\rho}\right)^{1/2}\text{Ra}_t^{1/2}
-\left(m_{ad} - \epsilon\right)^{1/2}.
+\frac{t_\chi}{t_b} =\text{Ra}_t^{1/2}.
 \label{eqn:timescales}
@@
 relative to the speed of sound; we see this reflected in the evolved Mach
-number scaling (Fig. \ref{fig:ma_v_eps}). The ratio in (\ref{eqn:timescales}) is
-independent of $\epsilon$ when $\epsilon \ll m_{ad}$.
+number scaling (Fig. \ref{fig:ma_v_eps}).
 
-The Fully Compressible Navier-Stokes equations,
+We solve the Fully Compressible Navier-Stokes equations,
 \begin{align}
@@
 \end{align}
-are evolved with the viscous stress tensor given by
+with the viscous stress tensor given by
 \begin{equation}
@@
 
-\begin{figure}[t!]
-\includegraphics[width=\textwidth]{./figs/snapshots_fig.png}
-\caption{Characteristic entropy fluctuations in evolved 2D flows roughly
-140$t_b$ after the start of simulations. 
-The time- and horizontally-averaged profile is removed in all cases.  
-(a) A low Ma flow at moderate Ra. (b) A high Ma flow at the same Ra as in (a).
-(c) A high Ma flow at high Ra.  In all cases, the broad upflow and narrow downflows
-traditionally seen in stratified convection are apparent.
-Shock systems can be seen in the upper atmosphere of the high Ma flows,
-for example at $(x, z) \sim (70, 15-19)$ in (b) and $(x, z) \sim 
-(65, 17-19)$ in (c).
-\label{fig:entropy_snapshots} }
-\end{figure}
-
 Low Ma flows (e.g., $\epsilon = 10^{-4}$)
@@
 amplitudes of thermodynamic fluctuations scale with $\epsilon$.
-
-\begin{figure}[t]
-\includegraphics[width=\textwidth]{./figs/re_and_nu_v_Ra.png}
-\caption{
-Flow properties at high and low $\epsilon$. 
-(a) Nu vs. Ra/Ra$_{\text{crit}}$.
-Errors bars indicate the variance of Nu with depth;
-large error bars indicate a poorly converged solution.
-(b) Re vs. Ra/Ra$_{\text{crit}}$.
-Re is measured at the midplane of the atmosphere.
-Larger symbols with white dots designate 3D runs.
- \label{fig:re_and_nu_v_ra}
-}
+\begin{figure}[t!]
+\includegraphics[width=\textwidth]{./figs/snapshots_fig.png}
+\caption{Characteristic entropy fluctuations in evolved 2D flows roughly
+140$t_b$ after the start of simulations. 
+The time- and horizontally-averaged profile is removed in all cases.  
+(a) A low Ma flow at moderate Ra. (b) A high Ma flow at the same Ra as in (a).
+(c) A high Ma flow at high Ra.  In all cases, the broad upflow and narrow downflows
+traditionally seen in stratified convection are apparent.
+Shock systems can be seen in the upper atmosphere of the high Ma flows,
+for example at $(x, z) \sim (70, 15-19)$ in (b) and $(x, z) \sim 
+(65, 17-19)$ in (c).
+\label{fig:entropy_snapshots} }
 \end{figure}
@@
 Nusselt number \cite{otero&all2002, johnston&doering2009}.
+\begin{figure}[t!]
+\includegraphics[width=\textwidth]{./figs/re_and_nu_v_Ra.png}
+\caption{
+Flow properties at high and low $\epsilon$. 
+(a) Nu vs. Ra/Ra$_{\text{crit}}$.
+Errors bars indicate the variance of Nu with depth;
+large error bars indicate a poorly converged solution.
+(b) Re vs. Ra/Ra$_{\text{crit}}$.
+Re is measured at the midplane of the atmosphere.
+Larger symbols with white dots designate 3D runs.
+ \label{fig:re_and_nu_v_ra}
+}
+\end{figure}
 

### 2017-07-27 code/plotting/base/movie_buddy.py
lots of plot updates

@@ -75,6 +75,7 @@ class MovieBuddy(PlotBuddy):
             bare -- If bare, then don't plot up any axis information (public talks, etc.)
 
         '''
+        print(xs.shape, zs.shape, field.shape)
         if self.idle: return
         if max == None:
             max = np.max(field)
@@ -271,8 +272,16 @@ class MovieBuddy(PlotBuddy):
 
                 if zlabel == None:
                     zlabel = field
+
+                if hlabel == 'x' and vlabel == 'y':
+                    xs, ys = np.meshgrid(self.x, self.x)
+                    field_base = field_base[:,:,0]
+                else:
+                    xs, ys = self.xs/length_div, self.zs/length_div
+                    if len(field_base.shape) == 3:
+                        field_base = field_base[:,0,:]
                 
-                self.plot_field(self.xs/length_div, self.zs/length_div, field_base, axis, \
+                self.plot_field(xs, ys, field_base, axis, \
                             zlabel, cmap=cmap, min=min, max=max, plot_title=plot_title,\
                             bare=bare)#, extra_label=field_base)
                 if length_div != 1:

### 2017-07-27 code/plotting/base/parameter_space_buddy.py

@@ -138,7 +138,13 @@ class ParameterSpaceBuddy():
                 for key_info in keys:
                     key, type = key_info
                     if type == 'val':
-                        storage[key] = (np.log(f[key][0]), 0, 0)
+                        if len(f[key].shape) == 1:
+                            if f[key].shape[0] == 1:
+                                storage[key] = (np.log(f[key][0]), 0, 0)
+                            else:
+                                storage[key+'_profile'] = f[key]
+                        else:
+                            storage[key+'_profile'] = f[key][0,0,:]
                     elif type == 'midplane':
                         current_field['g'] = f[key]
                         storage[key] = (current_field.interpolate(z=Lz/2)['g'][0], 0, 0)

### 2017-07-27 code/plotting/base/plot_buddy_base.py

@@ -204,6 +204,13 @@ class PlotBuddy:
         if 'slices' in self.file_dirs:
             f = h5py.File("{:s}".format(self.global_files['slices'][0][0]))
             self.x = np.array(f['scales']['x']['1.0'][:], dtype=np.float32)
+            try:
+                self.y = np.array(f['scales']['y']['1.0'][:], dtype=np.float32)
+                self.y_xx, self.y_yy = np.meshgrid(self.x, self.y)
+            except:
+                print("No y, must be 2D")
+                self.y = None
+                self.y_xx, self.y_yy = None, None
             self.z = np.array(f['scales']['z']['1.0'][:], dtype=np.float32)
             self.zs, self.xs = np.meshgrid(self.z,self.x)
             f.close()

### 2017-07-27 code/plotting/base/profile_buddy.py

@@ -329,7 +329,7 @@ class ProfileBuddy(PlotBuddy):
                     else:
                         Nu_6 = (F_conv + F_cond - kappa_ad_mean*grad_t_ad)/(nu_bottom)
 
-                   
+                  
                     ma_post = self.full_average_profiles['vel_rms'][i,:]/\
                                 np.sqrt(self.atmosphere['gamma']*T_full)
                    

### 2017-07-27 code/plotting/parameter_space_plots.py

@@ -54,7 +54,7 @@ def line_leastsq(x, y, y_uncert):
     p = np.array((slope, intercept))
     covar = np.array(((s, -sx),(-sx, sx2)))/Delta
     return p, covar
-START_FILE=100
+START_FILE=20
 N_FILES=1000
 golden_ratio=1.618
 FIGWIDTH=3+7.0/16
@@ -75,10 +75,10 @@ mach_threeD_dir = '/nobackup/eanders/sp2017/mach_eps_3D/'
 threeD_out_dir='/parameter_calcs/'
 param_keys = ['Ra', 'eps', 'nrhocz', 'Pr']
 
-keys = ['Nusselt', 'Nusselt_5', 'Nusselt_6', 'norm_5_kappa_flux_z',  
+keys = ['Nusselt_AB17', #'Nusselt_5', 'Nusselt_6', 'norm_5_kappa_flux_z',  
     'Re_rms', 'Ma_ad', 'Ma_iso', 'ln_rho1', 'T1', 'vel_rms',\
     'rho_full', 'T_full', 'kappa_flux_z', 'enthalpy_flux_z', 'PE_flux_z', 'KE_flux_z', 'viscous_flux_z', 'kappa_flux_z', 'kappa_flux_fluc_z']
-plot_keys = [('Nusselt_6', 'minmax'), ('Re_rms', 'midplane'), ('Ma_ad_post', 'minmax'), ('density_contrasts', 'val'), ('rho_full', 'logmaxovermin')]
+plot_keys = [('Nusselt_6', 'minmax'), ('Re_rms', 'midplane'), ('Ma_ad_post', 'minmax'), ('density_contrasts', 'val'), ('rho_full', 'logmaxovermin'), ('rho_full', 'val'), ('z', 'val')]
 
 root_buddy = ParameterSpaceBuddy(root_dir, parameters=param_keys)
 mach_buddy = ParameterSpaceBuddy(mach_dir, parameters=param_keys)
@@ -121,9 +121,9 @@ dirs_root = root_buddy.dir_info
 dirs_mach = mach_buddy.dir_info
 
 #RE and NU plot 
-fig = plt.figure(figsize=(FIGWIDTH, FIGHEIGHT))
-ax1 = fig.add_subplot(2,1,1)
-ax2 = fig.add_subplot(2,1,2)
+fig = plt.figure(figsize=(2.5*FIGWIDTH, FIGHEIGHT/2.2))
[…]

### 2017-07-27 code/plotting/snapshots_figure.py

@@ -3,70 +3,92 @@ matplotlib.use('Agg')
 matplotlib.rcParams.update({'font.size': 11, 'axes.labelsize': 10})
 from mpl_toolkits.axes_grid1 import make_axes_locatable
 import matplotlib.pyplot as plt
+plt.style.use('classic')
 import matplotlib.patheffects as PathEffects
 import matplotlib.colorbar as colorbar
 from base.plot_buddy import MovieBuddy
 import numpy as np
 
 FIGWIDTH=3+7.0/16
-FIGHEIGHT= FIGWIDTH*1.25
+FIGHEIGHT= FIGWIDTH*1
 
-start_file=59
+start_file=49
 n_files = 3
 
-dir1="/nobackup/eanders/sp2017/fc_poly_hydro/FC_poly_fixed_constMu_constKappa_2D_nrhocz3_Ra1.00e6_Pr1_eps1e-4_a4_nusselt_fixedT"
+dir1="/nobackup/eanders/sp2017/comps_data/FC_poly_fixed_constMu_constKappa_nrhocz3_Ra1.00e6_Pr1_eps1e-4_nusselt_fixedT_highres/"
+#dir1="/nobackup/eanders/sp2017/fc_poly_hydro/FC_poly_fixed_constMu_constKappa_2D_nrhocz3_Ra1.00e6_Pr1_eps1e-4_a4_nusselt_fixedT"
 dir2="/nobackup/eanders/sp2017/fc_poly_hydro/FC_poly_fixed_constMu_constKappa_2D_nrhocz3_Ra1.00e6_Pr1_eps5e-1_a4_nusselt_fixedT"
-dir3="/nobackup/eanders/sp2017/fc_poly_hydro/FC_poly_fixed_constMu_constKappa_2D_nrhocz3_Ra4.64e7_Pr1_eps5e-1_a4_nusselt_fixedT_2"
+dir3="/nobackup/eanders/sp2017/fc_poly_hydro/FC_poly_fixed_constMu_constKappa_2D_nrhocz3_Ra4.64e7_Pr1_eps5e-1_a4_nusselt_fixedT"
+dir4="/nobackup/bpbrown/polytrope-evan-3D/FC_poly_3D_nrhocz3_Ra1e6_Pr1_eps1e-4_a4/"
 
 
 stds=1
 
-def add_snapshot_subplot(ax, dir, start_file,  do_cbar=False, figure_index=0, n_files=3):
[…]

### 2017-07-27 referee_process/second_submission/referee_response.tex

@@
 \end{myquotation}
-We agree and Eqn. 3 shows now shows this clearly.
+We agree and Eqn. 3 now shows this clearly.
 We have revised our discussion of Fig. 2c such that it 
@@
 \end{myquotation}
-We have clarified the structure of the introduction paragraph, have included
-citations to prior work at high Ma, and have set the context for the study
-of fundamental heat transport conducted here at low as well as high Ma.
+We have clarified the structure of the introduction paragraph.  We included
+citations to prior work at high Ma and set the context for the present study
+of fundamental heat transport at both low and high Ma.
+The
+most important result of the paper is called out in the last paragraph of the
+introduction.
 

### 2017-08-01 tex/nusselt_paper.tex
density fig updates
adds a table of run parameters to the paper.

@@
 \usepackage{natbib}
+\usepackage{longtable}
 %\usepackage[colorlinks=True, linkcolor=blue, citecolor=blue]{hyperref}
@@
 \author{Evan H. Anders}
-\affiliation{Department of Astrophysical \& Planetary Sciences, University of Colorado -- Boulder}
-\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO}
+\affiliation{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
+\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
 \author{Benjamin P. Brown}
-\affiliation{Department of Astrophysical \& Planetary Sciences, University of Colorado -- Boulder}
-\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO}
+\affiliation{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
+\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
 \title{Convective heat transport in stratified atmospheres at low and high Mach number}
@@
 
-\begin{figure}[t]
-\includegraphics[width=0.5\textwidth]{./figs/density_v_ra.png}
-\caption{\label{fig:nrho_v_ra} 
-Solid symbols show the density contrast measured
-in density scale heights between the upper and lower boundary, 
-$n_\rho = \ln[\rho(z=0)/\rho(z=L_z)]$.
-Empty symbols show 
-$n_\rho = \ln[\text{max}(\rho)/\text{min}(\rho)]$. 
-At low $\epsilon$ the evolved
-$n_{\rho}$ is close to the initial conditions of $n_\rho = 3$.  
-At high $\epsilon$,
-the density stratification decreases.  Once the mean 
-Ma approaches 1 (at Ra/Ra$_{\text{crit}} \approx \{10^2, 10^3\}$ for $\epsilon = \{1, 0.5\}$
-as in Fig. \ref{fig:ma_v_eps}b), density inversions form within the thermal
-boundary layers. Larger symbols represent 3D runs.}
-\end{figure}
-
 In the evolved state, the flows can change the density stratification,
@@
 felt by the flows.
+
+\begin{figure}[t!]
+\includegraphics[width=\textwidth]{./figs/density_v_ra.png}
+\caption{\label{fig:nrho_v_ra} 
+Solid symbols show the density contrast measured
+in density scale heights between the upper and lower boundary, 
+$n_\rho = \ln[\rho(z=0)/\rho(z=L_z)]$.
+Empty symbols show 
+$n_\rho = \ln[\text{max}(\rho)/\text{min}(\rho)]$. 
+At low $\epsilon$ the evolved
+$n_{\rho}$ is close to the initial conditions of $n_\rho = 3$.  
+At high $\epsilon$,
+the density stratification decreases.  Once the mean 
+Ma approaches 1 (at Ra/Ra$_{\text{crit}} \approx \{10^2, 10^3\}$ for $\epsilon = \{1, 0.5\}$
+as in Fig. \ref{fig:ma_v_eps}b), density inversions form within the thermal
+boundary layers. Larger symbols represent 3D runs.}
+\end{figure}
 
@@
 \bibliography{../biblio.bib}
+
+\appendix
+\section{Table of run parameters}
+In table \ref{table:run_info}, we report both the input parameters ($\epsilon$, Ra$_t$, resolution)
+and output values (evolved Nu, Re, Ma, $n_\rho$) shown in the figures throughout this paper.
+Simulation input values are listed in the first six columns.  The evolved Nusselt
+number (Nu) is presented, as well as how far away the atmospheric maximum and minimum are from
+the mean.  The Reynolds number (Re) at the midplane is reported.  The Mach number (Ma) is reported
+in the same format as Nu.  The evolved number of density scale heights is reported, using the two
+measurements described in Fig. \ref{fig:nrho_v_ra}.
+
+%\begin{table}
+\begin{center}
+\begin{longtable}{ p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1.75cm} p{1.5cm} p{2.75cm} p{1cm} p{1.2cm}  }
+\caption{Input and output values of simulations.\label{table:run_info}}\\
+\hline
+$\epsilon$	&	Ra$_t$	&	3D	&	$n_z$	&	$n_x$	&	$n_y$	&	Nu					&	Re	&	Ma					&	$n_{\rho, \text{max}}$	&	$n_{\rho, \text{bounds}}$	\\
+\hline\hline \endfirsthead																													\\
+\multicolumn{11}{c}%
+{ \tablename\ \thetable{} -- continued from previous page} \\
+\hline
+$\epsilon$	&	Ra$_t$	&	3D	&	$n_z$	&	$n_x$	&	$n_y$	&	Nu					&	Re	&	Ma					&	$n_{\rho, \text{max}}$	&	$n_{\rho, \text{bounds}}$	\\
+\hline \hline \endhead
+\hline \endfoot
+\hline \endlastfoot
+
+\vspace{0.08cm}1	&	31.6	&	No	&	128	&	1024	&	---	&$	2.93	_{-	0.04	}^{+	0.00	}$&	7.96	&$	0.29	_{-	0.12	}^{+	2.10	}$&	2.12	&	2.11	\\
+\vspace{0.08cm}1	&	46.4	&	No	&	128	&	1024	&	---	&$	3.45	_{-	0.00	}^{+	0.00	}$&	10.77	&$	0.32	_{-	0.14	}^{+	2.30	}$&	2.05	&	2.02	\\
+\vspace{0.08cm}1	&	68.1	&	No	&	128	&	1024	&	---	&$	4.02	_{-	0.00	}^{+	0.00	}$&	14.20	&$	0.34	_{-	0.15	}^{+	2.51	}$&	1.95	&	1.91	\\
+\vspace{0.08cm}1	&	100	&	No	&	128	&	1024	&	---	&$	4.67	_{-	0.00	}^{+	0.00	}$&	18.50	&$	0.37	_{-	0.16	}^{+	2.71	}$&	1.83	&	1.78	\\
+\vspace{0.08cm}1	&	147	&	No	&	128	&	1024	&	---	&$	5.41	_{-	0.00	}^{+	0.00	}$&	23.90	&$	0.40	_{-	0.18	}^{+	2.94	}$&	1.71	&	1.64	\\
+\vspace{0.08cm}1	&	215	&	No	&	128	&	1024	&	---	&$	6.27	_{-	0.00	}^{+	0.01	}$&	30.91	&$	0.43	_{-	0.19	}^{+	3.20	}$&	1.57	&	1.50	\\
+\vspace{0.08cm}1	&	316	&	No	&	128	&	1024	&	---	&$	6.02	_{-	0.03	}^{+	0.06	}$&	33.82	&$	0.47	_{-	0.28	}^{+	4.63	}$&	1.36	&	1.30	\\
+\vspace{0.08cm}1	&	464	&	No	&	128	&	1024	&	---	&$	6.84	_{-	0.02	}^{+	0.03	}$&	44.84	&$	0.52	_{-	0.34	}^{+	5.31	}$&	1.20	&	1.13	\\
+\vspace{0.08cm}1	&	681	&	No	&	128	&	1024	&	---	&$	8.15	_{-	0.03	}^{+	0.06	}$&	62.50	&$	0.58	_{-	0.39	}^{+	5.85	}$&	1.00	&	0.91	\\
+\vspace{0.08cm}1	&	1000	&	No	&	128	&	1024	&	---	&$	9.73	_{-	0.03	}^{+	0.06	}$&	87.05	&$	0.64	_{-	0.45	}^{+	6.45	}$&	0.93	&	0.68	\\
+\vspace{0.08cm}1	&	1470	&	No	&	128	&	1024	&	---	&$	11.50	_{-	0.05	}^{+	0.09	}$&	118.63	&$	0.71	_{-	0.50	}^{+	7.07	}$&	0.95	&	0.45	\\
+\vspace{0.08cm}1	&	2150	&	No	&	128	&	1024	&	---	&$	13.19	_{-	0.08	}^{+	0.11	}$&	156.07	&$	0.76	_{-	0.54	}^{+	7.51	}$&	0.98	&	0.27	\\
+\vspace{0.08cm}1	&	3160	&	No	&	256	&	1024	&	---	&$	18.44	_{-	0.05	}^{+	0.17	}$&	220.66	&$	0.74	_{-	0.30	}^{+	5.01	}$&	1.28	&	0.08	\\
+\vspace{0.08cm}1	&	4640	&	No	&	256	&	1024	&	---	&$	20.47	_{-	0.09	}^{+	0.33	}$&	276.37	&$	0.76	_{-	0.30	}^{+	5.03	}$&	1.39	&	-0.11	\\
+\vspace{0.08cm}1	&	6810	&	No	&	256	&	1024	&	---	&$	16.27	_{-	0.11	}^{+	0.06	}$&	305.71	&$	0.83	_{-	0.59	}^{+	7.57	}$&	1.09	&	-0.07	\\
+\vspace{0.08cm}1	&	$10^4$	&	No	&	256	&	1024	&	---	&$	20.43	_{-	0.21	}^{+	0.24	}$&	397.69	&$	0.79	_{-	0.35	}^{+	5.49	}$&	1.26	&	-0.21	\\
+\vspace{0.08cm}1	&	$10^4$	&	Yes	&	128	&	256	&	256	&$	16.10	_{-	0.99	}^{+	0.15	}$&	176.84	&$	0.39	_{-	0.13	}^{+	3.78	}$&	1.24	&	0.41	\\
+\vspace{0.08cm}1	&	$10^{4.167}$	&	No	&	256	&	1024	&	---	&$	21.68	_{-	0.25	}^{+	0.26	}$&	497.30	&$	0.79	_{-	0.35	}^{+	5.15	}$&	1.31	&	-0.22	\\
+\vspace{0.08cm}1	&	$10^{4.33}$	&	No	&	256	&	1024	&	---	&$	18.76	_{-	0.09	}^{+	0.04	}$&	499.72	&$	0.77	_{-	0.52	}^{+	6.17	}$&	1.36	&	0.16	\\
+\vspace{0.08cm}1	&	$10^{4.5}$	&	No	&	256	&	1024	&	---	&$	25.74	_{-	0.24	}^{+	0.40	}$&	756.44	&$	0.81	_{-	0.34	}^{+	4.92	}$&	1.46	&	-0.38	\\
+\vspace{0.08cm}1	&	$10^{4.667}$	&	No	&	512	&	2048	&	---	&$	28.66	_{-	0.37	}^{+	0.34	}$&	925.71	&$	0.83	_{-	0.35	}^{+	4.92	}$&	1.57	&	-0.46	\\
+\vspace{0.08cm}1	&	$10^{4.833}$	&	No	&	512	&	2048	&	---	&$	30.92	_{-	0.81	}^{+	0.83	}$&	1085.26	&$	0.81	_{-	0.35	}^{+	4.80	}$&	1.61	&	-0.46	\\
+\vspace{0.08cm}1	&	$10^5$	&	No	&	512	&	2048	&	---	&$	33.60	_{-	0.41	}^{+	1.03	}$&	1356.44	&$	0.82	_{-	0.33	}^{+	4.51	}$&	1.72	&	-0.55	\\
+\vspace{0.08cm}1	&	$10^5$	&	Yes	&	256	&	512	&	512	&$	29.67	_{-	1.90	}^{+	0.44	}$&	562.40	&$	0.38	_{-	0.14	}^{+	3.71	}$&	1.67	&	-0.22	\\
+\vspace{0.08cm}0.5	&	14.7	&	No	&	64	&	256	&	---	&$	1.44	_{-	0.00	}^{+	0.00	}$&	2.25	&$	0.08	_{-	0.04	}^{+	0.10	}$&	2.90	&	2.90	\\
+\vspace{0.08cm}0.5	&	21.5	&	No	&	64	&	256	&	---	&$	2.12	_{-	0.01	}^{+	0.01	}$&	4.90	&$	0.15	_{-	0.07	}^{+	0.18	}$&	2.77	&	2.77	\\
+\vspace{0.08cm}0.5	&	31.6	&	No	&	64	&	256	&	---	&$	2.64	_{-	0.00	}^{+	0.00	}$&	7.20	&$	0.17	_{-	0.08	}^{+	0.22	}$&	2.68	&	2.68	\\
+\vspace{0.08cm}0.5	&	46.4	&	No	&	64	&	256	&	---	&$	3.09	_{-	0.00	}^{+	0.00	}$&	9.71	&$	0.19	_{-	0.09	}^{+	0.24	}$&	2.61	&	2.61	\\
+\vspace{0.08cm}0.5	&	68.1	&	No	&	64	&	256	&	---	&$	3.38	_{-	0.01	}^{+	0.01	}$&	12.18	&$	0.21	_{-	0.10	}^{+	0.29	}$&	2.57	&	2.57	\\
+\vspace{0.08cm}0.5	&	100	&	No	&	64	&	256	&	---	&$	3.72	_{-	0.01	}^{+	0.01	}$&	15.22	&$	0.22	_{-	0.11	}^{+	0.33	}$&	2.52	&	2.52	\\
+\vspace{0.08cm}0.5	&	100	&	Yes	&	64	&	128	&	128	&$	3.42	_{-	0.11	}^{+	0.06	}$&	13.42	&$	0.21	_{-	0.08	}^{+	0.33	}$&	2.56	&	2.57	\\
+\vspace{0.08cm}0.5	&	147	&	No	&	128	&	512	&	---	&$	4.68	_{-	0.01	}^{+	0.01	}$&	21.21	&$	0.24	_{-	0.12	}^{+	0.32	}$&	2.39	&	2.40	\\
+\vspace{0.08cm}0.5	&	215	&	No	&	128	&	512	&	---	&$	5.38	_{-	0.01	}^{+	0.02	}$&	27.44	&$	0.26	_{-	0.13	}^{+	0.35	}$&	2.31	&	2.31	\\
+\vspace{0.08cm}0.5	&	316	&	No	&	128	&	512	&	---	&$	5.91	_{-	0.01	}^{+	0.03	}$&	34.73	&$	0.28	_{-	0.14	}^{+	0.41	}$&	2.24	&	2.24	\\
+\vspace{0.08cm}0.5	&	464	&	No	&	128	&	512	&	---	&$	6.78	_{-	0.01	}^{+	0.01	}$&	46.22	&$	0.31	_{-	0.15	}^{+	0.44	}$&	2.13	&	2.12	\\
+\vspace{0.08cm}0.5	&	681	&	No	&	128	&	512	&	---	&$	7.26	_{-	0.02	}^{+	0.05	}$&	60.53	&$	0.34	_{-	0.20	}^{+	0.57	}$&	2.07	&	2.06	\\
+\vspace{0.08cm}0.5	&	1000	&	No	&	128	&	512	&	---	&$	7.87	_{-	0.04	}^{+	0.09	}$&	83.02	&$	0.39	_{-	0.26	}^{+	0.71	}$&	1.98	&	1.96	\\
+\vspace{0.08cm}0.5	&	1000	&	Yes	&	128	&	256	&	256	&$	6.83	_{-	0.25	}^{+	0.18	}$&	46.03	&$	0.23	_{-	0.08	}^{+	0.38	}$&	2.19	&	2.19	\\
+\vspace{0.08cm}0.5	&	1470	&	No	&	128	&	512	&	---	&$	9.37	_{-	0.05	}^{+	0.11	}$&	122.78	&$	0.47	_{-	0.32	}^{+	0.89	}$&	1.81	&	1.78	\\
+\vspace{0.08cm}0.5	&	2150	&	No	&	128	&	512	&	---	&$	10.47	_{-	0.08	}^{+	0.22	}$&	160.98	&$	0.52	_{-	0.37	}^{+	1.05	}$&	1.78	&	1.75	\\
+\vspace{0.08cm}0.5	&	3160	&	No	&	128	&	512	&	---	&$	12.09	_{-	0.06	}^{+	0.11	}$&	216.11	&$	0.58	_{-	0.41	}^{+	1.17	}$&	1.68	&	1.64	\\
+\vspace{0.08cm}0.5	&	4640	&	No	&	128	&	512	&	---	&$	14.67	_{-	0.21	}^{+	0.47	}$&	295.41	&$	0.65	_{-	0.47	}^{+	1.32	}$&	1.48	&	1.42	\\
+\vspace{0.08cm}0.5	&	6810	&	No	&	128	&	512	&	---	&$	17.62	_{-	0.17	}^{+	0.36	}$&	395.01	&$	0.68	_{-	0.43	}^{+	1.22	}$&	1.45	&	1.18	\\
+\vspace{0.08cm}0.5	&	$10^4$	&	No	&	128	&	512	&	---	&$	18.69	_{-	0.38	}^{+	0.63	}$&	487.35	&$	0.74	_{-	0.54	}^{+	1.50	}$&	1.51	&	1.24	\\
+\vspace{0.08cm}0.5	&	$10^4$	&	Yes	&	128	&	256	&	256	&$	12.89	_{-	0.62	}^{+	0.30	}$&	146.92	&$	0.23	_{-	0.08	}^{+	0.45	}$&	1.83	&	1.81	\\
+\vspace{0.08cm}0.5	&	$10^{4.167}$	&	No	&	128	&	512	&	---	&$	20.18	_{-	0.17	}^{+	0.40	}$&	625.83	&$	0.78	_{-	0.57	}^{+	1.53	}$&	1.55	&	1.18	\\
+\vspace{0.08cm}0.5	&	$10^{4.33}$	&	No	&	256	&	1024	&	---	&$	21.88	_{-	0.20	}^{+	0.66	}$&	784.29	&$	0.82	_{-	0.60	}^{+	1.61	}$&	1.64	&	1.18	\\
+\vspace{0.08cm}0.5	&	$10^{4.5}$	&	No	&	256	&	1024	&	---	&$	23.35	_{-	0.43	}^{+	0.80	}$&	954.16	&$	0.83	_{-	0.61	}^{+	1.62	}$&	1.71	&	1.22	\\
+\vspace{0.08cm}0.5	&	$10^{4.667}$	&	No	&	256	&	1024	&	---	&$	24.70	_{-	0.32	}^{+	0.83	}$&	1162.50	&$	0.84	_{-	0.62	}^{+	1.58	}$&	1.77	&	1.23	\\
+\vspace{0.08cm}0.5	&	$10^{4.833}$	&	No	&	256	&	1024	&	---	&$	24.25	_{-	0.23	}^{+	0.53	}$&	1261.88	&$	0.75	_{-	0.53	}^{+	1.38	}$&	1.84	&	1.37	\\
+\vspace{0.08cm}0.5	&	$10^5$	&	No	&	256	&	1024	&	---	&$	30.14	_{-	0.15	}^{+	0.39	}$&	1677.07	&$	0.71	_{-	0.34	}^{+	0.87	}$&	1.70	&	1.03	\\
+\vspace{0.08cm}0.5	&	$10^5$	&	Yes	&	256	&	512	&	512	&$	23.05	_{-	1.04	}^{+	1.41	}$&	429.63	&$	0.21	_{-	0.08	}^{+	0.43	}$&	1.95	&	1.59	\\
+\vspace{0.08cm}0.5	&	$10^{5.167}$	&	No	&	256	&	1024	&	---	&$	32.83	_{-	0.21	}^{+	0.54	}$&	2030.80	&$	0.70	_{-	0.32	}^{+	0.80	}$&	1.73	&	1.01	\\
+\vspace{0.08cm}0.5	&	$10^{5.33}$	&	No	&	256	&	1024	&	---	&$	35.24	_{-	0.48	}^{+	0.77	}$&	2461.71	&$	0.69	_{-	0.30	}^{+	0.73	}$&	1.77	&	1.00	\\
+\vspace{0.08cm}0.5	&	$10^{5.5}$	&	No	&	256	&	1024	&	---	&$	37.69	_{-	0.36	}^{+	0.70	}$&	3019.49	&$	0.69	_{-	0.28	}^{+	0.68	}$&	1.81	&	1.01	\\
+\vspace{0.08cm}0.5	&	$10^{5.667}$	&	No	&	256	&	1024	&	---	&$	41.09	_{-	0.54	}^{+	1.16	}$&	3685.02	&$	0.69	_{-	0.28	}^{+	0.67	}$&	1.84	&	0.99	\\
+\vspace{0.08cm}0.5	&	$10^{5.833}$	&	No	&	384	&	1536	&	---	&$	44.62	_{-	1.22	}^{+	1.73	}$&	4448.83	&$	0.68	_{-	0.27	}^{+	0.65	}$&	1.87	&	1.00	\\
+\vspace{0.08cm}0.5	&	$10^6$	&	No	&	512	&	2048	&	---	&$	45.86	_{-	1.90	}^{+	3.76	}$&	4943.73	&$	0.64	_{-	0.24	}^{+	0.62	}$&	1.95	&	1.11	\\
+\vspace{0.08cm}0.5	&	$10^6$	&	Yes	&	256	&	512	&	512	&$	40.53	_{-	0.72	}^{+	0.66	}$&	1291.61	&$	0.20	_{-	0.08	}^{+	0.46	}$&	2.15	&	1.47	\\
+\vspace{0.08cm}0.5	&	$10^{6.167}$	&	No	&	512	&	2048	&	---	&$	50.49	_{-	0.57	}^{+	1.42	}$&	6530.03	&$	0.69	_{-	0.26	}^{+	0.61	}$&	1.93	&	1.03	\\
+\vspace{0.08cm}0.5	&	$10^{6.33}$	&	No	&	512	&	2048	&	---	&$	52.19	_{-	1.93	}^{+	3.12	}$&	6898.73	&$	0.60	_{-	0.16	}^{+	0.47	}$&	2.04	&	1.16	\\
+\vspace{0.08cm}0.5	&	$10^{6.5}$	&	No	&	512	&	2048	&	---	&$	58.67	_{-	1.47	}^{+	1.93	}$&	9108.92	&$	0.65	_{-	0.22	}^{+	0.53	}$&	2.02	&	1.07	\\
+\vspace{0.08cm}0.5	&	$10^{6.667}$	&	No	&	512	&	2048	&	---	&$	60.07	_{-	3.84	}^{+	7.15	}$&	10135.36	&$	0.59	_{-	0.14	}^{+	0.41	}$&	2.08	&	1.15	\\
+\vspace{0.08cm}0.5	&	$10^{6.833}$	&	No	&	768	&	3072	&	---	&$	66.38	_{-	6.25	}^{+	12.74	}$&	12181.75	&$	0.59	_{-	0.14	}^{+	0.39	}$&	2.12	&	1.18	\\
+\vspace{0.08cm}0.5	&	$10^7$	&	No	&	768	&	3072	&	---	&$	69.11	_{-	8.11	}^{+	17.04	}$&	13771.71	&$	0.55	_{-	0.10	}^{+	0.32	}$&	2.17	&	1.21	\\
+\vspace{0.08cm}0.5	&	$10^{7.333}$	&	No	&	1024	&	4096	&	---	&$	88.26	_{-	9.52	}^{+	17.15	}$&	21760.02	&$	0.59	_{-	0.13	}^{+	0.36	}$&	2.17	&	1.13	\\
+\vspace{0.08cm}0.5	&	$10^{7.667}$	&	No	&	1024	&	4096	&	---	&$	133.62	_{-	15.48	}^{+	22.94	}$&	27996.91	&$	0.53	_{-	0.11	}^{+	0.25	}$&	2.27	&	1.22	\\
+\vspace{0.08cm}$10^{-4}$	&	14.7	&	No	&	64	&	256	&	---	&$	1.22	_{-	0.00	}^{+	0.00	}$&	1.26	&$	6.25	_{-	2.86	}^{+	3.65}\cdot 10^{-4}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	21.5	&	No	&	64	&	256	&	---	&$	1.90	_{-	0.01	}^{+	0.01	}$&	3.96	&$	1.63	_{-	0.76	}^{+	0.98}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	31.6	&	No	&	64	&	256	&	---	&$	2.48	_{-	0.01	}^{+	0.01	}$&	6.29	&$	2.16	_{-	1.01	}^{+	1.32}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	46.4	&	No	&	64	&	256	&	---	&$	2.91	_{-	0.00	}^{+	0.00	}$&	8.47	&$	2.43	_{-	1.16	}^{+	1.52}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	68.1	&	No	&	64	&	256	&	---	&$	3.30	_{-	0.01	}^{+	0.01	}$&	10.88	&$	2.62	_{-	1.28	}^{+	1.71}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	100	&	No	&	64	&	256	&	---	&$	3.75	_{-	0.01	}^{+	0.01	}$&	13.93	&$	2.82	_{-	1.39	}^{+	1.91}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	100	&	Yes	&	64	&	128	&	128	&$	3.19	_{-	0.10	}^{+	0.06	}$&	11.48	&$	2.53	_{-	9.97	}^{+	1.93}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	147	&	No	&	128	&	512	&	---	&$	4.33	_{-	0.01	}^{+	0.03	}$&	17.92	&$	3.04	_{-	1.53	}^{+	2.08}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	215	&	No	&	128	&	512	&	---	&$	4.90	_{-	0.02	}^{+	0.04	}$&	22.61	&$	3.22	_{-	1.63	}^{+	2.26}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	316	&	No	&	128	&	512	&	---	&$	5.60	_{-	0.01	}^{+	0.04	}$&	28.92	&$	3.41	_{-	1.74	}^{+	2.36}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	464	&	No	&	128	&	512	&	---	&$	6.38	_{-	0.02	}^{+	0.06	}$&	37.10	&$	3.61	_{-	1.84	}^{+	2.44}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	681	&	No	&	128	&	512	&	---	&$	6.64	_{-	0.01	}^{+	0.01	}$&	46.60	&$	3.86	_{-	2.14	}^{+	3.18}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	1000	&	No	&	128	&	512	&	---	&$	7.97	_{-	0.07	}^{+	0.28	}$&	65.85	&$	4.51	_{-	2.66	}^{+	3.95}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	1000	&	Yes	&	128	&	256	&	256	&$	6.72	_{-	0.19	}^{+	0.57	}$&	38.32	&$	2.88	_{-	1.09	}^{+	2.55}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	1470	&	No	&	128	&	512	&	---	&$	9.46	_{-	0.10	}^{+	0.33	}$&	85.91	&$	4.68	_{-	2.43	}^{+	3.47}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	2150	&	No	&	128	&	512	&	---	&$	10.16	_{-	0.05	}^{+	0.12	}$&	121.67	&$	5.62	_{-	3.47	}^{+	5.23}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	3160	&	No	&	128	&	512	&	---	&$	10.48	_{-	0.06	}^{+	0.08	}$&	172.16	&$	6.87	_{-	4.96	}^{+	7.75}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	4640	&	No	&	128	&	512	&	---	&$	12.19	_{-	0.10	}^{+	0.22	}$&	232.13	&$	7.88	_{-	5.91	}^{+	9.5}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	6810	&	No	&	128	&	512	&	---	&$	14.63	_{-	0.11	}^{+	0.20	}$&	323.63	&$	8.78	_{-	6.43	}^{+	9.88}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^4$	&	No	&	128	&	512	&	---	&$	15.21	_{-	0.14	}^{+	0.32	}$&	391.38	&$	9.30	_{-	7.11	}^{+	11.7}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^4$	&	Yes	&	128	&	256	&	256	&$	11.92	_{-	0.40	}^{+	1.34	}$&	115.06	&$	2.85	_{-	1.13	}^{+	3.11}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^{4.167}$	&	No	&	192	&	768	&	---	&$	17.46	_{-	0.56	}^{+	1.30	}$&	509.77	&$	9.86	_{-	7.49	}^{+	12.1}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^{4.33}$	&	No	&	192	&	768	&	---	&$	16.05	_{-	0.06	}^{+	0.03	}$&	606.29	&$	1.02	_{-	0.80	}^{+	1.35}\cdot 10^{-2}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^{4.5}$	&	No	&	192	&	768	&	---	&$	20.03	_{-	0.39	}^{+	0.91	}$&	828.29	&$	1.15	_{-	0.89	}^{+	1.52}\cdot 10^{-2}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^{4.667}$	&	No	&	192	&	768	&	---	&$	24.33	_{-	0.53	}^{+	0.96	}$&	1120.39	&$	1.31	_{-	1.02	}^{+	1.79}\cdot 10^{-2}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^{4.833}$	&	No	&	256	&	1024	&	---	&$	23.33	_{-	0.45	}^{+	0.55	}$&	1314.40	&$	1.34	_{-	1.05	}^{+	1.97}\cdot 10^{-2}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^5$	&	No	&	256	&	1024	&	---	&$	27.83	_{-	0.47	}^{+	0.42	}$&	1766.70	&$	1.50	_{-	1.17	}^{+	2.19}\cdot 10^{-2}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^5$	&	Yes	&	256	&	512	&	512	&$	21.11	_{-	1.69	}^{+	4.74	}$&	319.84	&$	2.46	_{-	1.07	}^{+	2.90}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^{5.167}$	&	No	&	256	&	1024	&	---	&$	36.38	_{-	1.85	}^{+	2.94	}$&	2427.10	&$	1.72	_{-	1.36	}^{+	2.58}\cdot 10^{-2}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^{5.33}$	&	No	&	256	&	1024	&	---	&$	38.93	_{-	2.43	}^{+	4.36	}$&	2987.80	&$	1.79	_{-	1.43	}^{+	2.73}\cdot 10^{-2}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^{5.5}$	&	No	&	256	&	1024	&	---	&$	44.63	_{-	3.00	}^{+	5.01	}$&	3935.62	&$	1.93	_{-	1.57	}^{+	2.94}\cdot 10^{-2}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^{5.667}$	&	No	&	384	&	1536	&	---	&$	42.89	_{-	5.99	}^{+	8.40	}$&	4340.88	&$	1.81	_{-	1.49	}^{+	2.86}\cdot 10^{-2}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^{5.833}$	&	No	&	384	&	1536	&	---	&$	51.48	_{-	4.94	}^{+	8.45	}$&	6230.83	&$	2.25	_{-	1.89	}^{+	3.69}\cdot 10^{-2}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^6$	&	No	&	512	&	2048	&	---	&$	69.68	_{-	15.80	}^{+	28.24	}$&	7684.29	&$	2.10	_{-	1.74	}^{+	3.15}\cdot 10^{-2}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^6$	&	Yes	&	256	&	512	&	512	&$	38.50	_{-	4.71	}^{+	12.54	}$&	920.21	&$	2.26	_{-	1.02	}^{+	2.84}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	14.7	&	No	&	64	&	256	&	---	&$	1.22	_{-	0.00	}^{+	0.00	}$&	1.26	&$	1.98	_{-	0.90	}^{+	1.16}\cdot 10^{-5}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	21.5	&	No	&	64	&	256	&	---	&$	1.90	_{-	0.01	}^{+	0.01	}$&	3.96	&$	5.17	_{-	2.39	}^{+	3.09}\cdot 10^{-5}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	31.6	&	No	&	64	&	256	&	---	&$	2.48	_{-	0.01	}^{+	0.01	}$&	6.29	&$	6.83	_{-	3.20	}^{+	4.17}\cdot 10^{-5}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	46.4	&	No	&	64	&	256	&	---	&$	2.91	_{-	0.00	}^{+	0.00	}$&	8.47	&$	7.67	_{-	3.65	}^{+	4.80}\cdot 10^{-5}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	68.1	&	No	&	64	&	256	&	---	&$	3.30	_{-	0.01	}^{+	0.01	}$&	10.88	&$	8.28	_{-	4.03	}^{+	5.42}\cdot 10^{-5}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	100	&	No	&	64	&	256	&	---	&$	3.75	_{-	0.01	}^{+	0.01	}$&	13.93	&$	8.92	_{-	4.40	}^{+	6.04}\cdot 10^{-5}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	147	&	No	&	128	&	512	&	---	&$	4.32	_{-	0.04	}^{+	0.10	}$&	17.96	&$	9.64	_{-	4.88	}^{+	6.70}\cdot 10^{-5}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	215	&	No	&	128	&	512	&	---	&$	4.86	_{-	0.08	}^{+	0.16	}$&	22.61	&$	1.02	_{-	0.52	}^{+	0.75}\cdot 10^{-4}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	316	&	No	&	128	&	512	&	---	&$	5.59	_{-	0.01	}^{+	0.02	}$&	28.82	&$	1.08	_{-	0.55	}^{+	0.74}\cdot 10^{-4}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	464	&	No	&	256	&	1024	&	---	&$	6.37	_{-	0.05	}^{+	0.06	}$&	36.98	&$	1.14	_{-	0.58	}^{+	0.77}\cdot 10^{-4}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	681	&	No	&	256	&	1024	&	---	&$	7.09	_{-	0.01	}^{+	0.03	}$&	46.75	&$	1.19	_{-	0.60	}^{+	0.80}\cdot 10^{-4}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	1000	&	No	&	256	&	1024	&	---	&$	7.34	_{-	0.04	}^{+	0.04	}$&	61.47	&$	1.34	_{-	0.79	}^{+	1.18}\cdot 10^{-4}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	1470	&	No	&	256	&	1024	&	---	&$	7.83	_{-	0.07	}^{+	0.17	}$&	84.73	&$	1.58	_{-	1.10	}^{+	1.70}\cdot 10^{-4}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	2150	&	No	&	384	&	768	&	---	&$	8.96	_{-	0.10	}^{+	0.42	}$&	118.62	&$	1.80	_{-	1.27	}^{+	1.93}\cdot 10^{-4}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	3160	&	No	&	384	&	768	&	---	&$	10.90	_{-	0.20	}^{+	0.43	}$&	176.32	&$	2.19	_{-	1.57	}^{+	2.38}\cdot 10^{-4}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	4640	&	No	&	384	&	768	&	---	&$	13.94	_{-	2.13	}^{+	6.38	}$&	228.90	&$	2.43	_{-	1.81	}^{+	2.81}\cdot 10^{-4}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	6810	&	No	&	384	&	768	&	---	&$	14.83	_{-	0.47	}^{+	1.58	}$&	318.28	&$	2.74	_{-	2.01	}^{+	3.08}\cdot 10^{-4}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-7}$	&	$10^4$	&	No	&	512	&	1024	&	---	&$	17.54	_{-	1.77	}^{+	4.52	}$&	392.35	&$	2.87	_{-	2.15	}^{+	3.41}\cdot 10^{-4}	$&	3.00	&	3.00	\\
+
+\hline
+\end{longtable}
+\end{center}
+%\end{table}
+
 \end{document}

### 2017-08-01 tex/nusselt_paper.tex
removes the table of doom

--- 2017-07-27 tex/nusselt_paper.tex
@@
 \bibliography{../biblio.bib}
+
 \end{document}

### 2017-08-02 tex/nusselt_paper.tex
adds words about 3D stuff in Fig. 2, and also Fig. 4b.  Rearranges section titles, and the density stratification section.

@@
 \begin{abstract}
-%Convection in astrophysical systems is stratified and
-%often occurs at high Rayleigh number (Ra) and low
-%Mach number (Ma).
-We study stratified convection in the context of 
+We study fully compressible convection in the context of 
 plane-parallel, polytropically stratified atmospheres. 
@@
 timescales of the atmospheric buoyancy time,
-$t_b = \tau_I \sqrt{L_z\,m\,c_P/g\,\epsilon\,n_\rho}$.
+$t_b = \tau_I \sqrt{L_z\,m\,c_P/g\,\epsilon\,n_\rho}$, where
+$c_P = R \gamma/(\gamma-1) = 2.5$ is the specific heat at constant pressure.
 
@@
 where $\Delta S_0 = \epsilon\ln (1 + L_z) = \epsilon n_\rho / m$ 
-is the initial entropy difference across the domain,
-$c_P = \gamma/(\gamma-1)$ is the specific heat at
-constant pressure, $\nu$ is the thermal diffusivity, 
-and $\chi$ is the kinematic viscosity.
+is the initial specific entropy difference across the domain,
+$\chi$ is the thermal diffusivity, 
+and $\nu$ is the kinematic viscosity.
 Throughout this work we specify
@@
 The diffusivities scale as
-$\chi_t, \nu_t \propto \sqrt{g L_z^3 \epsilon / \text{Ra}_t}$.
+$\chi_t, \nu_t \propto \sqrt{g L_z^3 (\Delta S_0 / c_P) / \text{Ra}_t}$.
 Defining the thermal diffusion timescale as $t_\chi \equiv L_z^2 / \chi$, the
@@
 (\ref{eqn:timescales}). In the second, we fix Ra and vary $\epsilon$,
-scaling the buoyancy time $t_b$ as $\epsilon^{-1/2}$
+scaling the dynamical timescales $(t_b, t_\chi)$ as $\epsilon^{-1/2}$
 relative to the speed of sound; we see this reflected in the evolved Mach
@@
 
-We solve the Fully Compressible Navier-Stokes equations,
+We use $\ln \rho$ and $T$ as our thermodynamic variables and solve the Fully 
+Compressible Navier-Stokes equations,
 \begin{align}
@@
 
-\subsection{Fluid Numbers \& Flows}
+\subsection{Evolved fluid numbers \& flow morphology}
 
@@
 
-Low Ma flows (e.g., $\epsilon = 10^{-4}$)
+In 2D, low Ma flows (e.g., $\epsilon = 10^{-4}$)
 display the classic narrow downflow and broad upflow lanes of stratified
@@
 domain repeatedly before diffusing (Fig. \ref{fig:entropy_snapshots}c).
+In 3D, the same upflow/downflow asymmetry is seen, but downflow lanes no
+longer span the depth of the domain (Fig. \ref{fig:entropy_snapshots}d-f).
 As evidenced by the colorbar scalings, the
@@
 \includegraphics[width=\textwidth]{./figs/snapshots_fig.png}
-\caption{Characteristic entropy fluctuations in evolved 2D flows roughly
-140$t_b$ after the start of simulations. 
-The time- and horizontally-averaged profile is removed in all cases.  
+\caption{Characteristic entropy fluctuations in evolved flows roughly
+$\{$140, 60$\}$ $t_b$ after the start of simulations for $\{$2D, 3D$\}$ runs. 
+The time- and horizontally-averaged profile is removed in vertical slices (a)-(d). 
+The time- averaged mean value is removed in horizontal slices (e) and (f).
 (a) A low Ma flow at moderate Ra. (b) A high Ma flow at the same Ra as in (a).
-(c) A high Ma flow at high Ra.  In all cases, the broad upflow and narrow downflows
-traditionally seen in stratified convection are apparent.
+(c) A high Ma flow at high Ra. (d)-(f) A low Ma 3D run at the same parameters as in (a),
+where (d) is a vertical ($x$, $z$) slice at $y = L_y/2$, (e) is a horizontal slice
+at $z = L_z$, and (f) is a horizontal slice at $z = L_z/2$.
 Shock systems can be seen in the upper atmosphere of the high Ma flows,
-for example at $(x, z) \sim (70, 15-19)$ in (b) and $(x, z) \sim 
-(65, 17-19)$ in (c).
+for example at $(x, z) \sim (5, 15-19)$ in (b) and $(x, z) \sim 
+(50, 15-19)$ in (c).
 \label{fig:entropy_snapshots} }
@@
 In incompressible Boussinesq convection, where $\grad S = 0$ only when 
-$\grad T = 0$, this definition reduces to the traditionally defined
+$\grad T = 0$, and where $\kappa$ is constant with depth and time,
+this definition reduces to the traditionally defined
 Nusselt number \cite{otero&all2002, johnston&doering2009}.
@@
 
-\subsection{Change of Stratification}
+\subsection{Evolved stratification}
 
-In the evolved state, the flows can change the density stratification,
-as shown in Fig. \ref{fig:nrho_v_ra}.
-We measure the 
+In the evolved state, the flows can change the density stratification.
+In Fig. \ref{fig:nrho_v_ra}a, we measure the 
 time- and horizontally-averaged density profile in two ways. Empty symbols
-show the density difference
-between the max and min value of the profile, while solid symbols
-show the difference between the top and bottom of the atmosphere. 
-We find that supersonic flows support persistent density inversions 
-in the boundary layers, as
-was reported by \cite{brandenburg&all2005}.  This is visible when
+show the number of density scale heights between the maximum and minimum of the
+atmospheric density profile.  Solid symbols
+show the number of density scale heights between the top and bottom of the atmosphere. 
+We find that near-sonic and supersonic flows support significant, 
+persistent density inversions in the boundary layers, as
+was reported previously \cite{brandenburg&all2005}.  This is visible when
 solid symbols lie below empty symbols.  We find this in 2D and 3D, even
-at very large $\epsilon$.
+at very large $\epsilon$.  Sample evolved density profiles are displayed in
+Fig. \ref{fig:nrho_v_ra}b.
+
 Surprisingly, the evolved $n_\rho$ is always less than the initial $n_\rho = 3$,
@@
 \caption{\label{fig:nrho_v_ra} 
-Solid symbols show the density contrast measured
+(a) Solid symbols show the density contrast measured
 in density scale heights between the upper and lower boundary, 
@@
 as in Fig. \ref{fig:ma_v_eps}b), density inversions form within the thermal
-boundary layers. Larger symbols represent 3D runs.}
+boundary layers. Larger symbols represent 3D runs. (b) The natural log of time-
+and horizontally-averaged density profiles are shown for select simulations,
+to illustrate the inversions which appear in the boundary layers.}
 \end{figure}
 
+\vspace{-0.5cm}
 \section{Discussion \& Future Work}
-In summary, we have found that the evolved flow properties of stratified,
-compressible convection scale in a manner reminiscent of RBC.
+We have found that the evolved flow properties of stratified,
+compressible convection scale in a manner reminiscent of incompressible,
+Boussinesq \RB convection.
 We argue that polytropically stratified atmospheres are the natural
@@
 these polytropic atmospheres evolves in a complex
-manner.  Future work should aim to 
+manner, and future work should aim to 
 understand the importance of stratification on
@@
 
+\appendix
+\section{Table of simulation parameters}
+In table \ref{table:run_info}, we report both the input parameters ($\epsilon$, Ra$_t$, resolution)
+and output values (evolved Nu, Re, Ma, $n_\rho$) of select simulations.  All 3D simulations
+are listed, and the corresponding 2D simulations at the same parameters are included.  A full
+table of all information is included as a CSV file in the supplemental materials.
+
+Simulation input values are listed in the first six columns.  The mean evolved Nu
+is presented, as well as how far away the atmospheric maximum and minimum are from
+the mean.  Re at the midplane is reported.  Ma is reported
+in the same format as Nu.  The evolved number of density scale heights is reported, using the two
+metrics described in Fig. \ref{fig:nrho_v_ra}.
+
+%\begin{table}
+\begin{center}
+\begin{longtable}{ p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1.75cm} p{1.5cm} p{2.75cm} p{1cm} p{1.2cm}  }
+\caption{Input and output values of select simulations.\label{table:run_info}}\\
+\hline
+$\epsilon$	&	Ra$_t$	&	3D	&	$n_z$	&	$n_x$	&	$n_y$	&	Nu					&	Re	&	Ma					&	$n_{\rho, \text{max}}$	&	$n_{\rho, \text{bounds}}$	\\
+\hline\hline \endfirsthead																													\\
+\multicolumn{11}{c}%
+{ \tablename\ \thetable{} -- continued from previous page} \\
+\hline
+$\epsilon$	&	Ra$_t$	&	3D	&	$n_z$	&	$n_x$	&	$n_y$	&	Nu					&	Re	&	Ma					&	$n_{\rho, \text{max}}$	&	$n_{\rho, \text{bounds}}$	\\
+\hline \hline \endhead
+\hline \endfoot
+\hline \endlastfoot
+
+\vspace{0.08cm}1	&	$10^4$	&	No	&	256	&	1024	&	---	&$	20.43	_{-	0.21	}^{+	0.24	}$&	397.69	&$	0.79	_{-	0.35	}^{+	5.49	}$&	1.26	&	-0.21	\\
+\vspace{0.08cm}1	&	$10^5$	&	No	&	512	&	2048	&	---	&$	33.60	_{-	0.41	}^{+	1.03	}$&	1356.44	&$	0.82	_{-	0.33	}^{+	4.51	}$&	1.72	&	-0.55	\\
+\vspace{0.08cm}0.5	&	100	&	No	&	64	&	256	&	---	&$	3.72	_{-	0.01	}^{+	0.01	}$&	15.22	&$	0.22	_{-	0.11	}^{+	0.33	}$&	2.52	&	2.52	\\
+\vspace{0.08cm}0.5	&	1000	&	No	&	128	&	512	&	---	&$	7.87	_{-	0.04	}^{+	0.09	}$&	83.02	&$	0.39	_{-	0.26	}^{+	0.71	}$&	1.98	&	1.96	\\
+\vspace{0.08cm}0.5	&	$10^4$	&	No	&	128	&	512	&	---	&$	18.69	_{-	0.38	}^{+	0.63	}$&	487.35	&$	0.74	_{-	0.54	}^{+	1.50	}$&	1.51	&	1.24	\\
+\vspace{0.08cm}0.5	&	$10^5$	&	No	&	256	&	1024	&	---	&$	30.14	_{-	0.15	}^{+	0.39	}$&	1677.07	&$	0.71	_{-	0.34	}^{+	0.87	}$&	1.70	&	1.03	\\
+\vspace{0.08cm}0.5	&	$10^6$	&	No	&	512	&	2048	&	---	&$	45.86	_{-	1.90	}^{+	3.76	}$&	4943.73	&$	0.64	_{-	0.24	}^{+	0.62	}$&	1.95	&	1.11	\\
+\vspace{0.08cm}$10^{-4}$	&	100	&	No	&	64	&	256	&	---	&$	3.75	_{-	0.01	}^{+	0.01	}$&	13.93	&$	2.82	_{-	1.39	}^{+	1.91}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	1000	&	No	&	128	&	512	&	---	&$	7.97	_{-	0.07	}^{+	0.28	}$&	65.85	&$	4.51	_{-	2.66	}^{+	3.95}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^4$	&	No	&	128	&	512	&	---	&$	15.21	_{-	0.14	}^{+	0.32	}$&	391.38	&$	9.30	_{-	7.11	}^{+	11.7}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^5$	&	No	&	256	&	1024	&	---	&$	27.83	_{-	0.47	}^{+	0.42	}$&	1766.70	&$	1.50	_{-	1.17	}^{+	2.19}\cdot 10^{-2}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^6$	&	No	&	512	&	2048	&	---	&$	69.68	_{-	15.80	}^{+	28.24	}$&	7684.29	&$	2.10	_{-	1.74	}^{+	3.15}\cdot 10^{-2}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}1	&	$10^4$	&	Yes	&	128	&	256	&	256	&$	16.10	_{-	0.99	}^{+	0.15	}$&	176.84	&$	0.39	_{-	0.13	}^{+	3.78	}$&	1.24	&	0.41	\\
+\vspace{0.08cm}1	&	$10^5$	&	Yes	&	256	&	512	&	512	&$	29.67	_{-	1.90	}^{+	0.44	}$&	562.40	&$	0.38	_{-	0.14	}^{+	3.71	}$&	1.67	&	-0.22	\\
+\vspace{0.08cm}0.5	&	100	&	Yes	&	64	&	128	&	128	&$	3.42	_{-	0.11	}^{+	0.06	}$&	13.42	&$	0.21	_{-	0.08	}^{+	0.33	}$&	2.56	&	2.57	\\
+\vspace{0.08cm}0.5	&	1000	&	Yes	&	128	&	256	&	256	&$	6.83	_{-	0.25	}^{+	0.18	}$&	46.03	&$	0.23	_{-	0.08	}^{+	0.38	}$&	2.19	&	2.19	\\
+\vspace{0.08cm}0.5	&	$10^4$	&	Yes	&	128	&	256	&	256	&$	12.89	_{-	0.62	}^{+	0.30	}$&	146.92	&$	0.23	_{-	0.08	}^{+	0.45	}$&	1.83	&	1.81	\\
+\vspace{0.08cm}0.5	&	$10^5$	&	Yes	&	256	&	512	&	512	&$	23.05	_{-	1.04	}^{+	1.41	}$&	429.63	&$	0.21	_{-	0.08	}^{+	0.43	}$&	1.95	&	1.59	\\
+\vspace{0.08cm}0.5	&	$10^6$	&	Yes	&	256	&	512	&	512	&$	40.53	_{-	0.72	}^{+	0.66	}$&	1291.61	&$	0.20	_{-	0.08	}^{+	0.46	}$&	2.15	&	1.47	\\
+\vspace{0.08cm}$10^{-4}$	&	100	&	Yes	&	64	&	128	&	128	&$	3.19	_{-	0.10	}^{+	0.06	}$&	11.48	&$	2.53	_{-	9.97	}^{+	1.93}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	1000	&	Yes	&	128	&	256	&	256	&$	6.72	_{-	0.19	}^{+	0.57	}$&	38.32	&$	2.88	_{-	1.09	}^{+	2.55}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^4$	&	Yes	&	128	&	256	&	256	&$	11.92	_{-	0.40	}^{+	1.34	}$&	115.06	&$	2.85	_{-	1.13	}^{+	3.11}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^5$	&	Yes	&	256	&	512	&	512	&$	21.11	_{-	1.69	}^{+	4.74	}$&	319.84	&$	2.46	_{-	1.07	}^{+	2.90}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\vspace{0.08cm}$10^{-4}$	&	$10^6$	&	Yes	&	256	&	512	&	512	&$	38.50	_{-	4.71	}^{+	12.54	}$&	920.21	&$	2.26	_{-	1.02	}^{+	2.84}\cdot 10^{-3}	$&	3.00	&	3.00	\\
+\hline
+\end{longtable}
+\end{center}
+%\end{table}
+
 \end{document}

### 2017-08-04 tex/nusselt_paper.tex
submission versio for prfluids

@@
 
+\vspace{-0.5cm}
 \subsection{Evolved fluid numbers \& flow morphology}
@@
 domain repeatedly before diffusing (Fig. \ref{fig:entropy_snapshots}c).
-In 3D, the same upflow/downflow asymmetry is seen, but downflow lanes no
-longer span the depth of the domain (Fig. \ref{fig:entropy_snapshots}d-f).
 As evidenced by the colorbar scalings, the
 amplitudes of thermodynamic fluctuations scale with $\epsilon$.
+
+In 3D, the same upflow/downflow asymmetry is seen, but other aspects 
+of the flow are distinctly different.  Fig. \ref{fig:entropy_snapshots}d-f show select
+snapshots of a 3D simulation with the same input parameters as the 2D case in Fig. \ref{fig:entropy_snapshots}a.
+In 2D, large-scale, coherent 
+spinners dominate the  flow, leading to a single upflow and downflow.  
+New downflowing plumes at the upper boundary are efficiently swept into the large 
+coherent structure (near $x \sim 1$ and spanning the vertical domain).  The 
+behavior of downflows in 3D is strikingly different (Fig. \ref{fig:entropy_snapshots}d).
+In 3D, many individual plumes detach from 
+the upper boundary, but do not organize into a single dominant downflow 
+in the same fashion.  Horizontal cuts near the top of the domain 
+(Fig. \ref{fig:entropy_snapshots}e) reveal 
+a network of narrow downflow lanes surrounding broad upflows. 
+Stronger clusters of downflows near the surface are linked to 
+sheets of low entropy at the midplane of the domain (Fig. \ref{fig:entropy_snapshots}f).
+As the flows evolve in time, new downflows appear at the top of the domain in 
+the middle of upflows and join the surrounding downflow network, 
+causing the convective structures to fragment.  There is no preferred orientation 
+in the newly forming downflows, and the convective flow field constantly evolves, 
+which appears to prevent the occurrence of either spinners or windy states.
+
 \begin{figure}[t!]
@@
 (a) A low Ma flow at moderate Ra. (b) A high Ma flow at the same Ra as in (a).
-(c) A high Ma flow at high Ra. (d)-(f) A low Ma 3D run at the same parameters as in (a),
-where (d) is a vertical ($x$, $z$) slice at $y = L_y/2$, (e) is a horizontal slice
-at $z = L_z$, and (f) is a horizontal slice at $z = L_z/2$.
+(c) A high Ma flow at high Ra. 
 Shock systems can be seen in the upper atmosphere of the high Ma flows,
@@
 (50, 15-19)$ in (c).
+(d)-(f) A low Ma 3D run at the same parameters as in (a),
+where (d) is a vertical ($x$, $z$) slice at $y = L_y/2$, (e) is a horizontal slice
+at $z = L_z$, and (f) is a horizontal slice at $z = L_z/2$.
 \label{fig:entropy_snapshots} }
@@
 
+\vspace{-0.5cm}
 \subsection{Evolved stratification}
@@
 solid symbols lie below empty symbols.  We find this in 2D and 3D, even
-at very large $\epsilon$.  Sample evolved density profiles are displayed in
-Fig. \ref{fig:nrho_v_ra}b.
+at very large $\epsilon$.
+
+Sample evolved density profiles are displayed in Fig. \ref{fig:nrho_v_ra}b.
+The natural log of the temporally and horizontally averaged density profile, 
+$\ln \rho = \ln \rho_0 + \ln\rho_1$, is displayed for four cases.  At low $\epsilon$
+(dotted green line), the density stratification is, to first order, unchanged from
+the initial density stratification.  At high $\epsilon$, in both 2D (solid purple line)
+and 3D (dashed purple line and dash-dot-dot red line), the evolved stratification differs
+significantly from the initial state and does not increase monotonically with depth.
+To measure the number of density scale heights between two points in the atmosphere,
+$z_1$ \& $z_2$, we calculate $n_\rho(z_1, z_2) = \ln\rho(z_2) - \ln\rho(z_1)$.  Thus,
+the values plotted in Fig. \ref{fig:nrho_v_ra}a for the cases in Fig. \ref{fig:nrho_v_ra}b
+can be directly read off.  For example, at $\epsilon = 1$ and Ra/Ra$_{\text{crit}} \sim 10^5$
+(dash-dot-dot red line), measuring the stratification between the boundaries retrieves
+$n_\rho(L_z, 0) \approx -0.3$, but measuring between the maximum and minimum value of
+the profile retrieves $n_\rho(\text{min, max}) \approx 1.3$.
 

### 2017-08-29 tex/nusselt_paper.tex
publication-like .tex

@@
 %\documentclass[iop]{emulateapj}
-\documentclass[aps, prfluids, onecolumn, notitlepage, nofootinbib, groupedaddress, amsfonts, amssymb, amsmath]{revtex4-1}
+\documentclass[aps, pre, onecolumn, nofootinbib, notitlepage, groupedaddress, amsfonts, amssymb, amsmath, longbibliography]{revtex4-1}
 \usepackage{graphicx}
+\usepackage{hyperref}
+\usepackage{xcolor}
+\hypersetup{
+    colorlinks,
+    linkcolor={red!50!black},
+    citecolor={blue!50!black},
+    urlcolor={blue!80!black}
+}
 \usepackage{bm}
@@
 \usepackage{longtable}
-%\usepackage[colorlinks=True, linkcolor=blue, citecolor=blue]{hyperref}
-%\usepackage[all]{hypcap}
-
-\bibliographystyle{apsrev}
+\LTcapwidth=0.87\textwidth
 
@@
 \newcommand\mnras{{MNRAS}}%
-          % Monthly Notices of the RAS
 
 \begin{document}
-%%%%% Create nice title and abstract
 \author{Evan H. Anders}
@@
 incompressible Rayleigh-B\'{e}nard problem.  This scaling holds up in both 2D and 3D and is not
-appreciably affected by the magnitude of $\epsilon$. %think about last sentence.
+appreciably affected by the magnitude of $\epsilon$.
 \end{abstract}
@@
 
-%%%%% Body of the paper
 \section{Introduction}
@@
 and is the simplest stratified extension of RBC.
-The atmospheres studied are initially polytropically stratified,
+The atmospheres studied here are initially polytropically stratified,
 \begin{equation}
@@
 $\chi_t, \nu_t \propto \sqrt{g L_z^3 (\Delta S_0 / c_P) / \text{Ra}_t}$.
-Defining the thermal diffusion timescale as $t_\chi \equiv L_z^2 / \chi$, the
+Defining the thermal diffusion timescale as $t_\chi \equiv \tau_IL_z^2 / \chi$, the
 ratio of $t_\chi$ to the buoyancy time is
@@
 \sigma_{ij} \equiv \left(\frac{\partial u_i}{\partial x_j} + 
-\frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\grad\cdot\bm{u}\right).
+\frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\grad\cdot\bm{u}\right),
 	\label{eqn:stress_tensor}
 \end{equation}
-Taking an inner product of
+where $\delta_{ij}$ is the Kronecker delta. Taking an inner product of
 (\ref{eqn:momentum_eqn}) with $\rho\bm{u}$ and adding it to 
@@
 We utilize the 
-Dedalus\footnote{http://dedalus-project.org/} 
+Dedalus\footnote{\url{http://dedalus-project.org/}} 
 pseudospectral framework \cite{burns&all2016} to time-evolve  
@@
 is plotted as a function of Ra/Ra$_{\text{crit}}$.
-Larger symbols with white dots designate 3D runs.
+Larger symbols with inlaid circles designate 3D runs.
 \label{fig:ma_v_eps} }
@@
 is due to the formation of coherent high-velocity ``spinners,'' which form
-between upflow and downflow lanes in 2D.  These structures, which are reminiscent of flywheel
+between upflow and downflow lanes.  These structures, which are reminiscent of flywheel
 modes in RBC, do not appear in our 3D runs at these parameters
@@
 Re is measured at the midplane of the atmosphere.
-Larger symbols with white dots designate 3D runs.
+Larger symbols with inlaid circles designate 3D runs.
  \label{fig:re_and_nu_v_ra}
@@
 Fig. \ref{fig:re_and_nu_v_ra}b.  We find that Re
-depends on largely Ra, but not $\epsilon$, except when the flow regime
+depends largely on Ra, but not $\epsilon$, except when the flow regime
 changes.
@@
 the values plotted in Fig. \ref{fig:nrho_v_ra}a for the cases in Fig. \ref{fig:nrho_v_ra}b
-can be directly read off.  For example, at $\epsilon = 1$ and Ra/Ra$_{\text{crit}} \sim 10^5$
+can be directly read off.  For example, at $\epsilon = 1$ and Ra/Ra$_{\text{crit}} \sim 10^4$
 (dash-dot-dot red line), measuring the stratification between the boundaries retrieves
 $n_\rho(L_z, 0) \approx -0.3$, but measuring between the maximum and minimum value of
-the profile retrieves $n_\rho(\text{min, max}) \approx 1.3$.
+the profile retrieves $n_\rho(\text{min, max}) \approx 1.6$.
 
@@
 and turbulent pressure support plays a larger role than atmospheric slumping.
-This appears to arise as a result of the convection making the interior isentropic,
-tied with our fixed-temperature boundary conditions; 
+This appears to arise as a result of convection making the interior isentropic
+in the presence of fixed-temperature boundary conditions;
 we expect the behavior of the stratification to be dependent on the choice of
@@
 
-\bibliography{../biblio.bib}
-
 \appendix
@@
 
-Simulation input values are listed in the first six columns.  The mean evolved Nu
-is presented, as well as how far away the atmospheric maximum and minimum are from
-the mean.  Re at the midplane is reported.  Ma is reported
-in the same format as Nu.  The evolved number of density scale heights is reported, using the two
-metrics described in Fig. \ref{fig:nrho_v_ra}.
-
-%\begin{table}
 \begin{center}
 \begin{longtable}{ p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1.75cm} p{1.5cm} p{2.75cm} p{1cm} p{1.2cm}  }
-\caption{Input and output values of select simulations.\label{table:run_info}}\\
+\caption{Input simulation parameters of $\epsilon$, Ra, and resolution are given for
+select simulations.
+Output values of Nu, Ma, Re, and $n_\rho$, as plotted throughout the paper, are 
+provided for the corresponding run.  The mean of Nu and Ma is reported, as well
+as the distance from the mean to the atmospheric maximum and minimum.  Re is reported
+at the midplane.  The evolved $n_\rho$ is reported using the two metrics described
+in Fig. \ref{fig:nrho_v_ra}. \label{table:run_info}}\\
 \hline
@@
 \end{center}
-%\end{table}
 
+\bibliography{../biblio.bib}
 \end{document}
